### 2014-02-18 paper.tex
Added first version of the paper template

\documentclass[journal]{IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Do not use the stfloats baselinefloat ability as IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

% *** UTF8 ***
\usepackage[utf8]{inputenc}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{ANON paper}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Rolf Jagerman, Wendo Sabée, Martijn de Vos, Laurens Versluis}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~11, No.~4, December~2012}%
%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2012 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract goes here.
\end{abstract}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\subsection{Subsection Heading Here}
Subsection text here.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results.}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals use top floats exclusively.
% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
% floats. This can be corrected via the \fnbelowfloat command of the
% stfloats package.

\section{Conclusion}
The conclusion goes here.

\appendices
\section{Proof of the First Zonklar Equation}
Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{}
Appendix two text goes here.

% use section* for acknowledgement
\section*{Acknowledgment}
The authors would like to thank...

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

\end{document}

### 2014-02-19 paper.tex
Names are now ordered alphabetically.
Remove an enormous amount of comments and other stuff we don't really need

@@
 % Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
+% (uncomment the ones you want to load, see original template for descriptions)
 %\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
 %\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/tex-archive/info/epslatex/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
 %\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
 %\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
 %\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-
-% *** FLOAT PACKAGES ***
-%
 %\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
 %\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Do not use the stfloats baselinefloat ability as IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
+%\usepackage{dblfloatfix}
 %\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
-% Basically, \url{my_url_here}.
 
@@
 \begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-% Do not put math or special symbols in the title.
+
+	% Title of the paper
 	\title{ANON paper}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-
-\author{Rolf Jagerman, Wendo Sabée, Martijn de Vos, Laurens Versluis}
-
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
+	% Authors
+	\author{Rolf Jagerman, Wendo Sab\'ee, Laurens Versluis, Martijn de Vos}
 
@@
 	% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2012 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
 
@@
 		The abstract goes here.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Nunc et elit nec metus ultrices faucibus.
+Mauris volutpat libero eu arcu sodales, ac bibendum neque pulvinar.
+Sed et ipsum nunc.
+Quisque ac sem ut nunc tincidunt commodo.
+Cras at odio nibh.
+Pellentesque sodales ut tortor sed dictum.
+Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
 	\end{abstract}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
 
@@
 		I wish you the best of success.
-
-\subsection{Subsection Heading Here}
-Subsection text here.
-
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
-
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results.}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-
-% An example of a floating table. Note that, for IEEE style tables, the 
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals use top floats exclusively.
-% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
-% floats. This can be corrected via the \fnbelowfloat command of the
-% stfloats package.
 
@@
 		\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+			H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus 0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
 

### 2014-02-19 paper.tex
Tor design section and subsections
Also commented out the appendices for now
Added section 2C, D and E to the paper.

@@
 
+	\section{Tor design}
+
+		This section describes
+
+		\subsection{Onion routing}
+
+		\subsection{Directory servers}
+
+		\subsection{Relay and exit nodes}
+
+[gebruikt: the second generation onion router]
+The Tor network consists of several components.
+The clients in the Tor network are known as Onion Proxies.
+The software to run an Onion Proxy is available for free on the Tor website [linkje] and is easy to configure.
+The Onion Proxies are responsible for downloading the directory information, establish circuits across the network and handle connections from user applications.\\\\
+The routing in the network is done by Onion Routers, also called relay nodes.
+The relay nodes relays the data from the Onion Proxy to the webserver across a circuit (circuits are described in 2D).
+Each Onion Router is connected to every other Onion Router with a TLS connection [link naar TLS protocol].
+Each circuit has three type of Onion Routers [link naar download.pdf]:\begin{itemize}
+\item The entrance Tor router: this is the router that is directly connected to an Onion Proxy and can observe the origin of a request through the Tor network.
+The entrance router sends the packet to the middle Tor router.
+\item The middle Tor router: this router is connected to the entrance router and the exit router.
+\item The exit Tor router: this router is connected to the webserver. Note that the exit Tor router is the only router can that observe the final destination of the request.
+\end{itemize}
+The first router in a circuit is the entrance router. The entrance router sends the data to the middle router which forwards the data to the exit router.
+
+		\subsection{Circuit creation}
+
+As described in the previous section, data on the Tor networks travels over circuits.
+The data travels over the circuit in fixed-size cells that are 512 bytes long.
+Each cell has a header and a payload.
+The header consists of a number that identifies the circuit of the cell and a command that indicates what to do with the cell’s payload.\\\\
+Before a circuit can be established, a path has to be chosen.
+The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes [link naar cacr2011-20].
+Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.\\\\
+Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a webserver.
+Circuit setup uses the Diffie-Hellman key-exchange protocol [linkje] to establish a shared secret between nodes.
+To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake ($ g^x $) to the first node in her selected path (for example, OR1).
+OR1 sends a \emph{created} cell back with the second half of the key ($ g^y $) along with an hash of the final key.
+Now both Alice and OR1 has a shared key they use to encrypt and decrypt data between them.\\\\
+So now Alice has a connection with the first Onion Router in the circuit.
+To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1.
+This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2 ($ g^{x_2} $).
+OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2.
+When OR1 receives a created cell, OR1 passes this cell to Alice.
+Now Alice and OR2 share a common key: $ K = g^{x_2y_2} $.
+The same procedure can be used to extend the circuit with more nodes.
+
+		\subsection{Disadvantages}
+
+While Tor guaranteers anonimity, there are some disadvantages using it.
+The main disadvantage is that the Tor network is slow.
+According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.\\\\
+According to Dingleding et al [link naar 2009-03-11-performance.pdf], there are six reasons why Tor is not optimal.
+In this section, we will summarize these reasons and explain what could be done to fix them.\\\\
+First of all, the congestion control does not work well.
+The network has some problems handling bulk transfers, such as when downloading large files or streaming high-quality videos.
+The congestion control could be improved by using an unreliable protocol for links between Tor relays.\\\\
+Some Tor users put more traffic on the network than they contribute by running a Onion Router.
+This means that these users are slowing the network down as they use more traffic than giving to the network.
+A possible solution for this is to throttle certain protocols at exit nodes or at Onion Proxies.\\\\
+Also, the Tor network doesn’t have the capacity to handle all the users that want privacy on the Internet.
+By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
+Incentives such as LIRA [link naar lira paper] could make more users run a Onion Router, thus increasing the capacity of the network.\\\\
+The current path selection algorithm of Tor doesn’t distribute the load evenly over the network.
+The problem is that the current selection strategy is optimal when the network is fully loaded.
+Using a better path selection algorithm could increase the capacity of the network and the overall user experience.\\\\
+Another problem is that the Tor clients are not optimal at handling latency and connection failures.
+For example, if extending a circuit fails, the entire circuit is abandoned.
+An improvement would be to first try to extend the circuit to some other places.
+If that fails, the circuit could be abandoned.
+Also, a better timeout mechanism could be chosen for building circuits.\\\\
+Much of the overhead of the network is in downloading the directory information.
+There is also overhead in the TLS connection between the nodes in the network.
+Removing the empty TLS application record which could reduce the overhead in the TCP/IP header with 6.3\%.
+
 	\section{Conclusion}
@@
 	\appendices
-		\section{Proof of the First Zonklar Equation}
-			Appendix one text goes here.
+%		\section{Proof of the First Zonklar Equation}
+%			Appendix one text goes here.
 
@@
 			% if you want by leaving the argument blank
-		\section{}
-			Appendix two text goes here.
+%		\section{}
+%			Appendix two text goes here.
 
 		% use section* for acknowledgement
-		\section*{Acknowledgment}
-			The authors would like to thank...
+%		\section*{Acknowledgment}
+%			The authors would like to thank...
 
@@
 		% by themselves when using endfloat and the captionsoff option.
-		\ifCLASSOPTIONcaptionsoff
-		  \newpage
-		\fi
+%		\ifCLASSOPTIONcaptionsoff
+%		  \newpage
+%		\fi
 

### 2014-02-19 paper.tex
Lipsum for the introduction
Tor design introduction

--- 2014-02-19 paper.tex
@@
 		% (should never be an issue)
-		I wish you the best of success.
+		\IEEEPARstart{L}{orem} ipsum dolor sit amet, consectetur adipiscing elit.
+Nunc et elit nec metus ultrices faucibus.
+Mauris volutpat libero eu arcu sodales, ac bibendum neque pulvinar.
+Sed et ipsum nunc.
+Quisque ac sem ut nunc tincidunt commodo.
+Cras at odio nibh.
+Pellentesque sodales ut tortor sed dictum.
+Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
+
+	\section{Tor design}
+		\label{sec:tor}
+		The implementation of The Onion Router was first described by the U.S.
+Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{bib:goldschlag}.
+
+		In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{bib:dingledine}.
+
+		\subsection{Onion routing}
+
+		\subsection{Directory servers}
+
+		\subsection{Relay and exit nodes}
+
+		\subsection{Circuit creation}
+
+		\subsection{Disadvantages}
 
@@
 
-		\bibitem{IEEEhowto:kopka}
-			H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus 0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+		\bibitem{bib:goldschlag}
+			David M. Goldschlag, Michael G. Reed, and Paul F. Syverson. "Hiding Routing Information", Workshop on Information Hiding, Cambridge, UK, May, 1996.
+
+		\bibitem{bib:dingledine}
+			Roger Dingledine, Nick Mathewson, Paul Syverson. "Tor: The Second-Generation Onion Router", 2002.
 

### 2014-02-19 paper.tex
Tor design, onion routing subsection

@@
 		\subsection{Onion routing}
+			As described in the original design paper of The Onion Router, network traffic is forwarded through a circuit of nodes, where each node only knows the previous and next node in the circuit.
+With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each others physical location.
+
+			Say we have a circuit of nodes $C = \{c_0, \dots, c_n\}$, where $c_0$ is our trusted client and $c_n$ is the exit node.
+Each node has its own public key $p$ and a corresponding private key $d$.
+For each node in $C$, $c_0$ generates a distinct secret $s$.
+
+			The payload of each packet flowing from $c_0$ to $c_n$ through circuit $C$ is first encrypted with $s_e$, the secret generated for node $c_e$.
+This is repeated for $s_{e-1}$, $s_{e-2}$, etc, until lastly it is encrypted with $s_1$.
+With each layer of encryption, a header is added with the address of next node in the circuit, plus the generated secret $s$ for the current node, encrypted its public key.
+
+			After node $c_1$ receives this packet from our trusted node $c_0$, it decrypts the secret $s_1$ with its private key $d_1$, and uses it to decrypt the rest of the packet.
+The result is a header with the address of node $c_2$ and the payload encrypted with secrets $s_2$ to $s_e$, which is forwarded to node $c_2$.
+
+			As node $c_x$ receives data from the previous node $c_{x-1}$, it peels off another layer of encryption, much as how you can peel an onion layer for layer, and forwards it to $c_{x+1}$.
+When exit node $c_n$ decrypts the last layer and forwards the unencrypted payload outside the network to the original destination that $c_0$ specified, acting as a traditional proxy.
+
+			When $c_n$ receives a response, this whole process is applied in reverse order, encrypting the payload with its secret along the way, instead of decrypting.
+When $c_0$ receives the packet, it peels off all the encryption layers to retrieve the unencrypted payload.
+
+			With the second generation onion routing used in Tor, a modified algorithm is used to derive the encryption keys, called \emph{telescoping path-building}, which also provides perfect forward secrecy.
+This algorithm is described in section \ref{ss:tor_circuit}.
 
@@
 		\subsection{Circuit creation}
+			\label{ss:tor_circuit}
 

### 2014-02-19 paper.tex
Tor design, directory servers subsection

@@
 		\subsection{Directory servers}
+			The original Onion Router implementation used in-band status updates where each node broadcasts know nodes to its neighbours.
+An attacker could exploit this to isolate and limit the knowledge of a client, forcing connections through malicious nodes.
+Beside possible security disadvantages, in-band status updates also have the disadvantage that it takes longer to propagate throughout the network and create a global consensus.
+
+			To mitigate these concerns, Directory Servers were introduced to Tor during its reimplementation to keep a redundant central consensus about the network.
+They act as HTTP servers to which Tor nodes can publish signed information about themselves.
+Tor clients can in turn download this information.
+
+			This information is signed by the Directory Servers before it is distributed to the Tor clients.
+The keys to verify these signatures are preloaded in the Tor software, along with the list of Directory Servers, which implies trust by the Tor client in the Directory Servers.
 

### 2014-02-19 paper.tex
Fixed some minor issues
Special thanks to:
-Laurens Versluis for reading this
-Dan Browny because it can

--- 2014-02-19 paper.tex
@@
 		% (should never be an issue)
-		\IEEEPARstart{L}{orem} ipsum dolor sit amet, consectetur adipiscing elit.
-Nunc et elit nec metus ultrices faucibus.
-Mauris volutpat libero eu arcu sodales, ac bibendum neque pulvinar.
-Sed et ipsum nunc.
-Quisque ac sem ut nunc tincidunt commodo.
-Cras at odio nibh.
-Pellentesque sodales ut tortor sed dictum.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
+		I wish you the best of success.
 
 	\section{Tor design}
-		\label{sec:tor}
-		The implementation of The Onion Router was first described by the U.S.
-Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{bib:goldschlag}.
 
-		In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{bib:dingledine}.
+		This section describes
 
@@
 
+[gebruikt: the second generation onion router]
+The Tor network consists of several components.
+The clients in the Tor network are known as Onion Proxies.
+The software to run an Onion Proxy is available for free on the Tor website [linkje] and is easy to configure.
+The Onion Proxies are responsible for downloading the directory information, establish circuits across the network and handle connections from user applications.\\\\
+The routing in the network is done by Onion Routers, also called relay nodes.
+The relay nodes relays the data from the Onion Proxy to the webserver across a circuit (circuits are described in 2D).
+Each Onion Router is connected to every other Onion Router with a TLS connection [link naar TLS protocol].
+Each circuit has three type of Onion Routers [link naar download.pdf]:\begin{itemize}
+\item The entrance Tor router: this is the router that is directly connected to an Onion Proxy and can observe the origin of a request through the Tor network.
+The entrance router sends the packet to the middle Tor router.
+\item The middle Tor router: this router is connected to the entrance router and the exit router.
+\item The exit Tor router: this router is connected to the webserver. Note that the exit Tor router is the only router that can observe the final destination of the request.
+\end{itemize}
+The first router in a circuit is the entrance router. The entrance router sends the data to one of the middle router which forwards the data to the exit router.
+
 		\subsection{Circuit creation}
 
+As described in the previous section, data on the Tor networks travels over circuits.
+The data travels over the circuit in fixed-size cells that are 512 bytes long.
+Each cell has a header and a payload.
+The header consists of a number that identifies the circuit of the cell and a command that indicates what to do with the cell’s payload.\\\\
+Before a circuit can be established, a path has to be chosen.
+The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes [link naar cacr2011-20].
+Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.\\\\
+Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a webserver.
+Circuit setup uses the Diffie-Hellman key-exchange protocol [linkje] to establish a shared secret between nodes.
+To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake ($ g^b $) to the first node in her selected path (for example, OR1).
+OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
+Now both Alice and OR1 have a shared key they use to encrypt and decrypt data between them.\\\\
+So now Alice has a connection with the first Onion Router in the circuit.
+To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1.
+This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2 ($ g^{a_2} $).
+OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2.
+When OR1 receives a created cell, OR1 passes this cell to Alice.
+Now Alice and OR2 share a common key: $ K = g^{a_2b_2} $.
+The same procedure can be used to extend the circuit with more nodes.
+
 		\subsection{Disadvantages}
+
+While Tor guaranteers anonimity, there are some disadvantages using it.
+The main disadvantage is that the Tor network is slow.
+According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.\\\\
+According to Dingleding et al [link naar 2009-03-11-performance.pdf], there are six reasons why Tor is not optimal.
+In this section, we will summarize these reasons and explain what could be done to fix them.\\\\
+First of all, the congestion control does not work well.
+The network has some problems handling bulk transfers, such as when downloading large files or streaming high-quality videos.
+The congestion control could be improved by using an unreliable protocol for links between Tor relays.\\\\
+Some Tor users put more traffic on the network than they contribute by running a Onion Router.
+This means that these users are slowing the network down as they use more traffic than giving to the network.
+A possible solution for this is to throttle certain protocols at exit nodes or at Onion Proxies.\\\\
+Also, the Tor network doesn’t have the capacity to handle all the users that want privacy on the Internet.
+By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
+Incentives such as LIRA [link naar lira paper] could make more users run a Onion Router, thus increasing the capacity of the network.\\\\
+The current path selection algorithm of Tor doesn’t distribute the load evenly over the network.
+The problem is that the current selection strategy is optimal when the network is fully loaded.
+Using a better path selection algorithm could increase the capacity of the network and the overall user experience.\\\\
+Another problem is that the Tor clients are not optimal at handling latency and connection failures.
+For example, if extending a circuit fails, the entire circuit is abandoned.
+An improvement would be to first try to extend the circuit to some other places.
+If that fails, the circuit could be abandoned.
+Also, a better timeout mechanism could be chosen for building circuits.\\\\
+Much of the overhead of the network is in downloading the directory information.
+There is also overhead in the TLS connection between the nodes in the network.
+Removing the empty TLS application record which could reduce the overhead in the TCP/IP header with 6.3\% [citaat].
 
@@
 
-		\bibitem{bib:goldschlag}
-			David M. Goldschlag, Michael G. Reed, and Paul F. Syverson. "Hiding Routing Information", Workshop on Information Hiding, Cambridge, UK, May, 1996.
-
-		\bibitem{bib:dingledine}
-			Roger Dingledine, Nick Mathewson, Paul Syverson. "Tor: The Second-Generation Onion Router", 2002.
+		\bibitem{IEEEhowto:kopka}
+			H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus 0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
 

### 2014-02-21 paper.tex

--- 2014-02-19 paper.tex
@@
 		\subsection{Relay and exit nodes}
+			[gebruikt: the second generation onion router]
+			The Tor network consists of several components.
+The clients in the Tor network are known as Onion Proxies.
+The software to run an Onion Proxy is available for free on the Tor website [linkje] and is easy to configure.
+The Onion Proxies are responsible for downloading the directory information, establish circuits across the network and handle connections from user applications.\\\\
+			The routing in the network is done by Onion Routers, also called relay nodes.
+The relay nodes relays the data from the Onion Proxy to the webserver across a circuit (circuits are described in 2D).
+Each Onion Router is connected to every other Onion Router with a TLS connection [link naar TLS protocol].
+Each circuit has three type of Onion Routers [link naar download.pdf]:
+			\begin{itemize}
+				\item The entrance Tor router: this is the router that is directly connected to an Onion Proxy and can observe the origin of a request through the Tor network.
+The entrance router sends the packet to the middle Tor router.
+				\item The middle Tor router: this router is connected to the entrance router and the exit router.
+				\item The exit Tor router: this router is connected to the webserver. Note that the exit Tor router is the only router that can observe the final destination of the request.
+			\end{itemize}
+			The first router in a circuit is the entrance router. The entrance router sends the data to one of the middle router which forwards the data to the exit router.
 
@@
 			\label{ss:tor_circuit}
+			As described in the previous section, data on the Tor networks travels over circuits.
+The data travels over the circuit in fixed-size cells that are 512 bytes long.
+Each cell has a header and a payload.
+The header consists of a number that identifies the circuit of the cell and a command that indicates what to do with the cell’s payload.\\\\
+			Before a circuit can be established, a path has to be chosen.
+The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes [link naar cacr2011-20].
+Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.\\\\
+			Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a webserver.
+Circuit setup uses the Diffie-Hellman key-exchange protocol [linkje] to establish a shared secret between nodes.
+To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake ($ g^b $) to the first node in her selected path (for example, OR1).
+OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
+Now both Alice and OR1 have a shared key they use to encrypt and decrypt data between them.\\\\
+			So now Alice has a connection with the first Onion Router in the circuit.
+To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1.
+This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2 ($ g^{a_2} $).
+OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2.
+When OR1 receives a created cell, OR1 passes this cell to Alice.
+Now Alice and OR2 share a common key: $ K = g^{a_2b_2} $.
+The same procedure can be used to extend the circuit with more nodes.
 
 		\subsection{Disadvantages}
+			While Tor guaranteers anonimity, there are some disadvantages using it.
+The main disadvantage is that the Tor network is slow.
+According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.\\\\
+			According to Dingleding et al [link naar 2009-03-11-performance.pdf], there are six reasons why Tor is not optimal.
+In this section, we will summarize these reasons and explain what could be done to fix them.\\\\
+			First of all, the congestion control does not work well.
+The network has some problems handling bulk transfers, such as when downloading large files or streaming high-quality videos.
+The congestion control could be improved by using an unreliable protocol for links between Tor relays.\\\\
+			Some Tor users put more traffic on the network than they contribute by running a Onion Router.
+This means that these users are slowing the network down as they use more traffic than giving to the network.
+A possible solution for this is to throttle certain protocols at exit nodes or at Onion Proxies.\\\\
+			Also, the Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
+By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
+Incentives such as LIRA [link naar lira paper] could make more users run a Onion Router, thus increasing the capacity of the network.\\\\
+			The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
+The problem is that the current selection strategy is optimal when the network is fully loaded.
+Using a better path selection algorithm could increase the capacity of the network and the overall user experience.\\\\
+			Another problem is that the Tor clients are not optimal at handling latency and connection failures.
+For example, if extending a circuit fails, the entire circuit is abandoned.
+An improvement would be to first try to extend the circuit to some other places.
+If that fails, the circuit could be abandoned.
+Also, a better timeout mechanism could be chosen for building circuits.\\\\
+			Much of the overhead of the network is in downloading the directory information.
+There is also overhead in the TLS connection between the nodes in the network.
+Removing the empty TLS application record which could reduce the overhead in the TCP/IP header with 6.3\% [citaat].
 

### 2014-02-25 paper.tex
Tone down the (unnecessary) mathematical notations a bit

@@
 
-			Say we have a circuit of nodes $C = \{c_0, \dots, c_n\}$, where $c_0$ is our trusted client and $c_n$ is the exit node.
-Each node has its own public key $p$ and a corresponding private key $d$.
-For each node in $C$, $c_0$ generates a distinct secret $s$.
+			Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry) relay node ($X$), a (middle) relay node ($Y$) and an exit node ($Z$).
+In this case, there are two relay nodes, but this is not a fixed number (and could be increased for more security).
+Each node has its own public key and a corresponding private key.
+When building the circuit, our client generates a distinct secret for each of these nodes.
 
-			The payload of each packet flowing from $c_0$ to $c_n$ through circuit $C$ is first encrypted with $s_e$, the secret generated for node $c_e$.
-This is repeated for $s_{e-1}$, $s_{e-2}$, etc, until lastly it is encrypted with $s_1$.
-With each layer of encryption, a header is added with the address of next node in the circuit, plus the generated secret $s$ for the current node, encrypted its public key.
+			The payload of each packet flowing through the circuit is first encrypted with the distinct secret for last node $Z$, then with the distinct secret for node $Y$, and last with the secret for node $X$.
+With each layer of encryption, a header is added with the address of the next node in the circuit, plus the used distinct secret encrypted with corresponding nodes public key.
 
-			After node $c_1$ receives this packet from our trusted node $c_0$, it decrypts the secret $s_1$ with its private key $d_1$, and uses it to decrypt the rest of the packet.
-The result is a header with the address of node $c_2$ and the payload encrypted with secrets $s_2$ to $s_e$, which is forwarded to node $c_2$.
+			After node $X$ receives this packet from out trusted node $C$, it decrypts the attached secret with its private key, and uses that secret to decrypt the rest of the packet.
+The result is a header with the address for node $Y$ and the payload encrypted with secrets for the following nodes in the circuit, which is forwarded to node $Y$.
 
-			As node $c_x$ receives data from the previous node $c_{x-1}$, it peels off another layer of encryption, much as how you can peel an onion layer for layer, and forwards it to $c_{x+1}$.
-When exit node $c_n$ decrypts the last layer and forwards the unencrypted payload outside the network to the original destination that $c_0$ specified, acting as a traditional proxy.
+			As a node receives a packet from the previous node, it peels off another layer of encryption, much as how you can peel an onion layer for layer, and forwards it to the next node in the circuit (as specified in the decrypted header).
+When exit node $Z$ decrypts the last layer, it forwards the unencrypted payload outside the network to the original destination that our trusted client $C$ tried to contact, acting as a traditional proxy.
 
-			When $c_n$ receives a response, this whole process is applied in reverse order, encrypting the payload with its secret along the way, instead of decrypting.
-When $c_0$ receives the packet, it peels off all the encryption layers to retrieve the unencrypted payload.
+			When exit node $Z$ receives a response, this whole process is applied in reverse order, encrypting the payload with its secret along the way, instead of decrypting.
+When our client $C$ receives the packet, it peels off all the encryption layers to retrieve the unencrypted payload.
 

### 2014-02-25 paper.tex
Added the .bib file

@@
 		The implementation of The Onion Router was first described by the U.S.
-Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{bib:goldschlag}.
+Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
 
-		In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{bib:dingledine}.
+		In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
 
@@
 		\subsection{Relay and exit nodes}
-			[gebruikt: the second generation onion router]
 			The Tor network consists of several components.
@@
 Each Onion Router is connected to every other Onion Router with a TLS connection [link naar TLS protocol].
-Each circuit has three type of Onion Routers [link naar download.pdf]:
+Each circuit has three type of Onion Routers \cite{mccoy2008shining}:
 			\begin{itemize}
@@
 		% (used to reserve space for the reference number labels box)
-	\begin{thebibliography}{1}
-
-		\bibitem{bib:goldschlag}
-			David M. Goldschlag, Michael G. Reed, and Paul F. Syverson. "Hiding Routing Information", Workshop on Information Hiding, Cambridge, UK, May, 1996.
-
-		\bibitem{bib:dingledine}
-			Roger Dingledine, Nick Mathewson, Paul Syverson. "Tor: The Second-Generation Onion Router", 2002.
-
-	\end{thebibliography}
+	\bibliography{paper}{}
+\bibliographystyle{plain}
 

### 2014-02-25 paper.tex
Added references

@@
 The clients in the Tor network are known as Onion Proxies.
-The software to run an Onion Proxy is available for free on the Tor website [linkje] and is easy to configure.
+The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy to configure.
 The Onion Proxies are responsible for downloading the directory information, establish circuits across the network and handle connections from user applications.\\\\
@@
 The relay nodes relays the data from the Onion Proxy to the webserver across a circuit (circuits are described in 2D).
-Each Onion Router is connected to every other Onion Router with a TLS connection [link naar TLS protocol].
+Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}.
 Each circuit has three type of Onion Routers \cite{mccoy2008shining}:
@@
 			Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a webserver.
-Circuit setup uses the Diffie-Hellman key-exchange protocol [linkje] to establish a shared secret between nodes.
+Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
 To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake ($ g^b $) to the first node in her selected path (for example, OR1).
@@
 According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.\\\\
-			According to Dingleding et al [link naar 2009-03-11-performance.pdf], there are six reasons why Tor is not optimal.
+			According to Dingleding et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal.
 In this section, we will summarize these reasons and explain what could be done to fix them.\\\\
@@
 By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
-Incentives such as LIRA [link naar lira paper] could make more users run a Onion Router, thus increasing the capacity of the network.\\\\
+Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network.\\\\
 			The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
@@
 There is also overhead in the TLS connection between the nodes in the network.
-Removing the empty TLS application record which could reduce the overhead in the TCP/IP header with 6.3\% [citaat].
+Removing the empty TLS application record which could reduce the overhead in the TCP/IP header with 6.3\%.
 

### 2014-03-09 paper.tex
Added the general (current) structure and
added a subsection of attacks and vulnerabilities of Tor.

@@
 
+\bibliographystyle{plain}
+
 % Title of the paper
-	\title{ANON paper}
+\title{30 years of privacy research for the masses \& \newline 15 years of decentralization attempts }
 % Authors
@@
 
-	\section{Tor design}
+\section{Introduction in Tor}
 \label{sec:tor}
@@
 
+\noindent		
 In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
@@
 The Onion Proxies are responsible for downloading the directory information, establish circuits across the network and handle connections from user applications.\\\\
+\noindent
 The routing in the network is done by Onion Routers, also called relay nodes.
@@
 \end{itemize}
+
 The first router in a circuit is the entrance router. The entrance router sends the data to one of the middle router which forwards the data to the exit router.
@@
 Each cell has a header and a payload.
-The header consists of a number that identifies the circuit of the cell and a command that indicates what to do with the cell’s payload.\\\\
+The header consists of a number that identifies the circuit of the cell and a command that indicates what to do with the cell’s payload.\\
+
+\noindent
 Before a circuit can be established, a path has to be chosen.
 The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes [link naar cacr2011-20].
-Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.\\\\
+Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.\\
+
+\noindent
 Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a webserver.
@@
 OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
-Now both Alice and OR1 have a shared key they use to encrypt and decrypt data between them.\\\\
+Now both Alice and OR1 have a shared key they use to encrypt and decrypt data between them.\\
+
+\noindent
 So now Alice has a connection with the first Onion Router in the circuit.
@@
 The main disadvantage is that the Tor network is slow.
-According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.\\\\
+According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.\\
+
+\noindent
 According to Dingleding et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal.
-In this section, we will summarize these reasons and explain what could be done to fix them.\\\\
+In this section, we will summarize these reasons and explain what could be done to fix them.\\
+
+\noindent
 First of all, the congestion control does not work well.
 The network has some problems handling bulk transfers, such as when downloading large files or streaming high-quality videos.
-The congestion control could be improved by using an unreliable protocol for links between Tor relays.\\\\
+The congestion control could be improved by using an unreliable protocol for links between Tor relays.\\
+
+\noindent
 Some Tor users put more traffic on the network than they contribute by running a Onion Router.
 This means that these users are slowing the network down as they use more traffic than giving to the network.
-A possible solution for this is to throttle certain protocols at exit nodes or at Onion Proxies.\\\\
+A possible solution for this is to throttle certain protocols at exit nodes or at Onion Proxies.\\
+
+\noindent
 Also, the Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
 By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
-Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network.\\\\
+Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network.\\
+
+\noindent
 The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
 The problem is that the current selection strategy is optimal when the network is fully loaded.
-Using a better path selection algorithm could increase the capacity of the network and the overall user experience.\\\\
+Using a better path selection algorithm could increase the capacity of the network and the overall user experience.\\
+
+\noindent
 Another problem is that the Tor clients are not optimal at handling latency and connection failures.
@@
 If that fails, the circuit could be abandoned.
-Also, a better timeout mechanism could be chosen for building circuits.\\\\
+Also, a better timeout mechanism could be chosen for building circuits.\\
+
+\noindent
 Much of the overhead of the network is in downloading the directory information.
@@
 Removing the empty TLS application record which could reduce the overhead in the TCP/IP header with 6.3\%.
+
+\section{Tor vulnerabilities and attacks}
+Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks [cites?].
+In this section we will summarize some of the most well known problems with Tor.
+
+\subsection{Browser based attacks}
+Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis.\\
+By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
+Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
+By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
+A similar system can be set up only using the HTML meta refresh tag.\\
+To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports. There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\
+The solution to this problem is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
+
+\section{Current decentralized systems}
+\section{Which components needs to be decentralized of Tor?}
+\section{Comparison existing  networks}
 
@@
 		% (used to reserve space for the reference number labels box)
-	\bibliography{paper}{}
-\bibliographystyle{plain}
+\bibliography{paper_references}
 

### 2014-03-10 paper.tex
two spaces
Added text about Gnutella and Freenet

@@
 \section{Current decentralized systems}
+
 \section{Which components needs to be decentralized of Tor?}
-\section{Comparison existing  networks}
+
+\section{Comparison existing decentralized  networks}
+Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
+Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan.
+Each of these decentralized networks will be discussed in the next section.
+Note that we're only considering fully decentralized networks here.
+Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]
+
+\subsection{Gnutella}
+Gnutella is a decentralized peer-to-peer network used for distributed search of files.
+Since the network is fully decentralized, peers in the network are called 'servents', a combination of servers and clients.
+Each client can act both as a server, answering queries, or as a client, requesting and executing search queries.
+In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available.
+These peers can be found on http://gnutellahosts.com.
+Once the peer has joined, there are several messages a servant can send out:
+\begin{itemize}
+\item A peer sends a PING message to it's neighbours to announce it's presents. This message is forwarded to other peers and each peer sends a PONG message back.
+\item The peer can issue QUERY answers. Other peers responds with a QUERY RESPONSE message to specify whether the file that was issued in the query, was found or not.
+\item To transfer items between peers, the GET and PUSH messages are being used.
+\end{itemize}
+Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file.
+To search for a file, a flooding algorithm is used.
+
+\subsection{Freenet}
+In Freenet, each data item is represented by a key that is independent of the location of the file.
+Freenet is called a loosely structured network because of this.
+To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.\\\\
+There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file.
+Another key is the Signed-Subspace key which enables personal namespaces.
+This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
+The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.\\\\
+The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
+Each peer has only knowledge about his neighbours.
+Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
+Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded anymore.
+Results of queries are being cached in intermediate nodes to reduce the time for a query response.
+
+\subsection{Freehaven}
+
+\subsection{Tapestry}
+
+\subsection{Kademlia}
+
+\subsection{Tarzan}
 

### 2014-03-10 paper.tex
Added text about Tapestry and Other anonymous p2p systems

@@
 Since the network is fully decentralized, peers in the network are called 'servents', a combination of servers and clients.
-Each client can act both as a server, answering queries, or as a client, requesting and executing search queries.
+Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.
 In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available.
@@
 
-\subsection{Freehaven}
+\subsection{Tribler}
 
 \subsection{Tapestry}
-
-\subsection{Kademlia}
+Tapestry is based on the plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
+A property of Tapestry is that it offers load distribution and routing locality.
+Tapastry is very similar to pastry [link naar pastry paper] but there are some small differences in in the handling of network locality and data replication.\\\\
+Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored.
+A peer can also function as a router, which forwards an incoming message.
+The routing algorithm is based on the destination ID of the packet.
+Routers are using local routing maps to route messages to the destination ID digit by digit.
+The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.\\\\
+Tapestry is a fundamental component of Oceanstore [linkje naar paper over Oceanstore], a decentralized storage system. Tapestry is also used in systems such as Bayeux and SpamWatch.
 
 \subsection{Tarzan}
+
+\subsection{Other anonymous systems}
+Some other decentralized peer-to-peer systems has been developed, focussing on anonymity.
+An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) [linkje naar AP3 paper] which makes cooperative, decentralized anonymous communication possible.
+The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms.
+Users are able to send and receive unicast, multicast and anycast messages anonymously.
+The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages.
+A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.\\\\
+<hier moet nog een stukje over i2p komen voor degene die dat paper heeft gelezen>
+
+\subsection{Comparison and differences}
 

### 2014-03-11 paper.tex
removed noindents

@@
 
-\noindent		
 In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
@@
 The Onion Proxies are responsible for downloading the directory information, establish circuits across the network and handle connections from user applications.\\\\
-\noindent
+
 The routing in the network is done by Onion Routers, also called relay nodes.
@@
 
-\noindent
 Before a circuit can be established, a path has to be chosen.
@@
 
-\noindent
 Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a webserver.
@@
 
-\noindent
 So now Alice has a connection with the first Onion Router in the circuit.
@@
 
-\noindent
 According to Dingleding et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal.
@@
 
-\noindent
 First of all, the congestion control does not work well.
@@
 
-\noindent
 Some Tor users put more traffic on the network than they contribute by running a Onion Router.
@@
 
-\noindent
 Also, the Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
@@
 
-\noindent
 The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
@@
 
-\noindent
 Another problem is that the Tor clients are not optimal at handling latency and connection failures.
@@
 
-\noindent
 Much of the overhead of the network is in downloading the directory information.

### 2014-03-11 paper.tex
added spaces to get the same layout

@@
 By misusing the exit policy of Tor one can reduce the time required to perform the analysis.\\
+
 By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
@@
 A similar system can be set up only using the HTML meta refresh tag.\\
+
 To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports. There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\
@@
 Once the peer has joined, there are several messages a servant can send out:
+
 \begin{itemize}
@@
 To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.\\\\
+
 There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file.
@@
 The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.\\\\
+
 The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
@@
 Tapastry is very similar to pastry [link naar pastry paper] but there are some small differences in in the handling of network locality and data replication.\\\\
+
 Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored.
@@
 The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.\\\\
+
 Tapestry is a fundamental component of Oceanstore [linkje naar paper over Oceanstore], a decentralized storage system. Tapestry is also used in systems such as Bayeux and SpamWatch.

### 2014-03-11 paper.tex
more layout changes
tabs spaces and palces are adapted see file for changes

@@
 The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
+Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.\\
+
 By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.\\
+A similar system can be set up only using the HTML meta refresh tag.
+To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\
 
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports. There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\
 The solution to this problem is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.

### 2014-03-11 paper.tex
Typo
edits
first commit in my branch!
hooray
Fix whitespace and indents

--- 2014-03-11 paper.tex
@@
 % Title of the paper
-\title{30 years of privacy research for the masses \& \newline 15 years of decentralization attempts }
+\title{30 years of privacy research for the masses \& \newline 15 years of decentralization attempts}
 % Authors
@@
 
-\section{Introduction in Tor}
+\section{Introduction to Tor}
 	\label{sec:tor}
@@
 The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy to configure.
-The Onion Proxies are responsible for downloading the directory information, establish circuits across the network and handle connections from user applications.\\\\
+The Onion Proxies are responsible for downloading the directory information, establish circuits across the network and handle connections from user applications.
 
@@
 Each cell has a header and a payload.
-The header consists of a number that identifies the circuit of the cell and a command that indicates what to do with the cell’s payload.\\
+The header consists of a number that identifies the circuit of the cell and a command that indicates what to do with the cell’s payload.
 
@@
 The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes [link naar cacr2011-20].
-Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.\\
+Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.
 
@@
 OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
-Now both Alice and OR1 have a shared key they use to encrypt and decrypt data between them.\\
+Now both Alice and OR1 have a shared key they use to encrypt and decrypt data between them.
 
@@
 The main disadvantage is that the Tor network is slow.
-According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.\\
+According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.
 
 		According to Dingleding et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal.
-In this section, we will summarize these reasons and explain what could be done to fix them.\\
+In this section, we will summarize these reasons and explain what could be done to fix them.
 
@@
 The network has some problems handling bulk transfers, such as when downloading large files or streaming high-quality videos.
-The congestion control could be improved by using an unreliable protocol for links between Tor relays.\\
+The congestion control could be improved by using an unreliable protocol for links between Tor relays.
 
@@
 This means that these users are slowing the network down as they use more traffic than giving to the network.
-A possible solution for this is to throttle certain protocols at exit nodes or at Onion Proxies.\\
+A possible solution for this is to throttle certain protocols at exit nodes or at Onion Proxies.
 
@@
 By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
-Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network.\\
+Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network.
 
@@
 The problem is that the current selection strategy is optimal when the network is fully loaded.
-Using a better path selection algorithm could increase the capacity of the network and the overall user experience.\\
+Using a better path selection algorithm could increase the capacity of the network and the overall user experience.
 
@@
 If that fails, the circuit could be abandoned.
-Also, a better timeout mechanism could be chosen for building circuits.\\
+Also, a better timeout mechanism could be chosen for building circuits.
 
@@
 			Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis.\\
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
 
@@
 Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
+
 			By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.\\
+A similar system can be set up only using the HTML meta refresh tag.
+To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
 
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports. There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\
-The solution to this problem is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
+			The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
 
 	\section{Current decentralized systems}
+		Current decentralized systems.
 
 	\section{Which components needs to be decentralized of Tor?}
+		Directory servers etc.
 
@@
 			\end{itemize}
+
 			Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file.
@@
 Freenet is called a loosely structured network because of this.
-To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.\\\\
+To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.
 
@@
 This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
-The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.\\\\
+The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.
 
@@
 
+		\subsection{NISAN}
+			Information about NISAN.
+
 		\subsection{Tribler}
+			Information about Tribler.
 
@@
 A property of Tapestry is that it offers load distribution and routing locality.
-Tapastry is very similar to pastry [link naar pastry paper] but there are some small differences in in the handling of network locality and data replication.\\\\
+Tapastry is very similar to pastry [link naar pastry paper] but there are some small differences in in the handling of network locality and data replication.
 
@@
 Routers are using local routing maps to route messages to the destination ID digit by digit.
-The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.\\\\
+The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.
 
@@
 		\subsection{Tarzan}
+			Information about Tarzan.
 
@@
 The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages.
-A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.\\\\
+A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.
+
 			<hier moet nog een stukje over i2p komen voor degene die dat paper heeft gelezen>

### 2014-03-11 paper.tex
Itemize style

@@
 		\begin{itemize}
-			\item The entrance Tor router: this is the router that is directly connected to an Onion Proxy and can observe the origin of a request through the Tor network.
+			\item{The entrance Tor router:} this router is directly connected to an Onion Proxy and can observe the origin of a request through the Tor network.
 The entrance router sends the packet to the middle Tor router.
-			\item The middle Tor router: this router is connected to the entrance router and the exit router.
-			\item The exit Tor router: this router is connected to the webserver. Note that the exit Tor router is the only router that can observe the final destination of the request.
+			\item{The middle Tor router:} this router is connected to the entrance router and the exit router.
+			\item{The exit Tor router:} this router is connected to the web server. Note that the exit Tor router is the only router that can observe the final destination of the request.
 		\end{itemize}

### 2014-03-11 paper.tex
Typo fixes

@@
 		The routing in the network is done by Onion Routers, also called relay nodes.
-The relay nodes relays the data from the Onion Proxy to the webserver across a circuit (circuits are described in 2D).
+The relay nodes relays the data from the Onion Proxy to the web server across a circuit (circuits are described in 2D).
 Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}.
@@
 
-		Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a webserver.
+		Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a web server.
 Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
@@
 	\subsection{Disadvantages}
-		While Tor guaranteers anonimity, there are some disadvantages using it.
+		While Tor guarantees anonymity, there are some disadvantages using it.
 The main disadvantage is that the Tor network is slow.
@@
 
-		According to Dingleding et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal.
+		According to Dingledine et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal.
 In this section, we will summarize these reasons and explain what could be done to fix them.
@@
 Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
-Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded anymore.
+Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
 Results of queries are being cached in intermediate nodes to reduce the time for a query response.

### 2014-03-11 paper.tex
Indent and layout consistency fixes for bib file
Added pasty paper and some pieces of text

--- 2014-03-11 paper.tex
@@
 % Title of the paper
-\title{30 years of privacy research for the masses \& \newline 15 years of decentralization attempts}
+\title{30 years of privacy research for the masses \& \newline 15 years of decentralization attempts }
 % Authors
@@
 
-\section{Introduction to Tor}
+\section{Introduction in Tor}
 \label{sec:tor}
@@
 The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy to configure.
-The Onion Proxies are responsible for downloading the directory information, establish circuits across the network and handle connections from user applications.
+The Onion Proxies are responsible for downloading the directory information, establish circuits across the network and handle connections from user applications.\\\\
 
@@
 Each cell has a header and a payload.
-The header consists of a number that identifies the circuit of the cell and a command that indicates what to do with the cell’s payload.
+The header consists of a number that identifies the circuit of the cell and a command that indicates what to do with the cell’s payload.\\
 
@@
 The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes [link naar cacr2011-20].
-Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.
+Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.\\
 
@@
 OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
-Now both Alice and OR1 have a shared key they use to encrypt and decrypt data between them.
+Now both Alice and OR1 have a shared key they use to encrypt and decrypt data between them.\\
 
@@
 The main disadvantage is that the Tor network is slow.
-According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.
+According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.\\
 
 According to Dingleding et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal.
-In this section, we will summarize these reasons and explain what could be done to fix them.
+In this section, we will summarize these reasons and explain what could be done to fix them.\\
 
@@
 The network has some problems handling bulk transfers, such as when downloading large files or streaming high-quality videos.
-The congestion control could be improved by using an unreliable protocol for links between Tor relays.
+The congestion control could be improved by using an unreliable protocol for links between Tor relays.\\
 
@@
 This means that these users are slowing the network down as they use more traffic than giving to the network.
-A possible solution for this is to throttle certain protocols at exit nodes or at Onion Proxies.
+A possible solution for this is to throttle certain protocols at exit nodes or at Onion Proxies.\\
 
@@
 By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
-Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network.
+Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network.\\
 
@@
 The problem is that the current selection strategy is optimal when the network is fully loaded.
-Using a better path selection algorithm could increase the capacity of the network and the overall user experience.
+Using a better path selection algorithm could increase the capacity of the network and the overall user experience.\\
 
@@
 If that fails, the circuit could be abandoned.
-Also, a better timeout mechanism could be chosen for building circuits.
+Also, a better timeout mechanism could be chosen for building circuits.\\
 
@@
 Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks [cites?].
-In this section we will summarize some of the most well known problems with Tor.
+In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, X attacks, Y attacks and Z attacks.
 
@@
 Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis.\\
 
@@
 The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
+Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.\\
 
@@
 To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\
 
@@
 \section{Current decentralized systems}
-		Current decentralized systems.
 
-	\section{Which components needs to be decentralized of Tor?}
-		Directory servers etc.
+\section{The difficulties of decentralizing Tor}
+
+\subsection{Bootstrapping new nodes}
+If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with.
+In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.
+Moving this system to a non peer-to-peer base is difficult.
+Dingledine et al.
+stated that this indeed is still an open problem.
+With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
+Some systems such as Tarzan, MorphMix and Pastra [citjes hiero] do have made some attempts towards a decentralized system, but have yet to find the final answer.
+
+\subsection{Incentives in decentralized systems}
 
@@
 \end{itemize}
-
 Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file.
@@
 Freenet is called a loosely structured network because of this.
-To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.
+To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.\\\\
 
@@
 This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
-The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.
+The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.\\\\
 
@@
 
-		\subsection{NISAN}
-			Information about NISAN.
-
 \subsection{Tribler}
-			Information about Tribler.
 
@@
 A property of Tapestry is that it offers load distribution and routing locality.
-Tapastry is very similar to pastry [link naar pastry paper] but there are some small differences in in the handling of network locality and data replication.
+Tapastry is very similar to pastry [link naar pastry paper] but there are some small differences in in the handling of network locality and data replication.\\\\
 
@@
 Routers are using local routing maps to route messages to the destination ID digit by digit.
-The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.
+The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.\\\\
 
@@
 \subsection{Tarzan}
-			Information about Tarzan.
 
@@
 The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages.
-A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.
-
+A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.\\\\
 <hier moet nog een stukje over i2p komen voor degene die dat paper heeft gelezen>
@@
 \section{Conclusion}
-		The conclusion goes here.
+We come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
+While there is a lot of research on decentralized systems, only a few are actually implemented.
+The systems that do exist such as X and Y (hier deze noemen aan de hand van de tabel) are getting things right, yet they often lack or have poor implementations on other aspects.\\
+While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
 

### 2014-03-12 paper.tex
Restructured the paper according to the meeting
Zie de notulen voor meer info

--- 2014-03-11 paper.tex
@@
 
-	\section{Tor vulnerabilities and attacks}
-		Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks [cites?].
-In this section we will summarize some of the most well known problems with Tor.
+\section{Problems when decentralizing}
+		hier komt de introductie
 
-		\subsection{Browser based attacks}
-			Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
-
-			By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-			By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
-
-			The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
+		\subsection{Bootstrapping}
 
 	\section{Current decentralized systems}
-		Current decentralized systems.
-
-	\section{Which components needs to be decentralized of Tor?}
-		Directory servers etc.
-
-	\section{Comparison existing decentralized  networks}
 		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
@@
 
-		\subsection{Other anonymous systems}
+		\subsection{Other decentralized systems}
 			Some other decentralized peer-to-peer systems has been developed, focussing on anonymity.
@@
 
+	\section{Tor vulnerabilities and attacks}
+		Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks [cites?].
+In this section we will summarize some of the most well known problems with Tor.
+
+		\subsection{Browser based attacks}
+			Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
+
+			By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
+Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
+
+			By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
+A similar system can be set up only using the HTML meta refresh tag.
+To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
+
+			The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
+
+	\section{Comparison existing decentralized  networks}
+
 		\subsection{Comparison and differences}
+			Comparison table.
 

### 2014-03-12 paper.tex
fixed merge conflicts from master

@@
 
-		\subsection{Bootstrapping}
+			\subsection{Bootstrapping new nodes}
+		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with.
+In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.
+Moving this system to a non peer-to-peer base is difficult.
+Dingledine et al.
+stated that this indeed is still an open problem.
+With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
+Some systems such as Tarzan, MorphMix and Pastra [citjes hiero] do have made some attempts towards a decentralized system, but have yet to find the final answer.
+
+		\subsection{Incentives in decentralized systems}
 
@@
 
+	\section{Comparison existing decentralized  networks}
+Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
+Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan.
+Each of these decentralized networks will be discussed in the next section.
+Note that we're only considering fully decentralized networks here.
+Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]
+
 		\subsection{Tapestry}
@@
 		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis.\\
 
@@
 To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\
 
 		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-	\section{Comparison existing decentralized  networks}
 
@@
 	\section{Conclusion}
-		The conclusion goes here.
+		We come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
+While there is a lot of research on decentralized systems, only a few are actually implemented.
+The systems that do exist such as X and Y (hier deze noemen aan de hand van de tabel) are getting things right, yet they often lack or have poor implementations on other aspects.\\
+While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
 

### 2014-03-12 paper.tex
.
Added basic introduction of the paper

--- 2014-03-12 paper.tex
@@
 	% (should never be an issue)
-	\IEEEPARstart{L}{orem} ipsum dolor sit amet, consectetur adipiscing elit.
-Nunc et elit nec metus ultrices faucibus.
-Mauris volutpat libero eu arcu sodales, ac bibendum neque pulvinar.
-Sed et ipsum nunc.
-Quisque ac sem ut nunc tincidunt commodo.
-Cras at odio nibh.
-Pellentesque sodales ut tortor sed dictum.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
+	\IEEEPARstart{W}{ith} the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate.
+In many cases however, internet usage is either censored or monitored by third parties.
+In recent years the need for anonymous internet communication has become more apparent.
+Revealing government wrongdoings, such as in the case of wikileaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.
+
+	Although much research has been done about anonymous internet communication, only few systems have been actually implemented and used in practice.
+One of the most important factors that impact anonymity in a communication system is the number of users.
+A sufficiently large numbers of users are required for the system to make guarantees about its ability to conceal and hide users' communication.
+This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
+Another important factor is for the system to be decentralized.
+Whenever a network has centralized components and a malicious third party gains control over these components, the functionality and perhaps even the anonymity of the system is compromised.
+
+	The most widely used anonymous communication system is TOR.
+In this paper we will analyze TOR and its semi centralized nature.
+Furthermore we will look at attempts that have been made to decentralize TOR as well as several other decentralized systems.
+
+	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview about Tor.
+After that we will talk about decentralization and its problems in section \ref{sec:problems}.
+Vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
+Afterwards, we will discuss the current state of decentralized internet systems in section \ref{sec:decentralized}.
+A comparison of existing decentralized networks is made in section \ref{sec:comparison}.
+Finally we will conclude and discuss our findings in section \ref{sec:conclusion}.
 

### 2014-03-12 paper.tex
Added section about Morph Mix

--- 2014-03-12 paper.tex
@@
 
+		\subsection{MorphMix}
+			MorphMix functions similar to both Tor and MIX networks.
+It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
+Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
+
+			MIX networks are high latency and traffic moves slow.
+Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
+Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
+MorphMix has been developed as a low latency and high performance network.
+As such, it will not hold messages for very long, nor will it use cover traffic.
+
+			In contrast to Tor, MorphMix does not feature a centralized node discovery.
+Instead, every node is free to chose a set of next nodes that will be the continuation of the anonymous tunnel.
+A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel.
+To prevent this, a witness node is appointed to mediate the setup of the anonymous tunnel.
+Although this makes the possibility of such an attack more difficult, it is not impossible.
+
+			An important part of MorphMix is the ability to detect malicious tunnels.
+Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly.
+Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel.
+This will reveal itself in the fact that the probability of the selection of certain nodes is increased.
+By using this information it becomes possible, to an extent, to detect malicious tunnels.
+
 		\subsection{Tribler}

### 2014-03-12 paper.tex
Cleared up some weird sentence structures

@@
 
-			In contrast to Tor, MorphMix does not feature a centralized node discovery.
-Instead, every node is free to chose a set of next nodes that will be the continuation of the anonymous tunnel.
+			In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism.
+Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel.
 A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel.
-To prevent this, a witness node is appointed to mediate the setup of the anonymous tunnel.
+To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel.
 Although this makes the possibility of such an attack more difficult, it is not impossible.

### 2014-03-12 paper.tex
Added an introduction to chapter IV and some text to chapter VI

--- 2014-03-12 paper.tex
@@
 \section{Problems when decentralizing}
-		hier komt de introductie
+		As we saw in the previous section, we would like to have a decentralized anonymous network.
+This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
+Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry.
+These networks will be described in more detail in the next chapter.
+Among these networks are some overlay anonymous networks such as Tarzan.
+
+		There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
+When removing this central authority, these components needs to be spread across the peers in the network.
+In this section we will explain the various problems that are involved when decentralizing Tor.
+In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
 
@@
 			Information about NISAN.
-
-		\subsection{MorphMix}
-			MorphMix functions similar to both Tor and MIX networks.
-It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
-Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
-
-			MIX networks are high latency and traffic moves slow.
-Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
-Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
-MorphMix has been developed as a low latency and high performance network.
-As such, it will not hold messages for very long, nor will it use cover traffic.
-
-			In contrast to Tor, MorphMix does not feature a centralized node discovery.
-Instead, every node is free to chose a set of next nodes that will be the continuation of the anonymous tunnel.
-A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel.
-To prevent this, a witness node is appointed to mediate the setup of the anonymous tunnel.
-Although this makes the possibility of such an attack more difficult, it is not impossible.
-
-			An important part of MorphMix is the ability to detect malicious tunnels.
-Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly.
-Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel.
-This will reveal itself in the fact that the probability of the selection of certain nodes is increased.
-By using this information it becomes possible, to an extent, to detect malicious tunnels.
 
@@
 
-		\subsection{Comparison and differences}
-			Comparison table.
+		In the last section, we discussedexisting decentralized peer-to-peer networks.
+In this section we will make a comparison between these networks.
+For each network, we will explain the following features:
+\begin{itemize}
+\item Compatibility with Tor. If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
+\item Public implementation. For each network we will explain whether a public implementation is available.
+\item Used in practice. Is the network used in practice?
+\item Attack resistance. We will explain the various weaknesses and possible attacks of each network.
+\end{itemize}
 

### 2014-03-12 paper.tex
wrote some about incentives
and added some references

@@
 	\subsection{Disadvantages}
+	\label{ss:tor_disadvantages}
 		While Tor guarantees anonymity, there are some disadvantages using it.
@@
 \section{Problems when decentralizing}
-		As we saw in the previous section, we would like to have a decentralized anonymous network.
-This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry.
-These networks will be described in more detail in the next chapter.
-Among these networks are some overlay anonymous networks such as Tarzan.
+		hier komt de introductie
 
-		There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
-When removing this central authority, these components needs to be spread across the peers in the network.
-In this section we will explain the various problems that are involved when decentralizing Tor.
-In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
+			\subsection{Bootstrapping new nodes}
+		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with.
+In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.
+Moving this system to a non peer-to-peer base is difficult.
+Dingledine et al.
+stated that this indeed is still an open problem.
+With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
+Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} do have made some attempts towards a decentralized system, but have yet to find the final answer.
 
-		\subsection{Bootstrapping}
+		\subsection{Incentives in decentralized systems}
+		As described in section \ref{ss:tor_disadvantages} people are using more bandwidth than that they donate.
+There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor.
+If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified.
+In other words the incentive data has to be accurate and reliable.
+Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.\\
+		Rahman \cite{rahman2009survey} ........
 
@@
 
+		\subsection{Comparison and differences}
+			Comparison table.
+
 	\section{Tor vulnerabilities and attacks}
 Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks [cites?].
-In this section we will summarize some of the most well known problems with Tor.
+In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, X attacks, Y attacks and Z attacks.
 
@@
 
-	\section{Comparison existing decentralized networks}
-
-		In the last section, we discussedexisting decentralized peer-to-peer networks.
-In this section we will make a comparison between these networks.
-For each network, we will explain the following features:
-\begin{itemize}
-\item Compatibility with Tor. If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
-\item Public implementation. For each network we will explain whether a public implementation is available.
-\item Used in practice. Is the network used in practice?
-\item Attack resistance. We will explain the various weaknesses and possible attacks of each network.
-\end{itemize}
-
 	\section{Conclusion}
-		The conclusion goes here.
+		We come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
+While there is a lot of research on decentralized systems, only a few are actually implemented.
+The systems that do exist such as X and Y (hier deze noemen aan de hand van de tabel) are getting things right, yet they often lack or have poor implementations on other aspects.\\
+While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
 

### 2014-03-13 paper.tex
completed incentive part

@@
 
+	\section{Tor vulnerabilities and attacks}
+Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks [cites?].
+In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, X attacks, Y attacks and Z attacks.
+
+		\subsection{Browser based attacks}
+		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis.\\
+
+		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
+Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.\\
+
+		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
+A similar system can be set up only using the HTML meta refresh tag.
+To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\
+
+		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
+
 \section{Problems when decentralizing}
@@
 Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.\\
-		Rahman \cite{rahman2009survey} ........
+
+		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network.
+The first thing that is described is the so called \emph{Warm-glow Model}.
+In this model determines the percentage of free-rides based on the probabilistic population distribution.
+If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.\\
+
+		The second proposal is using monetary schemes.
+While it is not exemplified a lot, the main idea is to use a virtual currency as incentive.
+The problems with this approach are the scalability and the hidden costs of this service.\\
+
+		The third proposal is \emph{Reciprocity-Based Schemes}.
+Using this approach a peer maintains a behavior history of other peers in the network.
+These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity.
+The formal are more suitable for longer relationships between peers.
+The latter is more scalable but they rely on third party and must handle trust issues themselves.
 
@@
 
-	\section{Tor vulnerabilities and attacks}
-Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks [cites?].
-In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, X attacks, Y attacks and Z attacks.
+	\section{Conclusion}
+		In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.
+Furthermore we looked at the main disadvantages and problems Tor currently has.
+We then made a bridge to decentralized systems.
+We first explained which problems one might face when decentralizing a system such as Tor.
+The next section shows which systems currently have a decentralized structure and/or mechanism.
+These systems are then compared to each other with their pros and cons.\\
 
-		\subsection{Browser based attacks}
-		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis.\\
+		From this table we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
+While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.
+The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity or XXXXXX.\\
 
-		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.\\
-
-		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\
-
-		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-	\section{Conclusion}
-		We come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
-While there is a lot of research on decentralized systems, only a few are actually implemented.
-The systems that do exist such as X and Y (hier deze noemen aan de hand van de tabel) are getting things right, yet they often lack or have poor implementations on other aspects.\\
 While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.

### 2014-03-13 paper.tex
Changed some weird sentence structure in the introduction

--- 2014-03-12 paper.tex
@@
 	% (should never be an issue)
-	\IEEEPARstart{L}{orem} ipsum dolor sit amet, consectetur adipiscing elit.
-Nunc et elit nec metus ultrices faucibus.
-Mauris volutpat libero eu arcu sodales, ac bibendum neque pulvinar.
-Sed et ipsum nunc.
-Quisque ac sem ut nunc tincidunt commodo.
-Cras at odio nibh.
-Pellentesque sodales ut tortor sed dictum.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
+	\IEEEPARstart{W}{ith} the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate.
+In many cases however, internet usage is either censored or monitored by third parties.
+In recent years the need for anonymous internet communication has become more apparent.
+Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.
+
+	Although much research has been done about anonymous internet communication, only few systems have been actually implemented and used in practice.
+One of the most important factors that impact anonymity in a communication system is the number of users.
+A sufficiently large numbers of users are required for the system to make guarantees about its ability to conceal and hide users' communication.
+This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
+Another important factor is for the system to be decentralized.
+Whenever a network has centralized components and a malicious third party gains control over these components, the functionality and perhaps even the anonymity of the system is compromised.
+
+	The most widely used anonymous communication system is TOR.
+In this paper we will analyze TOR and its semi centralized nature.
+Furthermore we will look at attempts that have been made to decentralize TOR as well as several other decentralized systems.
+
+	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview about Tor.
+After that we will talk about decentralization and its problems in section \ref{sec:problems}.
+Vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
+Afterwards, we will discuss the current state of decentralized internet systems in section \ref{sec:decentralized}.
+A comparison of existing decentralized networks is made in section \ref{sec:comparison}.
+Finally we will conclude and discuss our findings in section \ref{sec:conclusion}.
 
@@
 \section{Problems when decentralizing}
-		As we saw in the previous section, we would like to have a decentralized anonymous network.
-This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry.
-These networks will be described in more detail in the next chapter.
-Among these networks are some overlay anonymous networks such as Tarzan.
-
-		There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
-When removing this central authority, these components needs to be spread across the peers in the network.
-In this section we will explain the various problems that are involved when decentralizing Tor.
-In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
+		hier komt de introductie
 
@@
 
-		In the last section, we discussedexisting decentralized peer-to-peer networks.
-In this section we will make a comparison between these networks.
-For each network, we will explain the following features:
-\begin{itemize}
-\item Compatibility with Tor. If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
-\item Public implementation. For each network we will explain whether a public implementation is available.
-\item Used in practice. Is the network used in practice?
-\item Attack resistance. We will explain the various weaknesses and possible attacks of each network.
-\end{itemize}
+		\subsection{Comparison and differences}
+			Comparison table.
 

### 2014-03-13 paper.tex

@@
 
+		\subsection{MorphMix}
+			MorphMix functions similar to both Tor and MIX networks.
+It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
+Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
+
+			MIX networks are high latency and traffic moves slow.
+Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
+Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
+MorphMix has been developed as a low latency and high performance network.
+As such, it will not hold messages for very long, nor will it use cover traffic.
+
+			In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism.
+Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel.
+A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel.
+To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel.
+Although this makes the possibility of such an attack more difficult, it is not impossible.
+
+			An important part of MorphMix is the ability to detect malicious tunnels.
+Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly.
+Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel.
+This will reveal itself in the fact that the probability of the selection of certain nodes is increased.
+By using this information it becomes possible, to an extent, to detect malicious tunnels.
+
 		\subsection{Tribler}

### 2014-03-13 paper.tex
Added correct citing for MorphMix and changed some sentence structure.

@@
 		\subsection{MorphMix}
-			MorphMix functions similar to both Tor and MIX networks.
+			MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks.
 It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
@@
 To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel.
-Although this makes the possibility of such an attack more difficult, it is not impossible.
+Although this makes the possibility of such an attack more difficult, it doesn't make it impossible.
 

### 2014-03-13 paper.tex

--- 2014-03-13 paper.tex
@@
 
-		\subsection{Bootstrapping}
+			\subsection{Bootstrapping new nodes}
+		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with.
+In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.
+Moving this system to a non peer-to-peer base is difficult.
+Dingledine et al.
+stated that this indeed is still an open problem.
+With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
+Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} do have made some attempts towards a decentralized system, but have yet to find the final answer.
+
+		\subsection{Incentives in decentralized systems}
+		As described in section \ref{ss:tor_disadvantages} people are using more bandwidth than that they donate.
+There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor.
+If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified.
+In other words the incentive data has to be accurate and reliable.
+Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.\\
+
+		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network.
+The first thing that is described is the so called \emph{Warm-glow Model}.
+In this model determines the percentage of free-rides based on the probabilistic population distribution.
+If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.\\
+
+		The second proposal is using monetary schemes.
+While it is not exemplified a lot, the main idea is to use a virtual currency as incentive.
+The problems with this approach are the scalability and the hidden costs of this service.\\
+
+		The third proposal is \emph{Reciprocity-Based Schemes}.
+Using this approach a peer maintains a behavior history of other peers in the network.
+These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity.
+The formal are more suitable for longer relationships between peers.
+The latter is more scalable but they rely on third party and must handle trust issues themselves.
 
@@
 
-	\section{Tor vulnerabilities and attacks}
-		Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks [cites?].
-In this section we will summarize some of the most well known problems with Tor.
-
-		\subsection{Browser based attacks}
-			Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
-
-			By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-			By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
-
-			The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-	\section{Comparison existing decentralized  networks}
-
 		\subsection{Comparison and differences}
@@
 	\section{Conclusion}
-		The conclusion goes here.
+		In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.
+Furthermore we looked at the main disadvantages and problems Tor currently has.
+We then made a bridge to decentralized systems.
+We first explained which problems one might face when decentralizing a system such as Tor.
+The next section shows which systems currently have a decentralized structure and/or mechanism.
+These systems are then compared to each other with their pros and cons.\\
+
+		From this table we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
+While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.
+The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity or XXXXXX.\\
+
+While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
 

### 2014-03-13 paper.tex
Completed conclusion and added some references

@@
 	\section{Tor vulnerabilities and attacks}
-Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks [cites?].
-In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, X attacks, Y attacks and Z attacks.
+Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
+In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
 
@@
 
+		\subsection{Low-Resource Routing attacks}
+		Hier wat over routing attacks
+
+		\subsection{Sybil attacks}
+		Hier wat over sybil attacks
+
+		\subsection{Replay Attacks}
+		Hier wat over replay attacks
+
 \section{Problems when decentralizing}
@@
 		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with.
-In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.
+In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.\\
+
 Moving this system to a non peer-to-peer base is difficult.
@@
 While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.
-The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity or XXXXXX.\\
+The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of  attacks.\\
 
@@
 	\appendices
-%		\section{Proof of the First Zonklar Equation}
-%			Appendix one text goes here.
 
-			% you can choose not to have a title for an appendix
-			% if you want by leaving the argument blank
-%		\section{}
-%			Appendix two text goes here.
-
-		% use section* for acknowledgement
-%		\section*{Acknowledgment}
-%			The authors would like to thank...
-
-		% Can use something like this to put references on a page
-		% by themselves when using endfloat and the captionsoff option.
-%		\ifCLASSOPTIONcaptionsoff
-%		  \newpage
-%		\fi
-
-		% trigger a \newpage just before the given reference
-		% number - used to balance the columns on the last page
-		% adjust value as needed - may need to be readjusted if
-		% the document is modified later
-		%\IEEEtriggeratref{8}
-		% The "triggered" command can be changed if desired:
-		%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-		% references section
-
-		% can use a bibliography generated by BibTeX as a .bbl file
-		% BibTeX documentation can be easily obtained at:
-		% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-		% The IEEEtran BibTeX style support page is at:
-		% http://www.michaelshell.org/tex/ieeetran/bibtex/
-		%\bibliographystyle{IEEEtran}
-		% argument is your BibTeX string definitions and bibliography database(s)
-		%\bibliography{IEEEabrv,../bib/paper}
-		%
-		% <OR> manually copy in the resultant .bbl file
-		% set second argument of \begin to the number of references
-		% (used to reserve space for the reference number labels box)
 	\bibliography{paper_references}

### 2014-03-13 paper.tex
Added text

--- 2014-03-13 paper.tex
@@
 	% (should never be an issue)
-	\IEEEPARstart{W}{ith} the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate.
-In many cases however, internet usage is either censored or monitored by third parties.
-In recent years the need for anonymous internet communication has become more apparent.
-Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.
-
-	Although much research has been done about anonymous internet communication, only few systems have been actually implemented and used in practice.
-One of the most important factors that impact anonymity in a communication system is the number of users.
-A sufficiently large numbers of users are required for the system to make guarantees about its ability to conceal and hide users' communication.
-This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
-Another important factor is for the system to be decentralized.
-Whenever a network has centralized components and a malicious third party gains control over these components, the functionality and perhaps even the anonymity of the system is compromised.
-
-	The most widely used anonymous communication system is TOR.
-In this paper we will analyze TOR and its semi centralized nature.
-Furthermore we will look at attempts that have been made to decentralize TOR as well as several other decentralized systems.
-
-	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview about Tor.
-After that we will talk about decentralization and its problems in section \ref{sec:problems}.
-Vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
-Afterwards, we will discuss the current state of decentralized internet systems in section \ref{sec:decentralized}.
-A comparison of existing decentralized networks is made in section \ref{sec:comparison}.
-Finally we will conclude and discuss our findings in section \ref{sec:conclusion}.
+	\IEEEPARstart{L}{orem} ipsum dolor sit amet, consectetur adipiscing elit.
+Nunc et elit nec metus ultrices faucibus.
+Mauris volutpat libero eu arcu sodales, ac bibendum neque pulvinar.
+Sed et ipsum nunc.
+Quisque ac sem ut nunc tincidunt commodo.
+Cras at odio nibh.
+Pellentesque sodales ut tortor sed dictum.
+Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
 
@@
 
+		As we saw, the directory service generates overhead of the network.
+If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
+This means, we would like to have Tor decentralized.
+Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up.
+This is due to the fact that there are many problems decentralization brings along with.
+
 \section{Problems when decentralizing}
-		hier komt de introductie
+		As we saw in the previous section, we would like to have a decentralized anonymous network.
+This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
+Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry.
+These networks will be described in more detail in the next chapter.
+Among these networks are some overlay anonymous networks such as Tarzan.
+
+		There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
+When removing this central authority, these components needs to be spread across the peers in the network.
+In this section we will explain the various problems that are involved when decentralizing Tor.
+In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
 
 		\subsection{Bootstrapping}
+		Hier komt informatie over het bootstrappen.
+
+		\subsection{Key exchange}
+		When using a decentralized network, using a centralized authority for managing the keys, is not possible.
+This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them.
+Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
+Diffie-Hellman is for example used in the circuit setup in Onion Routing (see chapter I), however, it is possible for an adversary to manipulate with the keys send between two parties.
+This makes it possible for the adversary to decrypt all message sent between the two parties.
+
+		Tor currently uses an interactive forward-secret key-exchange protocol called the Tor authentication protocol (TAP) [linkje naar ace].
+This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
+There are several proposals for more efficient key exchange methods.
+One of them is ACE, an one-way authenticated key exchange protocol.
+The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
+ACE requires clients to send one extra element but that doesn't introduce any overhead because this element fits in the unused space in a cell.
 
@@
 			Gnutella is a decentralized peer-to-peer network used for distributed search of files.
-Since the network is fully decentralized, peers in the network are called 'servents', a combination of servers and clients.
+Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients.
 Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.
@@
 			There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file.
-Another key is the Signed-Subspace key which enables personal namespaces.
+Another key is the Signed-Subspace key (SSK) which enables personal namespaces.
 This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
@@
 Results of queries are being cached in intermediate nodes to reduce the time for a query response.
+To prevent looping of the requests, each request contains a random identifier.
+The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
 
@@
 
-		\subsection{MorphMix}
-			MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks.
-It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
-Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
-
-			MIX networks are high latency and traffic moves slow.
-Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
-Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
-MorphMix has been developed as a low latency and high performance network.
-As such, it will not hold messages for very long, nor will it use cover traffic.
-
-			In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism.
-Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel.
-A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel.
-To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel.
-Although this makes the possibility of such an attack more difficult, it doesn't make it impossible.
-
-			An important part of MorphMix is the ability to detect malicious tunnels.
-Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly.
-Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel.
-This will reveal itself in the fact that the probability of the selection of certain nodes is increased.
-By using this information it becomes possible, to an extent, to detect malicious tunnels.
-
 		\subsection{Tribler}
@@
 
+		\subsection{Pastry}
+			Information about Pastry.
+
 		\subsection{Tapestry}
-			Tapestry is based on the plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
+			Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
 A property of Tapestry is that it offers load distribution and routing locality.
@@
 
-			Tapestry is a fundamental component of Oceanstore [linkje naar paper over Oceanstore], a decentralized storage system. Tapestry is also used in systems such as Bayeux and SpamWatch.
+			Tapestry is a fundamental component of Oceanstore [linkje naar paper over Oceanstore], a decentralized storage system.
+Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
 

### 2014-03-13 paper.tex

@@
 
-		As we saw, the directory service generates overhead of the network.
-If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
-This means, we would like to have Tor decentralized.
-Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up.
-This is due to the fact that there are many problems decentralization brings along with.
-
 \section{Problems when decentralizing}
@@
 		\subsection{Bootstrapping}
-		Hier komt informatie over het bootstrappen.
-
-		\subsection{Key exchange}
-		When using a decentralized network, using a centralized authority for managing the keys, is not possible.
-This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them.
-Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
-Diffie-Hellman is for example used in the circuit setup in Onion Routing (see chapter I), however, it is possible for an adversary to manipulate with the keys send between two parties.
-This makes it possible for the adversary to decrypt all message sent between the two parties.
-
-		Tor currently uses an interactive forward-secret key-exchange protocol called the Tor authentication protocol (TAP) [linkje naar ace].
-This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
-There are several proposals for more efficient key exchange methods.
-One of them is ACE, an one-way authenticated key exchange protocol.
-The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
-ACE requires clients to send one extra element but that doesn't introduce any overhead because this element fits in the unused space in a cell.
 
@@
 			Gnutella is a decentralized peer-to-peer network used for distributed search of files.
-Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients.
+Since the network is fully decentralized, peers in the network are called 'servents', a combination of servers and clients.
 Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.
@@
 			There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file.
-Another key is the Signed-Subspace key (SSK) which enables personal namespaces.
+Another key is the Signed-Subspace key which enables personal namespaces.
 This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
@@
 Results of queries are being cached in intermediate nodes to reduce the time for a query response.
-To prevent looping of the requests, each request contains a random identifier.
-The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
 
@@
 
-		\subsection{Pastry}
-			Information about Pastry.
-
 		\subsection{Tapestry}
-			Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
+			Tapestry is based on the plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
 A property of Tapestry is that it offers load distribution and routing locality.
@@
 
-			Tapestry is a fundamental component of Oceanstore [linkje naar paper over Oceanstore], a decentralized storage system.
-Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
+			Tapestry is a fundamental component of Oceanstore [linkje naar paper over Oceanstore], a decentralized storage system. Tapestry is also used in systems such as Bayeux and SpamWatch.
 

### 2014-03-13 paper.tex
fixed conflicts

--- 2014-03-13 paper.tex
@@
 	\subsection{Disadvantages}
+	\label{ss:tor_disadvantages}
+
 		While Tor guarantees anonymity, there are some disadvantages using it.
@@
 
+	\section{Tor vulnerabilities and attacks}
+Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
+In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
+
+		\subsection{Browser based attacks}
+		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis.\\
+
+		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
+Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.\\
+
+		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
+A similar system can be set up only using the HTML meta refresh tag.
+To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\
+
+		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
+
+		\subsection{Low-Resource Routing attacks}
+		Hier wat over routing attacks
+
+		\subsection{Sybil attacks}
+		Hier wat over sybil attacks
+
+		\subsection{Replay Attacks}
+		Hier wat over replay attacks
+
 \section{Problems when decentralizing}
@@
 
-		\subsection{Bootstrapping}
+			\subsection{Bootstrapping new nodes}
+		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with.
+In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.\\
+
+Moving this system to a non peer-to-peer base is difficult.
+Dingledine et al.
+stated that this indeed is still an open problem.
+With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
+Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} do have made some attempts towards a decentralized system, but have yet to find the final answer.
+
+		\subsection{Incentives in decentralized systems}
+		As described in section \ref{ss:tor_disadvantages} people are using more bandwidth than that they donate.
+There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor.
+If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified.
+In other words the incentive data has to be accurate and reliable.
+Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.\\
+
+		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network.
+The first thing that is described is the so called \emph{Warm-glow Model}.
+In this model determines the percentage of free-rides based on the probabilistic population distribution.
+If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.\\
+
+		The second proposal is using monetary schemes.
+While it is not exemplified a lot, the main idea is to use a virtual currency as incentive.
+The problems with this approach are the scalability and the hidden costs of this service.\\
+
+		The third proposal is \emph{Reciprocity-Based Schemes}.
+Using this approach a peer maintains a behavior history of other peers in the network.
+These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity.
+The formal are more suitable for longer relationships between peers.
+The latter is more scalable but they rely on third party and must handle trust issues themselves.
 
@@
 
-			<hier moet nog een stukje over i2p komen voor degene die dat paper heeft gelezen>
-
-	\section{Tor vulnerabilities and attacks}
-		Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks [cites?].
-In this section we will summarize some of the most well known problems with Tor.
-
-		\subsection{Browser based attacks}
-			Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
-
-			By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-			By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
-
-			The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
 	\section{Comparison existing decentralized networks}
@@
 	\section{Conclusion}
-		The conclusion goes here.
+		In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.
+Furthermore we looked at the main disadvantages and problems Tor currently has.
+We then made a bridge to decentralized systems.
+We first explained which problems one might face when decentralizing a system such as Tor.
+The next section shows which systems currently have a decentralized structure and/or mechanism.
+These systems are then compared to each other with their pros and cons.\\
+
+		From this table we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
+While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.
+The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of  attacks.\\
+
+While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
 
 	\appendices
-%		\section{Proof of the First Zonklar Equation}
-%			Appendix one text goes here.
 
-			% you can choose not to have a title for an appendix
-			% if you want by leaving the argument blank
-%		\section{}
-%			Appendix two text goes here.
-
-		% use section* for acknowledgement
-%		\section*{Acknowledgment}
-%			The authors would like to thank...
-
-		% Can use something like this to put references on a page
-		% by themselves when using endfloat and the captionsoff option.
-%		\ifCLASSOPTIONcaptionsoff
-%		  \newpage
-%		\fi
-
-		% trigger a \newpage just before the given reference
-		% number - used to balance the columns on the last page
-		% adjust value as needed - may need to be readjusted if
-		% the document is modified later
-		%\IEEEtriggeratref{8}
-		% The "triggered" command can be changed if desired:
-		%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-		% references section
-
-		% can use a bibliography generated by BibTeX as a .bbl file
-		% BibTeX documentation can be easily obtained at:
-		% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-		% The IEEEtran BibTeX style support page is at:
-		% http://www.michaelshell.org/tex/ieeetran/bibtex/
-		%\bibliographystyle{IEEEtran}
-		% argument is your BibTeX string definitions and bibliography database(s)
-		%\bibliography{IEEEabrv,../bib/paper}
-		%
-		% <OR> manually copy in the resultant .bbl file
-		% set second argument of \begin to the number of references
-		% (used to reserve space for the reference number labels box)
 	\bibliography{paper_references}

### 2014-03-13 paper.tex

@@
 
+		As we saw, the directory service generates overhead of the network.
+If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
+This means, we would like to have Tor decentralized.
+Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up.
+This is due to the fact that there are many problems decentralization brings along with.
+
 \section{Problems when decentralizing}
@@
 
+		\subsection{Key exchange}
+		When using a decentralized network, using a centralized authority for managing the keys, is not possible.
+This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them.
+Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
+Diffie-Hellman is for example used in the circuit setup in Onion Routing (see chapter I), however, it is possible for an adversary to manipulate with the keys send between two parties.
+This makes it possible for the adversary to decrypt all message sent between the two parties.
+
+		Tor currently uses an interactive forward-secret key-exchange protocol called the Tor authentication protocol (TAP) [linkje naar ace].
+This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
+There are several proposals for more efficient key exchange methods.
+One of them is ACE, an one-way authenticated key exchange protocol.
+The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
+ACE requires clients to send one extra element but that doesn't introduce any overhead because this element fits in the unused space in a cell.
+
 	\section{Current decentralized systems}

### 2014-03-13 paper.tex
Changed some weird wording in part about morphmix

--- 2014-03-13 paper.tex
@@
 
-		As we saw, the directory service generates overhead of the network.
-If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
-This means, we would like to have Tor decentralized.
-Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up.
-This is due to the fact that there are many problems decentralization brings along with.
-
 \section{Problems when decentralizing}
-		As we saw in the previous section, we would like to have a decentralized anonymous network.
-This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry.
-These networks will be described in more detail in the next chapter.
-Among these networks are some overlay anonymous networks such as Tarzan.
-
-		There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
-When removing this central authority, these components needs to be spread across the peers in the network.
-In this section we will explain the various problems that are involved when decentralizing Tor.
-In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
+		hier komt de introductie
 
 		\subsection{Bootstrapping}
-		Hier komt informatie over het bootstrappen.
-
-		\subsection{Key exchange}
-		When using a decentralized network, using a centralized authority for managing the keys, is not possible.
-This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them.
-Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
-Diffie-Hellman is for example used in the circuit setup in Onion Routing (see chapter I), however, it is possible for an adversary to manipulate with the keys send between two parties.
-This makes it possible for the adversary to decrypt all message sent between the two parties.
-
-		Tor currently uses an interactive forward-secret key-exchange protocol called the Tor authentication protocol (TAP) [linkje naar ace].
-This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
-There are several proposals for more efficient key exchange methods.
-One of them is ACE, an one-way authenticated key exchange protocol.
-The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
-ACE requires clients to send one extra element but that doesn't introduce any overhead because this element fits in the unused space in a cell.
 
@@
 
+		\subsection{MorphMix}
+			MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks.
+It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
+Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
+
+			MIX networks typically are high latency and traffic moves slow.
+Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
+Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
+MorphMix has been developed as a low latency and high performance network.
+As such, it will not hold messages for very long, nor will it use cover traffic.
+
+			In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism.
+Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel.
+A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel.
+To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel.
+Although this makes the possibility of such an attack more difficult, it doesn't make it impossible.
+
+			An important part of MorphMix is the ability to detect malicious tunnels.
+Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly.
+Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel.
+This will reveal itself in the fact that the probability of the selection of certain nodes is increased.
+By using this information it becomes possible, to an extent, to detect malicious tunnels.
+
 		\subsection{Tribler}

### 2014-03-13 paper.tex
added text to browser based attacks

--- 2014-03-13 paper.tex
@@
 		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis.\\
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\
 
@@
 To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
+Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.\\
 
@@
 stated that this indeed is still an open problem.
-With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
+With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there may be a lot of malicious nodes in the network.
 Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} do have made some attempts towards a decentralized system, but have yet to find the final answer.
@@
 		\subsection{Incentives in decentralized systems}
-		As described in section \ref{ss:tor_disadvantages} people are using more bandwidth than that they donate.
+		As described in section \ref{ss:tor_disadvantages}, most users are using more bandwidth than that they donate.
 There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor.
@@
 
-		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network.
+		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a decentralized peer-to-peer network.
 The first thing that is described is the so called \emph{Warm-glow Model}.

### 2014-03-13 paper.tex
TOR -> Tor

--- 2014-03-13 paper.tex
@@
 
-	The most widely used anonymous communication system is TOR.
-In this paper we will analyze TOR and its semi centralized nature.
-Furthermore we will look at attempts that have been made to decentralize TOR as well as several other decentralized systems.
+	The most widely used anonymous communication system is Tor.
+In this paper we will analyze Tor and its semi centralized nature.
+Furthermore we will look at attempts that have been made to decentralize Tor as well as several other decentralized systems.
 

### 2014-03-13 paper.tex
Fix indents, extra \\ and other layour inconsistencies

@@
 	\label{sec:tor}
+
 	The implementation of The Onion Router was first described by the U.S.
@@
 Each circuit has three type of Onion Routers \cite{mccoy2008shining}:
+
 		\begin{itemize}
@@
 		\label{ss:tor_circuit}
+
 		As described in the previous section, data on the Tor networks travels over circuits.
@@
 The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.\\
+Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
 
@@
 To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.\\
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
 
@@
 			If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with.
-In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.\\
+In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.
 
@@
 In other words the incentive data has to be accurate and reliable.
-Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.\\
+Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.
 
@@
 In this model determines the percentage of free-rides based on the probabilistic population distribution.
-If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.\\
+If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.
 
@@
 While it is not exemplified a lot, the main idea is to use a virtual currency as incentive.
-The problems with this approach are the scalability and the hidden costs of this service.\\
+The problems with this approach are the scalability and the hidden costs of this service.
 
@@
 	\section{Comparison existing decentralized networks}
-
 		In the last section, we discussedexisting decentralized peer-to-peer networks.
@@
 The next section shows which systems currently have a decentralized structure and/or mechanism.
-These systems are then compared to each other with their pros and cons.\\
+These systems are then compared to each other with their pros and cons.
 
@@
 While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.
-The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of  attacks.\\
+The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of  attacks.
 

### 2014-03-13 paper.tex
Fix itemize layout

@@
 For each network, we will explain the following features:
+
 		\begin{itemize}
-\item Compatibility with Tor. If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
-\item Public implementation. For each network we will explain whether a public implementation is available.
-\item Used in practice. Is the network used in practice?
-\item Attack resistance. We will explain the various weaknesses and possible attacks of each network.
+			\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
+			\item{Public implementation:} For each network we will explain whether a public implementation is available.
+			\item{Used in practice:} Is the network used in practice?
+			\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
 		\end{itemize}

### 2014-03-13 paper.tex
Add section labels used in the introduction

@@
 	\section{Tor vulnerabilities and attacks}
+		\label{sec:attacks}
+
 		Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
@@
 	\section{Problems when decentralizing}
+		\label{sec:problems}
+
 		As we saw in the previous section, we would like to have a decentralized anonymous network.
@@
 	\section{Current decentralized systems}
+		\label{sec:decentralized}
+
 		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
@@
 	\section{Comparison existing decentralized  networks}
+		\label{sec:comparison}
+
 		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
@@
 	\section{Conclusion}
+		\label{sec:conclusion}
+
 		In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.

### 2014-03-13 paper.tex
Include and reference tor graphic

@@
+% !TeX spellcheck = en_GB
 \documentclass[journal]{IEEEtran}
@@
 %\usepackage{url}
+\usepackage{graphicx}
+\usepackage{epstopdf}
 
@@
 
-		Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry) relay node ($X$), a (middle) relay node ($Y$) and an exit node ($Z$).
-In this case, there are two relay nodes, but this is not a fixed number (and could be increased for more security).
+		Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry or guard) relay node ($X$), a (middle) relay node ($Y$) and an exit node ($Z$).
+In this case, there are three relay nodes, but this is not a fixed number.
+A visualisation of this path can be seen in figure \ref{fig:tor_layout}.
 Each node has its own public key and a corresponding private key.
@@
 
+		\begin{figure}[!t]
+			\centering
+			\includegraphics[width=0.4\textwidth]{graphics/tor.pdf}
+			\caption{The components of the Tor network.
+After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node, and uses it to communicate (anonymously) with the internet.}
+			\label{fig:tor_layout}
+		\end{figure}
+
 	\subsection{Directory servers}
@@
 They act as HTTP servers to which Tor nodes can publish signed information about themselves.
-Tor clients can in turn download this information.
+Tor clients can in turn download this information, as seen in figure \ref{fig:tor_layout}.
 

### 2014-03-13 paper.tex
Typo fix
Added the text about Pastry + fixed major issues
Moved the chapter about Tor vulnerabilities and attacks down, fixed
typos and removed duplicated text

@@
 
-	\section{Tor vulnerabilities and attacks}
-		\label{sec:attacks}
-
-		Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
-In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
-
-		\subsection{Browser based attacks}
-			Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
-
-			By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-			By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
-
-			The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-		\subsection{Low-Resource Routing attacks}
-			Hier wat over routing attacks
-
-		\subsection{Sybil attacks}
-			Hier wat over sybil attacks
-
-		\subsection{Replay Attacks}
-			Hier wat over replay attacks
-
-			As we saw, the directory service generates overhead of the network.
+		As we saw, the directory service generates overhead on the network.
 If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
@@
 
-	\section{Comparison existing decentralized  networks}
-		\label{sec:comparison}
-
-		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]
-
-		\subsection{Pastry}
-			Information about Pastry.
-
 		\subsection{Tapestry}
@@
 A property of Tapestry is that it offers load distribution and routing locality.
-Tapastry is very similar to pastry [link naar pastry paper] but there are some small differences in in the handling of network locality and data replication.
 
@@
 Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
+
+		\subsection{Pastry}
+			Pastry is very similar to Tapestry, but there are some small differences.
+One of these differences is the handling of network locality and data object replication.
+Plastry also uses the Plaxton mesh data structure for the routing algorithm.
+Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
+Each node can be found in about log(n) steps.
+
+			The Pastry overlay network is used in several applications, such as Scribe, Squirrel and PAST.
+Scribe is an system that has been built to send multicast messages.
+Instead of relying on the multicast infrastructure, multicast messages are sent using only unicast services.
+Pastry is used to create and manage multicast groups.
+Scribe makes use of the organization, robustness and reliability of the Pastry network.
+
+			Squirrel is a decentralized peer-to-peer web cache.
+The network uses Pastry to locate it's objects and for the routing algorithm.
+Squirrel allows users to share it's web cache with other users in the network, creating a large decentralized web cache.
+Squirrel however introduces some overhead when searching the cache.
+The challenge is to keep this overhead as low as possible.
+
+			PAST is a large scale persistent peer-to-peer network that has been designed to store files.
+It is built upon the Pastry network and the main focus of PAST is providing performance, scalability and security.
 
@@
 	\section{Comparison existing decentralized networks}
-		In the last section, we discussedexisting decentralized peer-to-peer networks.
+		In the last section, we discussed existing decentralized peer-to-peer networks.
 In this section we will make a comparison between these networks.
@@
 			\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
+			\item{Anonimity:} Does the network hide the identities of the sender and/or receiver?
 		\end{itemize}
+
+	\section{Tor vulnerabilities and attacks}
+		\label{sec:attacks}
+
+		Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
+In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
+
+		\subsection{Browser based attacks}
+			Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
+
+			By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
+Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
+
+			By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
+A similar system can be set up only using the HTML meta refresh tag.
+To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
+
+			The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
+
+		\subsection{Low-Resource Routing attacks}
+			Hier wat over routing attacks
+
+		\subsection{Sybil attacks}
+			Hier wat over sybil attacks
+
+		\subsection{Replay Attacks}
+			Hier wat over replay attacks
 

### 2014-03-13 paper.tex
Label for Comparison section
Indent fixes
Removed the HEADS :P

@@
 
-	Although much research has been done about anonymous internet communication, only few systems have been actually implemented and used in practice.
+	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and are being used in practice.
 One of the most important factors that impact anonymity in a communication system is the number of users.
@@
 This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
-Another important factor is for the system to be decentralized.
+Another important factor that impacts the anonymity of the system is decentralization.
 Whenever a network has centralized components and a malicious third party gains control over these components, the functionality and perhaps even the anonymity of the system is compromised.
@@
 	The most widely used anonymous communication system is Tor.
-In this paper we will analyze Tor and its semi centralized nature.
+In this paper we will analyze Tor and its semi-centralized nature.
 Furthermore we will look at attempts that have been made to decentralize Tor as well as several other decentralized systems.
 
-	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview about Tor.
-After that we will talk about decentralization and its problems in section \ref{sec:problems}.
+	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview of Tor.
+After that, we will talk about decentralization and its problems in section \ref{sec:problems}.
 Vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
@@
 A comparison of existing decentralized networks is made in section \ref{sec:comparison}.
-Finally we will conclude and discuss our findings in section \ref{sec:conclusion}.
+Finally, we will conclude and discuss our findings in section \ref{sec:conclusion}.
 
@@
 	In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
+In this section, we will explain the various compoments of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.
 
@@
 When building the circuit, our client generates a distinct secret for each of these nodes.
+More information about the circuit setup, can be found in II-D.
+Circuit creation.
 
@@
 The clients in the Tor network are known as Onion Proxies.
-The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy to configure.
-The Onion Proxies are responsible for downloading the directory information, establish circuits across the network and handle connections from user applications.
+The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy for users to configure.
+The Onion Proxies are responsible for downloading the directory information, establishing circuits across the network and handling connections from user applications.
 
 		The routing in the network is done by Onion Routers, also called relay nodes.
-The relay nodes relays the data from the Onion Proxy to the web server across a circuit (circuits are described in 2D).
+The relay nodes relay the data from the Onion Proxy to the web server across a circuit (circuits are described in II-D).
 Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}.
@@
 Each cell has a header and a payload.
-The header consists of a number that identifies the circuit of the cell and a command that indicates what to do with the cell’s payload.
+The header consists of a number that identifies the circuit the cell travels on and a command that indicates what to do with the cell’s payload.
 
@@
 OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
-Now both Alice and OR1 have a shared key they use to encrypt and decrypt data between them.
+Now both Alice and OR1 have a shared key they use to encrypt and decrypt data sent between them.
 
@@
 The congestion control could be improved by using an unreliable protocol for links between Tor relays.
+Goldberg et al.
+[linkje] have proposed PCTCP which could improve the response time of the Tor network with 60\% and the download time of files with 30\%.
 
@@
 This means that these users are slowing the network down as they use more traffic than giving to the network.
-A possible solution for this is to throttle certain protocols at exit nodes or at Onion Proxies.
+A possible solution for this is to throttle certain high-bandwidth protocols such as BitTorrent at exit nodes or at Onion Proxies.
 
@@
 By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
-Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network.
+Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network and making it faster.
 
@@
 The problem is that the current selection strategy is optimal when the network is fully loaded.
+This is not always the case.
 Using a better path selection algorithm could increase the capacity of the network and the overall user experience.
@@
 There is also overhead in the TLS connection between the nodes in the network.
-Removing the empty TLS application record which could reduce the overhead in the TCP/IP header with 6.3\%.
+According to Dingledine et al, removing the empty TLS application record could reduce the overhead in the TCP/IP header with 6.3\%.
 
@@
 
+		As we saw in the previous section, we would like to have a decentralized anonymous network.
+This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
+Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry [link].
+These networks will be described in more detail in the next chapter.
+Among these networks are some overlay anonymous networks such as Tarzan and Torks [link].
+
+		There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
+When removing this central authority, these components needs to be spread across the peers in the network.
+In this section we will explain the various problems that are involved when decentralizing Tor.
+In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
+
+		\subsection{Bootstrapping new nodes}
+			If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be a starting point where this new node can discover neighbors in the network to connect with.
+In Tor, a directory server can tell the new node what his neighbors are and where to find them \cite{dingledine2004tor}.
+
+			Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
+stated that this indeed is still an open problem.
+With decentralized systems, there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
+Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.
+Some of these issues can be found in the last section when comparing these systems.
+
+		\subsection{Incentives in decentralized systems}
+			As described in section \ref{ss:tor_disadvantages}, people are usually using more bandwidth than that they donate.
+There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor.
+If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified.
+In other words, the reputation data has to be accurate and reliable.
+Besides the integrity of this data, the traffic it generates on the network should have minimal impact on the overall performance.
+
+			Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network.
+The first proposal that is described is the so called \emph{Warm-glow Model}.
+This model determines the percentage of free-rides based on the probabilistic population distribution.
+If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.
+
+			The second proposal is using monetary schemes.
+While it is not exemplified a lot, the main idea is to use a virtual currency as incentive.
+The problems with this approach are the scalability and the hidden costs of this service.
+
+			The third proposal is \emph{Reciprocity-Based Schemes}.
+Using this approach, a peer maintains a behavior history of other peers in the network.
+These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity.
+The formal are more suitable for longer relationships between peers.
+The latter is more scalable but they rely on third party and must handle trust issues themselves.
+
+		\subsection{Key exchange}
+			With a decentralized network, using a centralized authority for managing the keys, is not possible.
+This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them.
+Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
+Diffie-Hellman is for example used in the circuit setup in Onion Routing (see secion II-D), however, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable for a man-in-the-middle attack.
+This weakness makes it possible for an adversary to decrypt all message sent between the two parties.
+
+			Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) [linkje naar ace].
+This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
+There are several proposals for more efficient key exchange methods.
+One of them is \emph{ACE}, an one-way authenticated key exchange protocol.
+The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
+ACE requires clients to send one extra element in the key exchange.
+This however, does not introduce any overhead because the element fits in the unused space in a cell.
+=======
 	\subsection{Bootstrapping new nodes}
@@
 
+		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
+Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
+Each of these decentralized networks will be discussed in the next section.
+Note that we're only considering fully decentralized networks here.
+Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.[link naar survey p2p?]
+
+		\subsection{Gnutella}
+			Gnutella is a decentralized peer-to-peer network used for distributed search of files.
+Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients.
+Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.
+In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available.
+These peers can for example be found on http://gnutellahosts.com.
+Once the peer has joined, there are several messages a servant can send out:
+
+			\begin{itemize}
+				\item A peer sends a PING message to it's neighbours to announce it's presents.
+This message is forwarded to other peers and each peer sends a PONG message back.
+This way, the newly joined peer can learn about his neighbours and the network topology.
+				\item The peer can issue QUERY answers. Other peers responds with a QUERY RESPONSE message to specify whether the file that was issued in the query, was found or not.
+				\item To transfer items between peers, the GET and PUSH messages are being used.
+			\end{itemize}
+
+			Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file.
+To search for a file, a flooding algorithm is used: each peer sends the request from another peer to each of it's neighbours in his routing table.
+=======
 		There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file.
@@
 
+			There are three types of file keys in Freenet: the first one is called the \emph{Keyword-Signed Key} (KSK) which is derived from a short description of the file.
+Another key is the \emph{Signed-Subspace key} (SSK) which enables personal namespaces.
+This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
+The third type of key is the \emph{Content-Hash Key} (CHK) which is used for updating and splitting of contents.
+
+			The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
+Each peer has only knowledge about his direct neighbours.
+Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
+Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
+Results of queries are being cached in intermediate nodes to reduce the time for a query response.
+To prevent looping of the requests, each request contains a random identifier.
+The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
+
+		\subsection{NISAN}
+			Information about NISAN.
+
+		\subsection{MorphMix}
+			MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks.
+It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
+Additionally, MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
+
+			MIX networks are typically high latency networks and traffic in it moves slow.
+Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
+Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
+MorphMix has been developed as a low latency and high performance network.
+As such, it will not hold messages for very long, nor will it use cover traffic.
+
+			In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism.
+Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel.
+A malicious node could select a colluding node to continue the tunnel and therefore control the entire tunnel.
+To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel.
+Although this makes the possibility of such an attack more difficult, it doesn't make it impossible.
+
+			An important part of MorphMix is the ability to detect malicious tunnels.
+Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly.
+Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel.
+This will reveal itself in the fact that the probability of the selection of certain nodes is increased.
+By using this information it becomes possible, to an extent, to detect malicious tunnels.
+=======
 		MIX networks typically are high latency and traffic moves slow.
@@
 
+		\subsection{Tapestry}
+			Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
+A property of Tapestry is that it offers load distribution and routing locality.
+
+			Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored.
+A peer can also function as a router, which forwards an incoming message.
+The routing algorithm is based on the destination ID of the packet.
+Routers are using local routing maps to route messages to the destination ID digit by digit.
+The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.
+
+			Tapestry is a fundamental component of OceanStore [linkje naar paper over OceanStore], a decentralized storage system.
+Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
+=======
 	\subsection{Tapestry}
@@
 \section{Comparison existing decentralized networks}
+	\label{sec:comparison}
+
 	In the last section, we discussed existing decentralized peer-to-peer networks.
@@
 
+			By running a HTTP exit node and a Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
+Every ten minutes, the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
+=======
 	\subsection{Sybil attacks}
@@
 
+			The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant, one would have to use HTTPS to prevent man-in-the-middle attacks.
+
+		\subsection{Low-Resource Routing attacks}
+			Hier wat over routing attacks
+
+		\subsection{Sybil attacks}
+			Hier wat over sybil attacks
+
+		\subsection{Replay Attacks}
+			Hier wat over replay attacks
+
+	\section{Conclusion}
+		\label{sec:conclusion}
+
+		In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.
+Furthermore, we looked at the main disadvantages and problems Tor is currently facing.
+We then made a bridge to decentralized systems.
+We first explained which problems one might face when decentralizing a system such as Tor.
+The next section shows which systems currently have a decentralized structure and/or mechanism.
+These systems are then compared to each other with their pros and cons.
+
+		From this table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
+While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.
+The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.
+
+		While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
+
+	\appendices
+=======
 	In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.

### 2014-03-13 paper.tex
And removed the =======

@@
 This however, does not introduce any overhead because the element fits in the unused space in a cell.
-=======
+
 	\subsection{Bootstrapping new nodes}
@@
 To search for a file, a flooding algorithm is used: each peer sends the request from another peer to each of it's neighbours in his routing table.
-=======
+
 		There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file.
@@
 By using this information it becomes possible, to an extent, to detect malicious tunnels.
-=======
+
 		MIX networks typically are high latency and traffic moves slow.
@@
 Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
-=======
+
 	\subsection{Tapestry}
@@
 Every ten minutes, the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-=======
+
 	\subsection{Sybil attacks}
@@
 	\appendices
-=======
+
 	In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.

### 2014-03-13 paper.tex
Removed the duplicate text
This was due to my merge conflict :(

@@
 
-	\subsection{Bootstrapping new nodes}
-		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with.
-In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.
-
-		Moving this system to a non peer-to-peer base is difficult.
-Dingledine et al.
-stated that this indeed is still an open problem.
-With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
-Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} do have made some attempts towards a decentralized system, but have yet to find the final answer.
-
-	\subsection{Incentives in decentralized systems}
-		As described in section \ref{ss:tor_disadvantages} people are using more bandwidth than that they donate.
-There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor.
-If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified.
-In other words the incentive data has to be accurate and reliable.
-Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.
-
-		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network.
-The first thing that is described is the so called \emph{Warm-glow Model}.
-In this model determines the percentage of free-rides based on the probabilistic population distribution.
-If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.
-
-		The second proposal is using monetary schemes.
-While it is not exemplified a lot, the main idea is to use a virtual currency as incentive.
-The problems with this approach are the scalability and the hidden costs of this service.
-
-		The third proposal is \emph{Reciprocity-Based Schemes}.
-Using this approach a peer maintains a behavior history of other peers in the network.
-These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity.
-The formal are more suitable for longer relationships between peers.
-The latter is more scalable but they rely on third party and must handle trust issues themselves.
-
-	\subsection{Key exchange}
-		When using a decentralized network, using a centralized authority for managing the keys, is not possible.
-This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them.
-Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
-Diffie-Hellman is for example used in the circuit setup in Onion Routing (see chapter I), however, it is possible for an adversary to manipulate with the keys send between two parties.
-This makes it possible for the adversary to decrypt all message sent between the two parties.
-
-		Tor currently uses an interactive forward-secret key-exchange protocol called the Tor authentication protocol (TAP) [linkje naar ace].
-This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
-There are several proposals for more efficient key exchange methods.
-One of them is ACE, an one-way authenticated key exchange protocol.
-The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
-ACE requires clients to send one extra element but that doesn't introduce any overhead because this element fits in the unused space in a cell.
-
 \section{Current decentralized systems}
@@
 
-		\subsection{Gnutella}
-			Gnutella is a decentralized peer-to-peer network used for distributed search of files.
-Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients.
-Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.
-In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available.
-These peers can for example be found on http://gnutellahosts.com.
-Once the peer has joined, there are several messages a servant can send out:
-
-			\begin{itemize}
-				\item A peer sends a PING message to it's neighbours to announce it's presents.
-This message is forwarded to other peers and each peer sends a PONG message back.
-This way, the newly joined peer can learn about his neighbours and the network topology.
-				\item The peer can issue QUERY answers. Other peers responds with a QUERY RESPONSE message to specify whether the file that was issued in the query, was found or not.
-				\item To transfer items between peers, the GET and PUSH messages are being used.
-			\end{itemize}
-
-			Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file.
-To search for a file, a flooding algorithm is used: each peer sends the request from another peer to each of it's neighbours in his routing table.
-
-		There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file.
-Another key is the Signed-Subspace key (SSK) which enables personal namespaces.
-This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
-The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.
-
-		The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
-Each peer has only knowledge about his neighbours.
-Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
-Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
-Results of queries are being cached in intermediate nodes to reduce the time for a query response.
-To prevent looping of the requests, each request contains a random identifier.
-The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
-
 	\subsection{NISAN}
@@
 
-		\subsection{NISAN}
-			Information about NISAN.
-
-		\subsection{MorphMix}
-			MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks.
-It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
-Additionally, MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
-
-			MIX networks are typically high latency networks and traffic in it moves slow.
-Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
-Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
-MorphMix has been developed as a low latency and high performance network.
-As such, it will not hold messages for very long, nor will it use cover traffic.
-
-			In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism.
-Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel.
-A malicious node could select a colluding node to continue the tunnel and therefore control the entire tunnel.
-To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel.
-Although this makes the possibility of such an attack more difficult, it doesn't make it impossible.
-
-			An important part of MorphMix is the ability to detect malicious tunnels.
-Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly.
-Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel.
-This will reveal itself in the fact that the probability of the selection of certain nodes is increased.
-By using this information it becomes possible, to an extent, to detect malicious tunnels.
-
-		MIX networks typically are high latency and traffic moves slow.
-Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
-Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
-MorphMix has been developed as a low latency and high performance network.
-As such, it will not hold messages for very long, nor will it use cover traffic.
-
-		In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism.
-Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel.
-A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel.
-To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel.
-Although this makes the possibility of such an attack more difficult, it doesn't make it impossible.
-
-		An important part of MorphMix is the ability to detect malicious tunnels.
-Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly.
-Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel.
-This will reveal itself in the fact that the probability of the selection of certain nodes is increased.
-By using this information it becomes possible, to an extent, to detect malicious tunnels.
-
 	\subsection{Tribler}
@@
 			Tapestry is a fundamental component of OceanStore [linkje naar paper over OceanStore], a decentralized storage system.
-Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
-
-	\subsection{Tapestry}
-		Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
-A property of Tapestry is that it offers load distribution and routing locality.
-
-		Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored.
-A peer can also function as a router, which forwards an incoming message.
-The routing algorithm is based on the destination ID of the packet.
-Routers are using local routing maps to route messages to the destination ID digit by digit.
-The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.
-
-		Tapestry is a fundamental component of Oceanstore [linkje naar paper over Oceanstore], a decentralized storage system.
 Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
@@
 
-			By running a HTTP exit node and a Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes, the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-	\subsection{Sybil attacks}
-		Hier wat over sybil attacks
-
-	\subsection{Replay Attacks}
-		Hier wat over replay attacks
-
-\section{Conclusion}
-	\label{sec:conclusion}
-
-			The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant, one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-		\subsection{Low-Resource Routing attacks}
-			Hier wat over routing attacks
-
 	\subsection{Sybil attacks}

### 2014-03-13 paper.tex
Added text at the replay attack

--- 2014-03-13 paper.tex
@@
 
-	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and are being used in practice.
+	Although much research has been done about anonymous internet communication, only few systems have been actually implemented and used in practice.
 One of the most important factors that impact anonymity in a communication system is the number of users.
@@
 This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
-Another important factor that impacts the anonymity of the system is decentralization.
+Another important factor is for the system to be decentralized.
 Whenever a network has centralized components and a malicious third party gains control over these components, the functionality and perhaps even the anonymity of the system is compromised.
@@
 	The most widely used anonymous communication system is Tor.
-In this paper we will analyze Tor and its semi-centralized nature.
+In this paper we will analyze Tor and its semi centralized nature.
 Furthermore we will look at attempts that have been made to decentralize Tor as well as several other decentralized systems.
 
-	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview of Tor.
-After that, we will talk about decentralization and its problems in section \ref{sec:problems}.
+	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview about Tor.
+After that we will talk about decentralization and its problems in section \ref{sec:problems}.
 Vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
@@
 A comparison of existing decentralized networks is made in section \ref{sec:comparison}.
-Finally, we will conclude and discuss our findings in section \ref{sec:conclusion}.
+Finally we will conclude and discuss our findings in section \ref{sec:conclusion}.
 
@@
 	In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
-In this section, we will explain the various compoments of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.
 
@@
 When building the circuit, our client generates a distinct secret for each of these nodes.
-More information about the circuit setup, can be found in II-D.
-Circuit creation.
 
@@
 The clients in the Tor network are known as Onion Proxies.
-The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy for users to configure.
-The Onion Proxies are responsible for downloading the directory information, establishing circuits across the network and handling connections from user applications.
+The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy to configure.
+The Onion Proxies are responsible for downloading the directory information, establish circuits across the network and handle connections from user applications.
 
 		The routing in the network is done by Onion Routers, also called relay nodes.
-The relay nodes relay the data from the Onion Proxy to the web server across a circuit (circuits are described in II-D).
+The relay nodes relays the data from the Onion Proxy to the web server across a circuit (circuits are described in 2D).
 Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}.
@@
 Each cell has a header and a payload.
-The header consists of a number that identifies the circuit the cell travels on and a command that indicates what to do with the cell’s payload.
+The header consists of a number that identifies the circuit of the cell and a command that indicates what to do with the cell’s payload.
 
@@
 OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
-Now both Alice and OR1 have a shared key they use to encrypt and decrypt data sent between them.
+Now both Alice and OR1 have a shared key they use to encrypt and decrypt data between them.
 
@@
 The congestion control could be improved by using an unreliable protocol for links between Tor relays.
-Goldberg et al.
-[linkje] have proposed PCTCP which could improve the response time of the Tor network with 60\% and the download time of files with 30\%.
 
@@
 This means that these users are slowing the network down as they use more traffic than giving to the network.
-A possible solution for this is to throttle certain high-bandwidth protocols such as BitTorrent at exit nodes or at Onion Proxies.
+A possible solution for this is to throttle certain protocols at exit nodes or at Onion Proxies.
 
@@
 By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
-Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network and making it faster.
+Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network.
 
@@
 The problem is that the current selection strategy is optimal when the network is fully loaded.
-This is not always the case.
 Using a better path selection algorithm could increase the capacity of the network and the overall user experience.
@@
 There is also overhead in the TLS connection between the nodes in the network.
-According to Dingledine et al, removing the empty TLS application record could reduce the overhead in the TCP/IP header with 6.3\%.
+Removing the empty TLS application record which could reduce the overhead in the TCP/IP header with 6.3\%.
 
-		As we saw, the directory service generates overhead on the network.
+	\section{Tor vulnerabilities and attacks}
+		\label{sec:attacks}
+
+		Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
+In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
+
+		\subsection{Browser based attacks}
+		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\
+
+		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
+Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
+
+		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
+A similar system can be set up only using the HTML meta refresh tag.
+To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
+Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.
+
+		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
+
+		\subsection{Low-Resource Routing attacks}
+			Hier wat over routing attacks
+
+		\subsection{Sybil attacks}
+			Hier wat over sybil attacks
+
+		\subsection{Replay Attacks}
+			A replay attack [cite naar replay attack paper] happens when a malicious entry node duplicates cells and send them again.
+Since Tor uses uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the connection to be torn down.
+
+			Using this, an accomplice exit router can therefore in cooperation with the entry node discover the sender and receiver's relationship.
+On top of that, this attack can also be used as a denial of service attack.
+This attack is according to the authors quite challenging to solve and does require some further research.
+
+			As we saw, the directory service generates overhead of the network.
 If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
@@
 In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
-
-		As we saw in the previous section, we would like to have a decentralized anonymous network.
-This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry [link].
-These networks will be described in more detail in the next chapter.
-Among these networks are some overlay anonymous networks such as Tarzan and Torks [link].
-
-		There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
-When removing this central authority, these components needs to be spread across the peers in the network.
-In this section we will explain the various problems that are involved when decentralizing Tor.
-In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
-
-		\subsection{Bootstrapping new nodes}
-			If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be a starting point where this new node can discover neighbors in the network to connect with.
-In Tor, a directory server can tell the new node what his neighbors are and where to find them \cite{dingledine2004tor}.
-
-			Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
-stated that this indeed is still an open problem.
-With decentralized systems, there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
-Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.
-Some of these issues can be found in the last section when comparing these systems.
-
-		\subsection{Incentives in decentralized systems}
-			As described in section \ref{ss:tor_disadvantages}, people are usually using more bandwidth than that they donate.
-There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor.
-If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified.
-In other words, the reputation data has to be accurate and reliable.
-Besides the integrity of this data, the traffic it generates on the network should have minimal impact on the overall performance.
-
-			Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network.
-The first proposal that is described is the so called \emph{Warm-glow Model}.
-This model determines the percentage of free-rides based on the probabilistic population distribution.
-If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.
-
-			The second proposal is using monetary schemes.
-While it is not exemplified a lot, the main idea is to use a virtual currency as incentive.
-The problems with this approach are the scalability and the hidden costs of this service.
-
-			The third proposal is \emph{Reciprocity-Based Schemes}.
-Using this approach, a peer maintains a behavior history of other peers in the network.
-These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity.
-The formal are more suitable for longer relationships between peers.
-The latter is more scalable but they rely on third party and must handle trust issues themselves.
-
-		\subsection{Key exchange}
-			With a decentralized network, using a centralized authority for managing the keys, is not possible.
-This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them.
-Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
-Diffie-Hellman is for example used in the circuit setup in Onion Routing (see secion II-D), however, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable for a man-in-the-middle attack.
-This weakness makes it possible for an adversary to decrypt all message sent between the two parties.
-
-			Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) [linkje naar ace].
-This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
-There are several proposals for more efficient key exchange methods.
-One of them is \emph{ACE}, an one-way authenticated key exchange protocol.
-The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
-ACE requires clients to send one extra element in the key exchange.
-This however, does not introduce any overhead because the element fits in the unused space in a cell.
 
@@
 
-		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.[link naar survey p2p?]
-
-		\subsection{Gnutella}
-			Gnutella is a decentralized peer-to-peer network used for distributed search of files.
-Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients.
-Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.
-In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available.
-These peers can for example be found on http://gnutellahosts.com.
-Once the peer has joined, there are several messages a servant can send out:
-
-			\begin{itemize}
-				\item A peer sends a PING message to it's neighbours to announce it's presents.
-This message is forwarded to other peers and each peer sends a PONG message back.
-This way, the newly joined peer can learn about his neighbours and the network topology.
-				\item The peer can issue QUERY answers. Other peers responds with a QUERY RESPONSE message to specify whether the file that was issued in the query, was found or not.
-				\item To transfer items between peers, the GET and PUSH messages are being used.
-			\end{itemize}
-
-			Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file.
-To search for a file, a flooding algorithm is used: each peer sends the request from another peer to each of it's neighbours in his routing table.
-
 			There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file.
@@
 Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
-
-			There are three types of file keys in Freenet: the first one is called the \emph{Keyword-Signed Key} (KSK) which is derived from a short description of the file.
-Another key is the \emph{Signed-Subspace key} (SSK) which enables personal namespaces.
-This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
-The third type of key is the \emph{Content-Hash Key} (CHK) which is used for updating and splitting of contents.
-
-			The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
-Each peer has only knowledge about his direct neighbours.
-Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
-Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
-Results of queries are being cached in intermediate nodes to reduce the time for a query response.
-To prevent looping of the requests, each request contains a random identifier.
-The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
-
-		\subsection{NISAN}
-			Information about NISAN.
-
-		\subsection{MorphMix}
-			MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks.
-It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
-Additionally, MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
-
-			MIX networks are typically high latency networks and traffic in it moves slow.
-Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
-Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
-MorphMix has been developed as a low latency and high performance network.
-As such, it will not hold messages for very long, nor will it use cover traffic.
-
-			In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism.
-Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel.
-A malicious node could select a colluding node to continue the tunnel and therefore control the entire tunnel.
-To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel.
-Although this makes the possibility of such an attack more difficult, it doesn't make it impossible.
-
-			An important part of MorphMix is the ability to detect malicious tunnels.
-Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly.
-Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel.
-This will reveal itself in the fact that the probability of the selection of certain nodes is increased.
-By using this information it becomes possible, to an extent, to detect malicious tunnels.
 
@@
 
-		\subsection{Tapestry}
-			Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
-A property of Tapestry is that it offers load distribution and routing locality.
+	\section{Comparison existing decentralized  networks}
+		\label{sec:comparison}
 
-			Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored.
-A peer can also function as a router, which forwards an incoming message.
-The routing algorithm is based on the destination ID of the packet.
-Routers are using local routing maps to route messages to the destination ID digit by digit.
-The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.
+		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
+Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan.
+Each of these decentralized networks will be discussed in the next section.
+Note that we're only considering fully decentralized networks here.
+Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]
 
-			Tapestry is a fundamental component of OceanStore [linkje naar paper over OceanStore], a decentralized storage system.
-Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
+		\subsection{Pastry}
+			Information about Pastry.
 
@@
 A property of Tapestry is that it offers load distribution and routing locality.
+Tapastry is very similar to pastry [link naar pastry paper] but there are some small differences in in the handling of network locality and data replication.
 
@@
 Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
-
-	\subsection{Pastry}
-		Pastry is very similar to Tapestry, but there are some small differences.
-One of these differences is the handling of network locality and data object replication.
-Plastry also uses the Plaxton mesh data structure for the routing algorithm.
-Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
-Each node can be found in about log(n) steps.
-
-		The Pastry overlay network is used in several applications, such as Scribe, Squirrel and PAST.
-Scribe is an system that has been built to send multicast messages.
-Instead of relying on the multicast infrastructure, multicast messages are sent using only unicast services.
-Pastry is used to create and manage multicast groups.
-Scribe makes use of the organization, robustness and reliability of the Pastry network.
-
-		Squirrel is a decentralized peer-to-peer web cache.
-The network uses Pastry to locate it's objects and for the routing algorithm.
-Squirrel allows users to share it's web cache with other users in the network, creating a large decentralized web cache.
-Squirrel however introduces some overhead when searching the cache.
-The challenge is to keep this overhead as low as possible.
-
-		PAST is a large scale persistent peer-to-peer network that has been designed to store files.
-It is built upon the Pastry network and the main focus of PAST is providing performance, scalability and security.
 
@@
 	\section{Comparison existing decentralized networks}
-	\label{sec:comparison}
-
 		In the last section, we discussed existing decentralized peer-to-peer networks.
@@
 			\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
-		\item{Anonimity:} Does the network hide the identities of the sender and/or receiver?
 		\end{itemize}
-
-\section{Tor vulnerabilities and attacks}
-	\label{sec:attacks}
-
-	Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
-In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
-
-	\subsection{Browser based attacks}
-		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
-
-		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
-
-		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-	\subsection{Low-Resource Routing attacks}
-		Hier wat over routing attacks
-
-			By running a HTTP exit node and a Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes, the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-	\subsection{Sybil attacks}
-		Hier wat over sybil attacks
-
-	\subsection{Replay Attacks}
-		Hier wat over replay attacks
 
@@
 		\label{sec:conclusion}
-
-			The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant, one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-		\subsection{Low-Resource Routing attacks}
-			Hier wat over routing attacks
-
-		\subsection{Sybil attacks}
-			Hier wat over sybil attacks
-
-		\subsection{Replay Attacks}
-			Hier wat over replay attacks
-
-	\section{Conclusion}
-		\label{sec:conclusion}
-
-		In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.
-Furthermore, we looked at the main disadvantages and problems Tor is currently facing.
-We then made a bridge to decentralized systems.
-We first explained which problems one might face when decentralizing a system such as Tor.
-The next section shows which systems currently have a decentralized structure and/or mechanism.
-These systems are then compared to each other with their pros and cons.
-
-		From this table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
-While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.
-The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.
-
-		While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
-
-	\appendices
 

### 2014-03-13 paper.tex

--- 2014-03-13 paper.tex
@@
 
+		\section{Tor vulnerabilities and attacks}
+	\label{sec:attacks}
+
+	Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
+In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
+
+		\subsection{Browser based attacks}
+		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\
+
+		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
+Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
+
+		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
+A similar system can be set up only using the HTML meta refresh tag.
+To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
+Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.
+
+		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
+
+		\subsection{Low-Resource Routing attacks}
+			Hier wat over routing attacks
+
+		\subsection{Sybil attacks}
+			Hier wat over sybil attacks
+
+		\subsection{Replay Attacks}
+			A replay attack [cite naar replay attack paper] happens when a malicious entry node duplicates cells and send them again.
+Since Tor uses uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the connection to be torn down.
+
+			Using this, an accomplice exit router can therefore in cooperation with the entry node discover the sender and receiver's relationship.
+On top of that, this attack can also be used as a denial of service attack.
+This attack is according to the authors quite challenging to solve and does require some further research.
+
 \section{Problems when decentralizing}
@@
 
-	As we saw in the previous section, we would like to have a decentralized anonymous network.
+	As we saw in section \ref{sec:tor}, we would like to have a decentralized anonymous network.
 This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
@@
 
-\section{Tor vulnerabilities and attacks}
-	\label{sec:attacks}
-
-	Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
-In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
-
-	\subsection{Browser based attacks}
-		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
-
-		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
-
-		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-	\subsection{Low-Resource Routing attacks}
-		Hier wat over routing attacks
-
-	\subsection{Sybil attacks}
-		Hier wat over sybil attacks
-
-	\subsection{Replay Attacks}
-		Hier wat over replay attacks
-
 	\section{Conclusion}

### 2014-03-13 paper.tex
Current decentralized systems, NISAN

--- 2014-03-13 paper.tex
@@
 
-	\section{Tor vulnerabilities and attacks}
-		\label{sec:attacks}
-
-		Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
-In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
-
-		\subsection{Browser based attacks}
-		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\
-
-		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
-Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.
-
-		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-		\subsection{Low-Resource Routing attacks}
-			Hier wat over routing attacks
-
-		\subsection{Sybil attacks}
-			Hier wat over sybil attacks
-
-		\subsection{Replay Attacks}
-			A replay attack [cite naar replay attack paper] happens when a malicious entry node duplicates cells and send them again.
-Since Tor uses uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the connection to be torn down.
-
-			Using this, an accomplice exit router can therefore in cooperation with the entry node discover the sender and receiver's relationship.
-On top of that, this attack can also be used as a denial of service attack.
-This attack is according to the authors quite challenging to solve and does require some further research.
-
-			As we saw, the directory service generates overhead of the network.
+		As we saw, the directory service generates overhead on the network.
 If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
@@
 	\subsection{NISAN}
-			Information about NISAN.
+		NISAN, or Network Information Service for Anonymization Networks \cite{panchenko2006nisan}, is an anonymization network which implements a distributed node discovery.
+Not only does a central node administrator (the Directory Server in Tor) imply trust in those servers, Panchenko et al.
+also argue that a central node administration (the Directory Server in Tor) does not scale, as the current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.
+
+		NISAN implements a DHT-based approach (Kademlia) for distributing node information, in such a way that does not require the client to know about all the nodes in the network (such as in Tor).
+To build a circuit, NISAN generates random IDs and searches for the closest hit throughout the network.
+This makes it possible to build a path with nodes picked in a random, uniform way among all nodes, without the trust of a third party.
+
+		This does not fully protect against fingerprinting or bridging attacks (passive attacks), and suggest to do random walks throughout the network to mitigate that.
+The authors admit however this decreases the protection against an active attack.
 
@@
 
-	\section{Comparison existing decentralized  networks}
-		\label{sec:comparison}
-
-		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]
-
-		\subsection{Pastry}
-			Information about Pastry.
-
 	\subsection{Tapestry}
@@
 Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
+
+	\subsection{Pastry}
+		Pastry is very similar to Tapestry, but there are some small differences.
+One of these differences is the handling of network locality and data object replication.
+Plastry also uses the Plaxton mesh data structure for the routing algorithm.
+Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
+Each node can be found in about log(n) steps.
+
+		The Pastry overlay network is used in several applications, such as Scribe, Squirrel and PAST.
+Scribe is an system that has been built to send multicast messages.
+Instead of relying on the multicast infrastructure, multicast messages are sent using only unicast services.
+Pastry is used to create and manage multicast groups.
+Scribe makes use of the organization, robustness and reliability of the Pastry network.
+
+		Squirrel is a decentralized peer-to-peer web cache.
+The network uses Pastry to locate it's objects and for the routing algorithm.
+Squirrel allows users to share it's web cache with other users in the network, creating a large decentralized web cache.
+Squirrel however introduces some overhead when searching the cache.
+The challenge is to keep this overhead as low as possible.
+
+		PAST is a large scale persistent peer-to-peer network that has been designed to store files.
+It is built upon the Pastry network and the main focus of PAST is providing performance, scalability and security.
 
@@
 		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
+		\item{Anonimity:} Does the network hide the identities of the sender and/or receiver?
 	\end{itemize}
+
+\section{Tor vulnerabilities and attacks}
+	\label{sec:attacks}
+
+	Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
+In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
+
+	\subsection{Browser based attacks}
+		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
+
+		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
+Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
+
+		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
+A similar system can be set up only using the HTML meta refresh tag.
+To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
+
+		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
+
+	\subsection{Low-Resource Routing attacks}
+		Hier wat over routing attacks
+
+	\subsection{Sybil attacks}
+		Hier wat over sybil attacks
+
+	\subsection{Replay Attacks}
+		Hier wat over replay attacks
 

### 2014-03-13 paper.tex
Current decentralized systems, Tarzan

@@
 	\subsection{Tarzan}
-		Information about Tarzan.
+		Tarzan [TARZAN PAPER] is a fully distributed peer-to-peer anonymity network.
+It implements a network address translator (NAT) to bridge between nodes running Tarzan and the internet.
+This means that services don\'t have to be aware of the fact they are running through Tarzan.
+
+		Tarzan requires knowledge of a few existing nodes to bootstrap and uses a gossiping protocol to discover other nodes.
+Nambiar et al.
+showed however that this does not scale beyond roughly 10,000 nodes [NISAN, SALSA PAPER].
+
+		Once Tarzan has knowledge of enough nodes, it achieves its anonymity with much like a Chaumian mix, with layered encryption and routing through multiple hops.
+In contrast to Tor and other networks, Tarzan uses cover traffic to provide protection against traffic analysis by a global advisory to find an initiator.
 

### 2014-03-13 paper.tex
Current decentralized systems, Torsk

@@
 
+	\subsection{Torsk}
+		Torsk [TORSKKKK PAPER] is an extension to Tor, designed to be an interoperable replacement for the circuit creation and Directory Service as used by Tor.
+The authors argue that the current Directory Service does not scale, with the percentage of the traffic in a network dedicated to node discovery growing as the number of nodes grow.
+With the 2009 version of Tor, they argue that 100\% of the networks traffic would consist of node discovery traffic with roughly 1.2 million clients.
+
+		Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority.
+The DHT is a combination of Kademlia DHT and Myrmic DHT.
+Kademlia DHT was chosen because it is already widely used and it has proven itself for a large number of users.
+
+		The Myrmic DHT runs on top of Kademlia, and introduces the Neighbourhood Authority.
+This authority issues certs to nodes that participate in the DHT, but it does not participate in the DHT itself.
+The NA makes this solution not a fully decentralized one, but its role is a lot smaller than the current Directory Servers.
+This does not solve the trust issue, but it does solve the scalability issue.
+
 	\subsection{Other decentralized systems}

### 2014-03-13 paper.tex
Vulnerabilities, Sybil attack

--- 2014-03-13 paper.tex
@@
 	\subsection{NISAN}
-		NISAN, or Network Information Service for Anonymization Networks \cite{panchenko2006nisan}, is an anonymization network which implements a distributed node discovery.
-Not only does a central node administrator (the Directory Server in Tor) imply trust in those servers, Panchenko et al.
-also argue that a central node administration (the Directory Server in Tor) does not scale, as the current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.
-
-		NISAN implements a DHT-based approach (Kademlia) for distributing node information, in such a way that does not require the client to know about all the nodes in the network (such as in Tor).
-To build a circuit, NISAN generates random IDs and searches for the closest hit throughout the network.
-This makes it possible to build a path with nodes picked in a random, uniform way among all nodes, without the trust of a third party.
-
-		This does not fully protect against fingerprinting or bridging attacks (passive attacks), and suggest to do random walks throughout the network to mitigate that.
-The authors admit however this decreases the protection against an active attack.
+		Information about NISAN.
 
@@
 	\subsection{Sybil attacks}
-		Hier wat over sybil attacks
+		The Sybil attack is an attack where a single attacker represents itself as multiple nodes in a peer-to-peer system.
+Abusing this, the attacker is able to propagate false assumptions about the network to other nodes.
+
+		First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or the other, except under what he call "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify itself.
+This must be done within a small enough time frame that an attacker can't do this in sequence, but all nodes must do them in parallel.
+
+		A fully distributed network that implements such a solution is the Bitcoin network [BITCOIN PAPER: http://s.kwma.kr/pdf/Bitcoin/bitcoin.pdf], in which computing power, and not the number of nodes is important for the general network consensus.
 

### 2014-03-13 paper.tex
Problems with decentralizing, NAT

@@
 
+	\subsection{NAT traversal}
+		A truly decentralized system requires the participating nodes to have direct connection to each other.
+Because of the limited availability of IPv4 network addresses, most consumer grade internet connections only provide one network address per subscriber, shared by all the devices connected to the subscribers network using Network Address Translation (NAT).
+With IPv4 network addresses getting more scarce, some Internet Service Providers even put more than one subscribers behind a single network address, using a carrier-grade NAT.
+
+		A NAT-based system works by creating a local, private network which a NAT-enabled router connects to the internet.
+The local network uses network addresses from the private ranges (e.g.
+10.0.0.0/8 or 192.168.0.0/16).
+
+		When a local device sends a packet to the internet, the router replaces these private addresses, including the source ports, with its own public address before forwarding it to the internet.
+It saves these translations in a local table.
+Once it receives packets, it looks in this table and replaces the public network address and port with the associated private network address and port.
+If no corresponding entry exists in the routers table, the packet is dropped.
+This means that when contacting a device behind a NAT, there must be an existing entry in this table.
+
+		There are several techniques to add an entry to the routers NAT table.
+Universal Plug and Play (UPnP) is one of those techniques, where the local device uses a HTTP request to the router to associate a port with the devices private network address.
+This technique is not available everywhere and sometimes considered a security risk.
+Different implementations of NAT require different techniques, such as \textit{hole punching}, \textit{relaying} or \textit{reversal}, as described by Wocker et al.
+[http://www.pap.vs.uni-due.de/files/wacker-nat-traversal.pdf].
+
 	\subsection{Incentives in decentralized systems}
@@
 	\subsection{Sybil attacks}
-		The Sybil attack is an attack where a single attacker represents itself as multiple nodes in a peer-to-peer system.
-Abusing this, the attacker is able to propagate false assumptions about the network to other nodes.
-
-		First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or the other, except under what he call "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify itself.
-This must be done within a small enough time frame that an attacker can't do this in sequence, but all nodes must do them in parallel.
-
-		A fully distributed network that implements such a solution is the Bitcoin network [BITCOIN PAPER: http://s.kwma.kr/pdf/Bitcoin/bitcoin.pdf], in which computing power, and not the number of nodes is important for the general network consensus.
+		Hier wat over sybil attacks
 

### 2014-03-13 paper.tex
Title fix
Remove duplicate text

--- 2014-03-13 paper.tex
@@
 
+		As we saw in the previous section, we would like to have a decentralized anonymous network.
+This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
+Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry [link].
+These networks will be described in more detail in the next chapter.
+Among these networks are some overlay anonymous networks such as Tarzan and Torks [link].
+
+		There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
+When removing this central authority, these components needs to be spread across the peers in the network.
+In this section we will explain the various problems that are involved when decentralizing Tor.
+In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
+
 		\subsection{Bootstrapping new nodes}
-		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with.
-In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.
+			If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be a starting point where this new node can discover neighbors in the network to connect with.
+In Tor, a directory server can tell the new node what his neighbors are and where to find them \cite{dingledine2004tor}.
 
-		Moving this system to a non peer-to-peer base is difficult.
-Dingledine et al.
+			Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
 stated that this indeed is still an open problem.
-With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
-Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} do have made some attempts towards a decentralized system, but have yet to find the final answer.
+With decentralized systems, there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
+Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.
+Some of these issues can be found in the last section when comparing these systems.
 
 		\subsection{Incentives in decentralized systems}
-		As described in section \ref{ss:tor_disadvantages} people are using more bandwidth than that they donate.
+			As described in section \ref{ss:tor_disadvantages}, people are usually using more bandwidth than that they donate.
 There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor.
 If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified.
-In other words the incentive data has to be accurate and reliable.
-Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.
+In other words, the reputation data has to be accurate and reliable.
+Besides the integrity of this data, the traffic it generates on the network should have minimal impact on the overall performance.
 
 			Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network.
-The first thing that is described is the so called \emph{Warm-glow Model}.
-In this model determines the percentage of free-rides based on the probabilistic population distribution.
+The first proposal that is described is the so called \emph{Warm-glow Model}.
+This model determines the percentage of free-rides based on the probabilistic population distribution.
 If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.
@@
 			The third proposal is \emph{Reciprocity-Based Schemes}.
-Using this approach a peer maintains a behavior history of other peers in the network.
+Using this approach, a peer maintains a behavior history of other peers in the network.
 These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity.
@@
 		\subsection{Key exchange}
-		When using a decentralized network, using a centralized authority for managing the keys, is not possible.
+			With a decentralized network, using a centralized authority for managing the keys, is not possible.
 This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them.
 Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
-Diffie-Hellman is for example used in the circuit setup in Onion Routing (see chapter I), however, it is possible for an adversary to manipulate with the keys send between two parties.
-This makes it possible for the adversary to decrypt all message sent between the two parties.
+Diffie-Hellman is for example used in the circuit setup in Onion Routing (see secion II-D), however, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable for a man-in-the-middle attack.
+This weakness makes it possible for an adversary to decrypt all message sent between the two parties.
 
-		Tor currently uses an interactive forward-secret key-exchange protocol called the Tor authentication protocol (TAP) [linkje naar ace].
+			Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) [linkje naar ace].
 This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
 There are several proposals for more efficient key exchange methods.
-One of them is ACE, an one-way authenticated key exchange protocol.
+One of them is \emph{ACE}, an one-way authenticated key exchange protocol.
 The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
-ACE requires clients to send one extra element but that doesn't introduce any overhead because this element fits in the unused space in a cell.
+ACE requires clients to send one extra element in the key exchange.
+This however, does not introduce any overhead because the element fits in the unused space in a cell.
 
@@
 
-		There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file.
-Another key is the Signed-Subspace key (SSK) which enables personal namespaces.
-This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
-The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.
-
-		The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
-Each peer has only knowledge about his neighbours.
-Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
-Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
-Results of queries are being cached in intermediate nodes to reduce the time for a query response.
-To prevent looping of the requests, each request contains a random identifier.
-The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
+		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
+Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
+Each of these decentralized networks will be discussed in the next section.
+Note that we're only considering fully decentralized networks here.
+Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.[link naar survey p2p?]
 
@@
 
-		MIX networks typically are high latency and traffic moves slow.
-Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
-Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
-MorphMix has been developed as a low latency and high performance network.
-As such, it will not hold messages for very long, nor will it use cover traffic.
+			There are three types of file keys in Freenet: the first one is called the \emph{Keyword-Signed Key} (KSK) which is derived from a short description of the file.
+Another key is the \emph{Signed-Subspace key} (SSK) which enables personal namespaces.
+This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
+The third type of key is the \emph{Content-Hash Key} (CHK) which is used for updating and splitting of contents.
 
-		In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism.
-Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel.
-A malicious node could select a colluding node to continue the tunnel and therefor control the entire tunnel.
-To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel.
-Although this makes the possibility of such an attack more difficult, it doesn't make it impossible.
-
-		An important part of MorphMix is the ability to detect malicious tunnels.
-Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly.
-Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel.
-This will reveal itself in the fact that the probability of the selection of certain nodes is increased.
-By using this information it becomes possible, to an extent, to detect malicious tunnels.
+			The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
+Each peer has only knowledge about his direct neighbours.
+Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
+Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
+Results of queries are being cached in intermediate nodes to reduce the time for a query response.
+To prevent looping of the requests, each request contains a random identifier.
+The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
 
@@
 
-		Tapestry is a fundamental component of Oceanstore [linkje naar paper over Oceanstore], a decentralized storage system.
+			Tapestry is a fundamental component of OceanStore [linkje naar paper over OceanStore], a decentralized storage system.
 Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
@@
 
-\section{Tor vulnerabilities and attacks}
-	\label{sec:attacks}
-
-	Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
-In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
-
-	\subsection{Browser based attacks}
-		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis.
-
-		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
-
-		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-	\subsection{Low-Resource Routing attacks}
-		Hier wat over routing attacks
-
-	\subsection{Sybil attacks}
-		The Sybil attack is an attack where a single attacker represents itself as multiple nodes in a peer-to-peer system.
-Abusing this, the attacker is able to propagate false assumptions about the network to other nodes.
-
-		First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or the other, except under what he call "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify itself.
-This must be done within a small enough time frame that an attacker can't do this in sequence, but all nodes must do them in parallel.
-
-		A fully distributed network that implements such a solution is the Bitcoin network [BITCOIN PAPER: http://s.kwma.kr/pdf/Bitcoin/bitcoin.pdf], in which computing power, and not the number of nodes is important for the general network consensus.
-
-	\subsection{Replay Attacks}
-		Hier wat over replay attacks
-
 	\section{Conclusion}
@@
 		In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.
-Furthermore we looked at the main disadvantages and problems Tor currently has.
+Furthermore, we looked at the main disadvantages and problems Tor is currently facing.
 We then made a bridge to decentralized systems.
@@
 
-	From this table we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
+		From this table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
 While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.

### 2014-03-13 paper.tex
More ident fixes

@@
 	\subsection{Sybil attacks}
-			Hier wat over sybil attacks
+		The Sybil attack is an attack where a single attacker represents itself as multiple nodes in a peer-to-peer system.
+Abusing this, the attacker is able to propagate false assumptions about the network to other nodes.
+
+		First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or the other, except under what he call "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify itself.
+This must be done within a small enough time frame that an attacker can't do this in sequence, but all nodes must do them in parallel.
+
+		A fully distributed network that implements such a solution is the Bitcoin network [BITCOIN PAPER: http://s.kwma.kr/pdf/Bitcoin/bitcoin.pdf], in which computing power, and not the number of nodes is important for the general network consensus.
 

### 2014-03-13 paper.tex

@@
 
-\section{Problems when decentralizing}
+\section{Problems with decentralizing}
 	\label{sec:problems}
@@
 Some of these issues can be found in the last section when comparing these systems.
+
+	\subsection{NAT traversal}
+		A truly decentralized system requires the participating nodes to have direct connection to each other.
+Because of the limited availability of IPv4 network addresses, most consumer grade internet connections only provide one network address per subscriber, shared by all the devices connected to the subscribers network using Network Address Translation (NAT).
+With IPv4 network addresses getting more scarce, some Internet Service Providers even put more than one subscribers behind a single network address, using a carrier-grade NAT.
+
+		A NAT-based system works by creating a local, private network which a NAT-enabled router connects to the internet.
+The local network uses network addresses from the private ranges (e.g.
+10.0.0.0/8 or 192.168.0.0/16).
+
+		When a local device sends a packet to the internet, the router replaces these private addresses, including the source ports, with its own public address before forwarding it to the internet.
+It saves these translations in a local table.
+Once it receives packets, it looks in this table and replaces the public network address and port with the associated private network address and port.
+If no corresponding entry exists in the routers table, the packet is dropped.
+This means that when contacting a device behind a NAT, there must be an existing entry in this table.
+
+		There are several techniques to add an entry to the routers NAT table.
+Universal Plug and Play (UPnP) is one of those techniques, where the local device uses a HTTP request to the router to associate a port with the devices private network address.
+This technique is not available everywhere and sometimes considered a security risk.
+Different implementations of NAT require different techniques, such as \textit{hole punching}, \textit{relaying} or \textit{reversal}, as described by Wocker et al.
+[http://www.pap.vs.uni-due.de/files/wacker-nat-traversal.pdf].
 

### 2014-03-13 paper.tex

@@
 	\subsection{NISAN}
-		Information about NISAN.
+		NISAN, or Network Information Service for Anonymization Networks \cite{panchenko2006nisan}, is an anonymization network which implements a distributed node discovery.
+Not only does a central node administrator (the Directory Server in Tor) imply trust in those servers, Panchenko et al.
+also argue that a central node administration (the Directory Server in Tor) does not scale, as the current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.
+
+		NISAN implements a DHT-based approach (Kademlia) for distributing node information, in such a way that does not require the client to know about all the nodes in the network (such as in Tor).
+To build a circuit, NISAN generates random IDs and searches for the closest hit throughout the network.
+This makes it possible to build a path with nodes picked in a random, uniform way among all nodes, without the trust of a third party.
+
+		This does not fully protect against fingerprinting or bridging attacks (passive attacks), and suggest to do random walks throughout the network to mitigate that.
+The authors admit however this decreases the protection against an active attack.
 
@@
 	\subsection{Tarzan}
-		Information about Tarzan.
+		Tarzan [TARZAN PAPER] is a fully distributed peer-to-peer anonymity network.
+It implements a network address translator (NAT) to bridge between nodes running Tarzan and the internet.
+This means that services don\'t have to be aware of the fact they are running through Tarzan.
+
+		Tarzan requires knowledge of a few existing nodes to bootstrap and uses a gossiping protocol to discover other nodes.
+Nambiar et al.
+showed however that this does not scale beyond roughly 10,000 nodes [NISAN, SALSA PAPER].
+
+		Once Tarzan has knowledge of enough nodes, it achieves its anonymity with much like a Chaumian mix, with layered encryption and routing through multiple hops.
+In contrast to Tor and other networks, Tarzan uses cover traffic to provide protection against traffic analysis by a global advisory to find an initiator.
+
+	\subsection{Torsk}
+		Torsk [TORSKKKK PAPER] is an extension to Tor, designed to be an interoperable replacement for the circuit creation and Directory Service as used by Tor.
+The authors argue that the current Directory Service does not scale, with the percentage of the traffic in a network dedicated to node discovery growing as the number of nodes grow.
+With the 2009 version of Tor, they argue that 100\% of the networks traffic would consist of node discovery traffic with roughly 1.2 million clients.
+
+		Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority.
+The DHT is a combination of Kademlia DHT and Myrmic DHT.
+Kademlia DHT was chosen because it is already widely used and it has proven itself for a large number of users.
+
+		The Myrmic DHT runs on top of Kademlia, and introduces the Neighbourhood Authority.
+This authority issues certs to nodes that participate in the DHT, but it does not participate in the DHT itself.
+The NA makes this solution not a fully decentralized one, but its role is a lot smaller than the current Directory Servers.
+This does not solve the trust issue, but it does solve the scalability issue.
 

### 2014-03-13 conclusion.tex
Split paper in a tex file per section to make merge issues less likely and easier to manage

--- 2014-03-13 paper.tex
@@
-% !TeX spellcheck = en_GB
-\documentclass[journal]{IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load, see original template for descriptions)
-%\usepackage{ifpdf}
-%\usepackage{cite}
-%\usepackage[cmex10]{amsmath}
-%\usepackage{algorithmic}
-%\usepackage{array}
-%\usepackage{fixltx2e}
-%\usepackage{stfloats}
-%\usepackage{dblfloatfix}
-%\usepackage{url}
-\usepackage{graphicx}
-\usepackage{epstopdf}
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-% *** UTF8 ***
-\usepackage[utf8]{inputenc}
-
-\begin{document}
-
-\bibliographystyle{plain}
-
-% Title of the paper
-\title{30 years of privacy research for the masses \& \newline 15 years of decentralization attempts}
-% Authors
-\author{Rolf Jagerman, Wendo Sab\'ee, Laurens Versluis, Martijn de Vos}
-
-% The paper headers
-%\markboth{Journal of \LaTeX\ Class Files,~Vol.~11, No.~4, December~2012}%
-%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-
-% make the title area
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
-\begin{abstract}
-	The abstract goes here.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Nunc et elit nec metus ultrices faucibus.
-Mauris volutpat libero eu arcu sodales, ac bibendum neque pulvinar.
-Sed et ipsum nunc.
-Quisque ac sem ut nunc tincidunt commodo.
-Cras at odio nibh.
-Pellentesque sodales ut tortor sed dictum.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
-\end{abstract}
-
-\section{Introduction}
-	% The very first letter is a 2 line initial drop letter followed
-	% by the rest of the first word in caps.
-	% 
-	% form to use if the first word consists of a single letter:
-	% \IEEEPARstart{A}{demo} file is ....
-	% 
-	% form to use if you need the single drop letter followed by
-	% normal text (unknown if ever used by IEEE):
-	% \IEEEPARstart{A}{}demo file is ....
-	% 
-	% Some journals put the first two words in caps:
-	% \IEEEPARstart{T}{his demo} file is ....
-	% 
-	% Here we have the typical use of a "T" for an initial drop letter
-	% and "HIS" in caps to complete the first word.
-	% You must have at least 2 lines in the paragraph with the drop letter
-	% (should never be an issue)
-	\IEEEPARstart{W}{ith} the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate.
-In many cases however, internet usage is either censored or monitored by third parties.
-In recent years the need for anonymous internet communication has become more apparent.
-Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.
-
-	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and are being used in practice.
-One of the most important factors that impact anonymity in a communication system is the number of users.
-A sufficiently large numbers of users are required for the system to make guarantees about its ability to conceal and hide users' communication.
-This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
-Another important factor that impacts the anonymity of the system is decentralization.
-Whenever a network has centralized components and a malicious third party gains control over these components, the functionality and perhaps even the anonymity of the system is compromised.
-
-	The most widely used anonymous communication system is Tor.
-In this paper we will analyze Tor and its semi-centralized nature.
-Furthermore we will look at attempts that have been made to decentralize Tor as well as several other decentralized systems.
-
-	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview of Tor.
-After that, we will talk about decentralization and its problems in section \ref{sec:problems}.
-Vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
-Afterwards, we will discuss the current state of decentralized internet systems in section \ref{sec:decentralized}.
-A comparison of existing decentralized networks is made in section \ref{sec:comparison}.
-Finally, we will conclude and discuss our findings in section \ref{sec:conclusion}.
-
-\section{Introduction to Tor}
-	\label{sec:tor}
-
-	The implementation of The Onion Router was first described by the U.S.
-Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
-
-	In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
-In this section, we will explain the various compoments of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.
-
-	\subsection{Onion routing}
-		As described in the original design paper of The Onion Router, network traffic is forwarded through a circuit of nodes, where each node only knows the previous and next node in the circuit.
-With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each others physical location.
-
-		Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry or guard) relay node ($X$), a (middle) relay node ($Y$) and an exit node ($Z$).
-In this case, there are three relay nodes, but this is not a fixed number.
-A visualisation of this path can be seen in figure \ref{fig:tor_layout}.
-Each node has its own public key and a corresponding private key.
-When building the circuit, our client generates a distinct secret for each of these nodes.
-More information about the circuit setup, can be found in II-D.
-Circuit creation.
-
-		The payload of each packet flowing through the circuit is first encrypted with the distinct secret for last node $Z$, then with the distinct secret for node $Y$, and last with the secret for node $X$.
-With each layer of encryption, a header is added with the address of the next node in the circuit, plus the used distinct secret encrypted with corresponding nodes public key.
-
-		After node $X$ receives this packet from out trusted node $C$, it decrypts the attached secret with its private key, and uses that secret to decrypt the rest of the packet.
-The result is a header with the address for node $Y$ and the payload encrypted with secrets for the following nodes in the circuit, which is forwarded to node $Y$.
-
-		As a node receives a packet from the previous node, it peels off another layer of encryption, much as how you can peel an onion layer for layer, and forwards it to the next node in the circuit (as specified in the decrypted header).
-When exit node $Z$ decrypts the last layer, it forwards the unencrypted payload outside the network to the original destination that our trusted client $C$ tried to contact, acting as a traditional proxy.
-
-		When exit node $Z$ receives a response, this whole process is applied in reverse order, encrypting the payload with its secret along the way, instead of decrypting.
-When our client $C$ receives the packet, it peels off all the encryption layers to retrieve the unencrypted payload.
-
-		With the second generation onion routing used in Tor, a modified algorithm is used to derive the encryption keys, called \emph{telescoping path-building}, which also provides perfect forward secrecy.
-This algorithm is described in section \ref{ss:tor_circuit}.
-
-		\begin{figure}[!t]
-			\centering
-			\includegraphics[width=0.4\textwidth]{graphics/tor.pdf}
-			\caption{The components of the Tor network.
-After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node, and uses it to communicate (anonymously) with the internet.}
-			\label{fig:tor_layout}
-		\end{figure}
-
-	\subsection{Directory servers}
-		The original Onion Router implementation used in-band status updates where each node broadcasts know nodes to its neighbours.
-An attacker could exploit this to isolate and limit the knowledge of a client, forcing connections through malicious nodes.
-Beside possible security disadvantages, in-band status updates also have the disadvantage that it takes longer to propagate throughout the network and create a global consensus.
-
-		To mitigate these concerns, Directory Servers were introduced to Tor during its reimplementation to keep a redundant central consensus about the network.
-They act as HTTP servers to which Tor nodes can publish signed information about themselves.
-Tor clients can in turn download this information, as seen in figure \ref{fig:tor_layout}.
-
-		This information is signed by the Directory Servers before it is distributed to the Tor clients.
-The keys to verify these signatures are preloaded in the Tor software, along with the list of Directory Servers, which implies trust by the Tor client in the Directory Servers.
-
-	\subsection{Relay and exit nodes}
-		The Tor network consists of several components.
-The clients in the Tor network are known as Onion Proxies.
-The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy for users to configure.
-The Onion Proxies are responsible for downloading the directory information, establishing circuits across the network and handling connections from user applications.
-
-		The routing in the network is done by Onion Routers, also called relay nodes.
-The relay nodes relay the data from the Onion Proxy to the web server across a circuit (circuits are described in II-D).
-Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}.
-Each circuit has three type of Onion Routers \cite{mccoy2008shining}:
-
-		\begin{itemize}
-			\item{The entrance Tor router:} this router is directly connected to an Onion Proxy and can observe the origin of a request through the Tor network.
-The entrance router sends the packet to the middle Tor router.
-			\item{The middle Tor router:} this router is connected to the entrance router and the exit router.
-			\item{The exit Tor router:} this router is connected to the web server. Note that the exit Tor router is the only router that can observe the final destination of the request.
-		\end{itemize}
-
-		The first router in a circuit is the entrance router. The entrance router sends the data to one of the middle router which forwards the data to the exit router.
-
-	\subsection{Circuit creation}
-		\label{ss:tor_circuit}
-
-		As described in the previous section, data on the Tor networks travels over circuits.
-The data travels over the circuit in fixed-size cells that are 512 bytes long.
-Each cell has a header and a payload.
-The header consists of a number that identifies the circuit the cell travels on and a command that indicates what to do with the cell’s payload.
-
-		Before a circuit can be established, a path has to be chosen.
-The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes [link naar cacr2011-20].
-Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.
-
-		Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a web server.
-Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
-To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake ($ g^b $) to the first node in her selected path (for example, OR1).
-OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
-Now both Alice and OR1 have a shared key they use to encrypt and decrypt data sent between them.
-
-		So now Alice has a connection with the first Onion Router in the circuit.
-To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1.
-This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2 ($ g^{a_2} $).
-OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2.
-When OR1 receives a created cell, OR1 passes this cell to Alice.
-Now Alice and OR2 share a common key: $ K = g^{a_2b_2} $.
-The same procedure can be used to extend the circuit with more nodes.
-
-	\subsection{Disadvantages}
-		\label{ss:tor_disadvantages}
-
-		While Tor guarantees anonymity, there are some disadvantages using it.
-The main disadvantage is that the Tor network is slow.
-According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.
-
-		According to Dingledine et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal.
-In this section, we will summarize these reasons and explain what could be done to fix them.
-
-		First of all, the congestion control does not work well.
-The network has some problems handling bulk transfers, such as when downloading large files or streaming high-quality videos.
-The congestion control could be improved by using an unreliable protocol for links between Tor relays.
-Goldberg et al.
-[linkje] have proposed PCTCP which could improve the response time of the Tor network with 60\% and the download time of files with 30\%.
-
-		Some Tor users put more traffic on the network than they contribute by running a Onion Router.
-This means that these users are slowing the network down as they use more traffic than giving to the network.
-A possible solution for this is to throttle certain high-bandwidth protocols such as BitTorrent at exit nodes or at Onion Proxies.
-
-		Also, the Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
-By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
-Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network and making it faster.
-
-		The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
-The problem is that the current selection strategy is optimal when the network is fully loaded.
-This is not always the case.
-Using a better path selection algorithm could increase the capacity of the network and the overall user experience.
-
-		Another problem is that the Tor clients are not optimal at handling latency and connection failures.
-For example, if extending a circuit fails, the entire circuit is abandoned.
-An improvement would be to first try to extend the circuit to some other places.
-If that fails, the circuit could be abandoned.
-Also, a better timeout mechanism could be chosen for building circuits.
-
-		Much of the overhead of the network is in downloading the directory information.
-There is also overhead in the TLS connection between the nodes in the network.
-According to Dingledine et al, removing the empty TLS application record could reduce the overhead in the TCP/IP header with 6.3\%.
-
-		As we saw, the directory service generates overhead on the network.
-If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
-This means, we would like to have Tor decentralized.
-Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up.
-This is due to the fact that there are many problems decentralization brings along with.
-
-\section{Tor vulnerabilities and attacks}
-	\label{sec:attacks}
-
-	Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
-In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
-
-	\subsection{Browser based attacks}
-		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\
-
-		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
-Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.
-
-		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-	\subsection{Low-Resource Routing attacks}
-		Hier wat over routing attacks
-
-	\subsection{Sybil attacks}
-		The Sybil attack is an attack where a single attacker represents itself as multiple nodes in a peer-to-peer system.
-Abusing this, the attacker is able to propagate false assumptions about the network to other nodes.
-
-		First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or the other, except under what he call "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify itself.
-This must be done within a small enough time frame that an attacker can't do this in sequence, but all nodes must do them in parallel.
-
-		A fully distributed network that implements such a solution is the Bitcoin network [BITCOIN PAPER: http://s.kwma.kr/pdf/Bitcoin/bitcoin.pdf], in which computing power, and not the number of nodes is important for the general network consensus.
-
-	\subsection{Replay Attacks}
-		A replay attack [cite naar replay attack paper] happens when a malicious entry node duplicates cells and send them again.
-Since Tor uses uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the connection to be torn down.
-
-		Using this, an accomplice exit router can therefore in cooperation with the entry node discover the sender and receiver's relationship.
-On top of that, this attack can also be used as a denial of service attack.
-This attack is according to the authors quite challenging to solve and does require some further research.
-
-\section{Problems when decentralizing}
-	\label{sec:problems}
-
-	As we saw in section \ref{sec:tor}, we would like to have a decentralized anonymous network.
-This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry.
-These networks will be described in more detail in the next chapter.
-Among these networks are some overlay anonymous networks such as Tarzan.
-
-	There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
-When removing this central authority, these components needs to be spread across the peers in the network.
-In this section we will explain the various problems that are involved when decentralizing Tor.
-In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
-
-	As we saw in the previous section, we would like to have a decentralized anonymous network.
-This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry [link].
-These networks will be described in more detail in the next chapter.
-Among these networks are some overlay anonymous networks such as Tarzan and Torks [link].
-
-	There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
-When removing this central authority, these components needs to be spread across the peers in the network.
-In this section we will explain the various problems that are involved when decentralizing Tor.
-In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
-
-	\subsection{Bootstrapping new nodes}
-		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be a starting point where this new node can discover neighbors in the network to connect with.
-In Tor, a directory server can tell the new node what his neighbors are and where to find them \cite{dingledine2004tor}.
-
-		Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
-stated that this indeed is still an open problem.
-With decentralized systems, there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
-Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.
-Some of these issues can be found in the last section when comparing these systems.
-
-	\subsection{Incentives in decentralized systems}
-		As described in section \ref{ss:tor_disadvantages}, people are usually using more bandwidth than that they donate.
-There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor.
-If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified.
-In other words, the reputation data has to be accurate and reliable.
-Besides the integrity of this data, the traffic it generates on the network should have minimal impact on the overall performance.
-
-		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network.
-The first proposal that is described is the so called \emph{Warm-glow Model}.
-This model determines the percentage of free-rides based on the probabilistic population distribution.
-If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.
-
-		The second proposal is using monetary schemes.
-While it is not exemplified a lot, the main idea is to use a virtual currency as incentive.
-The problems with this approach are the scalability and the hidden costs of this service.
-
-		The third proposal is \emph{Reciprocity-Based Schemes}.
-Using this approach, a peer maintains a behavior history of other peers in the network.
-These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity.
-The formal are more suitable for longer relationships between peers.
-The latter is more scalable but they rely on third party and must handle trust issues themselves.
-
-	\subsection{Key exchange}
-		With a decentralized network, using a centralized authority for managing the keys, is not possible.
-This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them.
-Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
-Diffie-Hellman is for example used in the circuit setup in Onion Routing (see secion II-D), however, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable for a man-in-the-middle attack.
-This weakness makes it possible for an adversary to decrypt all message sent between the two parties.
-
-		Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) [linkje naar ace].
-This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
-There are several proposals for more efficient key exchange methods.
-One of them is \emph{ACE}, an one-way authenticated key exchange protocol.
-The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
-ACE requires clients to send one extra element in the key exchange.
-This however, does not introduce any overhead because the element fits in the unused space in a cell.
-
-\section{Current decentralized systems}
-	\label{sec:decentralized}
-
-	Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]
-
-	\subsection{Gnutella}
-		Gnutella is a decentralized peer-to-peer network used for distributed search of files.
-Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients.
-Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.
-In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available.
-These peers can be found on http://gnutellahosts.com.
-Once the peer has joined, there are several messages a servant can send out:
-
-		\begin{itemize}
-			\item A peer sends a PING message to it's neighbours to announce it's presents. This message is forwarded to other peers and each peer sends a PONG message back.
-			\item The peer can issue QUERY answers. Other peers responds with a QUERY RESPONSE message to specify whether the file that was issued in the query, was found or not.
-			\item To transfer items between peers, the GET and PUSH messages are being used.
-		\end{itemize}
-
-		Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file.
-To search for a file, a flooding algorithm is used.
-
-	\subsection{Freenet}
-		In Freenet, each data item is represented by a key that is independent of the location of the file.
-Freenet is called a loosely structured network because of this.
-To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.
-
-		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.[link naar survey p2p?]
-
-	\subsection{NISAN}
-		Information about NISAN.
-
-	\subsection{MorphMix}
-		MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks.
-It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
-Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
-
-			There are three types of file keys in Freenet: the first one is called the \emph{Keyword-Signed Key} (KSK) which is derived from a short description of the file.
-Another key is the \emph{Signed-Subspace key} (SSK) which enables personal namespaces.
-This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
-The third type of key is the \emph{Content-Hash Key} (CHK) which is used for updating and splitting of contents.
-
-			The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
-Each peer has only knowledge about his direct neighbours.
-Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
-Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
-Results of queries are being cached in intermediate nodes to reduce the time for a query response.
-To prevent looping of the requests, each request contains a random identifier.
-The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
-
-	\subsection{Tribler}
-		Information about Tribler.
-
-	\subsection{Tapestry}
-		Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
-A property of Tapestry is that it offers load distribution and routing locality.
-
-		Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored.
-A peer can also function as a router, which forwards an incoming message.
-The routing algorithm is based on the destination ID of the packet.
-Routers are using local routing maps to route messages to the destination ID digit by digit.
-The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.
-
-		Tapestry is a fundamental component of OceanStore [linkje naar paper over OceanStore], a decentralized storage system.
-Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
-
-	\subsection{Pastry}
-		Pastry is very similar to Tapestry, but there are some small differences.
-One of these differences is the handling of network locality and data object replication.
-Plastry also uses the Plaxton mesh data structure for the routing algorithm.
-Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
-Each node can be found in about log(n) steps.
-
-		The Pastry overlay network is used in several applications, such as Scribe, Squirrel and PAST.
-Scribe is an system that has been built to send multicast messages.
-Instead of relying on the multicast infrastructure, multicast messages are sent using only unicast services.
-Pastry is used to create and manage multicast groups.
-Scribe makes use of the organization, robustness and reliability of the Pastry network.
-
-		Squirrel is a decentralized peer-to-peer web cache.
-The network uses Pastry to locate it's objects and for the routing algorithm.
-Squirrel allows users to share it's web cache with other users in the network, creating a large decentralized web cache.
-Squirrel however introduces some overhead when searching the cache.
-The challenge is to keep this overhead as low as possible.
-
-		PAST is a large scale persistent peer-to-peer network that has been designed to store files.
-It is built upon the Pastry network and the main focus of PAST is providing performance, scalability and security.
-
-	\subsection{Tarzan}
-		Information about Tarzan.
-
-	\subsection{Other decentralized systems}
-		Some other decentralized peer-to-peer systems has been developed, focussing on anonymity.
-An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) [linkje naar AP3 paper] which makes cooperative, decentralized anonymous communication possible.
-The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms.
-Users are able to send and receive unicast, multicast and anycast messages anonymously.
-The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages.
-A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.
-
-\section{Comparison existing decentralized networks}
-	\label{sec:comparison}
-
-	In the last section, we discussed existing decentralized peer-to-peer networks.
-In this section we will make a comparison between these networks.
-For each network, we will explain the following features:
-
-	\begin{itemize}
-		\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
-		\item{Public implementation:} For each network we will explain whether a public implementation is available.
-		\item{Used in practice:} Is the network used in practice?
-		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
-		\item{Anonimity:} Does the network hide the identities of the sender and/or receiver?
-	\end{itemize}
-
-\section{Conclusion}
-	\label{sec:conclusion}
-
 In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.
@@
 While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
-
-\appendices
-
-\bibliography{paper_references}
-
-\end{document}

### 2014-03-13 decentralizing-problems.tex
Split paper in a tex file per section to make merge issues less likely and easier to manage

--- 2014-03-13 paper.tex
@@
-% !TeX spellcheck = en_GB
-\documentclass[journal]{IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load, see original template for descriptions)
-%\usepackage{ifpdf}
-%\usepackage{cite}
-%\usepackage[cmex10]{amsmath}
-%\usepackage{algorithmic}
-%\usepackage{array}
-%\usepackage{fixltx2e}
-%\usepackage{stfloats}
-%\usepackage{dblfloatfix}
-%\usepackage{url}
-\usepackage{graphicx}
-\usepackage{epstopdf}
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-% *** UTF8 ***
-\usepackage[utf8]{inputenc}
-
-\begin{document}
-
-\bibliographystyle{plain}
-
-% Title of the paper
-\title{30 years of privacy research for the masses \& \newline 15 years of decentralization attempts}
-% Authors
-\author{Rolf Jagerman, Wendo Sab\'ee, Laurens Versluis, Martijn de Vos}
-
-% The paper headers
-%\markboth{Journal of \LaTeX\ Class Files,~Vol.~11, No.~4, December~2012}%
-%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-
-% make the title area
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
-\begin{abstract}
-	The abstract goes here.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Nunc et elit nec metus ultrices faucibus.
-Mauris volutpat libero eu arcu sodales, ac bibendum neque pulvinar.
-Sed et ipsum nunc.
-Quisque ac sem ut nunc tincidunt commodo.
-Cras at odio nibh.
-Pellentesque sodales ut tortor sed dictum.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
-\end{abstract}
-
-\section{Introduction}
-	% The very first letter is a 2 line initial drop letter followed
-	% by the rest of the first word in caps.
-	% 
-	% form to use if the first word consists of a single letter:
-	% \IEEEPARstart{A}{demo} file is ....
-	% 
-	% form to use if you need the single drop letter followed by
-	% normal text (unknown if ever used by IEEE):
-	% \IEEEPARstart{A}{}demo file is ....
-	% 
-	% Some journals put the first two words in caps:
-	% \IEEEPARstart{T}{his demo} file is ....
-	% 
-	% Here we have the typical use of a "T" for an initial drop letter
-	% and "HIS" in caps to complete the first word.
-	% You must have at least 2 lines in the paragraph with the drop letter
-	% (should never be an issue)
-	\IEEEPARstart{W}{ith} the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate.
-In many cases however, internet usage is either censored or monitored by third parties.
-In recent years the need for anonymous internet communication has become more apparent.
-Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.
-
-	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and are being used in practice.
-One of the most important factors that impact anonymity in a communication system is the number of users.
-A sufficiently large numbers of users are required for the system to make guarantees about its ability to conceal and hide users' communication.
-This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
-Another important factor that impacts the anonymity of the system is decentralization.
-Whenever a network has centralized components and a malicious third party gains control over these components, the functionality and perhaps even the anonymity of the system is compromised.
-
-	The most widely used anonymous communication system is Tor.
-In this paper we will analyze Tor and its semi-centralized nature.
-Furthermore we will look at attempts that have been made to decentralize Tor as well as several other decentralized systems.
-
-	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview of Tor.
-After that, we will talk about decentralization and its problems in section \ref{sec:problems}.
-Vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
-Afterwards, we will discuss the current state of decentralized internet systems in section \ref{sec:decentralized}.
-A comparison of existing decentralized networks is made in section \ref{sec:comparison}.
-Finally, we will conclude and discuss our findings in section \ref{sec:conclusion}.
-
-\section{Introduction to Tor}
-	\label{sec:tor}
-
-	The implementation of The Onion Router was first described by the U.S.
-Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
-
-	In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
-In this section, we will explain the various compoments of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.
-
-	\subsection{Onion routing}
-		As described in the original design paper of The Onion Router, network traffic is forwarded through a circuit of nodes, where each node only knows the previous and next node in the circuit.
-With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each others physical location.
-
-		Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry or guard) relay node ($X$), a (middle) relay node ($Y$) and an exit node ($Z$).
-In this case, there are three relay nodes, but this is not a fixed number.
-A visualisation of this path can be seen in figure \ref{fig:tor_layout}.
-Each node has its own public key and a corresponding private key.
-When building the circuit, our client generates a distinct secret for each of these nodes.
-More information about the circuit setup, can be found in II-D.
-Circuit creation.
-
-		The payload of each packet flowing through the circuit is first encrypted with the distinct secret for last node $Z$, then with the distinct secret for node $Y$, and last with the secret for node $X$.
-With each layer of encryption, a header is added with the address of the next node in the circuit, plus the used distinct secret encrypted with corresponding nodes public key.
-
-		After node $X$ receives this packet from out trusted node $C$, it decrypts the attached secret with its private key, and uses that secret to decrypt the rest of the packet.
-The result is a header with the address for node $Y$ and the payload encrypted with secrets for the following nodes in the circuit, which is forwarded to node $Y$.
-
-		As a node receives a packet from the previous node, it peels off another layer of encryption, much as how you can peel an onion layer for layer, and forwards it to the next node in the circuit (as specified in the decrypted header).
-When exit node $Z$ decrypts the last layer, it forwards the unencrypted payload outside the network to the original destination that our trusted client $C$ tried to contact, acting as a traditional proxy.
-
-		When exit node $Z$ receives a response, this whole process is applied in reverse order, encrypting the payload with its secret along the way, instead of decrypting.
-When our client $C$ receives the packet, it peels off all the encryption layers to retrieve the unencrypted payload.
-
-		With the second generation onion routing used in Tor, a modified algorithm is used to derive the encryption keys, called \emph{telescoping path-building}, which also provides perfect forward secrecy.
-This algorithm is described in section \ref{ss:tor_circuit}.
-
-		\begin{figure}[!t]
-			\centering
-			\includegraphics[width=0.4\textwidth]{graphics/tor.pdf}
-			\caption{The components of the Tor network.
-After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node, and uses it to communicate (anonymously) with the internet.}
-			\label{fig:tor_layout}
-		\end{figure}
-
-	\subsection{Directory servers}
-		The original Onion Router implementation used in-band status updates where each node broadcasts know nodes to its neighbours.
-An attacker could exploit this to isolate and limit the knowledge of a client, forcing connections through malicious nodes.
-Beside possible security disadvantages, in-band status updates also have the disadvantage that it takes longer to propagate throughout the network and create a global consensus.
-
-		To mitigate these concerns, Directory Servers were introduced to Tor during its reimplementation to keep a redundant central consensus about the network.
-They act as HTTP servers to which Tor nodes can publish signed information about themselves.
-Tor clients can in turn download this information, as seen in figure \ref{fig:tor_layout}.
-
-		This information is signed by the Directory Servers before it is distributed to the Tor clients.
-The keys to verify these signatures are preloaded in the Tor software, along with the list of Directory Servers, which implies trust by the Tor client in the Directory Servers.
-
-	\subsection{Relay and exit nodes}
-		The Tor network consists of several components.
-The clients in the Tor network are known as Onion Proxies.
-The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy for users to configure.
-The Onion Proxies are responsible for downloading the directory information, establishing circuits across the network and handling connections from user applications.
-
-		The routing in the network is done by Onion Routers, also called relay nodes.
-The relay nodes relay the data from the Onion Proxy to the web server across a circuit (circuits are described in II-D).
-Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}.
-Each circuit has three type of Onion Routers \cite{mccoy2008shining}:
-
-		\begin{itemize}
-			\item{The entrance Tor router:} this router is directly connected to an Onion Proxy and can observe the origin of a request through the Tor network.
-The entrance router sends the packet to the middle Tor router.
-			\item{The middle Tor router:} this router is connected to the entrance router and the exit router.
-			\item{The exit Tor router:} this router is connected to the web server. Note that the exit Tor router is the only router that can observe the final destination of the request.
-		\end{itemize}
-
-		The first router in a circuit is the entrance router. The entrance router sends the data to one of the middle router which forwards the data to the exit router.
-
-	\subsection{Circuit creation}
-		\label{ss:tor_circuit}
-
-		As described in the previous section, data on the Tor networks travels over circuits.
-The data travels over the circuit in fixed-size cells that are 512 bytes long.
-Each cell has a header and a payload.
-The header consists of a number that identifies the circuit the cell travels on and a command that indicates what to do with the cell’s payload.
-
-		Before a circuit can be established, a path has to be chosen.
-The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes [link naar cacr2011-20].
-Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.
-
-		Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a web server.
-Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
-To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake ($ g^b $) to the first node in her selected path (for example, OR1).
-OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
-Now both Alice and OR1 have a shared key they use to encrypt and decrypt data sent between them.
-
-		So now Alice has a connection with the first Onion Router in the circuit.
-To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1.
-This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2 ($ g^{a_2} $).
-OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2.
-When OR1 receives a created cell, OR1 passes this cell to Alice.
-Now Alice and OR2 share a common key: $ K = g^{a_2b_2} $.
-The same procedure can be used to extend the circuit with more nodes.
-
-	\subsection{Disadvantages}
-		\label{ss:tor_disadvantages}
-
-		While Tor guarantees anonymity, there are some disadvantages using it.
-The main disadvantage is that the Tor network is slow.
-According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.
-
-		According to Dingledine et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal.
-In this section, we will summarize these reasons and explain what could be done to fix them.
-
-		First of all, the congestion control does not work well.
-The network has some problems handling bulk transfers, such as when downloading large files or streaming high-quality videos.
-The congestion control could be improved by using an unreliable protocol for links between Tor relays.
-Goldberg et al.
-[linkje] have proposed PCTCP which could improve the response time of the Tor network with 60\% and the download time of files with 30\%.
-
-		Some Tor users put more traffic on the network than they contribute by running a Onion Router.
-This means that these users are slowing the network down as they use more traffic than giving to the network.
-A possible solution for this is to throttle certain high-bandwidth protocols such as BitTorrent at exit nodes or at Onion Proxies.
-
-		Also, the Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
-By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
-Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network and making it faster.
-
-		The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
-The problem is that the current selection strategy is optimal when the network is fully loaded.
-This is not always the case.
-Using a better path selection algorithm could increase the capacity of the network and the overall user experience.
-
-		Another problem is that the Tor clients are not optimal at handling latency and connection failures.
-For example, if extending a circuit fails, the entire circuit is abandoned.
-An improvement would be to first try to extend the circuit to some other places.
-If that fails, the circuit could be abandoned.
-Also, a better timeout mechanism could be chosen for building circuits.
-
-		Much of the overhead of the network is in downloading the directory information.
-There is also overhead in the TLS connection between the nodes in the network.
-According to Dingledine et al, removing the empty TLS application record could reduce the overhead in the TCP/IP header with 6.3\%.
-
-		As we saw, the directory service generates overhead on the network.
-If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
-This means, we would like to have Tor decentralized.
-Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up.
-This is due to the fact that there are many problems decentralization brings along with.
-
-\section{Tor vulnerabilities and attacks}
-	\label{sec:attacks}
-
-	Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
-In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
-
-	\subsection{Browser based attacks}
-		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\
-
-		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
-Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.
-
-		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-	\subsection{Low-Resource Routing attacks}
-		Hier wat over routing attacks
-
-	\subsection{Sybil attacks}
-		The Sybil attack is an attack where a single attacker represents itself as multiple nodes in a peer-to-peer system.
-Abusing this, the attacker is able to propagate false assumptions about the network to other nodes.
-
-		First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or the other, except under what he call "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify itself.
-This must be done within a small enough time frame that an attacker can't do this in sequence, but all nodes must do them in parallel.
-
-		A fully distributed network that implements such a solution is the Bitcoin network [BITCOIN PAPER: http://s.kwma.kr/pdf/Bitcoin/bitcoin.pdf], in which computing power, and not the number of nodes is important for the general network consensus.
-
-	\subsection{Replay Attacks}
-		A replay attack [cite naar replay attack paper] happens when a malicious entry node duplicates cells and send them again.
-Since Tor uses uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the connection to be torn down.
-
-		Using this, an accomplice exit router can therefore in cooperation with the entry node discover the sender and receiver's relationship.
-On top of that, this attack can also be used as a denial of service attack.
-This attack is according to the authors quite challenging to solve and does require some further research.
-
-\section{Problems with decentralizing}
-	\label{sec:problems}
-
 As we saw in section \ref{sec:tor}, we would like to have a decentralized anonymous network.
@@
 This however, does not introduce any overhead because the element fits in the unused space in a cell.
-
-\section{Current decentralized systems}
-	\label{sec:decentralized}
-
-	Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]
-
-	\subsection{Gnutella}
-		Gnutella is a decentralized peer-to-peer network used for distributed search of files.
-Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients.
-Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.
-In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available.
-These peers can be found on http://gnutellahosts.com.
-Once the peer has joined, there are several messages a servant can send out:
-
-		\begin{itemize}
-			\item A peer sends a PING message to it's neighbours to announce it's presents. This message is forwarded to other peers and each peer sends a PONG message back.
-			\item The peer can issue QUERY answers. Other peers responds with a QUERY RESPONSE message to specify whether the file that was issued in the query, was found or not.
-			\item To transfer items between peers, the GET and PUSH messages are being used.
-		\end{itemize}
-
-		Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file.
-To search for a file, a flooding algorithm is used.
-
-	\subsection{Freenet}
-		In Freenet, each data item is represented by a key that is independent of the location of the file.
-Freenet is called a loosely structured network because of this.
-To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.
-
-		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.[link naar survey p2p?]
-
-	\subsection{NISAN}
-		Information about NISAN.
-
-	\subsection{MorphMix}
-		MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks.
-It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
-Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
-
-			There are three types of file keys in Freenet: the first one is called the \emph{Keyword-Signed Key} (KSK) which is derived from a short description of the file.
-Another key is the \emph{Signed-Subspace key} (SSK) which enables personal namespaces.
-This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
-The third type of key is the \emph{Content-Hash Key} (CHK) which is used for updating and splitting of contents.
-
-			The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
-Each peer has only knowledge about his direct neighbours.
-Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
-Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
-Results of queries are being cached in intermediate nodes to reduce the time for a query response.
-To prevent looping of the requests, each request contains a random identifier.
-The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
-
-	\subsection{Tribler}
-		Information about Tribler.
-
-	\subsection{Tapestry}
-		Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
-A property of Tapestry is that it offers load distribution and routing locality.
-
-		Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored.
-A peer can also function as a router, which forwards an incoming message.
-The routing algorithm is based on the destination ID of the packet.
-Routers are using local routing maps to route messages to the destination ID digit by digit.
-The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.
-
-		Tapestry is a fundamental component of OceanStore [linkje naar paper over OceanStore], a decentralized storage system.
-Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
-
-	\subsection{Pastry}
-		Pastry is very similar to Tapestry, but there are some small differences.
-One of these differences is the handling of network locality and data object replication.
-Plastry also uses the Plaxton mesh data structure for the routing algorithm.
-Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
-Each node can be found in about log(n) steps.
-
-		The Pastry overlay network is used in several applications, such as Scribe, Squirrel and PAST.
-Scribe is an system that has been built to send multicast messages.
-Instead of relying on the multicast infrastructure, multicast messages are sent using only unicast services.
-Pastry is used to create and manage multicast groups.
-Scribe makes use of the organization, robustness and reliability of the Pastry network.
-
-		Squirrel is a decentralized peer-to-peer web cache.
-The network uses Pastry to locate it's objects and for the routing algorithm.
-Squirrel allows users to share it's web cache with other users in the network, creating a large decentralized web cache.
-Squirrel however introduces some overhead when searching the cache.
-The challenge is to keep this overhead as low as possible.
-
-		PAST is a large scale persistent peer-to-peer network that has been designed to store files.
-It is built upon the Pastry network and the main focus of PAST is providing performance, scalability and security.
-
-	\subsection{Tarzan}
-		Information about Tarzan.
-
-	\subsection{Other decentralized systems}
-		Some other decentralized peer-to-peer systems has been developed, focussing on anonymity.
-An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) [linkje naar AP3 paper] which makes cooperative, decentralized anonymous communication possible.
-The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms.
-Users are able to send and receive unicast, multicast and anycast messages anonymously.
-The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages.
-A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.
-
-\section{Comparison existing decentralized networks}
-	\label{sec:comparison}
-
-	In the last section, we discussed existing decentralized peer-to-peer networks.
-In this section we will make a comparison between these networks.
-For each network, we will explain the following features:
-
-	\begin{itemize}
-		\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
-		\item{Public implementation:} For each network we will explain whether a public implementation is available.
-		\item{Used in practice:} Is the network used in practice?
-		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
-		\item{Anonimity:} Does the network hide the identities of the sender and/or receiver?
-	\end{itemize}
-
-\section{Conclusion}
-	\label{sec:conclusion}
-
-	In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.
-Furthermore, we looked at the main disadvantages and problems Tor is currently facing.
-We then made a bridge to decentralized systems.
-We first explained which problems one might face when decentralizing a system such as Tor.
-The next section shows which systems currently have a decentralized structure and/or mechanism.
-These systems are then compared to each other with their pros and cons.
-
-	From this table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
-While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.
-The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.
-
-	While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
-
-\appendices
-
-\bibliography{paper_references}
-
-\end{document}

### 2014-03-13 introduction.tex
Split paper in a tex file per section to make merge issues less likely and easier to manage

--- 2014-03-13 paper.tex
@@
-% !TeX spellcheck = en_GB
-\documentclass[journal]{IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load, see original template for descriptions)
-%\usepackage{ifpdf}
-%\usepackage{cite}
-%\usepackage[cmex10]{amsmath}
-%\usepackage{algorithmic}
-%\usepackage{array}
-%\usepackage{fixltx2e}
-%\usepackage{stfloats}
-%\usepackage{dblfloatfix}
-%\usepackage{url}
-\usepackage{graphicx}
-\usepackage{epstopdf}
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-% *** UTF8 ***
-\usepackage[utf8]{inputenc}
-
-\begin{document}
-
-\bibliographystyle{plain}
-
-% Title of the paper
-\title{30 years of privacy research for the masses \& \newline 15 years of decentralization attempts}
-% Authors
-\author{Rolf Jagerman, Wendo Sab\'ee, Laurens Versluis, Martijn de Vos}
-
-% The paper headers
-%\markboth{Journal of \LaTeX\ Class Files,~Vol.~11, No.~4, December~2012}%
-%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-
-% make the title area
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
-\begin{abstract}
-	The abstract goes here.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Nunc et elit nec metus ultrices faucibus.
-Mauris volutpat libero eu arcu sodales, ac bibendum neque pulvinar.
-Sed et ipsum nunc.
-Quisque ac sem ut nunc tincidunt commodo.
-Cras at odio nibh.
-Pellentesque sodales ut tortor sed dictum.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
-\end{abstract}
-
-\section{Introduction}
 % The very first letter is a 2 line initial drop letter followed
@@
 Finally, we will conclude and discuss our findings in section \ref{sec:conclusion}.
-
-\section{Introduction to Tor}
-	\label{sec:tor}
-
-	The implementation of The Onion Router was first described by the U.S.
-Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
-
-	In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
-In this section, we will explain the various compoments of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.
-
-	\subsection{Onion routing}
-		As described in the original design paper of The Onion Router, network traffic is forwarded through a circuit of nodes, where each node only knows the previous and next node in the circuit.
-With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each others physical location.
-
-		Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry or guard) relay node ($X$), a (middle) relay node ($Y$) and an exit node ($Z$).
-In this case, there are three relay nodes, but this is not a fixed number.
-A visualisation of this path can be seen in figure \ref{fig:tor_layout}.
-Each node has its own public key and a corresponding private key.
-When building the circuit, our client generates a distinct secret for each of these nodes.
-More information about the circuit setup, can be found in II-D.
-Circuit creation.
-
-		The payload of each packet flowing through the circuit is first encrypted with the distinct secret for last node $Z$, then with the distinct secret for node $Y$, and last with the secret for node $X$.
-With each layer of encryption, a header is added with the address of the next node in the circuit, plus the used distinct secret encrypted with corresponding nodes public key.
-
-		After node $X$ receives this packet from out trusted node $C$, it decrypts the attached secret with its private key, and uses that secret to decrypt the rest of the packet.
-The result is a header with the address for node $Y$ and the payload encrypted with secrets for the following nodes in the circuit, which is forwarded to node $Y$.
-
-		As a node receives a packet from the previous node, it peels off another layer of encryption, much as how you can peel an onion layer for layer, and forwards it to the next node in the circuit (as specified in the decrypted header).
-When exit node $Z$ decrypts the last layer, it forwards the unencrypted payload outside the network to the original destination that our trusted client $C$ tried to contact, acting as a traditional proxy.
-
-		When exit node $Z$ receives a response, this whole process is applied in reverse order, encrypting the payload with its secret along the way, instead of decrypting.
-When our client $C$ receives the packet, it peels off all the encryption layers to retrieve the unencrypted payload.
-
-		With the second generation onion routing used in Tor, a modified algorithm is used to derive the encryption keys, called \emph{telescoping path-building}, which also provides perfect forward secrecy.
-This algorithm is described in section \ref{ss:tor_circuit}.
-
-		\begin{figure}[!t]
-			\centering
-			\includegraphics[width=0.4\textwidth]{graphics/tor.pdf}
-			\caption{The components of the Tor network.
-After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node, and uses it to communicate (anonymously) with the internet.}
-			\label{fig:tor_layout}
-		\end{figure}
-
-	\subsection{Directory servers}
-		The original Onion Router implementation used in-band status updates where each node broadcasts know nodes to its neighbours.
-An attacker could exploit this to isolate and limit the knowledge of a client, forcing connections through malicious nodes.
-Beside possible security disadvantages, in-band status updates also have the disadvantage that it takes longer to propagate throughout the network and create a global consensus.
-
-		To mitigate these concerns, Directory Servers were introduced to Tor during its reimplementation to keep a redundant central consensus about the network.
-They act as HTTP servers to which Tor nodes can publish signed information about themselves.
-Tor clients can in turn download this information, as seen in figure \ref{fig:tor_layout}.
-
-		This information is signed by the Directory Servers before it is distributed to the Tor clients.
-The keys to verify these signatures are preloaded in the Tor software, along with the list of Directory Servers, which implies trust by the Tor client in the Directory Servers.
-
-	\subsection{Relay and exit nodes}
-		The Tor network consists of several components.
-The clients in the Tor network are known as Onion Proxies.
-The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy for users to configure.
-The Onion Proxies are responsible for downloading the directory information, establishing circuits across the network and handling connections from user applications.
-
-		The routing in the network is done by Onion Routers, also called relay nodes.
-The relay nodes relay the data from the Onion Proxy to the web server across a circuit (circuits are described in II-D).
-Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}.
-Each circuit has three type of Onion Routers \cite{mccoy2008shining}:
-
-		\begin{itemize}
-			\item{The entrance Tor router:} this router is directly connected to an Onion Proxy and can observe the origin of a request through the Tor network.
-The entrance router sends the packet to the middle Tor router.
-			\item{The middle Tor router:} this router is connected to the entrance router and the exit router.
-			\item{The exit Tor router:} this router is connected to the web server. Note that the exit Tor router is the only router that can observe the final destination of the request.
-		\end{itemize}
-
-		The first router in a circuit is the entrance router. The entrance router sends the data to one of the middle router which forwards the data to the exit router.
-
-	\subsection{Circuit creation}
-		\label{ss:tor_circuit}
-
-		As described in the previous section, data on the Tor networks travels over circuits.
-The data travels over the circuit in fixed-size cells that are 512 bytes long.
-Each cell has a header and a payload.
-The header consists of a number that identifies the circuit the cell travels on and a command that indicates what to do with the cell’s payload.
-
-		Before a circuit can be established, a path has to be chosen.
-The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes [link naar cacr2011-20].
-Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.
-
-		Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a web server.
-Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
-To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake ($ g^b $) to the first node in her selected path (for example, OR1).
-OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
-Now both Alice and OR1 have a shared key they use to encrypt and decrypt data sent between them.
-
-		So now Alice has a connection with the first Onion Router in the circuit.
-To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1.
-This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2 ($ g^{a_2} $).
-OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2.
-When OR1 receives a created cell, OR1 passes this cell to Alice.
-Now Alice and OR2 share a common key: $ K = g^{a_2b_2} $.
-The same procedure can be used to extend the circuit with more nodes.
-
-	\subsection{Disadvantages}
-		\label{ss:tor_disadvantages}
-
-		While Tor guarantees anonymity, there are some disadvantages using it.
-The main disadvantage is that the Tor network is slow.
-According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.
-
-		According to Dingledine et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal.
-In this section, we will summarize these reasons and explain what could be done to fix them.
-
-		First of all, the congestion control does not work well.
-The network has some problems handling bulk transfers, such as when downloading large files or streaming high-quality videos.
-The congestion control could be improved by using an unreliable protocol for links between Tor relays.
-Goldberg et al.
-[linkje] have proposed PCTCP which could improve the response time of the Tor network with 60\% and the download time of files with 30\%.
-
-		Some Tor users put more traffic on the network than they contribute by running a Onion Router.
-This means that these users are slowing the network down as they use more traffic than giving to the network.
-A possible solution for this is to throttle certain high-bandwidth protocols such as BitTorrent at exit nodes or at Onion Proxies.
-
-		Also, the Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
-By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
-Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network and making it faster.
-
-		The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
-The problem is that the current selection strategy is optimal when the network is fully loaded.
-This is not always the case.
-Using a better path selection algorithm could increase the capacity of the network and the overall user experience.
-
-		Another problem is that the Tor clients are not optimal at handling latency and connection failures.
-For example, if extending a circuit fails, the entire circuit is abandoned.
-An improvement would be to first try to extend the circuit to some other places.
-If that fails, the circuit could be abandoned.
-Also, a better timeout mechanism could be chosen for building circuits.
-
-		Much of the overhead of the network is in downloading the directory information.
-There is also overhead in the TLS connection between the nodes in the network.
-According to Dingledine et al, removing the empty TLS application record could reduce the overhead in the TCP/IP header with 6.3\%.
-
-		As we saw, the directory service generates overhead on the network.
-If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
-This means, we would like to have Tor decentralized.
-Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up.
-This is due to the fact that there are many problems decentralization brings along with.
-
-\section{Tor vulnerabilities and attacks}
-	\label{sec:attacks}
-
-	Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
-In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
-
-	\subsection{Browser based attacks}
-		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\
-
-		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
-Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.
-
-		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-	\subsection{Low-Resource Routing attacks}
-		Hier wat over routing attacks
-
-	\subsection{Sybil attacks}
-		The Sybil attack is an attack where a single attacker represents itself as multiple nodes in a peer-to-peer system.
-Abusing this, the attacker is able to propagate false assumptions about the network to other nodes.
-
-		First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or the other, except under what he call "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify itself.
-This must be done within a small enough time frame that an attacker can't do this in sequence, but all nodes must do them in parallel.
-
-		A fully distributed network that implements such a solution is the Bitcoin network [BITCOIN PAPER: http://s.kwma.kr/pdf/Bitcoin/bitcoin.pdf], in which computing power, and not the number of nodes is important for the general network consensus.
-
-	\subsection{Replay Attacks}
-		A replay attack [cite naar replay attack paper] happens when a malicious entry node duplicates cells and send them again.
-Since Tor uses uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the connection to be torn down.
-
-		Using this, an accomplice exit router can therefore in cooperation with the entry node discover the sender and receiver's relationship.
-On top of that, this attack can also be used as a denial of service attack.
-This attack is according to the authors quite challenging to solve and does require some further research.
-
-\section{Problems when decentralizing}
-	\label{sec:problems}
-
-	As we saw in section \ref{sec:tor}, we would like to have a decentralized anonymous network.
-This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry.
-These networks will be described in more detail in the next chapter.
-Among these networks are some overlay anonymous networks such as Tarzan.
-
-	There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
-When removing this central authority, these components needs to be spread across the peers in the network.
-In this section we will explain the various problems that are involved when decentralizing Tor.
-In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
-
-	As we saw in the previous section, we would like to have a decentralized anonymous network.
-This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry [link].
-These networks will be described in more detail in the next chapter.
-Among these networks are some overlay anonymous networks such as Tarzan and Torks [link].
-
-	There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
-When removing this central authority, these components needs to be spread across the peers in the network.
-In this section we will explain the various problems that are involved when decentralizing Tor.
-In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
-
-	\subsection{Bootstrapping new nodes}
-		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be a starting point where this new node can discover neighbors in the network to connect with.
-In Tor, a directory server can tell the new node what his neighbors are and where to find them \cite{dingledine2004tor}.
-
-		Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
-stated that this indeed is still an open problem.
-With decentralized systems, there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
-Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.
-Some of these issues can be found in the last section when comparing these systems.
-
-	\subsection{Incentives in decentralized systems}
-		As described in section \ref{ss:tor_disadvantages}, people are usually using more bandwidth than that they donate.
-There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor.
-If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified.
-In other words, the reputation data has to be accurate and reliable.
-Besides the integrity of this data, the traffic it generates on the network should have minimal impact on the overall performance.
-
-		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network.
-The first proposal that is described is the so called \emph{Warm-glow Model}.
-This model determines the percentage of free-rides based on the probabilistic population distribution.
-If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.
-
-		The second proposal is using monetary schemes.
-While it is not exemplified a lot, the main idea is to use a virtual currency as incentive.
-The problems with this approach are the scalability and the hidden costs of this service.
-
-		The third proposal is \emph{Reciprocity-Based Schemes}.
-Using this approach, a peer maintains a behavior history of other peers in the network.
-These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity.
-The formal are more suitable for longer relationships between peers.
-The latter is more scalable but they rely on third party and must handle trust issues themselves.
-
-	\subsection{Key exchange}
-		With a decentralized network, using a centralized authority for managing the keys, is not possible.
-This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them.
-Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
-Diffie-Hellman is for example used in the circuit setup in Onion Routing (see secion II-D), however, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable for a man-in-the-middle attack.
-This weakness makes it possible for an adversary to decrypt all message sent between the two parties.
-
-		Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) [linkje naar ace].
-This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
-There are several proposals for more efficient key exchange methods.
-One of them is \emph{ACE}, an one-way authenticated key exchange protocol.
-The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
-ACE requires clients to send one extra element in the key exchange.
-This however, does not introduce any overhead because the element fits in the unused space in a cell.
-
-\section{Current decentralized systems}
-	\label{sec:decentralized}
-
-	Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]
-
-	\subsection{Gnutella}
-		Gnutella is a decentralized peer-to-peer network used for distributed search of files.
-Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients.
-Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.
-In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available.
-These peers can be found on http://gnutellahosts.com.
-Once the peer has joined, there are several messages a servant can send out:
-
-		\begin{itemize}
-			\item A peer sends a PING message to it's neighbours to announce it's presents. This message is forwarded to other peers and each peer sends a PONG message back.
-			\item The peer can issue QUERY answers. Other peers responds with a QUERY RESPONSE message to specify whether the file that was issued in the query, was found or not.
-			\item To transfer items between peers, the GET and PUSH messages are being used.
-		\end{itemize}
-
-		Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file.
-To search for a file, a flooding algorithm is used.
-
-	\subsection{Freenet}
-		In Freenet, each data item is represented by a key that is independent of the location of the file.
-Freenet is called a loosely structured network because of this.
-To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.
-
-		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.[link naar survey p2p?]
-
-	\subsection{NISAN}
-		Information about NISAN.
-
-	\subsection{MorphMix}
-		MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks.
-It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
-Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
-
-			There are three types of file keys in Freenet: the first one is called the \emph{Keyword-Signed Key} (KSK) which is derived from a short description of the file.
-Another key is the \emph{Signed-Subspace key} (SSK) which enables personal namespaces.
-This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
-The third type of key is the \emph{Content-Hash Key} (CHK) which is used for updating and splitting of contents.
-
-			The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
-Each peer has only knowledge about his direct neighbours.
-Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
-Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
-Results of queries are being cached in intermediate nodes to reduce the time for a query response.
-To prevent looping of the requests, each request contains a random identifier.
-The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
-
-	\subsection{Tribler}
-		Information about Tribler.
-
-	\subsection{Tapestry}
-		Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
-A property of Tapestry is that it offers load distribution and routing locality.
-
-		Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored.
-A peer can also function as a router, which forwards an incoming message.
-The routing algorithm is based on the destination ID of the packet.
-Routers are using local routing maps to route messages to the destination ID digit by digit.
-The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.
-
-		Tapestry is a fundamental component of OceanStore [linkje naar paper over OceanStore], a decentralized storage system.
-Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
-
-	\subsection{Pastry}
-		Pastry is very similar to Tapestry, but there are some small differences.
-One of these differences is the handling of network locality and data object replication.
-Plastry also uses the Plaxton mesh data structure for the routing algorithm.
-Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
-Each node can be found in about log(n) steps.
-
-		The Pastry overlay network is used in several applications, such as Scribe, Squirrel and PAST.
-Scribe is an system that has been built to send multicast messages.
-Instead of relying on the multicast infrastructure, multicast messages are sent using only unicast services.
-Pastry is used to create and manage multicast groups.
-Scribe makes use of the organization, robustness and reliability of the Pastry network.
-
-		Squirrel is a decentralized peer-to-peer web cache.
-The network uses Pastry to locate it's objects and for the routing algorithm.
-Squirrel allows users to share it's web cache with other users in the network, creating a large decentralized web cache.
-Squirrel however introduces some overhead when searching the cache.
-The challenge is to keep this overhead as low as possible.
-
-		PAST is a large scale persistent peer-to-peer network that has been designed to store files.
-It is built upon the Pastry network and the main focus of PAST is providing performance, scalability and security.
-
-	\subsection{Tarzan}
-		Information about Tarzan.
-
-	\subsection{Other decentralized systems}
-		Some other decentralized peer-to-peer systems has been developed, focussing on anonymity.
-An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) [linkje naar AP3 paper] which makes cooperative, decentralized anonymous communication possible.
-The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms.
-Users are able to send and receive unicast, multicast and anycast messages anonymously.
-The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages.
-A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.
-
-\section{Comparison existing decentralized networks}
-	\label{sec:comparison}
-
-	In the last section, we discussed existing decentralized peer-to-peer networks.
-In this section we will make a comparison between these networks.
-For each network, we will explain the following features:
-
-	\begin{itemize}
-		\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
-		\item{Public implementation:} For each network we will explain whether a public implementation is available.
-		\item{Used in practice:} Is the network used in practice?
-		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
-		\item{Anonimity:} Does the network hide the identities of the sender and/or receiver?
-	\end{itemize}
-
-\section{Conclusion}
-	\label{sec:conclusion}
-
-	In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.
-Furthermore, we looked at the main disadvantages and problems Tor is currently facing.
-We then made a bridge to decentralized systems.
-We first explained which problems one might face when decentralizing a system such as Tor.
-The next section shows which systems currently have a decentralized structure and/or mechanism.
-These systems are then compared to each other with their pros and cons.
-
-	From this table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
-While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.
-The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.
-
-	While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
-
-\appendices
-
-\bibliography{paper_references}
-
-\end{document}

### 2014-03-13 paper.tex
Split paper in a tex file per section to make merge issues less likely and easier to manage

--- 2014-03-13 paper.tex
@@
 \usepackage[utf8]{inputenc}
+
+% Remove \clearpage after \include{}s
+\let\clearpage\relax
 
@@
 \section{Introduction}
-	% The very first letter is a 2 line initial drop letter followed
-	% by the rest of the first word in caps.
-	% 
-	% form to use if the first word consists of a single letter:
-	% \IEEEPARstart{A}{demo} file is ....
-	% 
-	% form to use if you need the single drop letter followed by
-	% normal text (unknown if ever used by IEEE):
-	% \IEEEPARstart{A}{}demo file is ....
-	% 
-	% Some journals put the first two words in caps:
-	% \IEEEPARstart{T}{his demo} file is ....
-	% 
-	% Here we have the typical use of a "T" for an initial drop letter
-	% and "HIS" in caps to complete the first word.
-	% You must have at least 2 lines in the paragraph with the drop letter
-	% (should never be an issue)
-	\IEEEPARstart{W}{ith} the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate.
-In many cases however, internet usage is either censored or monitored by third parties.
-In recent years the need for anonymous internet communication has become more apparent.
-Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.
-
-	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and are being used in practice.
-One of the most important factors that impact anonymity in a communication system is the number of users.
-A sufficiently large numbers of users are required for the system to make guarantees about its ability to conceal and hide users' communication.
-This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
-Another important factor that impacts the anonymity of the system is decentralization.
-Whenever a network has centralized components and a malicious third party gains control over these components, the functionality and perhaps even the anonymity of the system is compromised.
-
-	The most widely used anonymous communication system is Tor.
-In this paper we will analyze Tor and its semi-centralized nature.
-Furthermore we will look at attempts that have been made to decentralize Tor as well as several other decentralized systems.
-
-	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview of Tor.
-After that, we will talk about decentralization and its problems in section \ref{sec:problems}.
-Vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
-Afterwards, we will discuss the current state of decentralized internet systems in section \ref{sec:decentralized}.
-A comparison of existing decentralized networks is made in section \ref{sec:comparison}.
-Finally, we will conclude and discuss our findings in section \ref{sec:conclusion}.
+	\label{sec:introduction}
+	\include{introduction}
 
@@
 	\label{sec:tor}
-
-	The implementation of The Onion Router was first described by the U.S.
-Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
-
-	In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
-In this section, we will explain the various compoments of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.
-
-	\subsection{Onion routing}
-		As described in the original design paper of The Onion Router, network traffic is forwarded through a circuit of nodes, where each node only knows the previous and next node in the circuit.
-With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each others physical location.
-
-		Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry or guard) relay node ($X$), a (middle) relay node ($Y$) and an exit node ($Z$).
-In this case, there are three relay nodes, but this is not a fixed number.
-A visualisation of this path can be seen in figure \ref{fig:tor_layout}.
-Each node has its own public key and a corresponding private key.
-When building the circuit, our client generates a distinct secret for each of these nodes.
-More information about the circuit setup, can be found in II-D.
-Circuit creation.
-
-		The payload of each packet flowing through the circuit is first encrypted with the distinct secret for last node $Z$, then with the distinct secret for node $Y$, and last with the secret for node $X$.
-With each layer of encryption, a header is added with the address of the next node in the circuit, plus the used distinct secret encrypted with corresponding nodes public key.
-
-		After node $X$ receives this packet from out trusted node $C$, it decrypts the attached secret with its private key, and uses that secret to decrypt the rest of the packet.
-The result is a header with the address for node $Y$ and the payload encrypted with secrets for the following nodes in the circuit, which is forwarded to node $Y$.
-
-		As a node receives a packet from the previous node, it peels off another layer of encryption, much as how you can peel an onion layer for layer, and forwards it to the next node in the circuit (as specified in the decrypted header).
-When exit node $Z$ decrypts the last layer, it forwards the unencrypted payload outside the network to the original destination that our trusted client $C$ tried to contact, acting as a traditional proxy.
-
-		When exit node $Z$ receives a response, this whole process is applied in reverse order, encrypting the payload with its secret along the way, instead of decrypting.
-When our client $C$ receives the packet, it peels off all the encryption layers to retrieve the unencrypted payload.
-
-		With the second generation onion routing used in Tor, a modified algorithm is used to derive the encryption keys, called \emph{telescoping path-building}, which also provides perfect forward secrecy.
-This algorithm is described in section \ref{ss:tor_circuit}.
-
-		\begin{figure}[!t]
-			\centering
-			\includegraphics[width=0.4\textwidth]{graphics/tor.pdf}
-			\caption{The components of the Tor network.
-After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node, and uses it to communicate (anonymously) with the internet.}
-			\label{fig:tor_layout}
-		\end{figure}
-
-	\subsection{Directory servers}
-		The original Onion Router implementation used in-band status updates where each node broadcasts know nodes to its neighbours.
-An attacker could exploit this to isolate and limit the knowledge of a client, forcing connections through malicious nodes.
-Beside possible security disadvantages, in-band status updates also have the disadvantage that it takes longer to propagate throughout the network and create a global consensus.
-
-		To mitigate these concerns, Directory Servers were introduced to Tor during its reimplementation to keep a redundant central consensus about the network.
-They act as HTTP servers to which Tor nodes can publish signed information about themselves.
-Tor clients can in turn download this information, as seen in figure \ref{fig:tor_layout}.
-
-		This information is signed by the Directory Servers before it is distributed to the Tor clients.
-The keys to verify these signatures are preloaded in the Tor software, along with the list of Directory Servers, which implies trust by the Tor client in the Directory Servers.
-
-	\subsection{Relay and exit nodes}
-		The Tor network consists of several components.
-The clients in the Tor network are known as Onion Proxies.
-The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy for users to configure.
-The Onion Proxies are responsible for downloading the directory information, establishing circuits across the network and handling connections from user applications.
-
-		The routing in the network is done by Onion Routers, also called relay nodes.
-The relay nodes relay the data from the Onion Proxy to the web server across a circuit (circuits are described in II-D).
-Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}.
-Each circuit has three type of Onion Routers \cite{mccoy2008shining}:
-
-		\begin{itemize}
-			\item{The entrance Tor router:} this router is directly connected to an Onion Proxy and can observe the origin of a request through the Tor network.
-The entrance router sends the packet to the middle Tor router.
-			\item{The middle Tor router:} this router is connected to the entrance router and the exit router.
-			\item{The exit Tor router:} this router is connected to the web server. Note that the exit Tor router is the only router that can observe the final destination of the request.
-		\end{itemize}
-
-		The first router in a circuit is the entrance router. The entrance router sends the data to one of the middle router which forwards the data to the exit router.
-
-	\subsection{Circuit creation}
-		\label{ss:tor_circuit}
-
-		As described in the previous section, data on the Tor networks travels over circuits.
-The data travels over the circuit in fixed-size cells that are 512 bytes long.
-Each cell has a header and a payload.
-The header consists of a number that identifies the circuit the cell travels on and a command that indicates what to do with the cell’s payload.
-
-		Before a circuit can be established, a path has to be chosen.
-The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes [link naar cacr2011-20].
-Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.
-
-		Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a web server.
-Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
-To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake ($ g^b $) to the first node in her selected path (for example, OR1).
-OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
-Now both Alice and OR1 have a shared key they use to encrypt and decrypt data sent between them.
-
-		So now Alice has a connection with the first Onion Router in the circuit.
-To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1.
-This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2 ($ g^{a_2} $).
-OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2.
-When OR1 receives a created cell, OR1 passes this cell to Alice.
-Now Alice and OR2 share a common key: $ K = g^{a_2b_2} $.
-The same procedure can be used to extend the circuit with more nodes.
-
-	\subsection{Disadvantages}
-		\label{ss:tor_disadvantages}
-
-		While Tor guarantees anonymity, there are some disadvantages using it.
-The main disadvantage is that the Tor network is slow.
-According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.
-
-		According to Dingledine et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal.
-In this section, we will summarize these reasons and explain what could be done to fix them.
-
-		First of all, the congestion control does not work well.
-The network has some problems handling bulk transfers, such as when downloading large files or streaming high-quality videos.
-The congestion control could be improved by using an unreliable protocol for links between Tor relays.
-Goldberg et al.
-[linkje] have proposed PCTCP which could improve the response time of the Tor network with 60\% and the download time of files with 30\%.
-
-		Some Tor users put more traffic on the network than they contribute by running a Onion Router.
-This means that these users are slowing the network down as they use more traffic than giving to the network.
-A possible solution for this is to throttle certain high-bandwidth protocols such as BitTorrent at exit nodes or at Onion Proxies.
-
-		Also, the Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
-By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
-Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network and making it faster.
-
-		The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
-The problem is that the current selection strategy is optimal when the network is fully loaded.
-This is not always the case.
-Using a better path selection algorithm could increase the capacity of the network and the overall user experience.
-
-		Another problem is that the Tor clients are not optimal at handling latency and connection failures.
-For example, if extending a circuit fails, the entire circuit is abandoned.
-An improvement would be to first try to extend the circuit to some other places.
-If that fails, the circuit could be abandoned.
-Also, a better timeout mechanism could be chosen for building circuits.
-
-		Much of the overhead of the network is in downloading the directory information.
-There is also overhead in the TLS connection between the nodes in the network.
-According to Dingledine et al, removing the empty TLS application record could reduce the overhead in the TCP/IP header with 6.3\%.
-
-		As we saw, the directory service generates overhead on the network.
-If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
-This means, we would like to have Tor decentralized.
-Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up.
-This is due to the fact that there are many problems decentralization brings along with.
+	\include{tor-introduction}
 
@@
 	\label{sec:attacks}
+	\include{tor-attacks}
 
-	Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
-In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
-
-	\subsection{Browser based attacks}
-		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\
-
-		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
-Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
-
-		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
-To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
-Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.
-
-		The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.
-
-	\subsection{Low-Resource Routing attacks}
-		Hier wat over routing attacks
-
-	\subsection{Sybil attacks}
-		The Sybil attack is an attack where a single attacker represents itself as multiple nodes in a peer-to-peer system.
-Abusing this, the attacker is able to propagate false assumptions about the network to other nodes.
-
-		First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or the other, except under what he call "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify itself.
-This must be done within a small enough time frame that an attacker can't do this in sequence, but all nodes must do them in parallel.
-
-		A fully distributed network that implements such a solution is the Bitcoin network [BITCOIN PAPER: http://s.kwma.kr/pdf/Bitcoin/bitcoin.pdf], in which computing power, and not the number of nodes is important for the general network consensus.
-
-	\subsection{Replay Attacks}
-		A replay attack [cite naar replay attack paper] happens when a malicious entry node duplicates cells and send them again.
-Since Tor uses uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the connection to be torn down.
-
-		Using this, an accomplice exit router can therefore in cooperation with the entry node discover the sender and receiver's relationship.
-On top of that, this attack can also be used as a denial of service attack.
-This attack is according to the authors quite challenging to solve and does require some further research.
-
-\section{Problems when decentralizing}
+\section{Problems with decentralizing}
 	\label{sec:problems}
-
-	As we saw in section \ref{sec:tor}, we would like to have a decentralized anonymous network.
-This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry.
-These networks will be described in more detail in the next chapter.
-Among these networks are some overlay anonymous networks such as Tarzan.
-
-	There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
-When removing this central authority, these components needs to be spread across the peers in the network.
-In this section we will explain the various problems that are involved when decentralizing Tor.
-In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
-
-	As we saw in the previous section, we would like to have a decentralized anonymous network.
-This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry [link].
-These networks will be described in more detail in the next chapter.
-Among these networks are some overlay anonymous networks such as Tarzan and Torks [link].
-
-	There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
-When removing this central authority, these components needs to be spread across the peers in the network.
-In this section we will explain the various problems that are involved when decentralizing Tor.
-In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
-
-	\subsection{Bootstrapping new nodes}
-		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be a starting point where this new node can discover neighbors in the network to connect with.
-In Tor, a directory server can tell the new node what his neighbors are and where to find them \cite{dingledine2004tor}.
-
-		Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
-stated that this indeed is still an open problem.
-With decentralized systems, there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
-Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.
-Some of these issues can be found in the last section when comparing these systems.
-
-	\subsection{Incentives in decentralized systems}
-		As described in section \ref{ss:tor_disadvantages}, people are usually using more bandwidth than that they donate.
-There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor.
-If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified.
-In other words, the reputation data has to be accurate and reliable.
-Besides the integrity of this data, the traffic it generates on the network should have minimal impact on the overall performance.
-
-		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network.
-The first proposal that is described is the so called \emph{Warm-glow Model}.
-This model determines the percentage of free-rides based on the probabilistic population distribution.
-If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.
-
-		The second proposal is using monetary schemes.
-While it is not exemplified a lot, the main idea is to use a virtual currency as incentive.
-The problems with this approach are the scalability and the hidden costs of this service.
-
-		The third proposal is \emph{Reciprocity-Based Schemes}.
-Using this approach, a peer maintains a behavior history of other peers in the network.
-These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity.
-The formal are more suitable for longer relationships between peers.
-The latter is more scalable but they rely on third party and must handle trust issues themselves.
-
-	\subsection{Key exchange}
-		With a decentralized network, using a centralized authority for managing the keys, is not possible.
-This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them.
-Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
-Diffie-Hellman is for example used in the circuit setup in Onion Routing (see secion II-D), however, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable for a man-in-the-middle attack.
-This weakness makes it possible for an adversary to decrypt all message sent between the two parties.
-
-		Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) [linkje naar ace].
-This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
-There are several proposals for more efficient key exchange methods.
-One of them is \emph{ACE}, an one-way authenticated key exchange protocol.
-The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
-ACE requires clients to send one extra element in the key exchange.
-This however, does not introduce any overhead because the element fits in the unused space in a cell.
+	\include{decentralizing-problems}
 
@@
 	\label{sec:decentralized}
-
-	Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]
-
-	\subsection{Gnutella}
-		Gnutella is a decentralized peer-to-peer network used for distributed search of files.
-Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients.
-Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.
-In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available.
-These peers can be found on http://gnutellahosts.com.
-Once the peer has joined, there are several messages a servant can send out:
-
-		\begin{itemize}
-			\item A peer sends a PING message to it's neighbours to announce it's presents. This message is forwarded to other peers and each peer sends a PONG message back.
-			\item The peer can issue QUERY answers. Other peers responds with a QUERY RESPONSE message to specify whether the file that was issued in the query, was found or not.
-			\item To transfer items between peers, the GET and PUSH messages are being used.
-		\end{itemize}
-
-		Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file.
-To search for a file, a flooding algorithm is used.
-
-	\subsection{Freenet}
-		In Freenet, each data item is represented by a key that is independent of the location of the file.
-Freenet is called a loosely structured network because of this.
-To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.
-
-		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.[link naar survey p2p?]
-
-	\subsection{NISAN}
-		Information about NISAN.
-
-	\subsection{MorphMix}
-		MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks.
-It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
-Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
-
-			There are three types of file keys in Freenet: the first one is called the \emph{Keyword-Signed Key} (KSK) which is derived from a short description of the file.
-Another key is the \emph{Signed-Subspace key} (SSK) which enables personal namespaces.
-This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
-The third type of key is the \emph{Content-Hash Key} (CHK) which is used for updating and splitting of contents.
-
-			The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
-Each peer has only knowledge about his direct neighbours.
-Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
-Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
-Results of queries are being cached in intermediate nodes to reduce the time for a query response.
-To prevent looping of the requests, each request contains a random identifier.
-The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
-
-	\subsection{Tribler}
-		Information about Tribler.
-
-	\subsection{Tapestry}
-		Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
-A property of Tapestry is that it offers load distribution and routing locality.
-
-		Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored.
-A peer can also function as a router, which forwards an incoming message.
-The routing algorithm is based on the destination ID of the packet.
-Routers are using local routing maps to route messages to the destination ID digit by digit.
-The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.
-
-		Tapestry is a fundamental component of OceanStore [linkje naar paper over OceanStore], a decentralized storage system.
-Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
-
-	\subsection{Pastry}
-		Pastry is very similar to Tapestry, but there are some small differences.
-One of these differences is the handling of network locality and data object replication.
-Plastry also uses the Plaxton mesh data structure for the routing algorithm.
-Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
-Each node can be found in about log(n) steps.
-
-		The Pastry overlay network is used in several applications, such as Scribe, Squirrel and PAST.
-Scribe is an system that has been built to send multicast messages.
-Instead of relying on the multicast infrastructure, multicast messages are sent using only unicast services.
-Pastry is used to create and manage multicast groups.
-Scribe makes use of the organization, robustness and reliability of the Pastry network.
-
-		Squirrel is a decentralized peer-to-peer web cache.
-The network uses Pastry to locate it's objects and for the routing algorithm.
-Squirrel allows users to share it's web cache with other users in the network, creating a large decentralized web cache.
-Squirrel however introduces some overhead when searching the cache.
-The challenge is to keep this overhead as low as possible.
-
-		PAST is a large scale persistent peer-to-peer network that has been designed to store files.
-It is built upon the Pastry network and the main focus of PAST is providing performance, scalability and security.
-
-	\subsection{Tarzan}
-		Information about Tarzan.
-
-	\subsection{Other decentralized systems}
-		Some other decentralized peer-to-peer systems has been developed, focussing on anonymity.
-An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) [linkje naar AP3 paper] which makes cooperative, decentralized anonymous communication possible.
-The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms.
-Users are able to send and receive unicast, multicast and anycast messages anonymously.
-The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages.
-A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.
+	\include{systems-current}
 
@@
 	\label{sec:comparison}
-
-	In the last section, we discussed existing decentralized peer-to-peer networks.
-In this section we will make a comparison between these networks.
-For each network, we will explain the following features:
-
-	\begin{itemize}
-		\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
-		\item{Public implementation:} For each network we will explain whether a public implementation is available.
-		\item{Used in practice:} Is the network used in practice?
-		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
-		\item{Anonimity:} Does the network hide the identities of the sender and/or receiver?
-	\end{itemize}
+	\include{systems-comparison}
 
@@
 	\label{sec:conclusion}
-
-	In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.
-Furthermore, we looked at the main disadvantages and problems Tor is currently facing.
-We then made a bridge to decentralized systems.
-We first explained which problems one might face when decentralizing a system such as Tor.
-The next section shows which systems currently have a decentralized structure and/or mechanism.
-These systems are then compared to each other with their pros and cons.
-
-	From this table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
-While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.
-The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.
-
-	While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
+	\include{conclusion}
 

### 2014-03-13 systems-comparison.tex
Split paper in a tex file per section to make merge issues less likely and easier to manage

In the last section, we discussed existing decentralized peer-to-peer networks. In this section we will make a comparison between these networks. For each network, we will explain the following features:

\begin{itemize}
	\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
	\item{Public implementation:} For each network we will explain whether a public implementation is available.
	\item{Used in practice:} Is the network used in practice?
	\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
	\item{Anonimity:} Does the network hide the identities of the sender and/or receiver?
\end{itemize}

### 2014-03-13 systems-current.tex
Split paper in a tex file per section to make merge issues less likely and easier to manage

Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers]. Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan. Each of these decentralized networks will be discussed in the next section. Note that we're only considering fully decentralized networks here. Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]

\subsection{Gnutella}
	Gnutella is a decentralized peer-to-peer network used for distributed search of files. Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients. Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries. In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available. These peers can be found on http://gnutellahosts.com. Once the peer has joined, there are several messages a servant can send out:

	\begin{itemize}
		\item A peer sends a PING message to it's neighbours to announce it's presents. This message is forwarded to other peers and each peer sends a PONG message back.
		\item The peer can issue QUERY answers. Other peers responds with a QUERY RESPONSE message to specify whether the file that was issued in the query, was found or not.
		\item To transfer items between peers, the GET and PUSH messages are being used.
	\end{itemize}

	Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file. To search for a file, a flooding algorithm is used.

\subsection{Freenet}
	In Freenet, each data item is represented by a key that is independent of the location of the file. Freenet is called a loosely structured network because of this. To issue a query, the request is passed from client to client where each client makes a decision about the location to send the request next.

	Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers]. Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan. Each of these decentralized networks will be discussed in the next section. Note that we're only considering fully decentralized networks here. Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.[link naar survey p2p?]

\subsection{NISAN}
	NISAN, or Network Information Service for Anonymization Networks \cite{panchenko2006nisan}, is an anonymization network which implements a distributed node discovery. Not only does a central node administrator (the Directory Server in Tor) imply trust in those servers, Panchenko et al. also argue that a central node administration (the Directory Server in Tor) does not scale, as the current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.

	NISAN implements a DHT-based approach (Kademlia) for distributing node information, in such a way that does not require the client to know about all the nodes in the network (such as in Tor). To build a circuit, NISAN generates random IDs and searches for the closest hit throughout the network. This makes it possible to build a path with nodes picked in a random, uniform way among all nodes, without the trust of a third party.

	This does not fully protect against fingerprinting or bridging attacks (passive attacks), and suggest to do random walks throughout the network to mitigate that. The authors admit however this decreases the protection against an active attack.

\subsection{MorphMix}
	MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks. It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication. Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.

		There are three types of file keys in Freenet: the first one is called the \emph{Keyword-Signed Key} (KSK) which is derived from a short description of the file. Another key is the \emph{Signed-Subspace key} (SSK) which enables personal namespaces. This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file. The third type of key is the \emph{Content-Hash Key} (CHK) which is used for updating and splitting of contents.

		The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network. Each peer has only knowledge about his direct neighbours. Each request has a Hops-To-Live timer which indicates how many peers the request may traversal. Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more. Results of queries are being cached in intermediate nodes to reduce the time for a query response. To prevent looping of the requests, each request contains a random identifier. The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.

\subsection{Tribler}
	Information about Tribler.

\subsection{Tapestry}
	Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position. A property of Tapestry is that it offers load distribution and routing locality.

	Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored. A peer can also function as a router, which forwards an incoming message. The routing algorithm is based on the destination ID of the packet. Routers are using local routing maps to route messages to the destination ID digit by digit. The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.

	Tapestry is a fundamental component of OceanStore [linkje naar paper over OceanStore], a decentralized storage system. Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.

\subsection{Pastry}
	Pastry is very similar to Tapestry, but there are some small differences. One of these differences is the handling of network locality and data object replication. Plastry also uses the Plaxton mesh data structure for the routing algorithm. Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space. Each node can be found in about log(n) steps.

	The Pastry overlay network is used in several applications, such as Scribe, Squirrel and PAST. Scribe is an system that has been built to send multicast messages. Instead of relying on the multicast infrastructure, multicast messages are sent using only unicast services. Pastry is used to create and manage multicast groups. Scribe makes use of the organization, robustness and reliability of the Pastry network.

	Squirrel is a decentralized peer-to-peer web cache. The network uses Pastry to locate it's objects and for the routing algorithm. Squirrel allows users to share it's web cache with other users in the network, creating a large decentralized web cache. Squirrel however introduces some overhead when searching the cache. The challenge is to keep this overhead as low as possible.

	PAST is a large scale persistent peer-to-peer network that has been designed to store files. It is built upon the Pastry network and the main focus of PAST is providing performance, scalability and security.

\subsection{Tarzan}
	Tarzan [TARZAN PAPER] is a fully distributed peer-to-peer anonymity network. It implements a network address translator (NAT) to bridge between nodes running Tarzan and the internet. This means that services don\'t have to be aware of the fact they are running through Tarzan.

	Tarzan requires knowledge of a few existing nodes to bootstrap and uses a gossiping protocol to discover other nodes. Nambiar et al. showed however that this does not scale beyond roughly 10,000 nodes [NISAN, SALSA PAPER].

	Once Tarzan has knowledge of enough nodes, it achieves its anonymity with much like a Chaumian mix, with layered encryption and routing through multiple hops. In contrast to Tor and other networks, Tarzan uses cover traffic to provide protection against traffic analysis by a global advisory to find an initiator.

\subsection{Torsk}
	Torsk [TORSKKKK PAPER] is an extension to Tor, designed to be an interoperable replacement for the circuit creation and Directory Service as used by Tor. The authors argue that the current Directory Service does not scale, with the percentage of the traffic in a network dedicated to node discovery growing as the number of nodes grow. With the 2009 version of Tor, they argue that 100\% of the networks traffic would consist of node discovery traffic with roughly 1.2 million clients.

	Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority. The DHT is a combination of Kademlia DHT and Myrmic DHT. Kademlia DHT was chosen because it is already widely used and it has proven itself for a large number of users.

	The Myrmic DHT runs on top of Kademlia, and introduces the Neighbourhood Authority. This authority issues certs to nodes that participate in the DHT, but it does not participate in the DHT itself. The NA makes this solution not a fully decentralized one, but its role is a lot smaller than the current Directory Servers. This does not solve the trust issue, but it does solve the scalability issue.

\subsection{Other decentralized systems}
	Some other decentralized peer-to-peer systems has been developed, focussing on anonymity. An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) [linkje naar AP3 paper] which makes cooperative, decentralized anonymous communication possible. The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms. Users are able to send and receive unicast, multicast and anycast messages anonymously. The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages. A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.

### 2014-03-13 tor-attacks.tex
Split paper in a tex file per section to make merge issues less likely and easier to manage

Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}. In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.

\subsection{Browser based attacks}
	Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}. By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\

	By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user. The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server. Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.

	By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches. A similar system can be set up only using the HTML meta refresh tag. To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports. There are usually only a few exit nodes running on file sharing ports 4661 to 4666. Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.

	The solution for the JavaScript injection attack is disabling active content systems in the browser. For the HTML only variant one would have to use HTTPS to prevent man-in-the-middle attacks.

\subsection{Low-Resource Routing attacks}
	Hier wat over routing attacks

\subsection{Sybil attacks}
	The Sybil attack is an attack where a single attacker represents itself as multiple nodes in a peer-to-peer system. Abusing this, the attacker is able to propagate false assumptions about the network to other nodes.

	First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or the other, except under what he call "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify itself. This must be done within a small enough time frame that an attacker can't do this in sequence, but all nodes must do them in parallel.

	A fully distributed network that implements such a solution is the Bitcoin network [BITCOIN PAPER: http://s.kwma.kr/pdf/Bitcoin/bitcoin.pdf], in which computing power, and not the number of nodes is important for the general network consensus.

\subsection{Replay Attacks}
	A replay attack [cite naar replay attack paper] happens when a malicious entry node duplicates cells and send them again. Since Tor uses uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the connection to be torn down.

	Using this, an accomplice exit router can therefore in cooperation with the entry node discover the sender and receiver's relationship. On top of that, this attack can also be used as a denial of service attack. This attack is according to the authors quite challenging to solve and does require some further research.

### 2014-03-13 tor-introduction.tex
Split paper in a tex file per section to make merge issues less likely and easier to manage

The implementation of The Onion Router was first described by the U.S. Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.

In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}. In this section, we will explain the various compoments of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.

\subsection{Onion routing}
	As described in the original design paper of The Onion Router, network traffic is forwarded through a circuit of nodes, where each node only knows the previous and next node in the circuit. With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each others physical location.

	Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry or guard) relay node ($X$), a (middle) relay node ($Y$) and an exit node ($Z$). In this case, there are three relay nodes, but this is not a fixed number. A visualisation of this path can be seen in figure \ref{fig:tor_layout}. Each node has its own public key and a corresponding private key. When building the circuit, our client generates a distinct secret for each of these nodes. More information about the circuit setup, can be found in II-D. Circuit creation.

	The payload of each packet flowing through the circuit is first encrypted with the distinct secret for last node $Z$, then with the distinct secret for node $Y$, and last with the secret for node $X$. With each layer of encryption, a header is added with the address of the next node in the circuit, plus the used distinct secret encrypted with corresponding nodes public key.

	After node $X$ receives this packet from out trusted node $C$, it decrypts the attached secret with its private key, and uses that secret to decrypt the rest of the packet. The result is a header with the address for node $Y$ and the payload encrypted with secrets for the following nodes in the circuit, which is forwarded to node $Y$.

	As a node receives a packet from the previous node, it peels off another layer of encryption, much as how you can peel an onion layer for layer, and forwards it to the next node in the circuit (as specified in the decrypted header). When exit node $Z$ decrypts the last layer, it forwards the unencrypted payload outside the network to the original destination that our trusted client $C$ tried to contact, acting as a traditional proxy.

	When exit node $Z$ receives a response, this whole process is applied in reverse order, encrypting the payload with its secret along the way, instead of decrypting. When our client $C$ receives the packet, it peels off all the encryption layers to retrieve the unencrypted payload.

	With the second generation onion routing used in Tor, a modified algorithm is used to derive the encryption keys, called \emph{telescoping path-building}, which also provides perfect forward secrecy. This algorithm is described in section \ref{ss:tor_circuit}.

	\begin{figure}[!t]
		\centering
		\includegraphics[width=0.4\textwidth]{graphics/tor.pdf}
		\caption{The components of the Tor network. After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node, and uses it to communicate (anonymously) with the internet.}
		\label{fig:tor_layout}
	\end{figure}

\subsection{Directory servers}
	The original Onion Router implementation used in-band status updates where each node broadcasts know nodes to its neighbours. An attacker could exploit this to isolate and limit the knowledge of a client, forcing connections through malicious nodes. Beside possible security disadvantages, in-band status updates also have the disadvantage that it takes longer to propagate throughout the network and create a global consensus.

	To mitigate these concerns, Directory Servers were introduced to Tor during its reimplementation to keep a redundant central consensus about the network. They act as HTTP servers to which Tor nodes can publish signed information about themselves. Tor clients can in turn download this information, as seen in figure \ref{fig:tor_layout}.

	This information is signed by the Directory Servers before it is distributed to the Tor clients. The keys to verify these signatures are preloaded in the Tor software, along with the list of Directory Servers, which implies trust by the Tor client in the Directory Servers.

\subsection{Relay and exit nodes}
	The Tor network consists of several components. The clients in the Tor network are known as Onion Proxies. The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy for users to configure. The Onion Proxies are responsible for downloading the directory information, establishing circuits across the network and handling connections from user applications.

	The routing in the network is done by Onion Routers, also called relay nodes. The relay nodes relay the data from the Onion Proxy to the web server across a circuit (circuits are described in II-D). Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}. Each circuit has three type of Onion Routers \cite{mccoy2008shining}:

	\begin{itemize}
		\item{The entrance Tor router:} this router is directly connected to an Onion Proxy and can observe the origin of a request through the Tor network. The entrance router sends the packet to the middle Tor router.
		\item{The middle Tor router:} this router is connected to the entrance router and the exit router.
		\item{The exit Tor router:} this router is connected to the web server. Note that the exit Tor router is the only router that can observe the final destination of the request.
	\end{itemize}

	The first router in a circuit is the entrance router. The entrance router sends the data to one of the middle router which forwards the data to the exit router.

\subsection{Circuit creation}
	\label{ss:tor_circuit}

	As described in the previous section, data on the Tor networks travels over circuits. The data travels over the circuit in fixed-size cells that are 512 bytes long. Each cell has a header and a payload. The header consists of a number that identifies the circuit the cell travels on and a command that indicates what to do with the cell’s payload.

	Before a circuit can be established, a path has to be chosen. The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes [link naar cacr2011-20]. Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.

	Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a web server. Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes. To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake ($ g^b $) to the first node in her selected path (for example, OR1). OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key. Now both Alice and OR1 have a shared key they use to encrypt and decrypt data sent between them.

	So now Alice has a connection with the first Onion Router in the circuit. To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1. This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2 ($ g^{a_2} $). OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2. When OR1 receives a created cell, OR1 passes this cell to Alice. Now Alice and OR2 share a common key: $ K = g^{a_2b_2} $. The same procedure can be used to extend the circuit with more nodes.

\subsection{Disadvantages}
	\label{ss:tor_disadvantages}

	While Tor guarantees anonymity, there are some disadvantages using it. The main disadvantage is that the Tor network is slow. According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.

	According to Dingledine et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal. In this section, we will summarize these reasons and explain what could be done to fix them.

	First of all, the congestion control does not work well. The network has some problems handling bulk transfers, such as when downloading large files or streaming high-quality videos. The congestion control could be improved by using an unreliable protocol for links between Tor relays. Goldberg et al. [linkje] have proposed PCTCP which could improve the response time of the Tor network with 60\% and the download time of files with 30\%.

	Some Tor users put more traffic on the network than they contribute by running a Onion Router. This means that these users are slowing the network down as they use more traffic than giving to the network. A possible solution for this is to throttle certain high-bandwidth protocols such as BitTorrent at exit nodes or at Onion Proxies.

	Also, the Tor network doesn't have the capacity to handle all the users that want privacy on the Internet. By increasing the amount of Onion Routing in the Tor network, the capacity is increased. Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network and making it faster.

	The current path selection algorithm of Tor doesn't distribute the load evenly over the network. The problem is that the current selection strategy is optimal when the network is fully loaded. This is not always the case. Using a better path selection algorithm could increase the capacity of the network and the overall user experience.

	Another problem is that the Tor clients are not optimal at handling latency and connection failures. For example, if extending a circuit fails, the entire circuit is abandoned. An improvement would be to first try to extend the circuit to some other places. If that fails, the circuit could be abandoned. Also, a better timeout mechanism could be chosen for building circuits.

	Much of the overhead of the network is in downloading the directory information. There is also overhead in the TLS connection between the nodes in the network. According to Dingledine et al, removing the empty TLS application record could reduce the overhead in the TCP/IP header with 6.3\%.

	As we saw, the directory service generates overhead on the network. If we could replace this central authority, we could reduce the overhead of the network and improve the performance. This means, we would like to have Tor decentralized. Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up. This is due to the fact that there are many problems decentralization brings along with.

### 2014-03-14 paper.tex
Fixed conflict structure problem

--- 2014-03-13 paper.tex
@@
 	Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan.
+Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
 Each of these decentralized networks will be discussed in the next section.
 Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]
+Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.[link naar survey p2p?]
 
@@
 
-		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
-Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.[link naar survey p2p?]
+		There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file.
+Another key is the Signed-Subspace key (SSK) which enables personal namespaces.
+This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
+The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.
+
+		The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
+Each peer has only knowledge about his neighbours.
+Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
+Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
+Results of queries are being cached in intermediate nodes to reduce the time for a query response.
+To prevent looping of the requests, each request contains a random identifier.
+The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
 
@@
 
-			There are three types of file keys in Freenet: the first one is called the \emph{Keyword-Signed Key} (KSK) which is derived from a short description of the file.
-Another key is the \emph{Signed-Subspace key} (SSK) which enables personal namespaces.
-This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
-The third type of key is the \emph{Content-Hash Key} (CHK) which is used for updating and splitting of contents.
+		MIX networks are typically high latency networks and traffic in it moves slow.
+Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
+Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
+MorphMix has been developed as a low latency and high performance network.
+As such, it will not hold messages for very long, nor will it use cover traffic.
 
-			The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
-Each peer has only knowledge about his direct neighbours.
-Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
-Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
-Results of queries are being cached in intermediate nodes to reduce the time for a query response.
-To prevent looping of the requests, each request contains a random identifier.
-The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
+		In contrast to Tor, MorphMix does not feature a centralized node discovery mechanism.
+Instead, every node is free to chose a set of next nodes that will be the continuation of an anonymous tunnel.
+A malicious node could select a colluding node to continue the tunnel and therefore control the entire tunnel.
+To prevent this, a witness node is appointed to mediate the setup of an anonymous tunnel.
+Although this makes the possibility of such an attack more difficult, it doesn't make it impossible.
+
+		An important part of MorphMix is the ability to detect malicious tunnels.
+Tunnels that are set up by well behaving nodes will select the next nodes in the tunnel randomly.
+Malicious colluding nodes, however, will specifically select nodes that are part of the malicious network to continue the tunnel.
+This will reveal itself in the fact that the probability of the selection of certain nodes is increased.
+By using this information it becomes possible, to an extent, to detect malicious tunnels.
 

### 2014-03-14 paper.tex
Made figure span the width of the full page
Added text about the routing attacks

@@
 % to submit to, of course. )
+
+% setting paragraph indent
+\setlength{\parskip}{\baselineskip}
 
@@
 
+	\begin{figure*}[!t]
+		\centering
+		\includegraphics[width=0.8\textwidth]{graphics/tor.pdf}
+		\caption{The components of the Tor network.
+After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node, and uses it to communicate (anonymously) with the internet.}
+		\label{fig:tor_layout}
+	\end{figure*}
+
 	\subsection{Onion routing}
@@
 This algorithm is described in section \ref{ss:tor_circuit}.
-
-		\begin{figure}[!t]
-			\centering
-			\includegraphics[width=0.4\textwidth]{graphics/tor.pdf}
-			\caption{The components of the Tor network.
-After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node, and uses it to communicate (anonymously) with the internet.}
-			\label{fig:tor_layout}
-		\end{figure}
 
@@
 	\subsection{Low-Resource Routing attacks}
-		Hier wat over routing attacks
+		Another possible attack on the anonimity of tor is the so called \emph{low-resource routing attack} [linkje naar paper].
+With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resourcing, thus comprimising the anonimy Tor provides.
+The idea of this attack is that a malicious Onion router can lie about it's bandwidth, thus advertising a much higher bandwidth than it actually has.
+Because of the Tor path selection algorithm that prefers high-bandwidth nodes, the chance that a malicious entry node and exit node are chosen, is high.
+
+		Once a malicious entry node and exit node has been chosen, an analysis of the traffic can be done to link Onion proxies with the webservers he communicates with.
+Experimental research on a testbed, has shown that with an total of 66 nodes and 6 malicious nodes, is possible to compromise 46\% of the built circuits.
+On request of the Tor community, this attack hasn't been tested on the live Tor network.
+There are some extensions and improvements to this attack.
+It is possible to denial-of-service some of the well-used entry nodes, to force Tor clients to choose a new entry node, possibly a malicious one.
+
+		Bauer et al.
+proposed several solutions in his paper.
+The first one is to actually verify the resources of the nodes, for example, measuring the bandwidth and/or uptime of a node.
+Bandwidth can be checked centralized or decentralize: the disadvantages of a centralized bandwidth check, is that is generates much overhead on the network.
+With distributed bandwidth verification, Tor routers monitor each other but this is not enough to detect selective malicious nodes.
+Another solution is to restrict the amount of routers that can be on a single IP-address.
+The last solution proposed is to change the routing strategy.
 

### 2014-03-14 paper.tex
Use blackboard provided template

@@
 % !TeX spellcheck = en_GB
-\documentclass[journal]{IEEEtran}
+\documentclass{article}
+\usepackage{a4wide}
 
@@
 \author{Rolf Jagerman, Wendo Sab\'ee, Laurens Versluis, Martijn de Vos}
+\date{}
 
-% The paper headers
-%\markboth{Journal of \LaTeX\ Class Files,~Vol.~11, No.~4, December~2012}%
-%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
+\pagestyle{empty}
 
@@
 \maketitle
+\thispagestyle{empty}
 
@@
 	% (should never be an issue)
-	\IEEEPARstart{W}{ith} the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate.
+	With the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate.
 In many cases however, internet usage is either censored or monitored by third parties.
@@
 
-\appendices
-
+\bibliographystyle{plain}
 \bibliography{paper_references}

### 2014-03-14 paper.tex
Anonymity
Forgot a4wide package
Sort current systems by date

@@
 % setting paragraph indent
-\setlength{\parskip}{\baselineskip}
+% \setlength{\parskip}{\baselineskip}
 
@@
 
-	\subsection{Gnutella}
+	\subsection{Gnutella} % ~2000
 		Gnutella is a decentralized peer-to-peer network used for distributed search of files.
@@
 
-	\subsection{Freenet}
+	\subsection{Freenet} % 2001
 		In Freenet, each data item is represented by a key that is independent of the location of the file.
@@
 
-	\subsection{NISAN}
-		NISAN, or Network Information Service for Anonymization Networks \cite{panchenko2006nisan}, is an anonymization network which implements a distributed node discovery.
-Not only does a central node administrator (the Directory Server in Tor) imply trust in those servers, Panchenko et al.
-also argue that a central node administration (the Directory Server in Tor) does not scale, as the current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.
+	\subsection{Tapestry} % 2001
+		Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
+A property of Tapestry is that it offers load distribution and routing locality.
 
-		NISAN implements a DHT-based approach (Kademlia) for distributing node information, in such a way that does not require the client to know about all the nodes in the network (such as in Tor).
-To build a circuit, NISAN generates random IDs and searches for the closest hit throughout the network.
-This makes it possible to build a path with nodes picked in a random, uniform way among all nodes, without the trust of a third party.
+		Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored.
+A peer can also function as a router, which forwards an incoming message.
+The routing algorithm is based on the destination ID of the packet.
+Routers are using local routing maps to route messages to the destination ID digit by digit.
+The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.
 
-		This does not fully protect against fingerprinting or bridging attacks (passive attacks), and suggest to do random walks throughout the network to mitigate that.
-The authors admit however this decreases the protection against an active attack.
+		Tapestry is a fundamental component of OceanStore [linkje naar paper over OceanStore], a decentralized storage system.
+Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
 
-	\subsection{MorphMix}
+	\subsection{Pastry} % 2001
+		Pastry is very similar to Tapestry, but there are some small differences.
+One of these differences is the handling of network locality and data object replication.
+Plastry also uses the Plaxton mesh data structure for the routing algorithm.
+Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
+Each node can be found in about log(n) steps.
+
+		The Pastry overlay network is used in several applications, such as Scribe, Squirrel and PAST.
+Scribe is an system that has been built to send multicast messages.
+Instead of relying on the multicast infrastructure, multicast messages are sent using only unicast services.
+Pastry is used to create and manage multicast groups.
+Scribe makes use of the organization, robustness and reliability of the Pastry network.
+
+		Squirrel is a decentralized peer-to-peer web cache.
+The network uses Pastry to locate it's objects and for the routing algorithm.
+Squirrel allows users to share it's web cache with other users in the network, creating a large decentralized web cache.
+Squirrel however introduces some overhead when searching the cache.
+The challenge is to keep this overhead as low as possible.
+
+		PAST is a large scale persistent peer-to-peer network that has been designed to store files.
+It is built upon the Pastry network and the main focus of PAST is providing performance, scalability and security.
+
+	\subsection{MorphMix} % 2002
 		MorphMix \cite{rennhard2002introducing} functions similar to both Tor and MIX networks.
@@
 
-	\subsection{Tribler}
-		Information about Tribler.
-
-	\subsection{Tapestry}
-		Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
-A property of Tapestry is that it offers load distribution and routing locality.
-
-		Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored.
-A peer can also function as a router, which forwards an incoming message.
-The routing algorithm is based on the destination ID of the packet.
-Routers are using local routing maps to route messages to the destination ID digit by digit.
-The routing system ensures that each peer in the system can be found in a logarithmic amount of hops.
-
-		Tapestry is a fundamental component of OceanStore [linkje naar paper over OceanStore], a decentralized storage system.
-Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
-
-	\subsection{Pastry}
-		Pastry is very similar to Tapestry, but there are some small differences.
-One of these differences is the handling of network locality and data object replication.
-Plastry also uses the Plaxton mesh data structure for the routing algorithm.
-Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
-Each node can be found in about log(n) steps.
-
-		The Pastry overlay network is used in several applications, such as Scribe, Squirrel and PAST.
-Scribe is an system that has been built to send multicast messages.
-Instead of relying on the multicast infrastructure, multicast messages are sent using only unicast services.
-Pastry is used to create and manage multicast groups.
-Scribe makes use of the organization, robustness and reliability of the Pastry network.
-
-		Squirrel is a decentralized peer-to-peer web cache.
-The network uses Pastry to locate it's objects and for the routing algorithm.
-Squirrel allows users to share it's web cache with other users in the network, creating a large decentralized web cache.
-Squirrel however introduces some overhead when searching the cache.
-The challenge is to keep this overhead as low as possible.
-
-		PAST is a large scale persistent peer-to-peer network that has been designed to store files.
-It is built upon the Pastry network and the main focus of PAST is providing performance, scalability and security.
-
-	\subsection{Tarzan}
+	\subsection{Tarzan} % 2002
 		Tarzan [TARZAN PAPER] is a fully distributed peer-to-peer anonymity network.
@@
 
-	\subsection{Torsk}
+	\subsection{Tribler} % 2008
+		Information about Tribler.
+
+	\subsection{NISAN} % 2009
+		NISAN, or Network Information Service for Anonymization Networks \cite{panchenko2006nisan}, is an anonymization network which implements a distributed node discovery.
+Not only does a central node administrator (the Directory Server in Tor) imply trust in those servers, Panchenko et al.
+also argue that a central node administration (the Directory Server in Tor) does not scale, as the current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.
+
+		NISAN implements a DHT-based approach (Kademlia) for distributing node information, in such a way that does not require the client to know about all the nodes in the network (such as in Tor).
+To build a circuit, NISAN generates random IDs and searches for the closest hit throughout the network.
+This makes it possible to build a path with nodes picked in a random, uniform way among all nodes, without the trust of a third party.
+
+		This does not fully protect against fingerprinting or bridging attacks (passive attacks), and suggest to do random walks throughout the network to mitigate that.
+The authors admit however this decreases the protection against an active attack.
+
+	\subsection{Torsk} % 2009
 		Torsk [TORSKKKK PAPER] is an extension to Tor, designed to be an interoperable replacement for the circuit creation and Directory Service as used by Tor.
@@
 		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
-		\item{Anonimity:} Does the network hide the identities of the sender and/or receiver?
+		\item{Anonymity:} Does the network hide the identities of the sender and/or receiver?
 	\end{itemize}

### 2014-03-14 paper.tex
Removed duplicate text and added the abstract

--- 2014-03-14 paper.tex
@@
 \begin{abstract}
-	The abstract goes here.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Nunc et elit nec metus ultrices faucibus.
-Mauris volutpat libero eu arcu sodales, ac bibendum neque pulvinar.
-Sed et ipsum nunc.
-Quisque ac sem ut nunc tincidunt commodo.
-Cras at odio nibh.
-Pellentesque sodales ut tortor sed dictum.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
+	There are quite a few distributed anonymous communication networks such as Tor, yet when it comes to decentralized anonymous systems the numbers are rather small and certain problems arise.
+In this technical report we explain how Tor works and which problems it currently faces.
+After that, we talk about why would like to decentralize, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
+Finally, we provide a table in where we compare these projects against each other, which will also be public available on the Github page mention in this report.
+(We are going to mention it, right?)
 \end{abstract}
@@
 
-	As we saw in the previous section, we would like to have a decentralized anonymous network.
-This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry [link].
-These networks will be described in more detail in the next chapter.
-Among these networks are some overlay anonymous networks such as Tarzan and Torks [link].
-
-	There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
-When removing this central authority, these components needs to be spread across the peers in the network.
-In this section we will explain the various problems that are involved when decentralizing Tor.
-In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
-
 	\subsection{Bootstrapping new nodes}

### 2014-03-14 paper.tex
modified abstract

@@
 In this technical report we explain how Tor works and which problems it currently faces.
-After that, we talk about why would like to decentralize, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
+After that, we talk about why would like to decentralize peer-to-peer networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
 Finally, we provide a table in where we compare these projects against each other, which will also be public available on the Github page mention in this report.

### 2014-03-14 paper.tex
more modifications in the abstract
We want to decentralize the anonymous networks to create a peer-to-peer network

--- 2014-03-14 paper.tex
@@
 	There are quite a few distributed anonymous communication networks such as Tor, yet when it comes to decentralized anonymous systems the numbers are rather small and certain problems arise.
-In this technical report we explain how Tor works and which problems it currently faces.
-After that, we talk about why would like to decentralize, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
+In this technical report we explain how Tor works and which attacks are possible and which vulnerabilities currently exist in Tor.
+After that, we talk about why would like to decentralize these anonymous networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
 Finally, we provide a table in where we compare these projects against each other, which will also be public available on the Github page mention in this report.
-(We are going to mention it, right?)
 \end{abstract}

### 2014-03-14 paper.tex
Added the missing cites

--- 2014-03-14 paper.tex
@@
 	There are quite a few distributed anonymous communication networks such as Tor, yet when it comes to decentralized anonymous systems the numbers are rather small and certain problems arise.
-In this technical report we explain how Tor works and which problems it currently faces.
+In this technical report we explain how Tor works and which attacks are possible and which vulnerabilities currently exist in Tor.
 After that, we talk about why would like to decentralize peer-to-peer networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
 Finally, we provide a table in where we compare these projects against each other, which will also be public available on the Github page mention in this report.
-(We are going to mention it, right?)
 \end{abstract}
@@
 		Before a circuit can be established, a path has to be chosen.
-The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes [link naar cacr2011-20].
+The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes \cite{wang2012congestion}.
 Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.
@@
 The main disadvantage is that the Tor network is slow.
-According to the Tor Metrics project [link naar tor metrics project], it takes about 6 seconds to download 1 MiB of data.
+According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data.
 
@@
 Goldberg et al.
-[linkje] have proposed PCTCP which could improve the response time of the Tor network with 60\% and the download time of files with 30\%.
+\cite{alsabah2013pctcp} have proposed PCTCP which could improve the response time of the Tor network with 60\% and the download time of files with 30\%.
 
@@
 This means, we would like to have Tor decentralized.
-Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up.
+Many research has been done already on the decentralization of Tor \cite{wang2012octopus, alsabah2013pctcp} (WHICH CITES CAN BE ADDED HERE?
+A LOT ARE MORE SUITEABLE FOR THE CURRENT DECENTRALIZED SYSTEM SECTION) but so far, no anonymous, well-performing decentralized network has come up.
 This is due to the fact that there are many problems decentralization brings along with.
@@
 	\subsection{Low-Resource Routing attacks}
-		Another possible attack on the anonimity of tor is the so called \emph{low-resource routing attack} [linkje naar paper].
+		Another possible attack on the anonimity of tor is the so called \emph{low-resource routing attack} \cite{bauer2007low}.
 With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resourcing, thus comprimising the anonimy Tor provides.
@@
 
-		A fully distributed network that implements such a solution is the Bitcoin network [BITCOIN PAPER: http://s.kwma.kr/pdf/Bitcoin/bitcoin.pdf], in which computing power, and not the number of nodes is important for the general network consensus.
+		A fully distributed network that implements such a solution is the Bitcoin network \cite{nakamoto2008bitcoin}, in which computing power, and not the number of nodes is important for the general network consensus.
 
 	\subsection{Replay Attacks}
-		A replay attack [cite naar replay attack paper] happens when a malicious entry node duplicates cells and send them again.
+		A replay attack \cite{pries2008new} happens when a malicious entry node duplicates cells and send them again.
 Since Tor uses uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the connection to be torn down.
@@
 This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry.
+Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella \cite{ripeanu2001peer}, Freenet \cite{lua2005survey} and Tapestry.
 These networks will be described in more detail in the next chapter.
@@
 Different implementations of NAT require different techniques, such as \textit{hole punching}, \textit{relaying} or \textit{reversal}, as described by Wocker et al.
-[http://www.pap.vs.uni-due.de/files/wacker-nat-traversal.pdf].
+\cite{wacker2008nat}.
 
@@
 
-		Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) [linkje naar ace].
+		Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) \cite{backes2012ace}.
 This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
@@
 
-	Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers].
+	Many other decentralized peer-to-peer networks have been proposed and some have been implemented \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}.
 Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
@@
 Note that we're only considering fully decentralized networks here.
-Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.[link naar survey p2p?]
+Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.
 
@@
 	\subsection{Tapestry} % 2001
-		Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
+		Tapestry is based on the Plaxton mesh data structure, which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
 A property of Tapestry is that it offers load distribution and routing locality.
@@
 
-		Tapestry is a fundamental component of OceanStore [linkje naar paper over OceanStore], a decentralized storage system.
-Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
+		Tapestry is a fundamental component of OceanStore, a decentralized storage system. Tapestry is also used in systems such as Bayeux and SpamWatch, a decentralized spam-filtering system.
 
@@
 	\subsection{Tarzan} % 2002
-		Tarzan [TARZAN PAPER] is a fully distributed peer-to-peer anonymity network.
+		Tarzan \cite{freedman2002tarzan} is a fully distributed peer-to-peer anonymity network.
 It implements a network address translator (NAT) to bridge between nodes running Tarzan and the internet.
@@
 Nambiar et al.
-showed however that this does not scale beyond roughly 10,000 nodes [NISAN, SALSA PAPER].
+showed however that this does not scale beyond roughly 10,000 nodes \cite{panchenko2009nisan, nambiar2006salsa}.
 
@@
 	\subsection{Torsk} % 2009
-		Torsk [TORSKKKK PAPER] is an extension to Tor, designed to be an interoperable replacement for the circuit creation and Directory Service as used by Tor.
+		Torsk \cite{mclachlan2009scalable} is an extension to Tor, designed to be an interoperable replacement for the circuit creation and Directory Service as used by Tor.
 The authors argue that the current Directory Service does not scale, with the percentage of the traffic in a network dedicated to node discovery growing as the number of nodes grow.
@@
 		Some other decentralized peer-to-peer systems has been developed, focussing on anonymity.
-An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) [linkje naar AP3 paper] which makes cooperative, decentralized anonymous communication possible.
+An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible.
 The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms.

### 2014-03-14 paper.tex

@@
 In this technical report we explain how Tor works and which attacks are possible and which vulnerabilities currently exist in Tor.
-After that, we talk about why would like to decentralize peer-to-peer networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
+After that, we talk about why would like to decentralize these anonymous networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
 Finally, we provide a table in where we compare these projects against each other, which will also be public available on the Github page mention in this report.

### 2014-03-14 paper.tex
back to peer-to-peer!

--- 2014-03-14 paper.tex
@@
 In this technical report we explain how Tor works and which attacks are possible and which vulnerabilities currently exist in Tor.
-After that, we talk about why would like to decentralize peer-to-peer networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
+After that, we talk about why would like to decentralize these peer-to-peer networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
 Finally, we provide a table in where we compare these projects against each other, which will also be public available on the Github page mention in this report.

### 2014-03-14 paper.tex
Added the table to the paper
Please work in the table in the paper from now on :)

@@
 \usepackage{epstopdf}
+\usepackage{longtable}
+\usepackage{caption}
 
@@
 
+\begin{center}
+	\captionof{table}{A comparison of decentralized peer-to-peer overlay networks}
+    \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{1.6cm} | p{2.2cm} | p{2.0cm} | p{2cm} | p{2cm} | p{2cm} |}
+    \hline
+    	Name & Year & Compatible with Tor & Public implementation & Used in practice & Attack resistance & Provides anonymity \\ \hline
+	Gnutella & ~2000 & no & yes & yes, has millions of users & Vulnerable for DDoS attacks and attacks from misbehaving peers & Queries are anonymous, IP addresses are revealed when downloading files.\\ \hline
+	Freenet & 2001 & no & yes, implementations are based on the FCP (Freenet Client Protocol) & yes & Vulnerable for man-in-the-middle attacks and Trojan attacks & yes\\ \hline
+	Tapestry & 2001 & no & yes & yes, several applications are based on it such as OceanStore and Bayeux & Vulnerable for man-in-the-middle attacks and Trojan attacks & no\\ \hline
+	Pastry & 2001 & no & yes & yes & Vulnerable for man-in-the-middle attacks and Trojan attacks & no\\ \hline
+	Anonymizing peer-to-peer proxy (AP3) & 2004 & no & no & no & Provides anonymity even in the case of a large-scale attack by a coordinated set of malicious nodes & yes\\ \hline
+	Tarzan & 2002 & no & no(?) & no & ? & yes\\ \hline
+	MorphMix & 2002 & no & yes & no & yes, although depending on the number of colluding malicious nodes & yes\\ \hline
+	I2P & 2003 & no & yes & yes & ? & yes\\ \hline
+	Salsa & 2006 & no & ? & ? & ? & ?\\ \hline
+	Tribler & 2008 & no, based on BitTorrent & yes & yes & ? & not yet\\ \hline
+	Torks & 2009 & yes & implementation exists, but not public(?) & no & ? & yes\\ \hline
+	NISAN & 2009 & no & no & no & ? & yes\\ \hline
+    \end{longtable}
+\end{center}
+
 \section{Conclusion}

### 2014-03-15 table.tex
Moved the table to table.tex
And imported the table in paper.tex with the include command

\begin{center}
	\captionof{table}{A comparison of decentralized peer-to-peer overlay networks}
    \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{1.6cm} | p{2.2cm} | p{2.0cm} | p{2cm} | p{2cm} | p{2cm} |}
    \hline
    	Name & Year & Compatible with Tor & Public implementation & Used in practice & Attack resistance & Provides anonymity \\ \hline
	Gnutella & ~2000 & no & yes & yes, has millions of users & Vulnerable for DDoS attacks and attacks from misbehaving peers & Queries are anonymous, IP addresses are revealed when downloading files.\\ \hline
	Freenet & 2001 & no & yes, implementations are based on the FCP (Freenet Client Protocol) & yes & Vulnerable for man-in-the-middle attacks and Trojan attacks & yes\\ \hline
	Tapestry & 2001 & no & yes & yes, several applications are based on it such as OceanStore and Bayeux & Vulnerable for man-in-the-middle attacks and Trojan attacks & no\\ \hline
	Pastry & 2001 & no & yes & yes & Vulnerable for man-in-the-middle attacks and Trojan attacks & no\\ \hline
	Anonymizing peer-to-peer proxy (AP3) & 2004 & no & no & no & Provides anonymity even in the case of a large-scale attack by a coordinated set of malicious nodes & yes\\ \hline
	Tarzan & 2002 & no & no(?) & no & ? & yes\\ \hline
	MorphMix & 2002 & no & yes & no & yes, although depending on the number of colluding malicious nodes & yes\\ \hline
	I2P & 2003 & no & yes & yes & ? & yes\\ \hline
	Salsa & 2006 & no & ? & ? & ? & ?\\ \hline
	Tribler & 2008 & no, based on BitTorrent & yes & yes & ? & not yet\\ \hline
	Torks & 2009 & yes & implementation exists, but not public(?) & no & ? & yes\\ \hline
	NISAN & 2009 & no & no & no & ? & yes\\ \hline
    \end{longtable}
\end{center}

### 2014-03-15 alternative-internet-crawler/crawl_readme.py
Added the python crawler for the alternative internet readme and crawled all projects which are now JSON files.

@@ -1,0 +1,185 @@
+#!/usr/bin/python
+# -*- coding: utf-8 -*-
+"""
+
+    Alternative Internet Crawler
+    Rolf Jagerman, Wendo Sabée, Laurens Versluis, Martijn de Vos
+    TU Delft
+
+This crawler reads the projects from the alternative internet github page and finds additional information on Ohloh. It
+then writes the information to a bunch of JSON files.
+
+
+Usage:
+
+To crawl and place the resulting JSON information in a specified directory, use:
+
+    python crawl_readme.py -a [your-ohloh-api-key] -d [the-directory-to-store-in]
+
+To write to the default directory ("projects"), simply omit the -d parameter:
+
+    python crawl_readme.py -a [your-ohloh-api-key]
+
+"""
+
+from argparse import ArgumentParser
+import logging
+import json
+import re
+try:
+    from urllib.request import urlopen
+    from urllib.parse import urlencode
+except ImportError:
+    from urllib2 import urlopen
+    from urllib import urlencode
+try:
+    from elementtree import ElementTree
+except ImportError:
+    from xml.etree import ElementTree
+
+
+def get_readme():
+    """
+    Gets the contents of the README file from the alternative internet github page.
+    """
+    return urlopen('https://raw.github.com/redecentralize/alternative-internet/master/README.md')
+
+
+def get_projects():
+    """
+    Gets a list of projects with name and description that exist on the alternative internet github readme file.
+    """
+    projects = {}
+    current_project = ''
+    for line in get_readme():
+        if line[:4] == '### ':
+            current_project = line[4:].rstrip()
+            projects[current_project] = {'name': current_project, 'description': ''}
+        elif current_project != '' and line.rstrip() != '':
+            projects[current_project]['description'] += line.rstrip()
+    return projects
+
+
+def get_ohloh_api_request(url, api_key, params=None):
+    """
+    Sends an API request to Ohloh and returns the resulting xml tree or raises an exception if an error occurred.
+
+    Keyword arguments:
+    url -- The request url to get
+    api_key -- The Ohloh API key to use
+    params -- Additional parameters to send
+    """
+    parameters = {'api_key': api_key}
+    if params is not None:
+        for key, value in params.iteritems():
+            parameters[key] = value
+
+    xml = urlopen('%s?%s' % (url, urlencode(parameters)))
+
+    tree = ElementTree.parse(xml)
+    error = tree.getroot().find("error")
+    if error is not None:
[…]

### 2014-03-15 alternative-internet-crawler/generate_readme.py
Quick&Dirty parser to generate a markdown table

@@ -1,0 +1,117 @@
+#!/usr/bin/python
+# -*- coding: utf-8 -*-
+"""
+
+    Alternative Internet Readme Generator
+    Rolf Jagerman, Wendo Sabée, Laurens Versluis, Martijn de Vos
+    TU Delft
+
+This project reads the JSON files generated by the crawler and generates a table from the statistics.
+
+
+Usage:
+
+To generate and write a table to a specific and read from a specific directory, use:
+
+    python generate_readme.py -o [the-file-to-write-to] -d [the-directory-to-read-from]
+
+Otherwise, to use "readme.md" and "projects" as defaults, use:
+
+    python generate_readme.py
+
+"""
+
+from argparse import ArgumentParser
+from collections import OrderedDict
+import logging
+import json
+import os
+import codecs
+
+
+def get_projects(path):
+    """
+    Gets a list of projects with name and description that exist in the specified directory.
+    """
+
+    project_files = filter(lambda x: x.endswith('.json'), os.listdir(path))
+
+    projects = {}
+    for project_file in project_files:
+        project_file = '%s%s%s' % (path, os.sep, project_file)
+        logging.debug('Loading %s' % project_file)
+
+        project_data = open(project_file)
+        current_project = json.load(project_data)
+        projects[current_project['name']] = current_project
+
+    return projects
+
+
+def get_markdown_table_header(columns):
+    return '%s%s%s\n' % ('| ', ' | '.join(columns.values()), ' |')
+
+
+def get_markdown_table_divider(columns):
+    divider = {}
+    for key in columns.keys():
+        divider[key] = '-' * len(columns[key])
+    return get_markdown_table_header(divider)
+
+
+def get_markdown_table_entry(columns, project):
+    entry = []
+    for key in columns.keys():
+        try:
+            entry.append(project[key])
+        except:
+            entry.append('unknown')
+
+    return '%s%s%s\n' % ('| ', ' | '.join(entry), ' |')
+
+
+def run_parser(directory='projects', output='readme.md'):
+    table_columns = OrderedDict([('name', 'Name'), ('description', 'Description'), ('updated_at', 'Last activity'),
+                                 ('total_contributor_count', 'Contributors'), ('total_code_lines', 'LOC')])
+
+    projects = get_projects(directory)
+    logging.info('Loaded %s projects' % len(projects))
+
+    with codecs.open(output, 'w', 'utf-8-sig') as output_file:
[…]

### 2014-03-15 alternative-internet-crawler/generate_readme.py
Oops

@@ -53,9 +53,9 @@ def get_markdown_table_header(columns):
 
 
 def get_markdown_table_divider(columns):
-    divider = {}
-    for key in columns.keys():
-        divider[key] = '-' * len(columns[key])
+    divider = columns
+    for key in divider.keys():
+        divider[key] = '-' * len(divider[key])
     return get_markdown_table_header(divider)
 
 

### 2014-03-17 alternative-internet-crawler/generate_readme.py
Argument clarification

@@ -103,9 +103,9 @@ def main():
     #parser.add_argument('-a', '--api', action='store', dest='api', metavar="api", default='', required=True,
     #                    help='Your Ohloh API key.')
 
-    parser.add_argument('-d', '--directory', action='store', dest='directory', metavar="directory",
+    parser.add_argument('-d', '--directory', action='store', dest='directory', metavar='directory/',
                         default='projects', required=False, help='Directory to read the JSON files from')
-    parser.add_argument('-o', '--output', action='store', dest='output', metavar='output', default='readme.md',
+    parser.add_argument('-o', '--output', action='store', dest='output', metavar='output.md', default='readme.md',
                         required=False, help='File to write the generated table to')
 
     args = parser.parse_args()

### 2014-03-17 alternative-internet-crawler/generate_readme.py
Ugly, slighty hacky sort

@@ -36,14 +36,14 @@ def get_projects(path):
 
     project_files = filter(lambda x: x.endswith('.json'), os.listdir(path))
 
-    projects = {}
+    projects = []
     for project_file in project_files:
         project_file = '%s%s%s' % (path, os.sep, project_file)
         logging.debug('Loading %s' % project_file)
 
         project_data = open(project_file)
         current_project = json.load(project_data)
-        projects[current_project['name']] = current_project
+        projects.append(current_project)
 
     return projects
 
@@ -70,7 +70,17 @@ def get_markdown_table_entry(columns, project):
     return '%s%s%s\n' % ('| ', ' | '.join(entry), ' |')
 
 
-def run_parser(directory='projects', output='readme.md'):
+def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
+    unknown_entry = -99999 if sort_reverse else 'zzzzz'
+
+    sorted_list = sorted(dictionary, key=lambda k: (int(k[sort_on]) if k[sort_on].isdigit() else k[sort_on]) if sort_on in k.keys() else unknown_entry)
+    if sort_reverse:
+        sorted_list.reverse()
+
+    return sorted_list
+
+
+def run_parser(directory='projects', output='readme.md', sort_on='name', sort_reverse=False):
     table_columns = OrderedDict([('name', 'Name'), ('description', 'Description'), ('updated_at', 'Last activity'),
                                  ('total_contributor_count', 'Contributors'), ('total_code_lines', 'LOC')])
 
@@ -84,10 +94,13 @@ def run_parser(directory='projects', output='readme.md'):
         header = get_markdown_table_divider(table_columns)
         output_file.write(header)
 
-        for project in sorted(projects.keys()):
-            logging.debug('Parsing %s' % project)
-            entry = get_markdown_table_entry(table_columns, projects[project])
-            output_file.write(entry, )
+        for project in get_sorted_list(projects, sort_on, sort_reverse):
+            try:
+                logging.debug('Parsing %s' % project['name'])
+                entry = get_markdown_table_entry(table_columns, project)
+                output_file.write(entry)
+            except:
+                logging.warning('Parsing entry failed (%s)' % project)
 
     logging.info('Wrote table to %s' % output)
 
@@ -107,10 +120,14 @@ def main():
                         default='projects', required=False, help='Directory to read the JSON files from')
     parser.add_argument('-o', '--output', action='store', dest='output', metavar='output.md', default='readme.md',
[…]

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Ignore description

@@ -81,7 +81,7 @@ def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
 
 
 def run_parser(directory='projects', output='readme.md', sort_on='name', sort_reverse=False):
-    table_columns = OrderedDict([('name', 'Name'), ('description', 'Description'), ('updated_at', 'Last activity'),
+    table_columns = OrderedDict([('name', 'Name'), ('updated_at', 'Last activity'),
                                  ('total_contributor_count', 'Contributors'), ('total_code_lines', 'LOC')])
 
     projects = get_projects(directory)

### 2014-03-18 table.tex
Make the table a bit prettier

@@
 \begin{center}
-	\captionof{table}{A comparison of decentralized peer-to-peer overlay networks}
     \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{1.6cm} | p{2.2cm} | p{2.0cm} | p{2cm} | p{2cm} | p{2cm} |}
+  		\caption{A comparison of decentralized peer-to-peer overlay networks} \\ \hline
+	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{Attack resistance} & \textbf{Provides anonymity} \\ \hline
+		\endfirsthead
+		\multicolumn{7}{c}{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\ \hline
+	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{Attack resistance} & \textbf{Provides anonymity} \\ \hline
+		\endhead
+		\hline \multicolumn{7}{r}{\textit{Continued on next page}} \\
+		\endfoot
 		\hline
-    	Name & Year & Compatible with Tor & Public implementation & Used in practice & Attack resistance & Provides anonymity \\ \hline
+		\endlastfoot
+
 		Gnutella & ~2000 & no & yes & yes, has millions of users & Vulnerable for DDoS attacks and attacks from misbehaving peers & Queries are anonymous, IP addresses are revealed when downloading files.\\ \hline

### 2014-03-18 paper.tex
Moved the table to table.tex
And imported the table in paper.tex with the include command
Make the table a bit prettier
typo
Another typo

--- 2014-03-14 paper.tex
@@
 	In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
-In this section, we will explain the various compoments of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.
+In this section, we will explain the various components of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.
 
@@
 One of these differences is the handling of network locality and data object replication.
-Plastry also uses the Plaxton mesh data structure for the routing algorithm.
+Pastry also uses the Plaxton mesh data structure for the routing algorithm.
 Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
@@
 
+	\include{table}
+
 	In the last section, we discussed existing decentralized peer-to-peer networks.

### 2014-03-18 paper.tex
Added information about tribler

@@
 	\subsection{Tribler} % 2008
-		Information about Tribler.
+		Tribler is a social-based peer-to-peer file sharing system based on the bittorrent protocol.
+\cite{pouwelse2008tribler}.
+Tribler considers social phenomena and the sense of community as important parts of file sharing.
+Although the system is completely decentralized, it does not yet provide its users with anonymity.
+However, this is something that is currently undergoing research.
+
+		Tribler introduces a novel protocol called buddycast.
+Peer and content discovery use this protocol, which disseminates information epidemically.
+Additionally, the protocol allows users to find taste buddies, which are peers that share similar interests in files.
+This enables quick finding of content that a user is interested in and builds on the idea of social phenomena.
+
+		Although not an anonymization network, Tribler does accomplish a lot on decentralization.
+The buddycast protocol uses bittorrent infohashes to spread information completely decentralized throughout the network.
+With future work on anonymization this can be a promising approach to anonymous file sharing.
 

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Add option to generate links

@@ -48,22 +48,32 @@ def get_projects(path):
     return projects
 
 
-def get_markdown_table_header(columns):
-    return '%s%s%s\n' % ('| ', ' | '.join(columns.values()), ' |')
+def get_markdown_table_header(columns, add_links):
+    if add_links:
+        linked_columns = columns
+        for key in linked_columns.keys():
+            linked_columns[key] = '[%s](TABLE_%s.md)' % (linked_columns[key], linked_columns[key].replace(' ', '_').upper())
+        return get_markdown_table_header(linked_columns, add_links=False)
+    else:
+        return '%s%s%s\n' % ('| ', ' | '.join(columns.values()), ' |')
 
 
 def get_markdown_table_divider(columns):
     divider = columns
     for key in divider.keys():
         divider[key] = '-' * len(divider[key])
-    return get_markdown_table_header(divider)
+    return get_markdown_table_header(divider, add_links=False)
 
 
-def get_markdown_table_entry(columns, project):
+def get_markdown_table_entry(columns, project, add_links):
     entry = []
     for key in columns.keys():
         try:
-            entry.append(project[key])
+            if add_links and key == 'name':
+                project_anchor = filter(lambda c: c.isalpha() or c == " ", project[key]).replace(' ', '-').lower()
+                entry.append('[%s](README.md#%s)' % (project[key], project_anchor))
+            else:
+                entry.append(project[key])
         except:
             entry.append('unknown')
 
@@ -80,7 +90,7 @@ def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
     return sorted_list
 
 
-def run_parser(directory='projects', output='readme.md', sort_on='name', sort_reverse=False):
+def run_parser(directory='projects', output='readme.md', sort_on='name', sort_reverse=False, add_links=False):
     table_columns = OrderedDict([('name', 'Name'), ('updated_at', 'Last activity'),
                                  ('total_contributor_count', 'Contributors'), ('total_code_lines', 'LOC')])
 
@@ -88,7 +98,7 @@ def run_parser(directory='projects', output='readme.md', sort_on='name', sort_re
     logging.info('Loaded %s projects' % len(projects))
 
     with codecs.open(output, 'w', 'utf-8-sig') as output_file:
-        header = get_markdown_table_header(table_columns)
+        header = get_markdown_table_header(table_columns, add_links)
         output_file.write(header)
 
         header = get_markdown_table_divider(table_columns)
[…]

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Raise exception if we specify a nonexistent column for sorting

@@ -83,6 +83,9 @@ def get_markdown_table_entry(columns, project, add_links):
 def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
     unknown_entry = -99999 if sort_reverse else 'zzzzz'
 
+    if len(filter(lambda k: sort_on in k.keys(), dictionary)) < 1:
+        raise Exception('Column \'%s\' not found in any of the entries' % sort_on)
+
     sorted_list = sorted(dictionary, key=lambda k: (int(k[sort_on]) if k[sort_on].isdigit() else k[sort_on]) if sort_on in k.keys() else unknown_entry)
     if sort_reverse:
         sorted_list.reverse()

### 2014-03-18 paper.tex
Payload is not necessarily unencrypted when it leaves the tor network (think https, SSL, TLS, etc.)

@@
 		As a node receives a packet from the previous node, it peels off another layer of encryption, much as how you can peel an onion layer for layer, and forwards it to the next node in the circuit (as specified in the decrypted header).
-When exit node $Z$ decrypts the last layer, it forwards the unencrypted payload outside the network to the original destination that our trusted client $C$ tried to contact, acting as a traditional proxy.
+When exit node $Z$ decrypts the last layer, it forwards the payload outside the network to the original destination that our trusted client $C$ tried to contact, acting as a traditional proxy.
 

### 2014-03-18 paper.tex
"The implemention" is singular, so "a means" instead of "means"

@@
 	The implementation of The Onion Router was first described by the U.S.
-Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
+Navy Research Laboratory, as a means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
 

### 2014-03-18 paper.tex
Replaced "ditch" with "discontinue" and removed the unnecessary "such as onion routing" example.

@@
 
-	In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
-In this section, we will explain the various components of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.
+	In 2002, it was decided to discontinue the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
+In this section, we will explain the various components of Tor, the structure of the network, circuit creation and disadvantages of Tor.
 

### 2014-03-18 paper.tex
Fixed section about onion routing by cleaning up latex code, fixing typos and modifying some sentence structure.

@@
 		As described in the original design paper of The Onion Router, network traffic is forwarded through a circuit of nodes, where each node only knows the previous and next node in the circuit.
-With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each others physical location.
+With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each other's physical location.
 
-		Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry or guard) relay node ($X$), a (middle) relay node ($Y$) and an exit node ($Z$).
-In this case, there are three relay nodes, but this is not a fixed number.
+		Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry or guard) relay node ($X$), a (middle) relay node ($Y$) and an (exit) relay node ($Z$).
+In this case, there are three relay nodes, but this is not necessarily always the case as more middle relay nodes can be added.
 A visualisation of this path can be seen in figure \ref{fig:tor_layout}.
@@
 When building the circuit, our client generates a distinct secret for each of these nodes.
-More information about the circuit setup, can be found in II-D.
-Circuit creation.
+More information about the circuit setup, can be found in \ref{ss:tor_circuit}.
 

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Add formatter functions

@@ -23,6 +23,7 @@ Otherwise, to use "readme.md" and "projects" as defaults, use:
 
 from argparse import ArgumentParser
 from collections import OrderedDict
+from datetime import datetime
 import logging
 import json
 import os
@@ -65,17 +66,23 @@ def get_markdown_table_divider(columns):
     return get_markdown_table_header(divider, add_links=False)
 
 
+def get_markdown_table_entry_format_name(entry):
+    project_anchor = filter(lambda c: c.isalpha() or c == " ", entry).replace(' ', '-').lower()
+    return '[%s](README.md#%s)' % (entry, project_anchor)
+
+
 def get_markdown_table_entry(columns, project, add_links):
+    format_functions = {'name': lambda s, l: get_markdown_table_entry_format_name(s) if l else s,
+                        'updated_at': lambda s, l: datetime.strptime(s, '%Y-%m-%dT%H:%M:%SZ').strftime('%Y-%m-%d'),
+                        'total_contributor_count': lambda s, l: '%s contributors' % s,
+                        'total_code_lines': lambda s, l: '<{:>10,} K'.format(1) if (int(s) / 1000) <= 1 else '{:>10,} K'.format(int(s) / 1000)}
+
     entry = []
     for key in columns.keys():
         try:
-            if add_links and key == 'name':
-                project_anchor = filter(lambda c: c.isalpha() or c == " ", project[key]).replace(' ', '-').lower()
-                entry.append('[%s](README.md#%s)' % (project[key], project_anchor))
-            else:
-                entry.append(project[key])
+            entry.append(format_functions[key](project[key], add_links and key == 'name'))
         except:
-            entry.append('unknown')
+            entry.append(project[key] if key in project.keys() else 'unknown')
 
     return '%s%s%s\n' % ('| ', ' | '.join(entry), ' |')
 

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Add simple script to generate all tables

@@ -93,6 +93,8 @@ def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
     if len(filter(lambda k: sort_on in k.keys(), dictionary)) < 1:
         raise Exception('Column \'%s\' not found in any of the entries' % sort_on)
 
+    logging.info('Sorting on \'%s\'' % sort_on)
+
     sorted_list = sorted(dictionary, key=lambda k: (int(k[sort_on]) if k[sort_on].isdigit() else k[sort_on]) if sort_on in k.keys() else unknown_entry)
     if sort_reverse:
         sorted_list.reverse()

### 2014-03-18 alternative-internet-crawler/genreadme.sh

@@ -1,0 +1,10 @@
+#!/bin/sh
+
+# Name
+python generate_readme.py -l -s name -o TABLE_NAME.md
+# LOC
+python generate_readme.py -r -l -s total_code_lines -o TABLE_LOC.md
+# Contributors
+python generate_readme.py -r -l -s total_contributor_count -o TABLE_CONTRIBUTORS.md
+# Last activity
+python generate_readme.py -r -l -s updated_at -o TABLE_LAST_ACTIVITY.md

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Aligning with spaces doesn't work in github

@@ -75,7 +75,7 @@ def get_markdown_table_entry(columns, project, add_links):
     format_functions = {'name': lambda s, l: get_markdown_table_entry_format_name(s) if l else s,
                         'updated_at': lambda s, l: datetime.strptime(s, '%Y-%m-%dT%H:%M:%SZ').strftime('%Y-%m-%d'),
                         'total_contributor_count': lambda s, l: '%s contributors' % s,
-                        'total_code_lines': lambda s, l: '<{:>10,} K'.format(1) if (int(s) / 1000) <= 1 else '{:>10,} K'.format(int(s) / 1000)}
+                        'total_code_lines': lambda s, l: '<{:,} K'.format(1) if (int(s) / 1000) <= 1 else '{:,} K'.format(int(s) / 1000)}
 
     entry = []
     for key in columns.keys():

### 2014-03-18 paper.tex
Fixes for onion routing section

@@
 
-		After node $X$ receives this packet from out trusted node $C$, it decrypts the attached secret with its private key, and uses that secret to decrypt the rest of the packet.
+		After node $X$ receives this packet from our trusted node $C$, it decrypts the attached secret with its private key, and uses that secret to decrypt the rest of the packet.
 The result is a header with the address for node $Y$ and the payload encrypted with secrets for the following nodes in the circuit, which is forwarded to node $Y$.

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Few small fixes

@@ -51,7 +51,7 @@ def get_projects(path):
 
 def get_markdown_table_header(columns, add_links):
     if add_links:
-        linked_columns = columns
+        linked_columns = columns.copy()
         for key in linked_columns.keys():
             linked_columns[key] = '[%s](TABLE_%s.md)' % (linked_columns[key], linked_columns[key].replace(' ', '_').upper())
         return get_markdown_table_header(linked_columns, add_links=False)
@@ -60,7 +60,7 @@ def get_markdown_table_header(columns, add_links):
 
 
 def get_markdown_table_divider(columns):
-    divider = columns
+    divider = columns.copy()
     for key in divider.keys():
         divider[key] = '-' * len(divider[key])
     return get_markdown_table_header(divider, add_links=False)
@@ -82,7 +82,7 @@ def get_markdown_table_entry(columns, project, add_links):
         try:
             entry.append(format_functions[key](project[key], add_links and key == 'name'))
         except:
-            entry.append(project[key] if key in project.keys() else 'unknown')
+            entry.append(project[key] if key in project.keys() and not project[key] is None else 'unknown')
 
     return '%s%s%s\n' % ('| ', ' | '.join(entry), ' |')
 
@@ -95,7 +95,7 @@ def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
 
     logging.info('Sorting on \'%s\'' % sort_on)
 
-    sorted_list = sorted(dictionary, key=lambda k: (int(k[sort_on]) if k[sort_on].isdigit() else k[sort_on]) if sort_on in k.keys() else unknown_entry)
+    sorted_list = sorted(dictionary, key=lambda k: (int(k[sort_on]) if (not k[sort_on] is None and k[sort_on].isdigit()) else k[sort_on]) if sort_on in k.keys() else unknown_entry)
     if sort_reverse:
         sorted_list.reverse()
 

### 2014-03-18 paper.tex
Fixed long sentences and errors in the directory servers part

@@
 	\subsection{Directory servers}
-		The original Onion Router implementation used in-band status updates where each node broadcasts know nodes to its neighbours.
+		The original Onion Router implementation used in-band status updates.
+During such a status update each node broadcasts known nodes to its neighbours.
 An attacker could exploit this to isolate and limit the knowledge of a client, forcing connections through malicious nodes.
-Beside possible security disadvantages, in-band status updates also have the disadvantage that it takes longer to propagate throughout the network and create a global consensus.
+Another disadvantage is that in-band status updates take longer to propagate throughout the network and create a global consensus.
 
-		To mitigate these concerns, Directory Servers were introduced to Tor during its reimplementation to keep a redundant central consensus about the network.
+		To mitigate these concerns, Directory Servers were introduced to Tor during its reimplementation.
+These Directory Servers keep a redundant central consensus about the network.
 They act as HTTP servers to which Tor nodes can publish signed information about themselves.
@@
 
-		This information is signed by the Directory Servers before it is distributed to the Tor clients.
-The keys to verify these signatures are preloaded in the Tor software, along with the list of Directory Servers, which implies trust by the Tor client in the Directory Servers.
+		The information distributed by the Directory Servers is signed.
+The keys to verify these signatures are preloaded in the Tor software, along with the list of Directory Servers.
+This implies trust by the Tor client in the Directory Servers.
 

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Add option to generate all tables at once

@@ -74,13 +74,14 @@ def get_markdown_table_entry_format_name(entry):
 def get_markdown_table_entry(columns, project, add_links):
     format_functions = {'name': lambda s, l: get_markdown_table_entry_format_name(s) if l else s,
                         'updated_at': lambda s, l: datetime.strptime(s, '%Y-%m-%dT%H:%M:%SZ').strftime('%Y-%m-%d'),
-                        'total_contributor_count': lambda s, l: '%s contributors' % s,
+                        'total_contributor_count': lambda s, l: '%s contributor(s)' % s,
+                        'total_commit_count': lambda s, l: '%s commit(s)' % s,
                         'total_code_lines': lambda s, l: '<{:,} K'.format(1) if (int(s) / 1000) <= 1 else '{:,} K'.format(int(s) / 1000)}
 
     entry = []
     for key in columns.keys():
         try:
-            entry.append(format_functions[key](project[key], add_links and key == 'name'))
+            entry.append(format_functions[key](project[key], add_links))
         except:
             entry.append(project[key] if key in project.keys() and not project[key] is None else 'unknown')
 
@@ -102,12 +103,7 @@ def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
     return sorted_list
 
 
-def run_parser(directory='projects', output='readme.md', sort_on='name', sort_reverse=False, add_links=False):
-    table_columns = OrderedDict([('name', 'Name'), ('updated_at', 'Last activity'),
-                                 ('total_contributor_count', 'Contributors'), ('total_code_lines', 'LOC')])
-
-    projects = get_projects(directory)
-    logging.info('Loaded %s projects' % len(projects))
+def write_output(projects, table_columns, output='readme.md', sort_on='name', sort_reverse=False, add_links=False):
 
     with codecs.open(output, 'w', 'utf-8-sig') as output_file:
         header = get_markdown_table_header(table_columns, add_links)
@@ -125,6 +121,20 @@ def run_parser(directory='projects', output='readme.md', sort_on='name', sort_re
                 logging.warning('Parsing entry failed (%s)' % project)
 
     logging.info('Wrote table to %s' % output)
+
+
+def run_parser(directory='projects', output='readme.md', sort_on='name', sort_reverse=False, add_links=False, generate_all=False):
+    table_columns = OrderedDict([('name', 'Name'), ('updated_at', 'Last activity'),
[…]

### 2014-03-18 alternative-internet-crawler/genreadme.sh
Remove unneeded bashfile

@@ -1,10 +1,0 @@
-#!/bin/sh
-
-# Name
-python generate_readme.py -l -s name -o TABLE_NAME.md
-# LOC
-python generate_readme.py -r -l -s total_code_lines -o TABLE_LOC.md
-# Contributors
-python generate_readme.py -r -l -s total_contributor_count -o TABLE_CONTRIBUTORS.md
-# Last activity
-python generate_readme.py -r -l -s updated_at -o TABLE_LAST_ACTIVITY.md

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Fix sorting when entry is available, but None (null)

@@ -96,7 +96,7 @@ def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
 
     logging.info('Sorting on \'%s\'' % sort_on)
 
-    sorted_list = sorted(dictionary, key=lambda k: (int(k[sort_on]) if (not k[sort_on] is None and k[sort_on].isdigit()) else k[sort_on]) if sort_on in k.keys() else unknown_entry)
+    sorted_list = sorted(dictionary, key=lambda k: (int(k[sort_on]) if (not k[sort_on] is None and k[sort_on].isdigit()) else k[sort_on]) if sort_on in k.keys() and not k[sort_on] is None else unknown_entry)
     if sort_reverse:
         sorted_list.reverse()
 

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Sort preferences

@@ -132,7 +132,7 @@ def run_parser(directory='projects', output='readme.md', sort_on='name', sort_re
 
     if generate_all:
         for key in table_columns.keys():
-            write_output(projects=projects, table_columns=table_columns, output='TABLE_%s.md' % table_columns[key].upper().replace(' ', '_'), sort_on=key, sort_reverse=(not key == 'name'), add_links=add_links)
+            write_output(projects=projects, table_columns=table_columns, output='TABLE_%s.md' % table_columns[key].upper().replace(' ', '_'), sort_on=key, sort_reverse=(not (key == 'name' or key == 'main_language')), add_links=add_links)
     else:
         write_output(projects=projects, table_columns=table_columns, output=output, sort_on=sort_on, sort_reverse=sort_reverse, add_links=add_links)
 

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Proposed columns

@@ -124,8 +124,9 @@ def write_output(projects, table_columns, output='readme.md', sort_on='name', so
 
 
 def run_parser(directory='projects', output='readme.md', sort_on='name', sort_reverse=False, add_links=False, generate_all=False):
-    table_columns = OrderedDict([('name', 'Name'), ('updated_at', 'Last activity'),
-                                 ('total_contributor_count', 'Contributors'), ('total_code_lines', 'LOC'), ('main_language', 'Language')])
+    table_columns = OrderedDict([('name', 'Name'), ('main_language', 'Language'), ('updated_at', 'Last activity'),
+                                 ('total_code_lines', 'LOC'), ('total_commit_count', 'Commits'),
+                                 ('total_contributor_count', 'Contributors')])
 
     projects = get_projects(directory)
     logging.info('Loaded %s projects' % len(projects))

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Add a header at the top of the table

@@ -49,7 +49,16 @@ def get_projects(path):
     return projects
 
 
-def get_markdown_table_header(columns, add_links):
+def get_markdown_page_header():
+    header = '# Alternative Internet\n' + \
+             'Project statistics fetched from [Ohloh](https://www.ohloh.net).\n' +\
+             '\n' + \
+             '[< Back to list](README.md)\n' + \
+             '\n'
+    return header
+
+
+def get_markdown_table_header(columns, add_links, sort_on):
     if add_links:
         linked_columns = columns.copy()
         for key in linked_columns.keys():
@@ -106,7 +115,11 @@ def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
 def write_output(projects, table_columns, output='readme.md', sort_on='name', sort_reverse=False, add_links=False):
 
     with codecs.open(output, 'w', 'utf-8-sig') as output_file:
-        header = get_markdown_table_header(table_columns, add_links)
+        if add_links:
+            header = get_markdown_page_header()
+            output_file.write(header)
+
+        header = get_markdown_table_header(table_columns, add_links, sort_on)
         output_file.write(header)
 
         header = get_markdown_table_divider(table_columns)

### 2014-03-18 alternative-internet-crawler/generate_readme.py
Skip table header link if key == sorted_on

@@ -58,11 +58,12 @@ def get_markdown_page_header():
     return header
 
 
-def get_markdown_table_header(columns, add_links, sort_on):
+def get_markdown_table_header(columns, add_links, sort_on=None):
     if add_links:
         linked_columns = columns.copy()
         for key in linked_columns.keys():
-            linked_columns[key] = '[%s](TABLE_%s.md)' % (linked_columns[key], linked_columns[key].replace(' ', '_').upper())
+            if not key == sort_on:
+                linked_columns[key] = '[%s](TABLE_%s.md)' % (linked_columns[key], linked_columns[key].replace(' ', '_').upper())
         return get_markdown_table_header(linked_columns, add_links=False)
     else:
         return '%s%s%s\n' % ('| ', ' | '.join(columns.values()), ' |')

### 2014-03-18 paper.tex
Changed title
Do you guys like it?

--- 2014-03-18 paper.tex
@@
 % Title of the paper
-\title{30 years of privacy research for the masses \& \newline 15 years of decentralization attempts}
+\title{Fifteen years of decentralization attempts}
 % Authors
@@
 	The implementation of The Onion Router was first described by the U.S.
-Navy Research Laboratory, as a means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
+Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
 
-	In 2002, it was decided to discontinue the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
-In this section, we will explain the various components of Tor, the structure of the network, circuit creation and disadvantages of Tor.
+	In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
+In this section, we will explain the various components of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.
 
@@
 		As described in the original design paper of The Onion Router, network traffic is forwarded through a circuit of nodes, where each node only knows the previous and next node in the circuit.
-With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each other's physical location.
+With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each others physical location.
 
-		Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry or guard) relay node ($X$), a (middle) relay node ($Y$) and an (exit) relay node ($Z$).
-In this case, there are three relay nodes, but this is not necessarily always the case as more middle relay nodes can be added.
+		Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry or guard) relay node ($X$), a (middle) relay node ($Y$) and an exit node ($Z$).
+In this case, there are three relay nodes, but this is not a fixed number.
 A visualisation of this path can be seen in figure \ref{fig:tor_layout}.
@@
 When building the circuit, our client generates a distinct secret for each of these nodes.
-More information about the circuit setup, can be found in \ref{ss:tor_circuit}.
+More information about the circuit setup, can be found in II-D.
+Circuit creation.
 
@@
 		As a node receives a packet from the previous node, it peels off another layer of encryption, much as how you can peel an onion layer for layer, and forwards it to the next node in the circuit (as specified in the decrypted header).
-When exit node $Z$ decrypts the last layer, it forwards the payload outside the network to the original destination that our trusted client $C$ tried to contact, acting as a traditional proxy.
+When exit node $Z$ decrypts the last layer, it forwards the unencrypted payload outside the network to the original destination that our trusted client $C$ tried to contact, acting as a traditional proxy.
 

### 2014-03-18 paper.tex
Fixed some small typos

@@
 	\subsection{Tribler} % 2008
-		Tribler is a social-based peer-to-peer file sharing system based on the bittorrent protocol.
+		Tribler is a social-based peer-to-peer file sharing system based on the BiTtorrent protocol.
 \cite{pouwelse2008tribler}.
@@
 
-		Tribler introduces a novel protocol called buddycast.
+		Tribler introduces a novel protocol called BuddyCast.
 Peer and content discovery use this protocol, which disseminates information epidemically.
@@
 		Although not an anonymization network, Tribler does accomplish a lot on decentralization.
-The buddycast protocol uses bittorrent infohashes to spread information completely decentralized throughout the network.
-With future work on anonymization this can be a promising approach to anonymous file sharing.
+The BuddyCast protocol uses BitTorrent infohashes to spread information completely decentralized throughout the network.
+With future work on anonymization, this can be a promising approach to anonymous file sharing.
 

### 2014-03-18 paper.tex
added text -> github list

--- 2014-03-18 paper.tex
@@
 
+	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems  (available at https://github.com/redecentralize/alternative-internet).
+For each of the listed systems, we created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, tags, (main) programming language, amount of commits and much more.
+This table is available on the same Github page.
+We hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.
+
 \section{Conclusion}

### 2014-03-18 paper.tex
typo fix

@@
 	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems (available at https://github.com/redecentralize/alternative-internet).
-For each of the listed systems, we created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, tags, (main) programming language, amount of commits and much more.
+For each of the listed systems, we have created an entry in a table -- that is publicly available -- that shows the total lines of code (LOC), activity, amount of contributors, tags, (main) programming language, amount of commits, etc.
 This table is available on the same Github page.

### 2014-03-18 paper.tex
redesigned the text once more!

--- 2014-03-18 paper.tex
@@
 	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems (available at https://github.com/redecentralize/alternative-internet).
-For each of the listed systems, we created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, tags, (main) programming language, amount of commits and much more.
+For each of the listed systems, we have created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, tags, (main) programming language, amount of commits, etc.
 This table is available on the same Github page.
 We hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.
+This Github project, including the table, is publicly available.
 

### 2014-03-20 table.tex
Redesigned the table

@@
+\begin{landscape}
+
 \begin{center}
@@
 
-		Gnutella & ~2000 & no & yes & yes, has millions of users & Vulnerable for DDoS attacks and attacks from misbehaving peers & Queries are anonymous, IP addresses are revealed when downloading files.\\ \hline
-		Freenet & 2001 & no & yes, implementations are based on the FCP (Freenet Client Protocol) & yes & Vulnerable for man-in-the-middle attacks and Trojan attacks & yes\\ \hline
-		Tapestry & 2001 & no & yes & yes, several applications are based on it such as OceanStore and Bayeux & Vulnerable for man-in-the-middle attacks and Trojan attacks & no\\ \hline
-		Pastry & 2001 & no & yes & yes & Vulnerable for man-in-the-middle attacks and Trojan attacks & no\\ \hline
-		Anonymizing peer-to-peer proxy (AP3) & 2004 & no & no & no & Provides anonymity even in the case of a large-scale attack by a coordinated set of malicious nodes & yes\\ \hline
-		Tarzan & 2002 & no & no(?) & no & ? & yes\\ \hline
-		MorphMix & 2002 & no & yes & no & yes, although depending on the number of colluding malicious nodes & yes\\ \hline
-		I2P & 2003 & no & yes & yes & ? & yes\\ \hline
-		Salsa & 2006 & no & ? & ? & ? & ?\\ \hline
-		Tribler & 2008 & no, based on BitTorrent & yes & yes & ? & not yet\\ \hline
-		Torks & 2009 & yes & implementation exists, but not public(?) & no & ? & yes\\ \hline
-		NISAN & 2009 & no & no & no & ? & yes\\ \hline
+		Gnutella & ~2000 & & \checkmark & \checkmark & Vulnerable for DDoS attacks and attacks from misbehaving peers & \\ \hline
+		Freenet & 2001 & & \checkmark & \checkmark & Vulnerable for man-in-the-middle attacks and Trojan attacks & \checkmark\\ \hline
+		Tapestry & 2001 & & \checkmark & \checkmark & Vulnerable for man-in-the-middle attacks and Trojan attacks & \\ \hline
+		Pastry & 2001 & & \checkmark & \checkmark & Vulnerable for man-in-the-middle attacks and Trojan attacks & \\ \hline
+		Anonymizing peer-to-peer proxy (AP3) & 2004 & & & & Provides anonymity even in the case of a large-scale attack by a coordinated set of malicious nodes & \checkmark\\ \hline
+		Tarzan & 2002 & & & & ? & \checkmark\\ \hline
+		MorphMix & 2002 & & \checkmark & & yes, although depending on the number of colluding malicious nodes & \checkmark\\ \hline
+		I2P & 2003 & & \checkmark & \checkmark & ? & \checkmark\\ \hline
+		Salsa & 2006 & & ? & ? & ? & ?\\ \hline
+		Tribler & 2008 & & \checkmark & \checkmark & ? & not yet\\ \hline
+		Torks & 2009 & \checkmark & & & ? & \checkmark\\ \hline
+		NISAN & 2009 & & & & ? & \checkmark\\ \hline
     \end{longtable}
 \end{center}
+
+\end{landscape}

### 2014-03-20 table_old.tex
Redesigned the table

\begin{landscape}

\begin{center}
    \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{1.6cm} | p{2.2cm} | p{2.0cm} | p{2cm} | p{2cm} | p{2cm} |}
  		\caption{A comparison of decentralized peer-to-peer overlay networks} \\ \hline
	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{Attack resistance} & \textbf{Provides anonymity} \\ \hline
		\endfirsthead
		\multicolumn{7}{c}{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\ \hline
	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{Attack resistance} & \textbf{Provides anonymity} \\ \hline
		\endhead
		\hline \multicolumn{7}{r}{\textit{Continued on next page}} \\
		\endfoot
		\hline
		\endlastfoot

		Gnutella & ~2000 & no & yes & yes, has millions of users & Vulnerable for DDoS attacks and attacks from misbehaving peers & Queries are anonymous, IP addresses are revealed when downloading files.\\ \hline
		Freenet & 2001 & no & yes, implementations are based on the FCP (Freenet Client Protocol) & yes & Vulnerable for man-in-the-middle attacks and Trojan attacks & yes\\ \hline
		Tapestry & 2001 & no & yes & yes, several applications are based on it such as OceanStore and Bayeux & Vulnerable for man-in-the-middle attacks and Trojan attacks & no\\ \hline
		Pastry & 2001 & no & yes & yes & Vulnerable for man-in-the-middle attacks and Trojan attacks & no\\ \hline
		Anonymizing peer-to-peer proxy (AP3) & 2004 & no & no & no & Provides anonymity even in the case of a large-scale attack by a coordinated set of malicious nodes & yes\\ \hline
		Tarzan & 2002 & no & no(?) & no & ? & yes\\ \hline
		MorphMix & 2002 & no & yes & no & yes, although depending on the number of colluding malicious nodes & yes\\ \hline
		I2P & 2003 & no & yes & yes & ? & yes\\ \hline
		Salsa & 2006 & no & ? & ? & ? & ?\\ \hline
		Tribler & 2008 & no, based on BitTorrent & yes & yes & ? & not yet\\ \hline
		Torks & 2009 & yes & implementation exists, but not public(?) & no & ? & yes\\ \hline
		NISAN & 2009 & no & no & no & ? & yes\\ \hline
    \end{longtable}
\end{center}

\end{landscape}

### 2014-03-20 paper.tex
Redesigned the table

@@
 	The implementation of The Onion Router was first described by the U.S.
-Navy Research Laboratory, as means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
+Navy Research Laboratory, as a means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
 
-	In 2002, it was decided to ditch the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
-In this section, we will explain the various components of Tor such as Onion Routing, the structure of the network, circuit creation and disadvantages of Tor.
+	In 2002, it was decided to discontinue the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
+In this section, we will explain the various components of Tor, the structure of the network, circuit creation and disadvantages of Tor.
 

### 2014-03-20 paper.tex
Section 3 comes before section 4

@@
 	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview of Tor.
+Known vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
 After that, we will talk about decentralization and its problems in section \ref{sec:problems}.
-Vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
-Afterwards, we will discuss the current state of decentralized internet systems in section \ref{sec:decentralized}.
+The current state of decentralized internet systems is discussed in section \ref{sec:decentralized}.
 A comparison of existing decentralized networks is made in section \ref{sec:comparison}.

### 2014-03-20 table.tex
Split the 'attack resistance' column into 'DDos attack possible', 'Sybil Attack possible' and 'Man-in-the-middle attack possible'.
Please fill in the missing checkmarks/question marks :)

@@
 \begin{center}
-    \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{1.6cm} | p{2.2cm} | p{2.0cm} | p{2cm} | p{2cm} | p{2cm} |}
+    \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{1.6cm} | p{2.2cm} | p{2.2cm} | p{2.2cm} | p{2.0cm} | p{2cm} | p{2cm} | }
   		\caption{A comparison of decentralized peer-to-peer overlay networks} \\ \hline
-	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{Attack resistance} & \textbf{Provides anonymity} \\ \hline
+	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{DDoS attack possible} & \textbf{Sybil Attack possible} & \textbf{Man-in-the-middle attack possible} & \textbf{Provides anonymity} \\ \hline
 		\endfirsthead
@@
 
-		Gnutella & ~2000 & & \checkmark & \checkmark & Vulnerable for DDoS attacks and attacks from misbehaving peers & \\ \hline
-		Freenet & 2001 & & \checkmark & \checkmark & Vulnerable for man-in-the-middle attacks and Trojan attacks & \checkmark\\ \hline
-		Tapestry & 2001 & & \checkmark & \checkmark & Vulnerable for man-in-the-middle attacks and Trojan attacks & \\ \hline
-		Pastry & 2001 & & \checkmark & \checkmark & Vulnerable for man-in-the-middle attacks and Trojan attacks & \\ \hline
-		Anonymizing peer-to-peer proxy (AP3) & 2004 & & & & Provides anonymity even in the case of a large-scale attack by a coordinated set of malicious nodes & \checkmark\\ \hline
-		Tarzan & 2002 & & & & ? & \checkmark\\ \hline
-		MorphMix & 2002 & & \checkmark & & yes, although depending on the number of colluding malicious nodes & \checkmark\\ \hline
-		I2P & 2003 & & \checkmark & \checkmark & ? & \checkmark\\ \hline
-		Salsa & 2006 & & ? & ? & ? & ?\\ \hline
-		Tribler & 2008 & & \checkmark & \checkmark & ? & not yet\\ \hline
-		Torks & 2009 & \checkmark & & & ? & \checkmark\\ \hline
-		NISAN & 2009 & & & & ? & \checkmark\\ \hline
+		Gnutella & ~2000 & & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \\ \hline
+		Freenet & 2001 & & \checkmark & \checkmark & & \checkmark & \checkmark & \checkmark\\ \hline
+		Tapestry & 2001 & & \checkmark & \checkmark & & \checkmark & \checkmark & \\ \hline
+		Pastry & 2001 & & \checkmark & \checkmark & & \checkmark & \checkmark & \\ \hline
+		Anonymizing peer-to-peer proxy (AP3) & 2004 & & & & ? & ? & ? & \checkmark\\ \hline
+		Tarzan & 2002 & & & & ? & ? & ? & \checkmark\\ \hline
+		MorphMix & 2002 & & \checkmark & ? & ? & ? & ? & \checkmark \\ \hline
+		I2P & 2003 & & \checkmark & \checkmark & ? & ? & ? & \checkmark\\ \hline
+		Salsa & 2006 & & ? & ? & ? & ? & ? & ?\\ \hline
+		Tribler & 2008 & & \checkmark & \checkmark & ? & ? & ? &\\ \hline
+		Torks & 2009 & \checkmark & & & ? & ? & ? & \checkmark\\ \hline
+		NISAN & 2009 & & & & ? & ? & ? & \checkmark\\ \hline
     \end{longtable}

### 2014-03-20 paper.tex
Small fixes in 2.5

@@
 There is also overhead in the TLS connection between the nodes in the network.
-According to Dingledine et al, removing the empty TLS application record could reduce the overhead in the TCP/IP header with 6.3\%.
+According to Dingledine et al, removing the empty TLS application record could reduce the overhead in the TCP/IP header by 6.3\%.
 
@@
 A LOT ARE MORE SUITEABLE FOR THE CURRENT DECENTRALIZED SYSTEM SECTION) but so far, no anonymous, well-performing decentralized network has come up.
-This is due to the fact that there are many problems decentralization brings along with.
+This due to the many extra problems decentralization brings along with.
 

### 2014-03-20 paper.tex
Small fixes in browser based attacks

@@
 		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.
 
-		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
+		By running an HTTP exit node and a Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+The exit node injects an invisible iframe containing some JavaScript into any web page that passes through it, each sending a unique ID to a malicious web server.
 Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
@@
 		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
+Disabling JavaScript doest not mitigate the attack, because a similar attack can be set up only using the HTML meta refresh tag.
 To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
+There are usually only a few exit nodes running on file sharing ports, such as 4661 to 4666.
 Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.

### 2014-03-20 paper.tex
Small fixes in browser based attacks part 2
Removed the mathematical notation in 2.4

--- 2014-03-20 paper.tex
@@
 \usepackage{caption}
+\usepackage{pdflscape}
+\usepackage{bbding}
+\usepackage{pifont}
+\usepackage{wasysym}
+\usepackage{amssymb}
 
@@
 	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview of Tor.
-Known vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
 After that, we will talk about decentralization and its problems in section \ref{sec:problems}.
-The current state of decentralized internet systems is discussed in section \ref{sec:decentralized}.
+Vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
+Afterwards, we will discuss the current state of decentralized internet systems in section \ref{sec:decentralized}.
 A comparison of existing decentralized networks is made in section \ref{sec:comparison}.
@@
 Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
-To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake ($ g^b $) to the first node in her selected path (for example, OR1).
-OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
+To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake to the first node in her selected path (for example, OR1).
+OR1 sends a \emph{created} cell back with the second half of the key along with a hash of the final key.
 Now both Alice and OR1 have a shared key they use to encrypt and decrypt data sent between them.
@@
 To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1.
-This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2 ($ g^{a_2} $).
+This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2.
 OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2.
 When OR1 receives a created cell, OR1 passes this cell to Alice.
-Now Alice and OR2 share a common key: $ K = g^{a_2b_2} $.
+Now Alice and OR2 share a common key.
 The same procedure can be used to extend the circuit with more nodes.

### 2014-03-20 paper.tex
Fixes on Low-resouce routing attacks

--- 2014-03-20 paper.tex
@@
 		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-Disabling JavaScript doest not mitigate the attack, because a similar attack can be set up only using the HTML meta refresh tag.
+Disabling JavaScript does not mitigate this, because a similar attack can be set up only using the HTML meta refresh tag.
 To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
@@
 	\subsection{Low-Resource Routing attacks}
-		Another possible attack on the anonimity of tor is the so called \emph{low-resource routing attack} \cite{bauer2007low}.
-With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resourcing, thus comprimising the anonimy Tor provides.
+		Another possible attack on the anonymity of tor is the so called \emph{low-resource routing attack} \cite{bauer2007low}.
+With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resources, thus compromising the anonymity Tor provides.
 The idea of this attack is that a malicious Onion router can lie about it's bandwidth, thus advertising a much higher bandwidth than it actually has.
-Because of the Tor path selection algorithm that prefers high-bandwidth nodes, the chance that a malicious entry node and exit node are chosen, is high.
+Because of the Tor path selection algorithm that prefers high-bandwidth nodes, the chance that a malicious entry and exit node are chosen, is high.
 
-		Once a malicious entry node and exit node has been chosen, an analysis of the traffic can be done to link Onion proxies with the webservers he communicates with.
-Experimental research on a testbed, has shown that with an total of 66 nodes and 6 malicious nodes, is possible to compromise 46\% of the built circuits.
-On request of the Tor community, this attack hasn't been tested on the live Tor network.
+		Once a malicious entry and exit node have been chosen, an analysis of the traffic can be done to link Onion proxies with the web servers they communicates with.
+Experimental research in a test setting has shown that with an total of 66 non-malicious and 6 malicious nodes, is possible to compromise 46\% of the built circuits.
+At the request of the Tor community, this attack hasn't been tested on the live Tor network.
 There are some extensions and improvements to this attack.
-It is possible to denial-of-service some of the well-used entry nodes, to force Tor clients to choose a new entry node, possibly a malicious one.
+It is possible to perform a denial of service attack on well used entry nodes, forcing Tor clients to choose a new one.
+This improves the chance that a Tor client chooses a malicious entry node.
 
 		Bauer et al.
-proposed several solutions in his paper.
-The first one is to actually verify the resources of the nodes, for example, measuring the bandwidth and/or uptime of a node.
-Bandwidth can be checked centralized or decentralize: the disadvantages of a centralized bandwidth check, is that is generates much overhead on the network.
+proposed several solutions in their paper.
+The first one is to actually verify the resources of the nodes by, for example, measuring the bandwidth and/or uptime of a node.
+Bandwidth can be checked centralized or decentralized: the disadvantages of a centralized bandwidth check is that is generates much overhead on the network.
 With distributed bandwidth verification, Tor routers monitor each other but this is not enough to detect selective malicious nodes.

### 2014-03-20 paper.tex
Small fixes in replay attacks

@@
 		A replay attack \cite{pries2008new} happens when a malicious entry node duplicates cells and send them again.
-Since Tor uses uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the connection to be torn down.
+Since Tor uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the circuit to be destroyed.
 
-		Using this, an accomplice exit router can therefore in cooperation with the entry node discover the sender and receiver's relationship.
+		Using this, an accomplice exit router can therefore, in cooperation with the entry node, discover the sender and receiver's relationship.
 On top of that, this attack can also be used as a denial of service attack.
-This attack is according to the authors quite challenging to solve and does require some further research.
+According to Pries et al., defending against this attack is quite challenging to solve and requires some further research.
 

### 2014-03-20 paper.tex
Rewritten a sentence in the conclusion

--- 2014-03-20 paper.tex
@@
 
-	In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.
+	In this technical report we explained how Tor works and which components define a Tor network.
 Furthermore, we looked at the main disadvantages and problems Tor is currently facing.
@@
 We first explained which problems one might face when decentralizing a system such as Tor.
-The next section shows which systems currently have a decentralized structure and/or mechanism.
+After that, we've written which systems currently have a decentralized structure and/or mechanism.
 These systems are then compared to each other with their pros and cons.

### 2014-03-20 paper.tex
sentence fix

@@
 In this technical report we explain how Tor works and which attacks are possible and which vulnerabilities currently exist in Tor.
-After that, we talk about why would like to decentralize these peer-to-peer networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
+After that, we talk about why would like to decentralize peer-to-peer networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
 Finally, we provide a table in where we compare these projects against each other, which will also be public available on the Github page mention in this report.
@@
 
-	In this technical report we explained how Tor works and which components define a Tor network.
+	In this technical report we introduced Tor and explained how Tor works and which components define a Tor network.
 Furthermore, we looked at the main disadvantages and problems Tor is currently facing.
@@
 We first explained which problems one might face when decentralizing a system such as Tor.
-After that, we've written which systems currently have a decentralized structure and/or mechanism.
+The next section shows which systems currently have a decentralized structure and/or mechanism.
 These systems are then compared to each other with their pros and cons.

### 2014-03-20 paper.tex
fixed wrong refference
section 6 updated

@@
 		The routing in the network is done by Onion Routers, also called relay nodes.
-The relay nodes relay the data from the Onion Proxy to the web server across a circuit (circuits are described in II-D).
+The relay nodes relay the data from the Onion Proxy to the web server across a circuit (circuits are described in \ref{ss:tor_circuit}).
 Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}.
@@
 
-	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems (available at https://github.com/redecentralize/alternative-internet).
+	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of (anonymous) decentralized systems (available at https://github.com/redecentralize/alternative-internet).
 For each of the listed systems, we have created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, tags, (main) programming language, amount of commits, etc.

### 2014-03-20 table.tex
Redesigned the table, renamed columns and entered x for empty entries

@@
 \begin{center}
-    \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{1.6cm} | p{2.2cm} | p{2.2cm} | p{2.2cm} | p{2.0cm} | p{2cm} | p{2cm} | }
+    \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{1.6cm} | p{2.2cm} | p{2.2cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2cm} | }
   		\caption{A comparison of decentralized peer-to-peer overlay networks} \\ \hline
-	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{DDoS attack possible} & \textbf{Sybil Attack possible} & \textbf{Man-in-the-middle attack possible} & \textbf{Provides anonymity} \\ \hline
+	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{Secure against DDoS attack} & \textbf{Secure against Sybil Attack} & \textbf{Secure against man-in-the-middle attack} & \textbf{Provides anonymity} \\ \hline
 		\endfirsthead
@@
 
-		Gnutella & ~2000 & & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \\ \hline
-		Freenet & 2001 & & \checkmark & \checkmark & & \checkmark & \checkmark & \checkmark\\ \hline
-		Tapestry & 2001 & & \checkmark & \checkmark & & \checkmark & \checkmark & \\ \hline
-		Pastry & 2001 & & \checkmark & \checkmark & & \checkmark & \checkmark & \\ \hline
-		Anonymizing peer-to-peer proxy (AP3) & 2004 & & & & ? & ? & ? & \checkmark\\ \hline
-		Tarzan & 2002 & & & & ? & ? & ? & \checkmark\\ \hline
-		MorphMix & 2002 & & \checkmark & ? & ? & ? & ? & \checkmark \\ \hline
-		I2P & 2003 & & \checkmark & \checkmark & ? & ? & ? & \checkmark\\ \hline
-		Salsa & 2006 & & ? & ? & ? & ? & ? & ?\\ \hline
-		Tribler & 2008 & & \checkmark & \checkmark & ? & ? & ? &\\ \hline
-		Torks & 2009 & \checkmark & & & ? & ? & ? & \checkmark\\ \hline
-		NISAN & 2009 & & & & ? & ? & ? & \checkmark\\ \hline
+		Gnutella & 2000 & x & \checkmark & \checkmark & x & x & x & x \\ \hline
+		Freenet & 2001 & x & \checkmark & \checkmark & \checkmark & x & x & \checkmark\\ \hline
+		Tapestry & 2001 & x & \checkmark & \checkmark & \checkmark & x & x & x \\ \hline
+		Pastry & 2001 & x & \checkmark & \checkmark & \checkmark & x & x & x \\ \hline
+		Anonymizing peer-to-peer proxy (AP3) & 2004 & x & x & x & ? & ? & ? & \checkmark\\ \hline
+		Tarzan & 2002 & x & x & x & ? & ? & ? & \checkmark\\ \hline
+		MorphMix & 2002 & x & \checkmark & ? & ? & ? & ? & \checkmark \\ \hline
+		I2P & 2003 & x & \checkmark & \checkmark & ? & ? & ? & \checkmark\\ \hline
+		Salsa & 2006 & x & ? & ? & ? & ? & ? & ?\\ \hline
+		Tribler & 2008 & x & \checkmark & \checkmark & ? & ? & ? & x\\ \hline
+		Torks & 2009 & \checkmark & x & x & ? & ? & ? & \checkmark\\ \hline
+		NISAN & 2009 & x & x & x & ? & ? & ? & \checkmark\\ \hline
     \end{longtable}

### 2014-03-20 paper.tex
Key exchange fixes

--- 2014-03-20 paper.tex
@@
 \usepackage{caption}
-\usepackage{pdflscape}
-\usepackage{bbding}
-\usepackage{pifont}
-\usepackage{wasysym}
-\usepackage{amssymb}
 
@@
 Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
-To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake to the first node in her selected path (for example, OR1).
-OR1 sends a \emph{created} cell back with the second half of the key along with a hash of the final key.
+To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake ($ g^b $) to the first node in her selected path (for example, OR1).
+OR1 sends a \emph{created} cell back with the second half of the key ($ g^b $) along with a hash of the final key.
 Now both Alice and OR1 have a shared key they use to encrypt and decrypt data sent between them.
@@
 To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1.
-This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2.
+This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2 ($ g^{a_2} $).
 OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2.
 When OR1 receives a created cell, OR1 passes this cell to Alice.
-Now Alice and OR2 share a common key.
+Now Alice and OR2 share a common key: $ K = g^{a_2b_2} $.
 The same procedure can be used to extend the circuit with more nodes.
@@
 		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-A similar system can be set up only using the HTML meta refresh tag.
+Disabling JavaScript does not mitigate this, because a similar attack can be set up only using the HTML meta refresh tag.
 To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
+There are usually only a few exit nodes running on file sharing ports, such as 4661 to 4666.
 Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.
@@
 Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
-Diffie-Hellman is for example used in the circuit setup in Onion Routing (see secion II-D), however, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable for a man-in-the-middle attack.
+It is used in the circuit creation in Onion Routing (see section \ref{ss:tor_circuit}), for example.
+However, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable to a man-in-the-middle attack.
 This weakness makes it possible for an adversary to decrypt all message sent between the two parties.
@@
 		Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) \cite{backes2012ace}.
-This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
+This protocol uses telescoping, which means that the initiator negotiates session keys with each successive hop in the circuit.
 There are several proposals for more efficient key exchange methods.
-One of them is \emph{ACE}, an one-way authenticated key exchange protocol.
-The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
+One of them is \emph{ACE}, a one-way authenticated key exchange protocol.
+The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and nearly 19\% on the side of the Onion Routers.
 ACE requires clients to send one extra element in the key exchange.
-This however, does not introduce any overhead because the element fits in the unused space in a cell.
+This does not introduce any overhead however, because the element fits in the unused space in a cell.
 

### 2014-03-20 paper.tex
Problem with decentralizing fixes

@@
 
-	There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
+	There are advantages to using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
 When removing this central authority, these components needs to be spread across the peers in the network.

### 2014-03-20 paper.tex
Current system fixes
Freenet fixes

--- 2014-03-20 paper.tex
@@
 Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here.
+Note that we're only considering fully decentralized networks here, with the exception of Torsk (which is almost fully decentralized but still requires a Neighbourhood Authority).
 Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.
@@
 Another key is the Signed-Subspace key (SSK) which enables personal namespaces.
-This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
+This key contains a public and a private key.
+The private key is used to store the data and the public key is used in the queries for the file.
 The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.
@@
 To prevent looping of the requests, each request contains a random identifier.
-The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
+The peers that the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
 

### 2014-03-20 paper.tex
Pastry fixes
MorphMix fixes

@@
 Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
-Each node can be found in about log(n) steps.
+Each node can be found in about $\log(n)$ steps.
 
@@
 It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
-Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
+Additionally, MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
 
-		MIX networks are typically high latency networks and traffic in it moves slow.
+		MIX networks are typically high latency and traffic in it moves slow.
 Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
-Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
+Often, cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
 MorphMix has been developed as a low latency and high performance network.

### 2014-03-20 paper.tex
Tribler fixes
Table comparison fixes

@@
 	\subsection{Tribler} % 2008
-		Tribler is a social-based peer-to-peer file sharing system based on the BiTtorrent protocol.
+		Tribler is a social-based peer-to-peer file sharing system based on the BitTorrent protocol.
 \cite{pouwelse2008tribler}.
@@
 
-	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems (available at https://github.com/redecentralize/alternative-internet).
-For each of the listed systems, we have created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, tags, (main) programming language, amount of commits, etc.
+	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems\footnote{Found at https://github.com/redecentralize/alternative-internet}.
+For each of the listed systems, we have created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, (main) programming language, amount of commits, etc.
 This table is available on the same Github page.

### 2014-03-20 paper.tex
Conclusion fixes

@@
 	From this table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
-While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.
-The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.
+While there is a lot of research on decentralized systems, there is no system yet that can compete with Tor.
+The systems that do exist such as Tarzan, Torsk and Gnutella are getting some things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.
 

### 2014-03-20 paper.tex

@@
 
-	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems\footnote{Found at https://github.com/redecentralize/alternative-internet}.
-For each of the listed systems, we have created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, (main) programming language, amount of commits, etc.
-This table is available on the same Github page.
+	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of these systems maintained by redecentralize.org\footnote{Found at https://github.com/redecentralize/alternative-internet}.
+For each of the listed systems, we have created an entry in a table that shows statistics such as the total lines of code (LOC), activity, amount of contributors, (main) programming language and amount of commits, sourced from Ohloh.
+This table is available on the same Github repository.
 We hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.
-This Github project, including the table, is publicly available.
+This Github repository, including the table, is publicly available.
 

### 2014-03-20 paper.tex
IEEE template comment is unneeded now

@@
 \section{Introduction}
-	% The very first letter is a 2 line initial drop letter followed
-	% by the rest of the first word in caps.
-	% 
-	% form to use if the first word consists of a single letter:
-	% \IEEEPARstart{A}{demo} file is ....
-	% 
-	% form to use if you need the single drop letter followed by
-	% normal text (unknown if ever used by IEEE):
-	% \IEEEPARstart{A}{}demo file is ....
-	% 
-	% Some journals put the first two words in caps:
-	% \IEEEPARstart{T}{his demo} file is ....
-	% 
-	% Here we have the typical use of a "T" for an initial drop letter
-	% and "HIS" in caps to complete the first word.
-	% You must have at least 2 lines in the paragraph with the drop letter
-	% (should never be an issue)
 	With the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate.

### 2014-03-20 table.tex
Add \xmark

@@
 
-		Gnutella & 2000 & x & \checkmark & \checkmark & x & x & x & x \\ \hline
-		Freenet & 2001 & x & \checkmark & \checkmark & \checkmark & x & x & \checkmark\\ \hline
-		Tapestry & 2001 & x & \checkmark & \checkmark & \checkmark & x & x & x \\ \hline
-		Pastry & 2001 & x & \checkmark & \checkmark & \checkmark & x & x & x \\ \hline
-		Anonymizing peer-to-peer proxy (AP3) & 2004 & x & x & x & ? & ? & ? & \checkmark\\ \hline
-		Tarzan & 2002 & x & x & x & ? & ? & ? & \checkmark\\ \hline
-		MorphMix & 2002 & x & \checkmark & ? & ? & ? & ? & \checkmark \\ \hline
-		I2P & 2003 & x & \checkmark & \checkmark & ? & ? & ? & \checkmark\\ \hline
-		Salsa & 2006 & x & ? & ? & ? & ? & ? & ?\\ \hline
-		Tribler & 2008 & x & \checkmark & \checkmark & ? & ? & ? & x\\ \hline
-		Torks & 2009 & \checkmark & x & x & ? & ? & ? & \checkmark\\ \hline
-		NISAN & 2009 & x & x & x & ? & ? & ? & \checkmark\\ \hline
+		Gnutella & 2000 & \xmark & \checkmark & \checkmark & \xmark & \xmark & \xmark & \xmark \\ \hline
+		Freenet & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \checkmark \\ \hline
+		Tapestry & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \xmark \\ \hline
+		Pastry & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \xmark \\ \hline
+		Anonymizing peer-to-peer proxy (AP3) & 2004 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
+		Tarzan & 2002 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
+		MorphMix & 2002 & \xmark & \checkmark & ? & ? & ? & ? & \checkmark \\ \hline
+		I2P & 2003 & \xmark & \checkmark & \checkmark & ? & ? & ? & \checkmark\\ \hline
+		Salsa & 2006 & \xmark & ? & ? & ? & ? & ? & ?\\ \hline
+		Tribler & 2008 & \xmark & \checkmark & \checkmark & ? & ? & ? & \xmark \\ \hline
+		Torks & 2009 & \checkmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
+		NISAN & 2009 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
     \end{longtable}

### 2014-03-20 paper.tex
Add \xmark
Move table around a bit and put it in a table float to remove excessive whitespace
Changed some sentence structures and added sub headings to 2.5

--- 2014-03-20 paper.tex
@@
 
-		As described in the previous section, data on the Tor networks travels over circuits.
+		Data on the Tor network travels over several relay nodes before it reaches its destination.
+Such a selection of nodes is called a circuit.
+To ensure both good performance and anonymity, a path is chosen using a sophisticated path selection algorithm.
+This algorithm selects nodes based on the bandwidth of the nodes \cite{wang2012congestion}.
+Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup.
+The same node cannot be used more than once in a single circuit.
+
+		%As described in the previous section, data on the Tor networks travels over circuits.
 The data travels over the circuit in fixed-size cells that are 512 bytes long.
@@
 
-		Before a circuit can be established, a path has to be chosen.
+		%Before a circuit can be established, a path has to be chosen.
 The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes \cite{wang2012congestion}.
@@
 
-		First of all, the congestion control does not work well.
-The network has some problems handling bulk transfers, such as when downloading large files or streaming high-quality videos.
+		\subsubsection{Congestion control}
+		Tor's congestion control does not work well.
+The network has some problems handling bulk transfers, such as downloading large files or streaming high-quality videos.
 The congestion control could be improved by using an unreliable protocol for links between Tor relays.
 Goldberg et al.
-\cite{alsabah2013pctcp} have proposed PCTCP which could improve the response time of the Tor network with 60\% and the download time of files with 30\%.
+\cite{alsabah2013pctcp} have proposed PCTCP which could improve the response time of the Tor network by 60\% and the download time of files by 30\%.
 
+		\subsubsection{Bandwidth intensive applications}
 		Some Tor users put more traffic on the network than they contribute by running a Onion Router.
-This means that these users are slowing the network down as they use more traffic than giving to the network.
+This means that these users are slowing the network down as they use more traffic than giving back.
 A possible solution for this is to throttle certain high-bandwidth protocols such as BitTorrent at exit nodes or at Onion Proxies.
 
-		Also, the Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
+		\subsubsection{Traffic capacity and contribution}
+		The Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
 By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
@@
 
+		\subsubsection{Load balanced path selection}
 		The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
@@
 
-		Another problem is that the Tor clients are not optimal at handling latency and connection failures.
+		\subsubsection{Latency and connection failure handling}
+		Tor clients are not optimal at handling latency and connection failures.
 For example, if extending a circuit fails, the entire circuit is abandoned.
@@
 
+		\subsubsection{Directory information overhead}
 		Much of the overhead of the network is in downloading the directory information.
 There is also overhead in the TLS connection between the nodes in the network.
-According to Dingledine et al, removing the empty TLS application record could reduce the overhead in the TCP/IP header by 6.3\%.
+According to Dingledine et al, removing the empty TLS application record could reduce the overhead in the TCP/IP header with 6.3\%.
 
@@
 A LOT ARE MORE SUITEABLE FOR THE CURRENT DECENTRALIZED SYSTEM SECTION) but so far, no anonymous, well-performing decentralized network has come up.
-This due to the many extra problems decentralization brings along with.
+This is due to the fact that there are many problems decentralization brings along with.
 
@@
 		Traffic analysis can be used to attack the anonymity of a user (a Tor client) browsing the web using Tor \cite{abbott2007browser}.
-By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.
+By misusing the exit policy of Tor one can reduce the time required to perform the analysis from $O(nk)$ to $O(n+k)$ where $n$ is the number of exit nodes and $k$ is the number of entry guards.\\
 
-		By running an HTTP exit node and a Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
-The exit node injects an invisible iframe containing some JavaScript into any web page that passes through it, each sending a unique ID to a malicious web server.
+		By running a HTTP exit node and an Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+The exit node injects an invisible iframe containing some JavaScript into the web pages that pass by, each sending a unique ID to a malicious web server.
 Every ten minutes the Tor client chooses a new circuit and eventually an unlucky Tor client picks and uses the malicious entry node that was placed in the network.
@@
 		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
-Disabling JavaScript does not mitigate this, because a similar attack can be set up only using the HTML meta refresh tag.
+A similar system can be set up only using the HTML meta refresh tag.
 To increase the odds of a user choosing the malicious exit node, one can run the exit node on unpopular ports.
-There are usually only a few exit nodes running on file sharing ports, such as 4661 to 4666.
+There are usually only a few exit nodes running on file sharing ports 4661 to 4666.
 Since Tor prefers older circuits, using a denial of service attack against the older exit nodes forces Tor into creating a circuit with the malicious exit node.
@@
 	\subsection{Low-Resource Routing attacks}
-		Another possible attack on the anonymity of tor is the so called \emph{low-resource routing attack} \cite{bauer2007low}.
-With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resources, thus compromising the anonymity Tor provides.
+		Another possible attack on the anonimity of tor is the so called \emph{low-resource routing attack} \cite{bauer2007low}.
+With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resourcing, thus comprimising the anonimy Tor provides.
 The idea of this attack is that a malicious Onion router can lie about it's bandwidth, thus advertising a much higher bandwidth than it actually has.
-Because of the Tor path selection algorithm that prefers high-bandwidth nodes, the chance that a malicious entry and exit node are chosen, is high.
+Because of the Tor path selection algorithm that prefers high-bandwidth nodes, the chance that a malicious entry node and exit node are chosen, is high.
 
-		Once a malicious entry and exit node have been chosen, an analysis of the traffic can be done to link Onion proxies with the web servers they communicates with.
-Experimental research in a test setting has shown that with an total of 66 non-malicious and 6 malicious nodes, is possible to compromise 46\% of the built circuits.
-At the request of the Tor community, this attack hasn't been tested on the live Tor network.
+		Once a malicious entry node and exit node has been chosen, an analysis of the traffic can be done to link Onion proxies with the webservers he communicates with.
+Experimental research on a testbed, has shown that with an total of 66 nodes and 6 malicious nodes, is possible to compromise 46\% of the built circuits.
+On request of the Tor community, this attack hasn't been tested on the live Tor network.
 There are some extensions and improvements to this attack.
-It is possible to perform a denial of service attack on well used entry nodes, forcing Tor clients to choose a new one.
-This improves the chance that a Tor client chooses a malicious entry node.
+It is possible to denial-of-service some of the well-used entry nodes, to force Tor clients to choose a new entry node, possibly a malicious one.
 
 		Bauer et al.
-proposed several solutions in their paper.
-The first one is to actually verify the resources of the nodes by, for example, measuring the bandwidth and/or uptime of a node.
-Bandwidth can be checked centralized or decentralized: the disadvantages of a centralized bandwidth check is that is generates much overhead on the network.
+proposed several solutions in his paper.
+The first one is to actually verify the resources of the nodes, for example, measuring the bandwidth and/or uptime of a node.
+Bandwidth can be checked centralized or decentralize: the disadvantages of a centralized bandwidth check, is that is generates much overhead on the network.
 With distributed bandwidth verification, Tor routers monitor each other but this is not enough to detect selective malicious nodes.
@@
 		A replay attack \cite{pries2008new} happens when a malicious entry node duplicates cells and send them again.
-Since Tor uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the circuit to be destroyed.
+Since Tor uses uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the connection to be torn down.
 
-		Using this, an accomplice exit router can therefore, in cooperation with the entry node, discover the sender and receiver's relationship.
+		Using this, an accomplice exit router can therefore in cooperation with the entry node discover the sender and receiver's relationship.
 On top of that, this attack can also be used as a denial of service attack.
-According to Pries et al., defending against this attack is quite challenging to solve and requires some further research.
+This attack is according to the authors quite challenging to solve and does require some further research.
 
@@
 
-	There are advantages to using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
+	There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
 When removing this central authority, these components needs to be spread across the peers in the network.
@@
 Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
-It is used in the circuit creation in Onion Routing (see section \ref{ss:tor_circuit}), for example.
-However, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable to a man-in-the-middle attack.
+Diffie-Hellman is for example used in the circuit setup in Onion Routing (see secion II-D), however, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable for a man-in-the-middle attack.
 This weakness makes it possible for an adversary to decrypt all message sent between the two parties.
@@
 		Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) \cite{backes2012ace}.
-This protocol uses telescoping, which means that the initiator negotiates session keys with each successive hop in the circuit.
+This protocol uses telescoping which means that the initiator negotiates session keys with each successive hop in the circuit.
 There are several proposals for more efficient key exchange methods.
-One of them is \emph{ACE}, a one-way authenticated key exchange protocol.
-The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and nearly 19\% on the side of the Onion Routers.
+One of them is \emph{ACE}, an one-way authenticated key exchange protocol.
+The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and an efficiency improvement of nearly 19\% on the side of the Onion Routers.
 ACE requires clients to send one extra element in the key exchange.
-This does not introduce any overhead however, because the element fits in the unused space in a cell.
+This however, does not introduce any overhead because the element fits in the unused space in a cell.
 
@@
 Each of these decentralized networks will be discussed in the next section.
-Note that we're only considering fully decentralized networks here, with the exception of Torsk (which is almost fully decentralized but still requires a Neighbourhood Authority).
+Note that we're only considering fully decentralized networks here.
 Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.
@@
 Another key is the Signed-Subspace key (SSK) which enables personal namespaces.
-This key contains a public and a private key.
-The private key is used to store the data and the public key is used in the queries for the file.
+This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file.
 The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.
@@
 To prevent looping of the requests, each request contains a random identifier.
-The peers that the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
+The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
 
@@
 Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
-Each node can be found in about $\log(n)$ steps.
+Each node can be found in about log(n) steps.
 
@@
 It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
-Additionally, MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
+Additionally MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
 
-		MIX networks are typically high latency and traffic in it moves slow.
+		MIX networks are typically high latency networks and traffic in it moves slow.
 Messages will have to be stored on a node until enough messages have arrived to start sending them out in a random order.
-Often, cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
+Often times cover traffic is used to generate enough messages for the network to obfuscate the real communication, which in turn generates a lot of bandwidth overhead.
 MorphMix has been developed as a low latency and high performance network.
@@
 	\subsection{Tribler} % 2008
-		Tribler is a social-based peer-to-peer file sharing system based on the BitTorrent protocol.
+		Tribler is a social-based peer-to-peer file sharing system based on the BiTtorrent protocol.
 \cite{pouwelse2008tribler}.
@@
 
-	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems\footnote{Found at https://github.com/redecentralize/alternative-internet}.
-For each of the listed systems, we have created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, (main) programming language, amount of commits, etc.
+	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems (available at https://github.com/redecentralize/alternative-internet).
+For each of the listed systems, we have created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, tags, (main) programming language, amount of commits, etc.
 This table is available on the same Github page.
@@
 	From this table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
-While there is a lot of research on decentralized systems, there is no system yet that can compete with Tor.
-The systems that do exist such as Tarzan, Torsk and Gnutella are getting some things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.
+While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor.
+The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.
 

### 2014-03-20 paper.tex

--- 2014-03-20 paper.tex
@@
 \hyphenation{op-tical net-works semi-conduc-tor}
+\newcommand{\xmark}{\sffamily x}
 
@@
 
+		\subsubsection{Directory information overhead}
 		Much of the overhead of the network is in downloading the directory information.
@@
 
-	\include{table}
-
 	In the last section, we discussed existing decentralized peer-to-peer networks.
@@
 This Github repository, including the table, is publicly available.
+
+	\begin{landscape}
+		\begin{table}[p]
+			\include{table}
+		\end{table}
+	\end{landscape}
 

### 2014-03-20 paper.tex
expanded conclusion
Added a bunch of fixes and rewritten the abstract.

@@
 \begin{abstract}
-	There are quite a few distributed anonymous communication networks such as Tor, yet when it comes to decentralized anonymous systems the numbers are rather small and certain problems arise.
+	In the emerging world of ubiquitous internet access void of any privacy there are a number of anonymous communication overlay networks whose aim is to provide privacy to its users.
+Due to the nature of the internet, there is major difficulty getting these networks to become both decentralized and anonymous.
+This technical report lists reasons for having anonymous networks, discerns the problems in achieving decentralization in anonymous networks and sums up the biggest competitors in the field and their current status.
+To do so, we use one exemplary network, the Tor network.
+We explain how Tor works, what vulnerabilities this network currently has, and possible attacks that could be used to violate privacy and anonymity.
+The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.
+	%There are quite a few distributed anonymous communication networks such as Tor, yet when it comes to decentralized anonymous systems the numbers are rather small and certain problems arise.
 In this technical report we explain how Tor works and which attacks are possible and which vulnerabilities currently exist in Tor.
@@
 In this paper we will analyze Tor and its semi-centralized nature.
-Furthermore we will look at attempts that have been made to decentralize Tor as well as several other decentralized systems.
+Decentralizing Tor isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us and only a few well-used decentralized peer-to-peer overlay networks are active such as Gnutella \cite{ripeanu2001peer}, Freenet \cite{lua2005survey} and Tapestry.
 
-	This paper is structured as following: In section \ref{sec:tor} we will give an introduction and overview of Tor.
+	This technical report is structured as following: In section \ref{sec:tor} we will give an introduction and overview of Tor.
 Known vulnerabilities in Tor are discussed in section \ref{sec:attacks}.
@@
 
-		While Tor guarantees anonymity, there are some disadvantages using it.
-The main disadvantage is that the Tor network is slow.
-According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data.
-
+		While Tor offers its users a high level of anonymity, there are some disadvantages using it.
 According to Dingledine et al \cite{dingledine2009performance}, there are six reasons why Tor is not optimal.
@@
 		The Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
+According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data.
 By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
-Incentives such as LIRA \cite{jansen13lira} could make more users run a Onion Router, thus increasing the capacity of the network and making it faster.
+Incentives such as LIRA \cite{jansen13lira} could make more users run an Onion Router, thus increasing the capacity of the network and making it faster.
 
@@
 
-		As we saw, the directory service generates overhead on the network.
+		The directory service generates overhead on the network.
+Replacing this central authority with a decentralized component, could reduce the overhead of the network and improve performance.
+Furthermore, it would alleviate a security concern.
+A malicious adversary could gain control of the directory server and force a connection through a set of colluding nodes.
+In a decentralized environment such an attack would be much more difficult.
+In conclusion, this means that we would like to see Tor decentralized.
+Although much research has been done on the decentralization of Tor, it still uses centralized components today.
+		%As we saw, the directory service generates overhead on the network.
 If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
@@
 
-		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified via matches.
+		By performing traffic analysis to compare the unique IDs of the web server and the circuits passing trough the entry node, a user can be identified.
 Disabling JavaScript does not mitigate this, because a similar attack can be set up only using the HTML meta refresh tag.
@@
 With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resources, thus compromising the anonymity Tor provides.
-The idea of this attack is that a malicious Onion router can lie about it's bandwidth, thus advertising a much higher bandwidth than it actually has.
+The idea of this attack is that a malicious Onion router can lie about its bandwidth, thus advertising a much higher bandwidth than it actually has.
 Because of the Tor path selection algorithm that prefers high-bandwidth nodes, the chance that a malicious entry and exit node are chosen, is high.
 
-		Once a malicious entry and exit node have been chosen, an analysis of the traffic can be done to link Onion proxies with the web servers they communicates with.
+		Once a malicious entry and exit node have been chosen, an analysis of the traffic can be done to link Onion proxies with the web servers they communicate with.
 Experimental research in a test setting has shown that with an total of 66 non-malicious and 6 malicious nodes, is possible to compromise 46\% of the built circuits.
@@
 The first one is to actually verify the resources of the nodes by, for example, measuring the bandwidth and/or uptime of a node.
-Bandwidth can be checked centralized or decentralized: the disadvantages of a centralized bandwidth check is that is generates much overhead on the network.
+Bandwidth can be checked centralized or decentralized: the disadvantage of a centralized bandwidth check is that it generates much overhead on the network.
 With distributed bandwidth verification, Tor routers monitor each other but this is not enough to detect selective malicious nodes.
@@
 
-		First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or the other, except under what he call "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify itself.
-This must be done within a small enough time frame that an attacker can't do this in sequence, but all nodes must do them in parallel.
+		First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or another.
+The exception to this rule is what he calls "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify themselves.
+This must be done within a small enough time frame, so that an attacker can't do this in sequence, but all nodes must do them in parallel.
 
@@
 	\subsection{Replay Attacks}
-		A replay attack \cite{pries2008new} happens when a malicious entry node duplicates cells and send them again.
+		A replay attack \cite{pries2008new} happens when a malicious entry node duplicates cells and sends them again.
 Since Tor uses the counter mode of Advanced Encryption Standard (AES-CTR) for encryption and decryption, the counter will be wrong when the duplicated package arrives causing the circuit to be destroyed.
 
-		Using this, an accomplice exit router can therefore, in cooperation with the entry node, discover the sender and receiver's relationship.
-On top of that, this attack can also be used as a denial of service attack.
-According to Pries et al., defending against this attack is quite challenging to solve and requires some further research.
+		Using this, an accomplice exit router can, in cooperation with the entry node, discover the sender and receiver's relationship.
+This attack can also be used as a denial of service attack.
+According to Pries et al., defending against this attack is quite challenging to solve and requires further research.
 
@@
 
-	As we saw in section \ref{sec:tor}, we would like to have a decentralized anonymous network.
-This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us.
-Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella \cite{ripeanu2001peer}, Freenet \cite{lua2005survey} and Tapestry.
-These networks will be described in more detail in the next chapter.
-Among these networks are some overlay anonymous networks such as Tarzan.
-
 	There are advantages to using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
@@
 In this section we will explain the various problems that are involved when decentralizing Tor.
-In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
 
@@
 		Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
-stated that this indeed is still an open problem.
-With decentralized systems, there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network.
+stated that this is indeed still an open problem.
+With decentralized systems, there is no central directory server to tell a new node where to locate neighbors.
 Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.
-Some of these issues can be found in the last section when comparing these systems.
 
@@
 10.0.0.0/8 or 192.168.0.0/16).
-
 When a local device sends a packet to the internet, the router replaces these private addresses, including the source ports, with its own public address before forwarding it to the internet.
@@
 
-		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network.
+		Rahman \cite{rahman2009survey} proposes several options to build incentives in a peer-to-peer network.
 The first proposal that is described is the so called \emph{Warm-glow Model}.
@@
 These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity.
-The formal are more suitable for longer relationships between peers.
+The former are more suitable for longer relationships between peers.
 The latter is more scalable but they rely on third party and must handle trust issues themselves.
@@
 	\subsection{Key exchange}
-		With a decentralized network, using a centralized authority for managing the keys, is not possible.
+		With a decentralized network, using a centralized authority for managing the keys is not possible.
 This means that for secure communication, peers have to exchange the keys directly with each other, without a trusted party between them.
@@
 
-	Many other decentralized peer-to-peer networks have been proposed and some have been implemented \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}.
+	Many decentralized peer-to-peer networks have been proposed and some have been implemented \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}.
 Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
@@
 	\subsection{Tribler} % 2008
-		Tribler is a social-based peer-to-peer file sharing system based on the BitTorrent protocol.
-\cite{pouwelse2008tribler}.
+		Tribler is a social-based peer-to-peer file sharing system based on the BitTorrent protocol \cite{pouwelse2008tribler}.
 Tribler considers social phenomena and the sense of community as important parts of file sharing.
@@
 
-		Although not an anonymization network, Tribler does accomplish a lot on decentralization.
+		Although not an anonymization network, Tribler does accomplish a lot on the topic of decentralization.
 The BuddyCast protocol uses BitTorrent infohashes to spread information completely decentralized throughout the network.

### 2014-03-20 paper.tex
Fixed typos in abstract

@@
 \begin{abstract}
-	In the emerging world of ubiquitous internet access void of any privacy there are a number of anonymous communication overlay networks whose aim is to provide privacy to its users.
-Due to the nature of the internet, there is major difficulty getting these networks to become both decentralized and anonymous.
+	In the emerging world of ubiquitous internet access void of any privacy there are a number of anonymous communication overlay networks whose aim it is to provide privacy to its users.
+Due to the nature of the internet, there is major difficulty in getting these networks to become both decentralized and anonymous.
 This technical report lists reasons for having anonymous networks, discerns the problems in achieving decentralization in anonymous networks and sums up the biggest competitors in the field and their current status.
@@
 Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
-Each of these decentralized networks will be discussed in the next section.
+Each of these decentralized networks will be discussed in this section.
 Note that we're only considering fully decentralized networks here, with the exception of Torsk (which is almost fully decentralized but still requires a Neighbourhood Authority).
@@
 	While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
+We hope our effort by expanding the list of decentralized systems acts as an extra motivation to perform further research on this topic.
 

### 2014-03-20 table.tex
Table header
Added info about morphmix, salsa and tribler. Also renamed torks to torsk
Make the table more uniform

@@
-\begin{landscape}
-
 \begin{center}
-    \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{1.6cm} | p{2.2cm} | p{2.2cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2cm} | }
+    \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | }
   		\caption{A comparison of decentralized peer-to-peer overlay networks} \\ \hline
-	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{Secure against DDoS attack} & \textbf{Secure against Sybil Attack} & \textbf{Secure against man-in-the-middle attack} & \textbf{Provides anonymity} \\ \hline
+	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{(D)DoS protection} & \textbf{Sybil attack protection} & \textbf{MITM protection} & \textbf{Provides anonymity} \\ \hline
 		\endfirsthead
-		\multicolumn{7}{c}{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\ \hline
-	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{Attack resistance} & \textbf{Provides anonymity} \\ \hline
-		\endhead
-		\hline \multicolumn{7}{r}{\textit{Continued on next page}} \\
-		\endfoot
-		\hline
-		\endlastfoot
 
@@
 		Pastry & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \xmark \\ \hline
-		Anonymizing peer-to-peer proxy (AP3) & 2004 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
+		AP3 & 2004 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
 		Tarzan & 2002 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
@@
 \end{center}
-
-\end{landscape}

### 2014-03-20 paper.tex
Indents fixed
abstract is now a bit more clear :p

@@
 \begin{abstract}
-	In the emerging world of ubiquitous internet access void of any privacy there are a number of anonymous communication overlay networks whose aim it is to provide privacy to its users.
+	In the emerging world of ubiquitous internet access, void of any privacy, there are a number of anonymous communication overlay networks whose aim it is to provide privacy to its users.
 Due to the nature of the internet, there is major difficulty in getting these networks to become both decentralized and anonymous.
@@
 Although much research has been done on the decentralization of Tor, it still uses centralized components today.
-		%As we saw, the directory service generates overhead on the network.
-If we could replace this central authority, we could reduce the overhead of the network and improve the performance.
-This means, we would like to have Tor decentralized.
-Many research has been done already on the decentralization of Tor \cite{wang2012octopus, alsabah2013pctcp} (WHICH CITES CAN BE ADDED HERE?
-A LOT ARE MORE SUITEABLE FOR THE CURRENT DECENTRALIZED SYSTEM SECTION) but so far, no anonymous, well-performing decentralized network has come up.
-This due to the many extra problems decentralization brings along with.
 

### 2014-03-20 paper.tex
Fixed typo
changed certs to certificates

@@
 There are several proposals for more efficient key exchange methods.
-One of them is \emph{ACE}, a one-way authenticated key exchange protocol.
+One of them is \emph{ACE}, an one-way authenticated key exchange protocol.
 The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and nearly 19\% on the side of the Onion Routers.
@@
 		The Myrmic DHT runs on top of Kademlia, and introduces the Neighbourhood Authority.
-This authority issues certs to nodes that participate in the DHT, but it does not participate in the DHT itself.
+This authority issues certificates to nodes that participate in the DHT, but it does not participate in the DHT itself.
 The NA makes this solution not a fully decentralized one, but its role is a lot smaller than the current Directory Servers.

### 2014-03-20 paper.tex
Some sentence restructuring in the conclusion for more clarity.

--- 2014-03-20 paper.tex
@@
 
-	From this table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
-While there is a lot of research on decentralized systems, there is no system yet that can compete with Tor.
-The systems that do exist such as Tarzan, Torsk and Gnutella are getting some things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.
+	From the decentralization table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
+While a lot of research has been done on decentralized systems, there is no system yet that can compete with Tor.
+Decentralized systems that do exist such as Tarzan, Torsk or Gnutella, show promising attempts to decentralize and anonymize the internet.
+Yet each of these systems either lacks in performance or is vulnerable to some type of attack.
 

### 2014-03-21 alternative-internet-crawler/generate_tables.py
- instead of unknown

@@ -93,7 +93,7 @@ def get_markdown_table_entry(columns, project, add_links):
         try:
             entry.append(format_functions[key](project[key], add_links))
         except:
-            entry.append(project[key] if key in project.keys() and not project[key] is None else 'unknown')
+            entry.append(project[key] if key in project.keys() and not project[key] is None else '-')
 
     return '%s%s%s\n' % ('| ', ' | '.join(entry), ' |')
 

### 2014-03-21 alternative-internet-crawler/generate_tables.py
Add age column

@@ -81,12 +81,22 @@ def get_markdown_table_entry_format_name(entry):
     return '[%s](README.md#%s)' % (entry, project_anchor)
 
 
+def get_markdown_table_entry_format_timedelta(td):
+    sday = 60 * 60 * 24  # one day
+    if td.total_seconds() < sday * 30:  # ~one month
+        return '<1 month'
+    elif td.total_seconds() < sday * 356:  # ~one year
+        return '%s month(s)' % int(td.total_seconds() / (sday * 30))
+    else:
+        return '%s year(s)' % int(td.total_seconds() / (sday * 356))
+
 def get_markdown_table_entry(columns, project, add_links):
     format_functions = {'name': lambda s, l: get_markdown_table_entry_format_name(s) if l else s,
                         'updated_at': lambda s, l: datetime.strptime(s, '%Y-%m-%dT%H:%M:%SZ').strftime('%Y-%m-%d'),
                         'total_contributor_count': lambda s, l: '%s contributor(s)' % s,
                         'total_commit_count': lambda s, l: '%s commit(s)' % s,
-                        'total_code_lines': lambda s, l: '<{:,} K'.format(1) if (int(s) / 1000) <= 1 else '{:,} K'.format(int(s) / 1000)}
+                        'total_code_lines': lambda s, l: '<{:,} K'.format(1) if (int(s) / 1000) <= 1 else '{:,} K'.format(int(s) / 1000),
+                        'min_month': lambda s, l: '%s' % get_markdown_table_entry_format_timedelta(datetime.utcnow() - datetime.strptime(s, '%Y-%m-%dT%H:%M:%SZ'))}
 
     entry = []
     for key in columns.keys():
@@ -138,9 +148,9 @@ def write_output(projects, table_columns, output='readme.md', sort_on='name', so
 
 
 def run_parser(directory='projects', output='readme.md', sort_on='name', sort_reverse=False, add_links=False, generate_all=False):
-    table_columns = OrderedDict([('name', 'Name'), ('main_language', 'Language'), ('updated_at', 'Last activity'),
-                                 ('total_code_lines', 'LOC'), ('total_commit_count', 'Commits'),
-                                 ('total_contributor_count', 'Contributors')])
+    table_columns = OrderedDict([('name', 'Name'), ('main_language', 'Language'), ('min_month', 'Age'),
+                                 ('updated_at', 'Last activity'), ('total_code_lines', 'LOC'),
[…]

### 2014-03-21 alternative-internet-crawler/generate_tables.py
Specify default reverse columns

@@ -152,14 +152,19 @@ def run_parser(directory='projects', output='readme.md', sort_on='name', sort_re
                                  ('updated_at', 'Last activity'), ('total_code_lines', 'LOC'),
                                  ('total_commit_count', 'Commits'), ('total_contributor_count', 'Contributors')])
 
+    table_columns_default_reverse = ['updated_at', 'total_code_lines', 'total_commit_count', 'total_contributor_count']
+
     projects = get_projects(directory)
     logging.info('Loaded %s projects' % len(projects))
 
     if generate_all:
         for key in table_columns.keys():
-            write_output(projects=projects, table_columns=table_columns, output='TABLE_%s.md' % table_columns[key].upper().replace(' ', '_'), sort_on=key, sort_reverse=(not (key == 'name' or key == 'main_language')), add_links=add_links)
+            write_output(projects=projects, table_columns=table_columns,
+                         output='TABLE_%s.md' % table_columns[key].upper().replace(' ', '_'), sort_on=key,
+                         sort_reverse=(key in table_columns_default_reverse), add_links=add_links)
     else:
-        write_output(projects=projects, table_columns=table_columns, output=output, sort_on=sort_on, sort_reverse=sort_reverse, add_links=add_links)
+        write_output(projects=projects, table_columns=table_columns, output=output, sort_on=sort_on,
+                     sort_reverse=sort_reverse, add_links=add_links)
 
 
 def main():

### 2014-03-21 alternative-internet-crawler/generate_tables.py
Add comma seperator for commit and contribute count of 1,000 and over

@@ -93,8 +93,8 @@ def get_markdown_table_entry_format_timedelta(td):
 def get_markdown_table_entry(columns, project, add_links):
     format_functions = {'name': lambda s, l: get_markdown_table_entry_format_name(s) if l else s,
                         'updated_at': lambda s, l: datetime.strptime(s, '%Y-%m-%dT%H:%M:%SZ').strftime('%Y-%m-%d'),
-                        'total_contributor_count': lambda s, l: '%s contributor(s)' % s,
-                        'total_commit_count': lambda s, l: '%s commit(s)' % s,
+                        'total_contributor_count': lambda s, l: '{:,} contributor(s)'.format(int(s)),
+                        'total_commit_count': lambda s, l: '{:,} commit(s)'.format(int(s)),
                         'total_code_lines': lambda s, l: '<{:,} K'.format(1) if (int(s) / 1000) <= 1 else '{:,} K'.format(int(s) / 1000),
                         'min_month': lambda s, l: '%s' % get_markdown_table_entry_format_timedelta(datetime.utcnow() - datetime.strptime(s, '%Y-%m-%dT%H:%M:%SZ'))}
 

### 2014-03-21 paper.tex
Add I2P to conclusion (lot of checkmarks)

@@
 	In the last section, we discussed existing decentralized peer-to-peer networks.
-In this section we will make a comparison between these networks.
+In this section we will make a comparison between these networks, as seen in table \ref{tbl:comparison}.
 For each network, we will explain the following features:
@@
 		\begin{table}[p]
+			\centering
 			\include{table}
+			\caption{A comparison of decentralized peer-to-peer overlay networks}
+			\label{tbl:comparison}
 		\end{table}
@@
 While a lot of research has been done on decentralized systems, there is no system yet that can compete with Tor.
-Decentralized systems that do exist such as Tarzan, Torsk or Gnutella, show promising attempts to decentralize and anonymize the internet.
+Decentralized systems that do exist such as Tarzan, I2P, Torsk or Gnutella, show promising attempts to decentralize and anonymize the internet.
 Yet each of these systems either lacks in performance or is vulnerable to some type of attack.

### 2014-03-21 table.tex
Replaced a bunch of question marks in the table, still a few left

@@
-\begin{center}
-    \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | }
-  		\caption{A comparison of decentralized peer-to-peer overlay networks} \\ \hline
-	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{(D)DoS protection} & \textbf{Sybil attack protection} & \textbf{MITM protection} & \textbf{Provides anonymity} \\ \hline
-		\endfirsthead
+\begin{tabular}[p]{| l | l | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} |}
+	\hline
+	\textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in \newline practice} & \textbf{(D)DoS protection} & \textbf{Sybil attack protection} & \textbf{MITM \newline protection} & \textbf{Provides \newline anonymity} \\ \hline
 
@@
 	AP3 & 2004 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
-		Tarzan & 2002 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
-		MorphMix & 2002 & \xmark & \checkmark & ? & ? & ? & ? & \checkmark \\ \hline
-		I2P & 2003 & \xmark & \checkmark & \checkmark & ? & ? & ? & \checkmark\\ \hline
-		Salsa & 2006 & \xmark & ? & ? & ? & ? & ? & ?\\ \hline
-		Tribler & 2008 & \xmark & \checkmark & \checkmark & ? & ? & ? & \xmark \\ \hline
-		Torks & 2009 & \checkmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
-		NISAN & 2009 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
-    \end{longtable}
-\end{center}
+	Tarzan & 2002 & \xmark & \xmark & \xmark & ? & \checkmark & ? & \checkmark \\ \hline
+	MorphMix & 2002 & \xmark & \checkmark & \xmark & \checkmark & \xmark & ? & \checkmark \\ \hline
+	I2P & 2003 & \xmark & \checkmark & \checkmark & \checkmark & \checkmark & ? & \checkmark\\ \hline
+	Salsa & 2006 & \xmark & \xmark & \xmark & \checkmark & \checkmark & ? & \checkmark \\ \hline
+	Tribler & 2008 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \xmark \\ \hline
+	Torsk & 2009 & \checkmark & \xmark & \xmark & \checkmark & \checkmark & \checkmark & \checkmark \\ \hline
+	NISAN & 2009 & \xmark & \xmark & \xmark & ? & ? & \checkmark & \checkmark \\ \hline		
+\end{tabular}

### 2014-03-22 paper.tex
changes to 4 and 5
with respect to last meeting!

@@
 
-	There are advantages to using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
+	Decentralizing systems comes with a variety of problems.
+The most important reason why one would decentralize are security and anonymity.
+When having a central authority this authority can be used for bootstrapping, key management and to manage the reputation of the users, but if one of these authorities were taken control of, security of the anonymity could be compromised.
 When removing this central authority, these components needs to be spread across the peers in the network.
 In this section we will explain the various problems that are involved when decentralizing Tor.
-
-	\subsection{Bootstrapping new nodes}
-		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be a starting point where this new node can discover neighbors in the network to connect with.
-In Tor, a directory server can tell the new node what his neighbors are and where to find them \cite{dingledine2004tor}.
-
-		Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
-stated that this is indeed still an open problem.
-With decentralized systems, there is no central directory server to tell a new node where to locate neighbors.
-Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.
-
-	\subsection{NAT traversal}
-		A truly decentralized system requires the participating nodes to have direct connection to each other.
-Because of the limited availability of IPv4 network addresses, most consumer grade internet connections only provide one network address per subscriber, shared by all the devices connected to the subscribers network using Network Address Translation (NAT).
-With IPv4 network addresses getting more scarce, some Internet Service Providers even put more than one subscribers behind a single network address, using a carrier-grade NAT.
-
-		A NAT-based system works by creating a local, private network which a NAT-enabled router connects to the internet.
-The local network uses network addresses from the private ranges (e.g.
-10.0.0.0/8 or 192.168.0.0/16).
-When a local device sends a packet to the internet, the router replaces these private addresses, including the source ports, with its own public address before forwarding it to the internet.
-It saves these translations in a local table.
-Once it receives packets, it looks in this table and replaces the public network address and port with the associated private network address and port.
-If no corresponding entry exists in the routers table, the packet is dropped.
-This means that when contacting a device behind a NAT, there must be an existing entry in this table.
-
-		There are several techniques to add an entry to the routers NAT table.
-Universal Plug and Play (UPnP) is one of those techniques, where the local device uses a HTTP request to the router to associate a port with the devices private network address.
-This technique is not available everywhere and sometimes considered a security risk.
-Different implementations of NAT require different techniques, such as \textit{hole punching}, \textit{relaying} or \textit{reversal}, as described by Wocker et al.
-\cite{wacker2008nat}.
 
@@
 
+			\subsection{NAT traversal}
+		A truly decentralized system requires the participating nodes to have direct connection to each other.
+Because of the limited availability of IPv4 network addresses, most consumer grade internet connections only provide one network address per subscriber, shared by all the devices connected to the subscribers network using Network Address Translation (NAT).
+With IPv4 network addresses getting more scarce, some Internet Service Providers even put more than one subscribers behind a single network address, using a carrier-grade NAT.
+
+		A NAT-based system works by creating a local, private network which a NAT-enabled router connects to the internet.
+The local network uses network addresses from the private ranges (e.g.
+10.0.0.0/8 or 192.168.0.0/16).
+When a local device sends a packet to the internet, the router replaces these private addresses, including the source ports, with its own public address before forwarding it to the internet.
+It saves these translations in a local table.
+Once it receives packets, it looks in this table and replaces the public network address and port with the associated private network address and port.
+If no corresponding entry exists in the routers table, the packet is dropped.
+This means that when contacting a device behind a NAT, there must be an existing entry in this table.
+
+		There are several techniques to add an entry to the routers NAT table.
+Universal Plug and Play (UPnP) is one of those techniques, where the local device uses a HTTP request to the router to associate a port with the devices private network address.
+This technique is not available everywhere and sometimes considered a security risk.
+Different implementations of NAT require different techniques, such as \textit{hole punching}, \textit{relaying} or \textit{reversal}, as described by Wocker et al.
+\cite{wacker2008nat}.
+
+	\subsection{Bootstrapping new nodes}
+		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be a starting point where this new node can discover neighbors in the network to connect with.
+In Tor, a directory server can tell the new node what his neighbors are and where to find them \cite{dingledine2004tor}.
+
+		Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
+stated that this is indeed still an open problem.
+With decentralized systems, there is no central directory server to tell a new node where to locate neighbors.
+Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.
+
 	\subsection{Key exchange}
@@
 
-\section{Current decentralized systems}
+\section{Decentralized privacy enhancing systems}
 	\label{sec:decentralized}
 
-	Many decentralized peer-to-peer networks have been proposed and some have been implemented \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}.
-Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
-Each of these decentralized networks will be discussed in this section.
+	Many decentralized peer-to-peer networks have been proposed, yet only some have been implemented and are currently in use and still actively maintained \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}.
+In this section, some popular peer-to-peer overlay networks are discussed.
+Most of these networks are used in practice and can be used to compare Tor with.
 Note that we're only considering fully decentralized networks here, with the exception of Torsk (which is almost fully decentralized but still requires a Neighbourhood Authority).

### 2014-03-22 paper.tex
changed conclusion

@@
 
-	In this technical report we explained how Tor works and which components define a Tor network.
+	We explained how Tor works and which components define a Tor network.
 Furthermore, we looked at the main disadvantages and problems Tor is currently facing.
@@
 
-	From the decentralization table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
+	From table \ref{tbl:comparison}, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
 While a lot of research has been done on decentralized systems, there is no system yet that can compete with Tor.

### 2014-03-23 paper.tex
Added a subsection about the content on tor

@@
 Although much research has been done on the decentralization of Tor, it still uses centralized components today.
+
+		\subsection{The content on Tor}
+			The anonymous communication with Tor can also be used for distribution illegal content or setting up illegal services.
+Illegal content and services such as drugs trading or child pornography, is a serious problem Tor is facing.
+A recent example is the shutdown of \emph{Silk Road}, an online market for trading drugs.
+This market operated as a hidden Tor service.
+These hidden services are accessed through their onion address and not through their IP-address, hiding the physical location of the service.
+This makes it very hard for agencies to track and shut down these operations.
+
+			The illegal content travels unencrypted through a Tor exit node.
+Users running a Tor exit node, could be held responsible for distributing illegal content.
+A possible solution could be to filter the illegal content from the legal content.
+While content filtering is a viable solution, not many research has been done on it.
+It is also an open question whether filtering content is in line with the principles of Tor and the internet.
 

### 2014-03-23 paper.tex
Improved the section on 'Tor stinks' and added a reference

@@
 
-		\subsection{The content on Tor}
+		\subsection{Tor stinks}
 			The anonymous communication with Tor can also be used for distribution illegal content or setting up illegal services.
-Illegal content and services such as drugs trading or child pornography, is a serious problem Tor is facing.
+Illegal content and services is a serious problem Tor is facing.
 A recent example is the shutdown of \emph{Silk Road}, an online market for trading drugs.
@@
 
+			A recent research on the content and popularity analysis of Tor hidden services \cite{biryukov2013content} has shown that although there are Tor hidden services that distributes illegal content, many hidden services are however resources devoted to human rights, freedom of speech and information which is prohibited in some countries.
+It is not clear which type of service is more popular on Tor.
+
 			The illegal content travels unencrypted through a Tor exit node.
 Users running a Tor exit node, could be held responsible for distributing illegal content.
+The possibility of redirecting illegal content, refrains users from running an exit node.
 A possible solution could be to filter the illegal content from the legal content.
-While content filtering is a viable solution, not many research has been done on it.
-It is also an open question whether filtering content is in line with the principles of Tor and the internet.
+While content filtering is a viable solution, it is an open question whether filtering content is in line with the principles of Tor and the internet.
+We think however that filtering the content on Tor, could make more users run an exit node and thus improve the quality of the network.
 

### 2014-03-23 paper.tex
itemized 2.5.1 - 2.5.6

@@
 
-		\subsubsection{Congestion control}
+		\begin{itemize}
+
+			\item
 				Tor's congestion control does not work well.
@@
 
-		\subsubsection{Bandwidth intensive applications}
+			\item
 			Some Tor users put more traffic on the network than they contribute by running a Onion Router.
@@
 
-		\subsubsection{Traffic capacity and contribution}
+			\item
 				The Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
@@
 
-		\subsubsection{Load balanced path selection}
+			\item
 				The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
@@
 
-		\subsubsection{Latency and connection failure handling}
+			\item
 				Tor clients are not optimal at handling latency and connection failures.
@@
 
-		\subsubsection{Directory information overhead}
+			\item
 				Much of the overhead of the network is in downloading the directory information.
@@
 Although much research has been done on the decentralization of Tor, it still uses centralized components today.
+
+		\end{itemize}
 
@@
 
-	We explained how Tor works and which components define a Tor network.
+	We explained how the leading privacy enhancing technology Tor works and which components define a Tor network.
 Furthermore, we looked at the main disadvantages and problems Tor is currently facing.

### 2014-03-23 paper.tex
table change and changed multiple @ sybil
Processed feedback for abstract and introduction

--- 2014-03-23 paper.tex
@@
 \begin{abstract}
-	In the emerging world of ubiquitous internet access, void of any privacy, there are a number of anonymous communication overlay networks whose aim it is to provide privacy to its users.
+	Ever since the introduction of the internet, it has been void of any privacy.
+A number of anonymous communication overlay networks exist whose aim it is to provide privacy to its users.
+However, due to the nature of the internet, there is major difficulty in getting these networks to become both decentralized and anonymous.
+We list reasons for having anonymous networks, discern the problems in achieving decentralization and sum up the biggest initiatives in the field and their current status.
+To do so, we use one exemplary network, the Tor network.
+We explain how Tor works, what vulnerabilities this network currently has, and possible attacks that could be used to violate privacy and anonymity.
+The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.
+
+	%In the emerging world of ubiquitous internet access, void of any privacy, there are a number of anonymous communication overlay networks whose aim it is to provide privacy to its users.
 Due to the nature of the internet, there is major difficulty in getting these networks to become both decentralized and anonymous.
@@
 The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.
+
 	%There are quite a few distributed anonymous communication networks such as Tor, yet when it comes to decentralized anonymous systems the numbers are rather small and certain problems arise.
@@
 \section{Introduction}
-	With the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate.
-In many cases however, internet usage is either censored or monitored by third parties.
-In recent years the need for anonymous internet communication has become more apparent.
+	All feelings of privacy on telephones, mobile phones or the internet is an illusion.
+In recent years the need for privacy enhancing technology has become more apparent.
 Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.
@@
 One of the most important factors that impact anonymity in a communication system is the number of users.
-A sufficiently large numbers of users are required for the system to make guarantees about its ability to conceal and hide users' communication.
+A sufficiently large numbers of users are required for a system to make guarantees about its ability to protect the privacy of its users.
 This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
-Another important factor that impacts the anonymity of the system is decentralization.
-Whenever a network has centralized components and a malicious third party gains control over these components, the functionality and perhaps even the anonymity of the system is compromised.
+To support a large number of users, such a network has to be decentralized.
+A lack of decentralization would otherwise result in bottlenecks that places constraints on the number of users that can be active.
 
@@
 In this paper we will analyze Tor and its semi-centralized nature.
-Decentralizing Tor isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us and only a few well-used decentralized peer-to-peer overlay networks are active such as Gnutella \cite{ripeanu2001peer}, Freenet \cite{lua2005survey} and Tapestry.
+Decentralizing Tor isn't an easy task: After 15 years of decentralization attempts, the network is still centralized.
+Only few decentralized alternatives to Tor exist, however they lack the userbase to be considered safe and useful.
+Examples include Gnutella \cite{ripeanu2001peer}, Freenet \cite{lua2005survey} and Tapestry.
 
@@
 
-		\subsection{The content on Tor}
-			The anonymous communication with Tor can also be used for distribution illegal content or setting up illegal services.
-Illegal content and services such as drugs trading or child pornography, is a serious problem Tor is facing.
-A recent example is the shutdown of \emph{Silk Road}, an online market for trading drugs.
-This market operated as a hidden Tor service.
-These hidden services are accessed through their onion address and not through their IP-address, hiding the physical location of the service.
-This makes it very hard for agencies to track and shut down these operations.
-
-			The illegal content travels unencrypted through a Tor exit node.
-Users running a Tor exit node, could be held responsible for distributing illegal content.
-A possible solution could be to filter the illegal content from the legal content.
-While content filtering is a viable solution, not many research has been done on it.
-It is also an open question whether filtering content is in line with the principles of Tor and the internet.
-
 \section{Tor vulnerabilities and attacks}
@@
 
-	Decentralizing systems comes with a variety of problems.
-The most important reason why one would decentralize are security and anonymity.
-When having a central authority this authority can be used for bootstrapping, key management and to manage the reputation of the users, but if one of these authorities were taken control of, security of the anonymity could be compromised.
+	There are advantages to using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users.
 When removing this central authority, these components needs to be spread across the peers in the network.
 In this section we will explain the various problems that are involved when decentralizing Tor.
+
+	\subsection{Bootstrapping new nodes}
+		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be a starting point where this new node can discover neighbors in the network to connect with.
+In Tor, a directory server can tell the new node what his neighbors are and where to find them \cite{dingledine2004tor}.
+
+		Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
+stated that this is indeed still an open problem.
+With decentralized systems, there is no central directory server to tell a new node where to locate neighbors.
+Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.
+
+	\subsection{NAT traversal}
+		A truly decentralized system requires the participating nodes to have direct connection to each other.
+Because of the limited availability of IPv4 network addresses, most consumer grade internet connections only provide one network address per subscriber, shared by all the devices connected to the subscribers network using Network Address Translation (NAT).
+With IPv4 network addresses getting more scarce, some Internet Service Providers even put more than one subscribers behind a single network address, using a carrier-grade NAT.
+
+		A NAT-based system works by creating a local, private network which a NAT-enabled router connects to the internet.
+The local network uses network addresses from the private ranges (e.g.
+10.0.0.0/8 or 192.168.0.0/16).
+When a local device sends a packet to the internet, the router replaces these private addresses, including the source ports, with its own public address before forwarding it to the internet.
+It saves these translations in a local table.
+Once it receives packets, it looks in this table and replaces the public network address and port with the associated private network address and port.
+If no corresponding entry exists in the routers table, the packet is dropped.
+This means that when contacting a device behind a NAT, there must be an existing entry in this table.
+
+		There are several techniques to add an entry to the routers NAT table.
+Universal Plug and Play (UPnP) is one of those techniques, where the local device uses a HTTP request to the router to associate a port with the devices private network address.
+This technique is not available everywhere and sometimes considered a security risk.
+Different implementations of NAT require different techniques, such as \textit{hole punching}, \textit{relaying} or \textit{reversal}, as described by Wocker et al.
+\cite{wacker2008nat}.
 
@@
 
-			\subsection{NAT traversal}
-		A truly decentralized system requires the participating nodes to have direct connection to each other.
-Because of the limited availability of IPv4 network addresses, most consumer grade internet connections only provide one network address per subscriber, shared by all the devices connected to the subscribers network using Network Address Translation (NAT).
-With IPv4 network addresses getting more scarce, some Internet Service Providers even put more than one subscribers behind a single network address, using a carrier-grade NAT.
-
-		A NAT-based system works by creating a local, private network which a NAT-enabled router connects to the internet.
-The local network uses network addresses from the private ranges (e.g.
-10.0.0.0/8 or 192.168.0.0/16).
-When a local device sends a packet to the internet, the router replaces these private addresses, including the source ports, with its own public address before forwarding it to the internet.
-It saves these translations in a local table.
-Once it receives packets, it looks in this table and replaces the public network address and port with the associated private network address and port.
-If no corresponding entry exists in the routers table, the packet is dropped.
-This means that when contacting a device behind a NAT, there must be an existing entry in this table.
-
-		There are several techniques to add an entry to the routers NAT table.
-Universal Plug and Play (UPnP) is one of those techniques, where the local device uses a HTTP request to the router to associate a port with the devices private network address.
-This technique is not available everywhere and sometimes considered a security risk.
-Different implementations of NAT require different techniques, such as \textit{hole punching}, \textit{relaying} or \textit{reversal}, as described by Wocker et al.
-\cite{wacker2008nat}.
-
-	\subsection{Bootstrapping new nodes}
-		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be a starting point where this new node can discover neighbors in the network to connect with.
-In Tor, a directory server can tell the new node what his neighbors are and where to find them \cite{dingledine2004tor}.
-
-		Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
-stated that this is indeed still an open problem.
-With decentralized systems, there is no central directory server to tell a new node where to locate neighbors.
-Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.
-
 	\subsection{Key exchange}
@@
 
-\section{Decentralized privacy enhancing systems}
+\section{Current decentralized systems}
 	\label{sec:decentralized}
 
-	Many decentralized peer-to-peer networks have been proposed, yet only some have been implemented and are currently in use and still actively maintained \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}.
-In this section, some popular peer-to-peer overlay networks are discussed.
-Most of these networks are used in practice and can be used to compare Tor with.
+	Many decentralized peer-to-peer networks have been proposed and some have been implemented \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}.
+Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan.
+Each of these decentralized networks will be discussed in this section.
 Note that we're only considering fully decentralized networks here, with the exception of Torsk (which is almost fully decentralized but still requires a Neighbourhood Authority).
@@
 
-	We explained how Tor works and which components define a Tor network.
+	In this technical report we explained how Tor works and which components define a Tor network.
 Furthermore, we looked at the main disadvantages and problems Tor is currently facing.
@@
 
-	From table \ref{tbl:comparison}, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
+	From the decentralization table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
 While a lot of research has been done on decentralized systems, there is no system yet that can compete with Tor.

### 2014-03-23 paper.tex

--- 2014-03-23 paper.tex
@@
 	\subsection{Sybil attacks}
-		The Sybil attack is an attack where a single attacker represents itself as multiple nodes in a peer-to-peer system.
+		The Sybil attack is an attack where a single attacker represents itself as millions of nodes in a peer-to-peer system.
 Abusing this, the attacker is able to propagate false assumptions about the network to other nodes.

### 2014-03-23 table.tex

@@
 	\hline
-	\textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in \newline practice} & \textbf{(D)DoS protection} & \textbf{Sybil attack protection} & \textbf{MITM \newline protection} & \textbf{Provides \newline anonymity} \\ \hline
+	\textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in \newline practice} & \textbf{(D)DoS protection} & \textbf{Sybil attack protection} & \textbf{MITM \newline protection} & \textbf{Unlinkability} \\ \hline
 

### 2014-03-23 paper.tex
Moved text out of itemize that didn't belong and improved the introduction

@@
 \section{Introduction}
-	All feelings of privacy on telephones, mobile phones or the internet is an illusion.
+	All feelings of privacy on the internet, telephones or mail is an illusion.
 In recent years the need for privacy enhancing technology has become more apparent.
@@
 
-	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and are being used in practice.
+	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and only one is actively being used in practice.
 One of the most important factors that impact anonymity in a communication system is the number of users.
-A sufficiently large numbers of users are required for a system to make guarantees about its ability to protect the privacy of its users.
+A sufficiently large numbers of users is required for a system to make guarantees about its ability to protect the privacy of its users.
 This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
 To support a large number of users, such a network has to be decentralized.
-A lack of decentralization would otherwise result in bottlenecks that places constraints on the number of users that can be active.
+A lack of decentralization would otherwise result in bottlenecks that place constraints on the number of users.
 
@@
 
+		\end{itemize}
+
 		The directory service generates overhead on the network.
 Replacing this central authority with a decentralized component, could reduce the overhead of the network and improve performance.
-Furthermore, it would alleviate a security concern.
-A malicious adversary could gain control of the directory server and force a connection through a set of colluding nodes.
-In a decentralized environment such an attack would be much more difficult.
 In conclusion, this means that we would like to see Tor decentralized.
 Although much research has been done on the decentralization of Tor, it still uses centralized components today.
-
-		\end{itemize}
 

### 2014-03-24 paper.tex
Added more fixes for introduction, abstract and Tor chapter

@@
 \section{Introduction}
-	All feelings of privacy on the internet, telephones or mail is an illusion.
+	All feelings of privacy on the internet or over telephones is an illusion.
 In recent years the need for privacy enhancing technology has become more apparent.
@@
 One of the most important factors that impact anonymity in a communication system is the number of users.
-A sufficiently large numbers of users is required for a system to make guarantees about its ability to protect the privacy of its users.
+A sufficiently large numbers of users are required for a system to make guarantees about its ability to protect the privacy of its users.
 This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
@@
 In this paper we will analyze Tor and its semi-centralized nature.
+Tor struggles to keep up with the bandwidth demands of its users.
+As the number of users increases, the need to decentralize Tor becomes more urgent.
 Decentralizing Tor isn't an easy task: After 15 years of decentralization attempts, the network is still centralized.
@@
 
-	The implementation of The Onion Router was first described by the U.S.
+	The implementation of The Onion Router (Tor) was first described in 1996 by the U.S.
 Navy Research Laboratory, as a means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
+The idea behind onion routing traces back to 1981, where Chaum described it in his famous paper "Untraceable electronic mail, return addresses, and digital pseudonyms" \cite{chaum1981untraceable}.
 
@@
 		\subsection{Tor stinks}
-			The anonymous communication with Tor can also be used for distribution illegal content or setting up illegal services.
-Illegal content and services is a serious problem Tor is facing.
-A recent example is the shutdown of \emph{Silk Road}, an online market for trading drugs.
-This market operated as a hidden Tor service.
-These hidden services are accessed through their onion address and not through their IP-address, hiding the physical location of the service.
+			Because communication over Tor is untraceable, it is used as a tool for distributors of illegal content or providers of illegal services.
+This is a serious problem that is disrupting Tor's public image.
+A recent example is the shutdown of \emph{Silk Road}, which is an online market for trading prohibited substances.
+The market operated as a hidden Tor service.
+These services are accessed through an onion address and not an IP-address, hiding the physical location of the service.
 This makes it very hard for agencies to track and shut down these operations.

### 2014-03-24 paper.tex
Fix indents

--- 2014-03-23 paper.tex
@@
 \begin{abstract}
-	Ever since the introduction of the internet, it has been void of any privacy.
-A number of anonymous communication overlay networks exist whose aim it is to provide privacy to its users.
-However, due to the nature of the internet, there is major difficulty in getting these networks to become both decentralized and anonymous.
-We list reasons for having anonymous networks, discern the problems in achieving decentralization and sum up the biggest initiatives in the field and their current status.
-To do so, we use one exemplary network, the Tor network.
-We explain how Tor works, what vulnerabilities this network currently has, and possible attacks that could be used to violate privacy and anonymity.
-The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.
-
-	%In the emerging world of ubiquitous internet access, void of any privacy, there are a number of anonymous communication overlay networks whose aim it is to provide privacy to its users.
+	In the emerging world of ubiquitous internet access, void of any privacy, there are a number of anonymous communication overlay networks whose aim it is to provide privacy to its users.
 Due to the nature of the internet, there is major difficulty in getting these networks to become both decentralized and anonymous.
@@
 The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.
-
 	%There are quite a few distributed anonymous communication networks such as Tor, yet when it comes to decentralized anonymous systems the numbers are rather small and certain problems arise.
@@
 \section{Introduction}
-	All feelings of privacy on telephones, mobile phones or the internet is an illusion.
-In recent years the need for privacy enhancing technology has become more apparent.
+	With the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate.
+In many cases however, internet usage is either censored or monitored by third parties.
+In recent years the need for anonymous internet communication has become more apparent.
 Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.
@@
 One of the most important factors that impact anonymity in a communication system is the number of users.
-A sufficiently large numbers of users are required for a system to make guarantees about its ability to protect the privacy of its users.
+A sufficiently large numbers of users are required for the system to make guarantees about its ability to conceal and hide users' communication.
 This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
-To support a large number of users, such a network has to be decentralized.
-A lack of decentralization would otherwise result in bottlenecks that places constraints on the number of users that can be active.
+Another important factor that impacts the anonymity of the system is decentralization.
+Whenever a network has centralized components and a malicious third party gains control over these components, the functionality and perhaps even the anonymity of the system is compromised.
 
@@
 In this paper we will analyze Tor and its semi-centralized nature.
-Decentralizing Tor isn't an easy task: After 15 years of decentralization attempts, the network is still centralized.
-Only few decentralized alternatives to Tor exist, however they lack the userbase to be considered safe and useful.
-Examples include Gnutella \cite{ripeanu2001peer}, Freenet \cite{lua2005survey} and Tapestry.
+Decentralizing Tor isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us and only a few well-used decentralized peer-to-peer overlay networks are active such as Gnutella \cite{ripeanu2001peer}, Freenet \cite{lua2005survey} and Tapestry.
 
@@
 		\begin{itemize}
-
-			\item
-				Tor's congestion control does not work well.
+			\item Tor's congestion control does not work well.
 The network has some problems handling bulk transfers, such as downloading large files or streaming high-quality videos.
@@
 
-			\item
-			Some Tor users put more traffic on the network than they contribute by running a Onion Router.
+			\item Some Tor users put more traffic on the network than they contribute by running a Onion Router.
 This means that these users are slowing the network down as they use more traffic than giving back.
@@
 
-			\item
-				The Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
+			\item The Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
 According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data.
@@
 
-			\item
-				The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
+			\item The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
 The problem is that the current selection strategy is optimal when the network is fully loaded.
@@
 
-			\item
-				Tor clients are not optimal at handling latency and connection failures.
+			\item Tor clients are not optimal at handling latency and connection failures.
 For example, if extending a circuit fails, the entire circuit is abandoned.
@@
 
-			\item
-				Much of the overhead of the network is in downloading the directory information.
+			\item Much of the overhead of the network is in downloading the directory information.
 There is also overhead in the TLS connection between the nodes in the network.
@@
 Although much research has been done on the decentralization of Tor, it still uses centralized components today.
-
 		\end{itemize}

### 2014-03-24 paper.tex
Rename current table
Add section about alternative internet plus table

@@
 
-	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of these systems maintained by redecentralize.org\footnote{Found at https://github.com/redecentralize/alternative-internet}.
-For each of the listed systems, we have created an entry in a table that shows statistics such as the total lines of code (LOC), activity, amount of contributors, (main) programming language and amount of commits, sourced from Ohloh.
+	\subsection{Alternative Internet Project}
+		Redecentralize.org is a project that describes itself with the aim to \textquoteleft start of a new information revolutions\textquoteright~by \textquoteleft bringing decentralized in the hands of billions\textquoteright~\cite{aboutredecentralizeorg}.
+One of the ways they do this, is by maintaining a Github repository\footnote{Found at https://github.com/redecentralize/alternative-internet} with projects that in some way help to decentralize the internet.
+This ranges from self hosted cloud applications, to crypto currencies, to anonymous networks.
+
+		As a contribution to (anonymous) decentralized system research, we have improved and updated the list of these decentralized systems.
+For each of the listed systems, we have created an entry in a table that shows statistics such as the total lines of code (LOC), age, number of contributors and commits, activity and (main) programming language, sourced from Ohloh.
 This table is available on the same Github repository.
-We hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.
-This Github repository, including the table, is publicly available.
+
+		An excerpt of the table is included as table \ref{tbl:altinternet}.
+In this instance, we chose to sort the table on the number of commits, because we found that this most accurately represented projects that have been established for some time and have been active in the past days.
+Other statistics such as LOC might not be very relevant on their own, because some projects include big libraries or other projects.
+
+		In the table we notice that three of the entries are privacy enhancing networks that aim to provide unlinkability (Freenet, Tor, GNUnet), plus one that is currently in the process of implementing such a feature (Tribler).
+Furthermore we notice that, once above a certain threshold, none of the statistics have a clear effect on a projects popularity.
+For example, Freenet and Tor have similar statistics, while the number of Tor users \cite{tormetricsprojectwebsite} is several orders of magnitude higher than Freenet \cite{freenetstatistics}.
+
+		So although clear differences aren't directly noticeable, we hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.
 
@@
 				\centering
-			\include{table}
+				\include{tbl-currentsystems}
 				\caption{A comparison of decentralized peer-to-peer overlay networks}
 				\label{tbl:comparison}
+			\end{table}
+
+			\begin{table}[p]
+				\centering
+				\include{tbl-alternativeinternet}
+				\caption{A list with the top 10 projects from the Alternative Internet repository as of 2014-03-15, sorted on the number of commits.}
+				\label{tbl:altinternet}
 			\end{table}

### 2014-03-24 tbl-alternativeinternet.tex
And the actual table

\begin{tabular}[p]{| r | l | p{3cm} | p{3cm} | p{3cm} | p{3cm} | p{3cm} | p{3cm} |}
	\hline
	\textbf{\#} & \textbf{Name} & \textbf{Language} & \textbf{Age} & \textbf{Last activity} & \textbf{LOC} & \textbf{Commits} & \textbf{Contributors} \\ \hline

	1 & ownCloud & PHP & 6 year(s) & 2014-03-15 & 1,297 K & 34,391 commit(s) & 392 contributor(s) \\ \hline
	2 & Freenet & Java & 13 year(s) & 2014-03-15 & 442 K & 32,009 commit(s) & 183 contributor(s) \\ \hline
	3 & Tor & C & 12 year(s) & 2014-03-13 & 329 K & 29,200 commit(s) & 184 contributor(s) \\ \hline
	4 & GNUnet & C & 8 year(s) & 2014-03-13 & 427 K & 21,398 commit(s) & 37 contributor(s) \\ \hline
	5 & StatusNet & PHP & 6 year(s) & 2014-03-14 & 230 K & 14,877 commit(s) & 92 contributor(s) \\ \hline
	6 & Diaspora* & Ruby & 3 year(s) & 2014-03-14 & 51 K & 14,202 commit(s) & 368 contributor(s) \\ \hline
	7 & SlapOS & Python & 8 year(s) & 2014-03-15 & 588 K & 14,046 commit(s) & 93 contributor(s) \\ \hline
	8 &Tahoe-LAFS & Python & 7 year(s) & 2014-03-13 & 158 K & 11,565 commit(s) & 54 contributor(s) \\ \hline
	9 & Tribler & Python & 8 year(s) & 2014-03-15 & 148 K & 11,521 commit(s) & 48 contributor(s) \\ \hline
	10 & Lorea & PHP & 6 year(s) & 2014-03-12 & 873 K & 11,066 commit(s) & 96 contributor(s) \\ \hline
\end{tabular}

### 2014-03-24 paper.tex
Move tables down the page to avoid whitespace
Sentence fix

@@
 Furthermore we notice that, once above a certain threshold, none of the statistics have a clear effect on a projects popularity.
-For example, Freenet and Tor have similar statistics, while the number of Tor users \cite{tormetricsprojectwebsite} is several orders of magnitude higher than Freenet \cite{freenetstatistics}.
+For example, Freenet and Tor have similar statistics, while the number of Tor users \cite{tormetricsprojectwebsite} is several orders of magnitude higher than the number of Freenet users \cite{freenetstatistics}.
 
 		So although clear differences aren't directly noticeable, we hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.
-
-		\begin{landscape}
-			\begin{table}[p]
-				\centering
-				\include{tbl-currentsystems}
-				\caption{A comparison of decentralized peer-to-peer overlay networks}
-				\label{tbl:comparison}
-			\end{table}
-
-			\begin{table}[p]
-				\centering
-				\include{tbl-alternativeinternet}
-				\caption{A list with the top 10 projects from the Alternative Internet repository as of 2014-03-15, sorted on the number of commits.}
-				\label{tbl:altinternet}
-			\end{table}
-		\end{landscape}
 
@@
 
+\begin{landscape}
+	\begin{table}[p]
+		\centering
+		\include{tbl-currentsystems}
+		\caption{A comparison of decentralized peer-to-peer overlay networks}
+		\label{tbl:comparison}
+	\end{table}
+
+	\begin{table}[p]
+		\centering
+		\include{tbl-alternativeinternet}
+		\caption{A list with the top 10 projects from the Alternative Internet repository as of 2014-03-15, sorted on the number of commits.}
+		\label{tbl:altinternet}
+	\end{table}
+\end{landscape}
+
 \bibliographystyle{plain}

### 2014-03-24 paper.tex
first round of typo fixes

@@
 
-		By running an HTTP exit node and a Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+		By running a HTTP exit node and a Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
 The exit node injects an invisible iframe containing some JavaScript into any web page that passes through it, each sending a unique ID to a malicious web server.
@@
 The idea of this attack is that a malicious Onion router can lie about its bandwidth, thus advertising a much higher bandwidth than it actually has.
-Because of the Tor path selection algorithm that prefers high-bandwidth nodes, the chance that a malicious entry and exit node are chosen, is high.
+Because of the Tor path selection algorithm that prefers high-bandwidth nodes, the chance that a malicious entry and exit node are chosen is high.
 
@@
 
-		First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or another.
+		First described by Douceur \cite{douceur2002sybil}, he mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or another.
 The exception to this rule is what he calls "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify themselves.
@@
 	Decentralizing systems comes with a variety of problems.
-The most important reason why one would decentralize are security and anonymity.
+The most important reasons why one would decentralize are security and anonymity.
 When having a central authority this authority can be used for bootstrapping, key management and to manage the reputation of the users, but if one of these authorities were taken control of, security of the anonymity could be compromised.

### 2014-03-24 paper.tex
second round of typo fixes

@@
 The most important reasons why one would decentralize are security and anonymity.
-When having a central authority this authority can be used for bootstrapping, key management and to manage the reputation of the users, but if one of these authorities were taken control of, security of the anonymity could be compromised.
+When having a central authority, this authority can be used for bootstrapping, key management and to manage the reputation of the users.
+If one of these authorities were taken control of, security of the anonymity could be compromised.
 When removing this central authority, these components needs to be spread across the peers in the network.

### 2014-03-24 paper.tex
Fixed typos

--- 2014-03-24 paper.tex
@@
 To do so, we use one exemplary network, the Tor network.
-We explain how Tor works, what vulnerabilities this network currently has, and possible attacks that could be used to violate privacy and anonymity.
+We explain how Tor works, what vulnerabilities this network currently has and possible attacks that could be used to violate privacy and anonymity.
 The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.
@@
 	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and are being used in practice.
-One of the most important factors that impact anonymity in a communication system is the number of users.
+One of the most important factors that impacts anonymity in a communication system is the number of users.
 A sufficiently large numbers of users are required for the system to make guarantees about its ability to conceal and hide users' communication.
@@
 		\caption{The components of the Tor network.
-After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node, and uses it to communicate (anonymously) with the internet.}
+After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node.
+This circuit is used to communicate (anonymously) with the internet.}
 		\label{fig:tor_layout}
@@
 The network has some problems handling bulk transfers, such as downloading large files or streaming high-quality videos.
-The congestion control could be improved by using an unreliable protocol for links between Tor relays.
+The congestion control could be improved by using an unreliable protocol such as UDP for links between Tor relays.
 Goldberg et al.
@@
 
-			\item The Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
+			\item The Tor network doesn't have the capacity to handle all the users that want privacy on the internet.
 According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data.
@@
 	\subsection{Low-Resource Routing attacks}
-		Another possible attack on the anonymity of tor is the so called \emph{low-resource routing attack} \cite{bauer2007low}.
+		Another possible attack on the anonymity of Tor is the so called \emph{low-resource routing attack} \cite{bauer2007low}.
 With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resources, thus compromising the anonymity Tor provides.
@@
 		Once a malicious entry and exit node have been chosen, an analysis of the traffic can be done to link Onion proxies with the web servers they communicate with.
-Experimental research in a test setting has shown that with an total of 66 non-malicious and 6 malicious nodes, is possible to compromise 46\% of the built circuits.
+Experimental research in a test setting has shown that with a total of 66 non-malicious and 6 malicious nodes, is possible to compromise 46\% of the built circuits.
 At the request of the Tor community, this attack hasn't been tested on the live Tor network.
@@
 This attack can also be used as a denial of service attack.
-According to Pries et al., defending against this attack is quite challenging to solve and requires further research.
+According to Pries et al., defending against this attack is quite challenging and requires further research.
 

### 2014-03-24 paper.tex
Changes in section about illegal content and tor

@@
 			The anonymous communication with Tor can also be used for distribution illegal content or setting up illegal services.
-Illegal content and services is a serious problem Tor is facing.
+Illegal content and services are a serious problem that Tor is facing.
 A recent example is the shutdown of \emph{Silk Road}, an online market for trading drugs.
@@
 
-			A recent research on the content and popularity analysis of Tor hidden services \cite{biryukov2013content} has shown that although there are Tor hidden services that distributes illegal content, many hidden services are however resources devoted to human rights, freedom of speech and information which is prohibited in some countries.
+			A recent research on the content and popularity analysis of Tor hidden services \cite{biryukov2013content} has shown that although there are Tor hidden services that distributes illegal content, many hidden services are resources devoted to human rights, freedom of speech and information which is prohibited in some countries.
 It is not clear which type of service is more popular on Tor.
 
-			The illegal content travels unencrypted through a Tor exit node.
-Users running a Tor exit node, could be held responsible for distributing illegal content.
-The possibility of redirecting illegal content, refrains users from running an exit node.
+			Unless hidden services are used, content travels unencrypted through a Tor exit node.
+Users running a Tor exit node could be held responsible for distributing illegal content.
+The possibility of being seen as the originator of illegal content refrains users from running an exit node.
 A possible solution could be to filter the illegal content from the legal content.
-While content filtering is a viable solution, it is an open question whether filtering content is in line with the principles of Tor and the internet.
-We think however that filtering the content on Tor, could make more users run an exit node and thus improve the quality of the network.
+While content filtering could be a possible solution, it is an open question whether filtering is in line with the principles of Tor and the internet.
+We think however that filtering the content on Tor could make more users run an exit node and thus improve the quality of the network.
 

### 2014-03-24 paper.tex
More fixes

--- 2014-03-24 paper.tex
@@
 To do so, we use one exemplary network, the Tor network.
-We explain how Tor works, what vulnerabilities this network currently has and possible attacks that could be used to violate privacy and anonymity.
+We explain how Tor works, what vulnerabilities this network currently has, and possible attacks that could be used to violate privacy and anonymity.
 The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.
+
 	%There are quite a few distributed anonymous communication networks such as Tor, yet when it comes to decentralized anonymous systems the numbers are rather small and certain problems arise.
@@
 \section{Introduction}
-	With the introduction and commercialization of the internet in 1995, it has become an important tool for anyone to freely and easily communicate.
-In many cases however, internet usage is either censored or monitored by third parties.
-In recent years the need for anonymous internet communication has become more apparent.
+	All feelings of privacy on the internet or over telephones is an illusion.
+In recent years the need for privacy enhancing technology has become more apparent.
 Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.
 
-	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and are being used in practice.
-One of the most important factors that impacts anonymity in a communication system is the number of users.
-A sufficiently large numbers of users are required for the system to make guarantees about its ability to conceal and hide users' communication.
+	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and only one is actively being used in practice.
+One of the most important factors that impact anonymity in a communication system is the number of users.
+A sufficiently large numbers of users are required for a system to make guarantees about its ability to protect the privacy of its users.
 This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
-Another important factor that impacts the anonymity of the system is decentralization.
-Whenever a network has centralized components and a malicious third party gains control over these components, the functionality and perhaps even the anonymity of the system is compromised.
+To support a large number of users, such a network has to be decentralized.
+A lack of decentralization would otherwise result in bottlenecks that place constraints on the number of users.
 
@@
 In this paper we will analyze Tor and its semi-centralized nature.
-Decentralizing Tor isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us and only a few well-used decentralized peer-to-peer overlay networks are active such as Gnutella \cite{ripeanu2001peer}, Freenet \cite{lua2005survey} and Tapestry.
+Tor struggles to keep up with the bandwidth demands of its users.
+As the number of users increases, the need to decentralize Tor becomes more urgent.
+Decentralizing Tor isn't an easy task: After 15 years of decentralization attempts, the network is still centralized.
+Only few decentralized alternatives to Tor exist, however they lack the userbase to be considered safe and useful.
+Examples include Gnutella \cite{ripeanu2001peer}, Freenet \cite{lua2005survey} and Tapestry.
 
@@
 		\caption{The components of the Tor network.
-After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node.
-This circuit is used to communicate (anonymously) with the internet.}
+After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node, and uses it to communicate (anonymously) with the internet.}
 		\label{fig:tor_layout}
@@
 		\begin{itemize}
-			\item Tor's congestion control does not work well.
+
+			\item
+				Tor's congestion control does not work well.
 The network has some problems handling bulk transfers, such as downloading large files or streaming high-quality videos.
-The congestion control could be improved by using an unreliable protocol such as UDP for links between Tor relays.
+The congestion control could be improved by using an unreliable protocol for links between Tor relays.
 Goldberg et al.
@@
 
-			\item Some Tor users put more traffic on the network than they contribute by running a Onion Router.
+			\item
+			Some Tor users put more traffic on the network than they contribute by running a Onion Router.
 This means that these users are slowing the network down as they use more traffic than giving back.
@@
 
-			\item The Tor network doesn't have the capacity to handle all the users that want privacy on the internet.
+			\item
+				The Tor network doesn't have the capacity to handle all the users that want privacy on the Internet.
 According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data.
@@
 
-			\item The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
+			\item
+				The current path selection algorithm of Tor doesn't distribute the load evenly over the network.
 The problem is that the current selection strategy is optimal when the network is fully loaded.
@@
 
-			\item Tor clients are not optimal at handling latency and connection failures.
+			\item
+				Tor clients are not optimal at handling latency and connection failures.
 For example, if extending a circuit fails, the entire circuit is abandoned.
@@
 
-			\item Much of the overhead of the network is in downloading the directory information.
+			\item
+				Much of the overhead of the network is in downloading the directory information.
 There is also overhead in the TLS connection between the nodes in the network.
@@
 
+		\end{itemize}
+
 		The directory service generates overhead on the network.
 Replacing this central authority with a decentralized component, could reduce the overhead of the network and improve performance.
-Furthermore, it would alleviate a security concern.
-A malicious adversary could gain control of the directory server and force a connection through a set of colluding nodes.
-In a decentralized environment such an attack would be much more difficult.
 In conclusion, this means that we would like to see Tor decentralized.
 Although much research has been done on the decentralization of Tor, it still uses centralized components today.
-		\end{itemize}
 
 		\subsection{Tor stinks}
-			The anonymous communication with Tor can also be used for distribution illegal content or setting up illegal services.
-Illegal content and services is a serious problem Tor is facing.
-A recent example is the shutdown of \emph{Silk Road}, an online market for trading drugs.
-This market operated as a hidden Tor service.
-These hidden services are accessed through their onion address and not through their IP-address, hiding the physical location of the service.
+			Because communication over Tor is untraceable, it is used as a tool for distributors of illegal content and providers of illegal services.
+This is a serious problem that is disrupting Tor's public image.
+A recent example is the shutdown of \emph{Silk Road}, which is an online market for trading prohibited substances.
+The market operated as a hidden Tor service.
+These services are accessed through an onion address and not an IP-address, hiding the physical location of the service.
 This makes it very hard for agencies to track and shut down these operations.
@@
 	\subsection{Low-Resource Routing attacks}
-		Another possible attack on the anonymity of Tor is the so called \emph{low-resource routing attack} \cite{bauer2007low}.
+		Another possible attack on the anonymity of tor is the so called \emph{low-resource routing attack} \cite{bauer2007low}.
 With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resources, thus compromising the anonymity Tor provides.
@@
 		Once a malicious entry and exit node have been chosen, an analysis of the traffic can be done to link Onion proxies with the web servers they communicate with.
-Experimental research in a test setting has shown that with a total of 66 non-malicious and 6 malicious nodes, is possible to compromise 46\% of the built circuits.
+Experimental research in a test setting has shown that with an total of 66 non-malicious and 6 malicious nodes, is possible to compromise 46\% of the built circuits.
 At the request of the Tor community, this attack hasn't been tested on the live Tor network.
@@
 This attack can also be used as a denial of service attack.
-According to Pries et al., defending against this attack is quite challenging and requires further research.
+According to Pries et al., defending against this attack is quite challenging to solve and requires further research.
 
@@
 
-	\subsection{Alternative Internet Project}
-		Redecentralize.org is a project that describes itself with the aim to \textquoteleft start of a new information revolutions\textquoteright~by \textquoteleft bringing decentralized in the hands of billions\textquoteright~\cite{aboutredecentralizeorg}.
-One of the ways they do this, is by maintaining a Github repository\footnote{Found at https://github.com/redecentralize/alternative-internet} with projects that in some way help to decentralize the internet.
-This ranges from self hosted cloud applications, to crypto currencies, to anonymous networks.
+	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of these systems maintained by redecentralize.org\footnote{Found at https://github.com/redecentralize/alternative-internet}.
+For each of the listed systems, we have created an entry in a table that shows statistics such as the total lines of code (LOC), activity, amount of contributors, (main) programming language and amount of commits, sourced from Ohloh.
+This table is available on the same Github repository.
+We hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.
+This Github repository, including the table, is publicly available.
 
-		As a contribution to (anonymous) decentralized system research, we have improved and updated the list of these decentralized systems.
-For each of the listed systems, we have created an entry in a table that shows statistics such as the total lines of code (LOC), age, number of contributors and commits, activity and (main) programming language, sourced from Ohloh.
-This table is available on the same Github repository.
-
-		An excerpt of the table is included as table \ref{tbl:altinternet}.
-In this instance, we chose to sort the table on the number of commits, because we found that this most accurately represented projects that have been established for some time and have been active in the past days.
-Other statistics such as LOC might not be very relevant on their own, because some projects include big libraries or other projects.
-
-		In the table we notice that three of the entries are privacy enhancing networks that aim to provide unlinkability (Freenet, Tor, GNUnet), plus one that is currently in the process of implementing such a feature (Tribler).
-Furthermore we notice that, once above a certain threshold, none of the statistics have a clear effect on a projects popularity.
-For example, Freenet and Tor have similar statistics, while the number of Tor users \cite{tormetricsprojectwebsite} is several orders of magnitude higher than the number of Freenet users \cite{freenetstatistics}.
-
-		So although clear differences aren't directly noticeable, we hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.
+	\begin{landscape}
+		\begin{table}[p]
+			\centering
+			\include{table}
+			\caption{A comparison of decentralized peer-to-peer overlay networks}
+			\label{tbl:comparison}
+		\end{table}
+	\end{landscape}
 
@@
 
-\begin{landscape}
-	\begin{table}[p]
-		\centering
-		\include{tbl-currentsystems}
-		\caption{A comparison of decentralized peer-to-peer overlay networks}
-		\label{tbl:comparison}
-	\end{table}
-
-	\begin{table}[p]
-		\centering
-		\include{tbl-alternativeinternet}
-		\caption{A list with the top 10 projects from the Alternative Internet repository as of 2014-03-15, sorted on the number of commits.}
-		\label{tbl:altinternet}
-	\end{table}
-\end{landscape}
-
 \bibliographystyle{plain}

### 2014-03-24 paper.tex
fixed typos

--- 2014-03-24 paper.tex
@@
 Diffie-Hellman is a very popular algorithm for exchanging keys between two parties.
-It is used in the circuit creation in Onion Routing (see section \ref{ss:tor_circuit}), for example.
+It is used in the circuit creation in Onion Routing (see section \ref{ss:tor_circuit}) for example.
 However, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable to a man-in-the-middle attack.
-This weakness makes it possible for an adversary to decrypt all message sent between the two parties.
+This weakness makes it possible for an adversary to decrypt all messages sent between the two parties.
 
@@
 One of them is \emph{ACE}, an one-way authenticated key exchange protocol.
-The authors of this methods claim to have an 46\% efficiency improvement on the side of the client and nearly 19\% on the side of the Onion Routers.
+The authors of this methods claim to have a 46\% efficiency improvement on the side of the client and nearly 19\% on the side of the Onion Routers.
 ACE requires clients to send one extra element in the key exchange.
@@
 		Gnutella is a decentralized peer-to-peer network used for distributed search of files.
-Since the network is fully decentralized, peers in the network are called 'servents', a combination of the words servers and clients.
+Since the network is fully decentralized, peers in the network are called \emph{servents}, a combination of the words servers and clients.
 Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.
@@
 These peers can be found on http://gnutellahosts.com.
-Once the peer has joined, there are several messages a servant can send out:
+Once the peer has joined, there are several messages a servent can send out:
 
 		\begin{itemize}
-			\item A peer sends a PING message to it's neighbours to announce it's presents. This message is forwarded to other peers and each peer sends a PONG message back.
+			\item A peer sends a PING message to it's neighbours to announce it's presence. This message is forwarded to other peers and each peer sends a PONG message back.
 			\item The peer can issue QUERY answers. Other peers responds with a QUERY RESPONSE message to specify whether the file that was issued in the query, was found or not.
@@
 
-		Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the topology nor the contents of the file.
+		Gnutella is an unstructured network which means that the placement of data items is not based on any knowledge of the network topology nor the contents of the file.
 To search for a file, a flooding algorithm is used.

### 2014-03-24 paper.tex

--- 2014-03-24 paper.tex
@@
 
+		\end{itemize}
+
 		The directory service generates overhead on the network.
 Replacing this central authority with a decentralized component, could reduce the overhead of the network and improve performance.
-Furthermore, it would alleviate a security concern.
-A malicious adversary could gain control of the directory server and force a connection through a set of colluding nodes.
-In a decentralized environment such an attack would be much more difficult.
 In conclusion, this means that we would like to see Tor decentralized.
 Although much research has been done on the decentralization of Tor, it still uses centralized components today.
-		\end{itemize}
 
 		\subsection{Tor stinks}
-			The anonymous communication with Tor can also be used for distribution illegal content or setting up illegal services.
-Illegal content and services are a serious problem that Tor is facing.
-A recent example is the shutdown of \emph{Silk Road}, an online market for trading drugs.
-This market operated as a hidden Tor service.
-These hidden services are accessed through their onion address and not through their IP-address, hiding the physical location of the service.
+			Because communication over Tor is untraceable, it is used as a tool for distributors of illegal content and providers of illegal services.
+This is a serious problem that is disrupting Tor's public image.
+A recent example is the shutdown of \emph{Silk Road}, which is an online market for trading prohibited substances.
+The market operated as a hidden Tor service.
+These services are accessed through an onion address and not an IP-address, hiding the physical location of the service.
 This makes it very hard for agencies to track and shut down these operations.

### 2014-03-24 paper.tex
Removed sentence about filtering
Remove commented out paragraphs
Fix indent
Typo

@@
 The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.
-
-	%In the emerging world of ubiquitous internet access, void of any privacy, there are a number of anonymous communication overlay networks whose aim it is to provide privacy to its users.
-Due to the nature of the internet, there is major difficulty in getting these networks to become both decentralized and anonymous.
-This technical report lists reasons for having anonymous networks, discerns the problems in achieving decentralization in anonymous networks and sums up the biggest competitors in the field and their current status.
-To do so, we use one exemplary network, the Tor network.
-We explain how Tor works, what vulnerabilities this network currently has, and possible attacks that could be used to violate privacy and anonymity.
-The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.
-
-	%There are quite a few distributed anonymous communication networks such as Tor, yet when it comes to decentralized anonymous systems the numbers are rather small and certain problems arise.
-In this technical report we explain how Tor works and which attacks are possible and which vulnerabilities currently exist in Tor.
-After that, we talk about why would like to decentralize peer-to-peer networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized.
-Finally, we provide a table in where we compare these projects against each other, which will also be public available on the Github page mention in this report.
 \end{abstract}
@@
 
-		%As described in the previous section, data on the Tor networks travels over circuits.
-The data travels over the circuit in fixed-size cells that are 512 bytes long.
-Each cell has a header and a payload.
-The header consists of a number that identifies the circuit the cell travels on and a command that indicates what to do with the cell’s payload.
-
-		%Before a circuit can be established, a path has to be chosen.
-The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes \cite{wang2012congestion}.
-Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.
-
 		Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a web server.
@@
 		\end{itemize}
-
 			The directory service generates overhead on the network.
@@
 While content filtering could be a possible solution, it is an open question whether filtering is in line with the principles of Tor and the internet.
-We think however that filtering the content on Tor could make more users run an exit node and thus improve the quality of the network.
 
@@
 	\subsection{Other decentralized systems}
-		Some other decentralized peer-to-peer systems has been developed, focussing on anonymity.
+		Some other decentralized peer-to-peer systems have been developed, focussing on anonymity.
 An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible.

### 2014-03-24 paper.tex
fixed minor issues

--- 2014-03-24 paper.tex
@@
 
-		Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority.
+		Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority (NA).
 The DHT is a combination of Kademlia DHT and Myrmic DHT.
@@
 
-	\subsection{Other decentralized systems}
-		Some other decentralized peer-to-peer systems has been developed, focussing on anonymity.
-An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible.
+	\subsection{Anonymizing Peer-to-Peer Proxy}
+		Anothe proposed decentralized, anonymizing overlay network is Anonymizing Peer-to-Peer Proxy (AP3) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible.
 The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms.
@@
 		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
-		\item{Anonymity:} Does the network hide the identities of the sender and/or receiver?
+		\item{Unlinkability:} Does the network hide the identities of the sender and/or receiver?
 	\end{itemize}

### 2014-03-24 paper.tex

--- 2014-03-24 paper.tex
@@
 
-	\subsection{Other decentralized systems}
-		Some other decentralized peer-to-peer systems have been developed, focussing on anonymity.
-An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible.
+	\subsection{Anonymizing Peer-to-Peer Proxy}
+		Another proposed decentralized, anonymizing overlay network is Anonymizing Peer-to-Peer Proxy (AP3) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible.
 The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms.

### 2014-03-24 paper.tex
typo fixes round 3

--- 2014-03-24 paper.tex
@@
 While content filtering could be a possible solution, it is an open question whether filtering is in line with the principles of Tor and the internet.
+We think however that filtering the content on Tor could make more users run an exit node and thus improve the quality of the network.
 
@@
 
-		Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
+		Moving this system to a peer-to-peer base is difficult: Dingledine et al.
 stated that this is indeed still an open problem.
@@
 It is used in the circuit creation in Onion Routing (see section \ref{ss:tor_circuit}) for example.
-However, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable to a man-in-the-middle attack.
+However, it is possible for an adversary to manipulate the keys send between two parties, making the protocol vulnerable to a man-in-the-middle attack.
 This weakness makes it possible for an adversary to decrypt all messages sent between the two parties.
@@
 
-		Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority (NA).
+		Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority.
 The DHT is a combination of Kademlia DHT and Myrmic DHT.
@@
 
-	\subsection{Anonymizing Peer-to-Peer Proxy}
-		Anothe proposed decentralized, anonymizing overlay network is Anonymizing Peer-to-Peer Proxy (AP3) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible.
+	\subsection{Other decentralized systems}
+		Some other decentralized peer-to-peer systems has been developed, focussing on anonymity.
+An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible.
 The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms.
@@
 		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
-		\item{Unlinkability:} Does the network hide the identities of the sender and/or receiver?
+		\item{Anonymity:} Does the network hide the identities of the sender and/or receiver?
 	\end{itemize}

### 2014-03-24 paper.tex
Table caption

@@
 		\include{tbl-currentsystems}
-		\caption{A comparison of decentralized peer-to-peer overlay networks}
+		\caption{A comparison of decentralized peer-to-peer overlay networks.}
 		\label{tbl:comparison}
@@
 		\include{tbl-alternativeinternet}
-		\caption{A list with the top 10 projects from the Alternative Internet repository as of 2014-03-15, sorted on the number of commits.}
+		\caption{The top 10 projects from the Alternative Internet repository by number of commits (as of 2014-03-15).}
 		\label{tbl:altinternet}

### 2014-03-24 paper.tex
typo fix round 5

--- 2014-03-24 paper.tex
@@
 		\begin{itemize}
-			\item A peer sends a PING message to it's neighbours to announce it's presence. This message is forwarded to other peers and each peer sends a PONG message back.
+			\item A peer sends a PING message to its neighbours to announce its presence. This message is forwarded to other peers and each peer sends a PONG message back.
 			\item The peer can issue QUERY answers. Other peers responds with a QUERY RESPONSE message to specify whether the file that was issued in the query, was found or not.
@@
 	\subsection{Tapestry} % 2001
-		Tapestry is based on the Plaxton mesh data structure, which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
+		Tapestry is based on the Plaxton mesh data structure, which maintains pointers to nodes in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position.
 A property of Tapestry is that it offers load distribution and routing locality.
@@
 		The Pastry overlay network is used in several applications, such as Scribe, Squirrel and PAST.
-Scribe is an system that has been built to send multicast messages.
+Scribe is a system that has been built to send multicast messages.
 Instead of relying on the multicast infrastructure, multicast messages are sent using only unicast services.
@@
 		Squirrel is a decentralized peer-to-peer web cache.
-The network uses Pastry to locate it's objects and for the routing algorithm.
-Squirrel allows users to share it's web cache with other users in the network, creating a large decentralized web cache.
+The network uses Pastry to locate its objects and for the routing algorithm.
+Squirrel allows users to share its web cache with other users in the network, creating a large decentralized web cache.
 Squirrel however introduces some overhead when searching the cache.

### 2014-03-24 paper.tex
Added figure for bandwidth increase due to hops

--- 2014-03-24 paper.tex
@@
 
+		\begin{figure*}[!t]
+				\centering
+				\includegraphics[width=0.95\textwidth]{graphics/hops.pdf}
+				\caption{As traffic moves over Tor nodes, the total amount of bandwidth used in the network increases. By using $n$ hops, the total amount of network traffic would be multiplied by $2(n+1)$.}
+				\label{fig:hops}
+			\end{figure*}
+
 		While Tor offers its users a high level of anonymity, there are some disadvantages using it.
@@
 According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data.
+Due to the fact that traffic travels over multiple Tor nodes, the total amount of transfered data in the network multiplies.
+This is illustrated in figure \ref{fig:hops}.
+By having $n$ hops, the amount of transfered traffic would be multiplied by $2(n+1)$.
+This means that a 1GB transfer, using only 1 hop, would actually cost the network 4GB.
 By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
@@
 
-		Moving this system to a peer-to-peer base is difficult: Dingledine et al.
+		Moving this system to a non peer-to-peer base is difficult: Dingledine et al.
 stated that this is indeed still an open problem.
@@
 It is used in the circuit creation in Onion Routing (see section \ref{ss:tor_circuit}) for example.
-However, it is possible for an adversary to manipulate the keys send between two parties, making the protocol vulnerable to a man-in-the-middle attack.
+However, it is possible for an adversary to manipulate with the keys send between two parties, making the protocol vulnerable to a man-in-the-middle attack.
 This weakness makes it possible for an adversary to decrypt all messages sent between the two parties.
@@
 		\include{tbl-currentsystems}
-		\caption{A comparison of decentralized peer-to-peer overlay networks.}
+		\caption{A comparison of decentralized peer-to-peer overlay networks}
 		\label{tbl:comparison}
@@
 		\include{tbl-alternativeinternet}
-		\caption{The top 10 projects from the Alternative Internet repository by number of commits (as of 2014-03-15).}
+		\caption{A list with the top 10 projects from the Alternative Internet repository as of 2014-03-15, sorted on the number of commits.}
 		\label{tbl:altinternet}

### 2014-03-24 paper.tex
Indents, GB -> GiB
Typo fix round 6 - Last one!

--- 2014-03-24 paper.tex
@@
 
-	In the last section, we discussed existing decentralized peer-to-peer networks.
+	In the previous section, we discussed existing decentralized peer-to-peer networks.
 In this section we will make a comparison between these networks, as seen in table \ref{tbl:comparison}.

### 2014-03-24 paper.tex

@@
 
+		\begin{figure*}[!t]
+			\centering
+			\includegraphics[width=0.95\textwidth]{graphics/hops.pdf}
+			\caption{As traffic moves over Tor nodes, the total amount of bandwidth used in the network increases. By using $n$ hops, the total amount of network traffic would be multiplied by $2(n+1)$.}
+			\label{fig:hops}
+		\end{figure*}
+
 		While Tor offers its users a high level of anonymity, there are some disadvantages using it.
@@
 According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data.
+Due to the fact that traffic travels over multiple Tor nodes, the total amount of transfered data in the network multiplies.
+This is illustrated in figure \ref{fig:hops}.
+By having $n$ hops, the amount of transfered traffic would be multiplied by $2(n+1)$.
+This means that a 1 GiB transfer, using only 1 hop, would actually cost the network 4 GiB.
 By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
@@
 According to Dingledine et al, removing the empty TLS application record could reduce the overhead in the TCP/IP header by 6.3\%.
-
 		\end{itemize}

### 2014-03-24 paper.tex
Fixed some typos and added some more consistency

@@
 
-			A recent research on the content and popularity analysis of Tor hidden services \cite{biryukov2013content} has shown that although there are Tor hidden services that distributes illegal content, many hidden services are resources devoted to human rights, freedom of speech and information which is prohibited in some countries.
+			A recent research on the content and popularity of Tor's hidden services \cite{biryukov2013content} has shown that although there are Tor hidden services that distribute illegal content, many hidden services are resources devoted to human rights, freedom of speech and information which is prohibited in some countries.
 It is not clear which type of service is more popular on Tor.

### 2014-03-24 paper.tex
Typoo

@@
 According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data.
-Due to the fact that traffic travels over multiple Tor nodes, the total amount of transfered data in the network multiplies.
+Due to the fact that traffic travels over multiple Tor nodes, the total amount of transferred data in the network multiplies.
 This is illustrated in figure \ref{fig:hops}.
-By having $n$ hops, the amount of transfered traffic would be multiplied by $2(n+1)$.
+By having $n$ hops, the amount of transferred traffic would be multiplied by $2(n+1)$.
 This means that a 1 GiB transfer, using only 1 hop, would actually cost the network 4 GiB.

### 2014-03-24 paper.tex
Fixed some final typos, changed "other decentralized networks" to "AP3" and final cleanup

@@
 One of the most important factors that impact anonymity in a communication system is the number of users.
-A sufficiently large numbers of users are required for a system to make guarantees about its ability to protect the privacy of its users.
+A sufficiently large number of users are required for a system to make guarantees about its ability to protect the privacy of its users.
 This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users.
@@
 
-		The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network.
-Each peer has only knowledge about his neighbours.
-Each request has a Hops-To-Live timer which indicates how many peers the request may traversal.
+		The routing algorithm for storing and retrieving data is dynamic and can adjust to the topology of the network.
+Each peer only has knowledge about his neighbours.
+Each request has a Hops-To-Live timer which indicates how many peers the request may traverse.
 Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more.
@@
 
-		Like Gnutella, peers can take the role of a client, issuing requests and the role of a server where objects are stored.
+		Like Gnutella, peers can take the role of a client, issuing requests, and the role of a server where objects are stored.
 A peer can also function as a router, which forwards an incoming message.
@@
 Pastry also uses the Plaxton mesh data structure for the routing algorithm.
-Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space.
+Each peer in the network gets assigned a random 128-bit identifier that is uniformly sampled from the key space.
 Each node can be found in about $\log(n)$ steps.
@@
 It implements a network address translator (NAT) to bridge between nodes running Tarzan and the internet.
-This means that services don\'t have to be aware of the fact they are running through Tarzan.
+This means that services don't have to be aware of the fact they are running through Tarzan.
 
@@
 Not only does a central node administrator (the Directory Server in Tor) imply trust in those servers, Panchenko et al.
-also argue that a central node administration (the Directory Server in Tor) does not scale, as the current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.
+also argue that a central node administration (the Directory Server in Tor) does not scale.
+The current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.
 
@@
 
-	\subsection{Other decentralized systems}
-		Some other decentralized peer-to-peer systems has been developed, focussing on anonymity.
-An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible.
+	\subsection{AP3}
+		AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} makes cooperative, decentralized anonymous communication possible.
 The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms.

### 2014-03-25 paper.tex
Massive change after feedback

@@
 % Title of the paper
-\title{Fifteen years of decentralization attempts}
+\title{The fifteen year struggle of decentralizing privacy-enhancing technology}
 % Authors
@@
 \section{Introduction}
-	All feelings of privacy on the internet or over telephones is an illusion.
-In recent years the need for privacy enhancing technology has become more apparent.
-Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.
+	All feelings of privacy concerning browsing the internet, talking on the telephone or location tracking of cellphones are an illusion.
+In recent years the need for privacy-enhancing technology has become more apparent.
+Revelations by Edward Snowden of government misconduct and constitutional violations have sent shockwaves through the internet.
 
-	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and only one is actively being used in practice.
+	We failed to make an internet that is secure and private.
+Although much research has been done on anonymous internet communication, only few systems have been actually implemented and only one is actively being used.
 One of the most important factors that impact anonymity in a communication system is the number of users.
@@
 A lack of decentralization would otherwise result in bottlenecks that place constraints on the number of users.
+Relying on server bandwidth donations has proven to be a difficult to sustain strategy.
 
@@
 
-	In 2002, it was decided to discontinue the old code base and reimplement the project as Tor, the Second Generation Onion Router, introducing perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
+	In 2002, the Tor project discontinued their old code base and reimplement the project as Tor, the Second Generation Onion Router.
+They introduced perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
 In this section, we will explain the various components of Tor, the structure of the network, circuit creation and disadvantages of Tor.
@@
 	\subsection{Onion routing}
-		As described in the original design paper of The Onion Router, network traffic is forwarded through a circuit of nodes, where each node only knows the previous and next node in the circuit.
+		As described in the original design paper of The Onion Router \cite{goldschlag1996hiding}, network traffic is forwarded through a circuit of nodes, where each node only knows the previous and next node in the circuit.
 With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each other's physical location.
@@
 	\subsection{Directory servers}
-		The original Onion Router implementation used in-band status updates.
+		The original Onion Router used an unsafe, decentralized node discovery mechanism called in-band status updates.
 During such a status update each node broadcasts known nodes to its neighbours.
@@
 
-		\subsection{Tor stinks}
-			Because communication over Tor is untraceable, it is used as a tool for distributors of illegal content and providers of illegal services.
-This is a serious problem that is disrupting Tor's public image.
+		\subsection{Tor stinks?}
+			Tor is not only used by human rights activists.
+It is also used by distributors of illegal content and providers of illegal services, because it is deemed untraceable.
+This serious problem is disrupting Tor's public image.
 A recent example is the shutdown of \emph{Silk Road}, which is an online market for trading prohibited substances.
@@
 This makes it very hard for agencies to track and shut down these operations.
+			% Meer voorbeelden:
+			% - international business times -> silk road (zie wikipedia)
+			% - weapons of mass destruction (?)
 
@@
 
-	Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
-In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.
+	Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited through attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}.
+In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: browser based attacks, low-resource routing attacks, Sybil attacks and replay attacks.
 
@@
 
-	\subsection{Low-Resource Routing attacks}
+	\subsection{Low-resource routing attacks}
 		Another possible attack on the anonymity of Tor is the so called \emph{low-resource routing attack} \cite{bauer2007low}.
@@
 
-	\subsection{Replay Attacks}
+	\subsection{Replay attacks}
 		A replay attack \cite{pries2008new} happens when a malicious entry node duplicates cells and sends them again.
@@
 
-	Decentralizing systems comes with a variety of problems.
-The most important reasons why one would decentralize are security and anonymity.
-When having a central authority, this authority can be used for bootstrapping, key management and to manage the reputation of the users.
-If one of these authorities were taken control of, security of the anonymity could be compromised.
-When removing this central authority, these components needs to be spread across the peers in the network.
-In this section we will explain the various problems that are involved when decentralizing Tor.
+	Decentralization is a difficult research problem.
+A trusted central authority simplifies bootstrapping, key management and user reputation.
+If one of these authorities were taken control of, anonymity would be compromised.
+When decentralizing a central authority, its functionality needs to be dispersed across the peers in the network.
+In this section we will explain the various problems involving Tor decentralization.
 
 	\subsection{Incentives in decentralized systems}
-		As described in section \ref{ss:tor_disadvantages}, people are usually using more bandwidth than that they donate.
-There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor.
+		Tax evasion and environmental pollusion can be seen as forms of free-riding, a phenomenon that is prominent in Tor.
+People predominantly use more Tor bandwidth than they donate, see section \ref{ss:tor_disadvantages}.
+There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor, all have failed.
 If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified.
@@
 
-\section{Decentralized privacy enhancing systems}
+\section{Decentralized privacy-enhancing systems}
 	\label{sec:decentralized}
-
-	Many decentralized peer-to-peer networks have been proposed, yet only some have been implemented and are currently in use and still actively maintained \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}.
-In this section, some popular peer-to-peer overlay networks are discussed.
-Most of these networks are used in practice and can be used to compare Tor with.
-Note that we're only considering fully decentralized networks here, with the exception of Torsk (which is almost fully decentralized but still requires a Neighbourhood Authority).
-Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.
+	Fully decentralized systems with large scale usage are without exception based on the peer-to-peer paradigm.
+Many such systems have been proposed, yet only some have been implemented and are currently in use and actively maintained \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}.
+Here we focus on fully decentralized networks with the exception of Torsk (which is almost fully decentralized but still requires a Neighbourhood Authority).
 
@@
 Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.
-In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available.
-These peers can be found on http://gnutellahosts.com.
+In order for a client to bootstrap, a new peer connects to one of several known hosts that are almost always available \footnote{These peers can be found on http://gnutellahosts.com.}.
 Once the peer has joined, there are several messages a servent can send out:
@@
 	\subsection{Tribler} % 2008
-		Tribler is a social-based peer-to-peer file sharing system based on the BitTorrent protocol \cite{pouwelse2008tribler}.
+		Tribler is a social-based peer-to-peer file sharing system backwards compatible with the BitTorrent protocol \cite{pouwelse2008tribler}.
 Tribler considers social phenomena and the sense of community as important parts of file sharing.
 Although the system is completely decentralized, it does not yet provide its users with anonymity.
-However, this is something that is currently undergoing research.
+However, a modified Tor-like protocol for decentralized use is currently in beta.
 
@@
 This enables quick finding of content that a user is interested in and builds on the idea of social phenomena.
+		% Tribler wiki for better up-to-date information??
 
@@
 
-\section{Comparison existing decentralized networks}
-	\label{sec:comparison}
-
-	In the previous section, we discussed existing decentralized peer-to-peer networks.
+	In this section, we discussed existing decentralized peer-to-peer networks.
 In this section we will make a comparison between these networks, as seen in table \ref{tbl:comparison}.
@@
 
-	\subsection{Alternative Internet Project}
+\section{The documented struggle of alternative internet projects}
+	\label{sec:comparison}
+	The largest repository of decentralization attempts is located at http://redecentralize.org.
+The struggle and pains of these projects illustrates the difficulty of decentralization.
+No projects succeeded in creating an alternative internet infrastructure.
+This ranges from self hosted cloud applications, to crypto currencies, to anonymous networks.
+
+	% what do they have in common
+	% security issues
+	% 1-man projects
+	% lack of documentation
+	%
+
 	Redecentralize.org is a project that describes itself with the aim to \textquoteleft start of a new information revolutions\textquoteright~by \textquoteleft bringing decentralized in the hands of billions\textquoteright~\cite{aboutredecentralizeorg}.
@@
 
+	We made a significant contribution to this project index.
 	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of these decentralized systems.
@@
 
-		In the table we notice that three of the entries are privacy enhancing networks that aim to provide unlinkability (Freenet, Tor, GNUnet), plus one that is currently in the process of implementing such a feature (Tribler).
+		In the table we notice that three of the entries are privacy-enhancing networks that aim to provide unlinkability (Freenet, Tor, GNUnet), plus one that is currently in the process of implementing such a feature (Tribler).
 Furthermore we notice that, once above a certain threshold, none of the statistics have a clear effect on a projects popularity.
@@
 
-	We explained how the leading privacy enhancing technology Tor works and which components define a Tor network.
+	We explained how the leading privacy-enhancing technology Tor works and which components define a Tor network.
 Furthermore, we looked at the main disadvantages and problems Tor is currently facing.
-We then made a bridge to decentralized systems.
-We first explained which problems one might face when decentralizing a system such as Tor.
+We investigated the issues around decentralization.
 After that, we've written which systems currently have a decentralized structure and/or mechanism.
@@
 
-	From table \ref{tbl:comparison}, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today.
-While a lot of research has been done on decentralized systems, there is no system yet that can compete with Tor.
+	From table \ref{tbl:comparison}, we conclude that there is no fully decentralized system capable of offering Tor anonymity today.
 Decentralized systems that do exist such as Tarzan, I2P, Torsk or Gnutella, show promising attempts to decentralize and anonymize the internet.
@@
 
-	While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
-We hope our effort by expanding the list of decentralized systems acts as an extra motivation to perform further research on this topic.
+	For the first time we document in detail, the amount of wasted effort and pain spent in decentralization.
+The current generation of technology lead by Tor still has room for improvement, while the next generation is only just appearing on the horizon.
 
 \begin{landscape}
+
+	% Zelfde volgorde als hoofdstukken
+	% Deze bij hoofdstuk 5 plaatsen!!!
+	% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
 	\begin{table}[p]
@@
 
+	% Tabel kan inline tabel worden, zonder "last activity" en woordje "commit(s)"
 	\begin{table}[p]

### 2014-03-25 paper.tex
tabel inline en other changes

@@
 % Authors
-\author{Rolf Jagerman, Wendo Sab\'ee, Laurens Versluis, Martijn de Vos}
+\author{Rolf Jagerman, Wendo Sab\'ee, Laurens Versluis, Martijn de Vos\\ Supervised by Dr. Ir. Johan Pouwelse}
 \date{}
@@
 In recent years the need for privacy-enhancing technology has become more apparent.
-Revelations by Edward Snowden of government misconduct and constitutional violations have sent shockwaves through the internet.
+Revelations by Edward Snowden of government misconduct and constitutional violations have sent shock waves through the internet.
 
@@
 Decentralizing Tor isn't an easy task: After 15 years of decentralization attempts, the network is still centralized.
-Only few decentralized alternatives to Tor exist, however they lack the userbase to be considered safe and useful.
+Only few decentralized alternatives to Tor exist, however they lack the user base to be considered safe and useful.
 Examples include Gnutella \cite{ripeanu2001peer}, Freenet \cite{lua2005survey} and Tapestry.
@@
 
-	In 2002, the Tor project discontinued their old code base and reimplement the project as Tor, the Second Generation Onion Router.
+	In 2002, the Tor project discontinued their old code base and re-implement the project as Tor, the Second Generation Onion Router.
 They introduced perfect forward secrecy, directory servers, hidden services and more \cite{dingledine2004tor}.
@@
 		As described in the original design paper of The Onion Router \cite{goldschlag1996hiding}, network traffic is forwarded through a circuit of nodes, where each node only knows the previous and next node in the circuit.
-With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each other's physical location.
+With a sufficiently long circuit of (independent) nodes, this means that two communicating parties can remain oblivious of each others physical location.
 
@@
 In this case, there are three relay nodes, but this is not necessarily always the case as more middle relay nodes can be added.
-A visualisation of this path can be seen in figure \ref{fig:tor_layout}.
+A visualization of this path can be seen in figure \ref{fig:tor_layout}.
 Each node has its own public key and a corresponding private key.
@@
 This serious problem is disrupting Tor's public image.
-A recent example is the shutdown of \emph{Silk Road}, which is an online market for trading prohibited substances.
+A recent example is the shutdown of \emph{Silk Road}, which is an online market for trading prohibited substances, buying weapons of mass destruction and other illegal goods.
 The market operated as a hidden Tor service.
@@
 			% - weapons of mass destruction (?)
+			% Is de zin nu zo goed? Ik heb wat voorbeelden erbij gezet
 
@@
 	\subsection{Incentives in decentralized systems}
-		Tax evasion and environmental pollusion can be seen as forms of free-riding, a phenomenon that is prominent in Tor.
+		Tax evasion and environmental pollution can be seen as forms of free-riding, a phenomenon that is prominent in Tor.
 People predominantly use more Tor bandwidth than they donate, see section \ref{ss:tor_disadvantages}.
@@
 	\subsection{Bootstrapping new nodes}
-		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be a starting point where this new node can discover neighbors in the network to connect with.
-In Tor, a directory server can tell the new node what his neighbors are and where to find them \cite{dingledine2004tor}.
+		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be a starting point where this new node can discover neighbours in the network to connect with.
+In Tor, a directory server can tell the new node what his neighbours are and where to find them \cite{dingledine2004tor}.
 
@@
 stated that this is indeed still an open problem.
-With decentralized systems, there is no central directory server to tell a new node where to locate neighbors.
+With decentralized systems, there is no central directory server to tell a new node where to locate neighbours.
 Some systems such as Tarzan, MorphMix and Pastry \cite{rowstron2001pastry, rennhard2002introducing} are decentralized but they do suffer from performance issues.
@@
 Many such systems have been proposed, yet only some have been implemented and are currently in use and actively maintained \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}.
-Here we focus on fully decentralized networks with the exception of Torsk (which is almost fully decentralized but still requires a Neighbourhood Authority).
+Here we focus on fully decentralized networks with the exception of Torsk (which is almost fully decentralized but still requires a Neighborhood Authority).
 
@@
 
+			\subsection{AP3} %2004
+		AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} makes cooperative, decentralized anonymous communication possible.
+The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms.
+Users are able to send and receive unicast, multicast and anycast messages anonymously.
+The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages.
+A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.
+
 	\subsection{Tarzan} % 2002
@@
 
-	\subsection{AP3}
-		AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} makes cooperative, decentralized anonymous communication possible.
-The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms.
-Users are able to send and receive unicast, multicast and anycast messages anonymously.
-The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages.
-A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.
-
-	In this section, we discussed existing decentralized peer-to-peer networks.
-In this section we will make a comparison between these networks, as seen in table \ref{tbl:comparison}.
-For each network, we will explain the following features:
+	\subsection{Comparison}
+	In this subsection we will make a comparison between these networks, as seen in table \ref{tbl:comparison}. For each network, we will explain the following features:
 
@@
 
+	\begin{landscape}
+
+	% Zelfde volgorde als hoofdstukken
+	% Deze bij hoofdstuk 5 plaatsen!!!
+	% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
+	\begin{table}[p]
+		\centering
+		\include{tbl-currentsystems}
+		\caption{A comparison of decentralized peer-to-peer overlay networks}
+		\label{tbl:comparison}
+	\end{table}
+
+	\end{landscape}
+
 \section{The documented struggle of alternative internet projects}
 	\label{sec:comparison}
+
 	The largest repository of decentralization attempts is located at http://redecentralize.org.
@@
 
+			% Tabel moet nog mooi gemaakt worden
+	\begin{table}
+		\centering
+		\include{tbl-alternativeinternet}
+		\caption{A list with the top 10 projects from the Alternative Internet repository as of 2014-03-15, sorted on the number of commits.}
+		\label{tbl:altinternet}
+	\end{table}
+
+	\newpage
+
 \section{Conclusion}
@@
 
-\begin{landscape}
-
-	% Zelfde volgorde als hoofdstukken
-	% Deze bij hoofdstuk 5 plaatsen!!!
-	% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
-	\begin{table}[p]
-		\centering
-		\include{tbl-currentsystems}
-		\caption{A comparison of decentralized peer-to-peer overlay networks}
-		\label{tbl:comparison}
-	\end{table}
-
-	% Tabel kan inline tabel worden, zonder "last activity" en woordje "commit(s)"
-	\begin{table}[p]
-		\centering
-		\include{tbl-alternativeinternet}
-		\caption{A list with the top 10 projects from the Alternative Internet repository as of 2014-03-15, sorted on the number of commits.}
-		\label{tbl:altinternet}
-	\end{table}
-\end{landscape}
-
 \bibliographystyle{plain}

### 2014-03-25 tbl-alternativeinternet.tex
tabel inline en other changes

@@
-\begin{tabular}[p]{| r | l | p{3cm} | p{3cm} | p{3cm} | p{3cm} | p{3cm} | p{3cm} |}
+\begin{tabular}[p]{| r | l | p{2.2cm} | p{1.2cm} | p{2.2cm} | p{1.2cm} | p{1.5cm} | p{2.3cm} |}
 	\hline
@@
 
-	1 & ownCloud & PHP & 6 year(s) & 2014-03-15 & 1,297 K & 34,391 commit(s) & 392 contributor(s) \\ \hline
-	2 & Freenet & Java & 13 year(s) & 2014-03-15 & 442 K & 32,009 commit(s) & 183 contributor(s) \\ \hline
-	3 & Tor & C & 12 year(s) & 2014-03-13 & 329 K & 29,200 commit(s) & 184 contributor(s) \\ \hline
-	4 & GNUnet & C & 8 year(s) & 2014-03-13 & 427 K & 21,398 commit(s) & 37 contributor(s) \\ \hline
-	5 & StatusNet & PHP & 6 year(s) & 2014-03-14 & 230 K & 14,877 commit(s) & 92 contributor(s) \\ \hline
-	6 & Diaspora* & Ruby & 3 year(s) & 2014-03-14 & 51 K & 14,202 commit(s) & 368 contributor(s) \\ \hline
-	7 & SlapOS & Python & 8 year(s) & 2014-03-15 & 588 K & 14,046 commit(s) & 93 contributor(s) \\ \hline
-	8 &Tahoe-LAFS & Python & 7 year(s) & 2014-03-13 & 158 K & 11,565 commit(s) & 54 contributor(s) \\ \hline
-	9 & Tribler & Python & 8 year(s) & 2014-03-15 & 148 K & 11,521 commit(s) & 48 contributor(s) \\ \hline
-	10 & Lorea & PHP & 6 year(s) & 2014-03-12 & 873 K & 11,066 commit(s) & 96 contributor(s) \\ \hline
+	1 & ownCloud & PHP & 6 year(s) & 2014-03-15 & 1,297 K & 34,391 & 392 \\ \hline
+	2 & Freenet & Java & 13 year(s) & 2014-03-15 & 442 K & 32,009 & 183 \\ \hline
+	3 & Tor & C & 12 year(s) & 2014-03-13 & 329 K & 29,200 & 184 \\ \hline
+	4 & GNUnet & C & 8 year(s) & 2014-03-13 & 427 K & 21,398 & 37 \\ \hline
+	5 & StatusNet & PHP & 6 year(s) & 2014-03-14 & 230 K & 14,877 & 92 \\ \hline
+	6 & Diaspora* & Ruby & 3 year(s) & 2014-03-14 & 51 K & 14,202 & 368 \\ \hline
+	7 & SlapOS & Python & 8 year(s) & 2014-03-15 & 588 K & 14,046 & 93 \\ \hline
+	8 &Tahoe-LAFS & Python & 7 year(s) & 2014-03-13 & 158 K & 11,565 & 54 \\ \hline
+	9 & Tribler & Python & 8 year(s) & 2014-03-15 & 148 K & 11,521 & 48 \\ \hline
+	10 & Lorea & PHP & 6 year(s) & 2014-03-12 & 873 K & 11,066 & 96 \\ \hline
 \end{tabular}

### 2014-03-26 paper.tex
Remove commented out paragraphs
Fix indents
Move table down so it doesn't give a huge whitespace in the paper (might be a better solution)
\newpage gives ugly whitespace
Make references and footnotes clickable and add a PDF Index
Partially rewrote the part about increasing network costs as the number of hops in a cicruit increases

@@
 \usepackage{amssymb}
+\usepackage[bookmarks]{hyperref}
 
@@
 According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data.
+
 			Due to the fact that traffic travels over multiple Tor nodes, the total amount of transferred data in the network multiplies.
 This is illustrated in figure \ref{fig:hops}.
+Normally, when 1 GiB is transferred over the internet, it has a network cost of 2 GiB\footnote{1 GiB upload by the sender and 1 GiB download by the receiver, or 2 GiB in total.}.
 By having $n$ hops, the amount of transferred traffic would be multiplied by $2(n+1)$.
-This means that a 1 GiB transfer, using only 1 hop, would actually cost the network 4 GiB.
-By increasing the amount of Onion Routing in the Tor network, the capacity is increased.
+As Tor uses 3 hops by default, this means that a 1 GiB transfer would result in a network cost of 8 GiB.
+By increasing the amount of Onion Routing nodes in the Tor network, the capacity is increased.
 Incentives such as LIRA \cite{jansen13lira} could make more users run an Onion Router, thus increasing the capacity of the network and making it faster.
@@
 
-	\begin{landscape}
-
-	% Zelfde volgorde als hoofdstukken
-	% Deze bij hoofdstuk 5 plaatsen!!!
-	% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
-	\begin{table}[p]
-		\centering
-		\include{tbl-currentsystems}
-		\caption{A comparison of decentralized peer-to-peer overlay networks}
-		\label{tbl:comparison}
-	\end{table}
-
-	\end{landscape}
-
 \section{The documented struggle of alternative internet projects}
@@
 
-	\newpage
-
 \section{Conclusion}
@@
 
+\begin{landscape}
+	% Zelfde volgorde als hoofdstukken
+	% Deze bij hoofdstuk 5 plaatsen!!!
+	% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
+	\begin{table}[p]
+		\centering
+		\include{tbl-currentsystems}
+		\caption{A comparison of decentralized peer-to-peer overlay networks}
+		\label{tbl:comparison}
+	\end{table}
+\end{landscape}
+
 \bibliographystyle{plain}

### 2014-03-26 paper.tex
NA is not explained anymore, so better use the full name
period

@@
 This authority issues certificates to nodes that participate in the DHT, but it does not participate in the DHT itself.
-The NA makes this solution not a fully decentralized one, but its role is a lot smaller than the current Directory Servers.
+The Neighbourhood Authority makes this solution not a fully decentralized one, but its role is a lot smaller than the current Directory Servers.
 This does not solve the trust issue, but it does solve the scalability issue.

### 2014-03-26 paper.tex
Another set of changes that got reverted along the way

@@
 
-		By running a HTTP exit node and a Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
+		By running an HTTP exit node and a Tor router that eventually will act as an entry node in the network, an adversary can discover the identity of a user.
 The exit node injects an invisible iframe containing some JavaScript into any web page that passes through it, each sending a unique ID to a malicious web server.
@@
 		There are several techniques to add an entry to the routers NAT table.
-Universal Plug and Play (UPnP) is one of those techniques, where the local device uses a HTTP request to the router to associate a port with the devices private network address.
+Universal Plug and Play (UPnP) is one of those techniques, where the local device uses an HTTP request to the router to associate a port with the devices private network address.
 This technique is not available everywhere and sometimes considered a security risk.

### 2014-03-26 paper.tex
Removed the incorrect weapons of mass destructions comment and added source for silk road.

@@
 This serious problem is disrupting Tor's public image.
-A recent example is the shutdown of \emph{Silk Road}, which is an online market for trading prohibited substances, buying weapons of mass destruction and other illegal goods.
+A recent example is the shutdown of \emph{Silk Road}, which is an online market for trading prohibited substances and other illegal goods \cite{ibtimes2013}.
 The market operated as a hidden Tor service.

### 2014-03-26 tbl-currentsystems.tex
tabel inline en other changes
Modified table to use vertically oriented column headers

--- 2014-03-23 table.tex
@@
-\begin{tabular}[p]{| l | l | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} |}
+\begin{tabular}[p]{| l | l | l | l | l | l | l | l | l |}
 	\hline
-	\textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in \newline practice} & \textbf{(D)DoS protection} & \textbf{Sybil attack protection} & \textbf{MITM \newline protection} & \textbf{Unlinkability} \\ \hline
+	\parbox[t]{2mm}{\textbf{Name}} & \parbox[t]{2mm}{\textbf{Year}} & \parbox[t]{2mm}{\rotatebox[origin=l]{90}{\textbf{Tor interoperability}}} & \parbox[t]{2mm}{\rotatebox[origin=l]{90}{\textbf{Public implementation}}} & \parbox[t]{2mm}{\rotatebox[origin=l]{90}{\textbf{Used in practice}}} & \parbox[t]{2mm}{\rotatebox[origin=l]{90}{\textbf{(D)DoS protection}}} & \parbox[t]{2mm}{\rotatebox[origin=l]{90}{\textbf{Sybil attack protection}}} & \parbox[t]{2mm}{\rotatebox[origin=l]{90}{\textbf{MITM protection}}} & \parbox[t]{2mm}{\rotatebox[origin=l]{90}{\textbf{Unlinkability}}} \\ \hline
 
@@
 	Pastry & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \xmark \\ \hline
-	AP3 & 2004 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
 	Tarzan & 2002 & \xmark & \xmark & \xmark & ? & \checkmark & ? & \checkmark \\ \hline
@@
 	I2P & 2003 & \xmark & \checkmark & \checkmark & \checkmark & \checkmark & ? & \checkmark\\ \hline
+	AP3 & 2004 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
 	Salsa & 2006 & \xmark & \xmark & \xmark & \checkmark & \checkmark & ? & \checkmark \\ \hline

### 2014-03-26 paper.tex
Moved comparison table to chapter 5, removed landscape page
Indents.
Modified chapter 6 and 7 to be more structurally coherent

@@
 
+		% Zelfde volgorde als hoofdstukken
+		% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
+		\begin{table}[t]
+			\centering
+			\include{tbl-currentsystems}
+			\caption{A comparison of decentralized peer-to-peer overlay networks.}
+			\label{tbl:comparison}
+		\end{table}
+
 \section{The documented struggle of alternative internet projects}
@@
 	The largest repository of decentralization attempts is located at http://redecentralize.org.
+The aim of this repository is to \textquoteleft get decentralized products into the hands of billions\textquoteright \cite{aboutredecentralizeorg}.
+One of the ways they do this, is by maintaining a Github repository\footnote{Found at https://github.com/redecentralize/alternative-internet} with projects that in some way help to decentralize the internet.
 The struggle and pains of these projects illustrates the difficulty of decentralization.
 No projects succeeded in creating an alternative internet infrastructure.
-This ranges from self hosted cloud applications, to crypto currencies, to anonymous networks.
+The projects range from self hosted cloud applications, to crypto currencies, to anonymous networks.
 
@@
 
-	Redecentralize.org is a project that describes itself with the aim to \textquoteleft start of a new information revolutions\textquoteright~by \textquoteleft bringing decentralized in the hands of billions\textquoteright~\cite{aboutredecentralizeorg}.
+	%Redecentralize.org is a project that describes itself with the aim to \textquoteleft start of a new information revolutions\textquoteright~by \textquoteleft bringing decentralized in the hands of billions\textquoteright~\cite{aboutredecentralizeorg}.
 One of the ways they do this, is by maintaining a Github repository\footnote{Found at https://github.com/redecentralize/alternative-internet} with projects that in some way help to decentralize the internet.
-This ranges from self hosted cloud applications, to crypto currencies, to anonymous networks.
 
 	We made a significant contribution to this project index.
-	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of these decentralized systems.
+We have improved and updated the list of these decentralized systems.
 For each of the listed systems, we have created an entry in a table that shows statistics such as the total lines of code (LOC), age, number of contributors and commits, activity and (main) programming language, sourced from Ohloh.
@@
 	An excerpt of the table is included as table \ref{tbl:altinternet}.
-In this instance, we chose to sort the table on the number of commits, because we found that this most accurately represented projects that have been established for some time and have been active in the past days.
+In this instance, we chose to sort the table on the number of commits, because we find that this most accurately represents both the maturity and activity of the projects.
 Other statistics such as LOC might not be very relevant on their own, because some projects include big libraries or other projects.
@@
 
-	So although clear differences aren't directly noticeable, we hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.
+	So although clear differences aren't directly noticeable, we hope that this comparison will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.
 
@@
 Furthermore, we looked at the main disadvantages and problems Tor is currently facing.
-We investigated the issues around decentralization.
-After that, we've written which systems currently have a decentralized structure and/or mechanism.
-These systems are then compared to each other with their pros and cons.
+We investigated the issues around decentralization and compared systems that currently have a decentralized structure and/or mechanism.
 
@@
 The current generation of technology lead by Tor still has room for improvement, while the next generation is only just appearing on the horizon.
-
-\begin{landscape}
-	% Zelfde volgorde als hoofdstukken
-	% Deze bij hoofdstuk 5 plaatsen!!!
-	% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
-	\begin{table}[p]
-		\centering
-		\include{tbl-currentsystems}
-		\caption{A comparison of decentralized peer-to-peer overlay networks.}
-		\label{tbl:comparison}
-	\end{table}
-\end{landscape}
+The major problems involving decentralization are excruciatingly difficult to overcome.
+None of the projects have succeeded in making the internet secure and private.
 

### 2014-03-26 tbl-alternativeinternet.tex
Table column alignment, so they all fit on one row
Center table headers

@@
-\begin{tabular}[p]{| r | l | p{2.2cm} | p{1.2cm} | p{2.2cm} | p{1.2cm} | p{1.5cm} | p{2.3cm} |}
+\begin{tabular}[p]{| r | l | p{1.5cm} | r | r | r | r | r |}
 	\hline
-	\textbf{\#} & \textbf{Name} & \textbf{Language} & \textbf{Age} & \textbf{Last activity} & \textbf{LOC} & \textbf{Commits} & \textbf{Contributors} \\ \hline
+	\tblhead{\#} & \tblhead{Name} & \tblhead{Language} & \tblhead{Age} & \tblhead{Last activity} & \tblhead{LOC} & \tblhead{Commits} & \tblhead{Contributors} \\ \hline
 

### 2014-03-26 tbl-alternativeinternet.tex
year(s) to years

@@
 
-	1 & ownCloud & PHP & 6 year(s) & 2014-03-15 & 1,297 K & 34,391 & 392 \\ \hline
-	2 & Freenet & Java & 13 year(s) & 2014-03-15 & 442 K & 32,009 & 183 \\ \hline
-	3 & Tor & C & 12 year(s) & 2014-03-13 & 329 K & 29,200 & 184 \\ \hline
-	4 & GNUnet & C & 8 year(s) & 2014-03-13 & 427 K & 21,398 & 37 \\ \hline
-	5 & StatusNet & PHP & 6 year(s) & 2014-03-14 & 230 K & 14,877 & 92 \\ \hline
-	6 & Diaspora* & Ruby & 3 year(s) & 2014-03-14 & 51 K & 14,202 & 368 \\ \hline
-	7 & SlapOS & Python & 8 year(s) & 2014-03-15 & 588 K & 14,046 & 93 \\ \hline
-	8 &Tahoe-LAFS & Python & 7 year(s) & 2014-03-13 & 158 K & 11,565 & 54 \\ \hline
-	9 & Tribler & Python & 8 year(s) & 2014-03-15 & 148 K & 11,521 & 48 \\ \hline
-	10 & Lorea & PHP & 6 year(s) & 2014-03-12 & 873 K & 11,066 & 96 \\ \hline
+	1 & ownCloud & PHP & 6 years & 2014-03-15 & 1,297 K & 34,391 & 392 \\ \hline
+	2 & Freenet & Java & 13 years & 2014-03-15 & 442 K & 32,009 & 183 \\ \hline
+	3 & Tor & C & 12 years & 2014-03-13 & 329 K & 29,200 & 184 \\ \hline
+	4 & GNUnet & C & 8 years & 2014-03-13 & 427 K & 21,398 & 37 \\ \hline
+	5 & StatusNet & PHP & 6 years & 2014-03-14 & 230 K & 14,877 & 92 \\ \hline
+	6 & Diaspora* & Ruby & 3 years & 2014-03-14 & 51 K & 14,202 & 368 \\ \hline
+	7 & SlapOS & Python & 8 years & 2014-03-15 & 588 K & 14,046 & 93 \\ \hline
+	8 &Tahoe-LAFS & Python & 7 years & 2014-03-13 & 158 K & 11,565 & 54 \\ \hline
+	9 & Tribler & Python & 8 years & 2014-03-15 & 148 K & 11,521 & 48 \\ \hline
+	10 & Lorea & PHP & 6 years & 2014-03-12 & 873 K & 11,066 & 96 \\ \hline
 \end{tabular}

### 2014-03-26 paper.tex
Center table headers
find -> found

@@
 \newcommand{\xmark}{\sffamily x}
+\newcommand{\tblhead}[1]{\multicolumn{1}{| c |}{\textbf{#1}}}
 
@@
 	An excerpt of the table is included as table \ref{tbl:altinternet}.
-In this instance, we chose to sort the table on the number of commits, because we find that this most accurately represents both the maturity and activity of the projects.
+In this instance, we chose to sort the table on the number of commits, because we found that this most accurately represents both the maturity and activity of the projects.
 Other statistics such as LOC might not be very relevant on their own, because some projects include big libraries or other projects.

### 2014-03-26 paper.tex
Rewrote paragraph about altinternet repository partially

@@
 	We made a significant contribution to this project index.
-We have improved and updated the list of these decentralized systems.
-For each of the listed systems, we have created an entry in a table that shows statistics such as the total lines of code (LOC), age, number of contributors and commits, activity and (main) programming language, sourced from Ohloh.
-This table is available on the same Github repository.
+We created a table containing each of the listed systems that shows statistics such as the total lines of code (LOC), age, number of contributors and commits, activity and (main) programming language, sourced from Ohloh.
+This should make it easier to filter out poorly maintained or otherwise deprecated projects.
+The table is available on the same Github repository.
 
@@
 In this instance, we chose to sort the table on the number of commits, because we found that this most accurately represents both the maturity and activity of the projects.
-Other statistics such as LOC might not be very relevant on their own, because some projects include big libraries or other projects.
+Other statistics such as LOC might not be very relevant on their own, because some projects include big libraries or other projects in their repository.
 
@@
 
-	% Tabel moet nog mooi gemaakt worden
 	\begin{table}

### 2014-03-26 paper.tex
Made OR1 / OR2 more readable in the section about Tor circuit creation

@@
 Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
-To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake to the first node in her selected path (for example, OR1).
-OR1 sends a \emph{created} cell back with the second half of the key along with a hash of the final key.
-Now both Alice and OR1 have a shared key they use to encrypt and decrypt data sent between them.
+To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake to the first node in her selected path (for example, $ OR_1 $).
+$ OR_1 $ sends a \emph{created} cell back with the second half of the key along with a hash of the final key.
+Now both Alice and $ OR_1 $ have a shared key they use to encrypt and decrypt data sent between them.
 
 		So now Alice has a connection with the first Onion Router in the circuit.
-To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1.
+To extend the circuit to $ OR_2 $, Alice first sends a \emph{relay extend} cell to $ OR_1 $.
 This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2.
-OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2.
-When OR1 receives a created cell, OR1 passes this cell to Alice.
-Now Alice and OR2 share a common key.
+$ OR_1 $ takes this first half of the key and sends a \emph{create} cell with this key to $ OR_2 $.
+When $ OR_1 $ receives a created cell, $ OR_1 $ passes this cell to Alice.
+Now Alice and $ OR_2 $ share a common key.
 The same procedure can be used to extend the circuit with more nodes.

### 2014-03-26 paper.tex
Replaced a comma in an enumeration to 'and' (H6)

@@
 
-	In the table we notice that three of the entries are privacy-enhancing networks that aim to provide unlinkability (Freenet, Tor, GNUnet), plus one that is currently in the process of implementing such a feature (Tribler).
+	In the table we notice that three of the entries are privacy-enhancing networks that aim to provide unlinkability (Freenet, Tor and GNUnet), plus one that is currently in the process of implementing such a feature (Tribler).
 Furthermore we notice that, once above a certain threshold, none of the statistics have a clear effect on a projects popularity.

### 2014-03-26 paper.tex
Minor typo fixes

@@
 To extend the circuit to $ OR_2 $, Alice first sends a \emph{relay extend} cell to $ OR_1 $.
-This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2.
+This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and $ OR_2 $.
 $ OR_1 $ takes this first half of the key and sends a \emph{create} cell with this key to $ OR_2 $.
@@
 
-	The largest repository of decentralization attempts is located at http://redecentralize.org.
+	The largest repository of decentralization attempts is located at redecentralize.org.
 The aim of this repository is to \textquoteleft get decentralized products into the hands of billions\textquoteright \cite{aboutredecentralizeorg}.
@@
 
-	So although clear differences aren't directly noticeable, we hope that this comparison will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.
+	So although clear differences aren't directly noticeable, we hope that this comparison will provide more insight into which systems are more serious and mature than others, while also showing which ones are still actively maintained.
 

### 2014-03-26 paper.tex
typo fixes in intro

--- 2014-03-26 paper.tex
@@
 	The most widely used anonymous communication system is Tor.
-In this paper we will analyze Tor and its semi-centralized nature.
+In this technical report we will analyze Tor and its semi-centralized nature.
 Tor struggles to keep up with the bandwidth demands of its users.
 As the number of users increases, the need to decentralize Tor becomes more urgent.
-Decentralizing Tor isn't an easy task: After 15 years of decentralization attempts, the network is still centralized.
+Decentralizing Tor isn't an easy task: After fifteen years of decentralization attempts, the network is still partially centralized.
 Only few decentralized alternatives to Tor exist, however they lack the user base to be considered safe and useful.
@@
 Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
-To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake to the first node in her selected path (for example, $ OR_1 $).
-$ OR_1 $ sends a \emph{created} cell back with the second half of the key along with a hash of the final key.
-Now both Alice and $ OR_1 $ have a shared key they use to encrypt and decrypt data sent between them.
+To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake to the first node in her selected path (for example, OR1).
+OR1 sends a \emph{created} cell back with the second half of the key along with a hash of the final key.
+Now both Alice and OR1 have a shared key they use to encrypt and decrypt data sent between them.
 
 		So now Alice has a connection with the first Onion Router in the circuit.
-To extend the circuit to $ OR_2 $, Alice first sends a \emph{relay extend} cell to $ OR_1 $.
+To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1.
 This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2.
-$ OR_1 $ takes this first half of the key and sends a \emph{create} cell with this key to $ OR_2 $.
-When $ OR_1 $ receives a created cell, $ OR_1 $ passes this cell to Alice.
-Now Alice and $ OR_2 $ share a common key.
+OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2.
+When OR1 receives a created cell, OR1 passes this cell to Alice.
+Now Alice and OR2 share a common key.
 The same procedure can be used to extend the circuit with more nodes.

### 2014-03-26 paper.tex
The Onion Router was abbreviated as TOR, the current version is called Tor
Commented out paragraphs are bad, m'kay
would -> could

@@
 
-	The implementation of The Onion Router (Tor) was first described in 1996 by the U.S.
+	The implementation of The Onion Router (TOR) was first described in 1996 by the U.S.
 Navy Research Laboratory, as a means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
@@
 A trusted central authority simplifies bootstrapping, key management and user reputation.
-If one of these authorities were taken control of, anonymity would be compromised.
+If one of these authorities were taken control of, anonymity could be compromised.
 When decentralizing a central authority, its functionality needs to be dispersed across the peers in the network.

### 2014-03-26 paper.tex
Fixed minor typos + changed 'Directory Servers' to 'directory servers'

@@
 
-		To mitigate these concerns, Directory Servers were introduced to Tor during its reimplementation.
-These Directory Servers keep a redundant central consensus about the network.
+		To mitigate these concerns, directory servers were introduced to Tor during its reimplementation.
+These directory servers keep a redundant central consensus about the network.
 They act as HTTP servers to which Tor nodes can publish signed information about themselves.
@@
 
-		The information distributed by the Directory Servers is signed.
-The keys to verify these signatures are preloaded in the Tor software, along with the list of Directory Servers.
-This implies trust by the Tor client in the Directory Servers.
+		The information distributed by the directory servers is signed.
+The keys to verify these signatures are preloaded in the Tor software, along with the list of directory servers.
+This implies trust by the Tor client in the directory servers.
 
@@
 The same node cannot be used more than once in a single circuit.
-
-		%As described in the previous section, data on the Tor networks travels over circuits.
-The data travels over the circuit in fixed-size cells that are 512 bytes long.
-Each cell has a header and a payload.
-The header consists of a number that identifies the circuit the cell travels on and a command that indicates what to do with the cell’s payload.
-
-		%Before a circuit can be established, a path has to be chosen.
-The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes \cite{wang2012congestion}.
-Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.
 
@@
 It is used in the circuit creation in Onion Routing (see section \ref{ss:tor_circuit}) for example.
-However, it is possible for an adversary to manipulate the keys send between two parties, making the protocol vulnerable to a man-in-the-middle attack.
+However, it is possible for an adversary to manipulate the keys exchanged between two parties, making the protocol vulnerable to a man-in-the-middle attack.
 This weakness makes it possible for an adversary to decrypt all messages sent between the two parties.
@@
 		NISAN, or Network Information Service for Anonymization Networks \cite{panchenko2006nisan}, is an anonymization network which implements a distributed node discovery.
-Not only does a central node administrator (the Directory Server in Tor) imply trust in those servers, Panchenko et al.
-also argue that a central node administration (the Directory Server in Tor) does not scale.
+Not only does a central node administrator (the directory server in Tor) imply trust in those servers, Panchenko et al.
+also argue that a central node administration (the directory server in Tor) does not scale.
 The current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.
@@
 
-		Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority.
+		Instead of the directory servers, it uses a DHT and a new Neighbourhood Authority.
 The DHT is a combination of Kademlia DHT and Myrmic DHT.
@@
 This authority issues certificates to nodes that participate in the DHT, but it does not participate in the DHT itself.
-The Neighbourhood Authority makes this solution not a fully decentralized one, but its role is a lot smaller than the current Directory Servers.
+The Neighbourhood Authority makes this solution not a fully decentralized one, but its role is a lot smaller than the current directory servers.
 This does not solve the trust issue, but it does solve the scalability issue.
@@
 	%
-
-	%Redecentralize.org is a project that describes itself with the aim to \textquoteleft start of a new information revolutions\textquoteright~by \textquoteleft bringing decentralized in the hands of billions\textquoteright~\cite{aboutredecentralizeorg}.
-One of the ways they do this, is by maintaining a Github repository\footnote{Found at https://github.com/redecentralize/alternative-internet} with projects that in some way help to decentralize the internet.
 

### 2014-03-26 paper.tex
changed sentence in circuit creation
removed the \textit command from several words

@@
 
-		So now Alice has a connection with the first Onion Router in the circuit.
+		Alice now has a connection with the first Onion Router in the circuit.
 To extend the circuit to $ OR_2 $, Alice first sends a \emph{relay extend} cell to $ OR_1 $.
@@
 This technique is not available everywhere and sometimes considered a security risk.
-Different implementations of NAT require different techniques, such as \textit{hole punching}, \textit{relaying} or \textit{reversal}, as described by Wocker et al.
+Different implementations of NAT require different techniques, such as hole punching, relaying or reversal, as described by Wocker et al.
 \cite{wacker2008nat}.

### 2014-03-26 paper.tex
Removed more emphs

@@
 
-		With the second generation onion routing used in Tor, a modified algorithm is used to derive the encryption keys, called \emph{telescoping path-building}, which also provides perfect forward secrecy.
+		With the second generation onion routing used in Tor, a modified algorithm is used to derive the encryption keys, called telescoping path-building, which also provides perfect forward secrecy.
 This algorithm is described in section \ref{ss:tor_circuit}.
@@
 	\subsection{Low-resource routing attacks}
-		Another possible attack on the anonymity of Tor is the so called \emph{low-resource routing attack} \cite{bauer2007low}.
+		Another possible attack on the anonymity of Tor is the so called low-resource routing attack \cite{bauer2007low}.
 With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resources, thus compromising the anonymity Tor provides.
@@
 		Rahman \cite{rahman2009survey} proposes several options to build incentives in a peer-to-peer network.
-The first proposal that is described is the so called \emph{Warm-glow Model}.
+The first proposal that is described is the so called Warm-glow Model.
 This model determines the percentage of free-rides based on the probabilistic population distribution.
@@
 
-		The third proposal is \emph{Reciprocity-Based Schemes}.
+		The third proposal is Reciprocity-Based Schemes.
 Using this approach, a peer maintains a behavior history of other peers in the network.
@@
 
-		Tor currently uses an interactive forward-secret key-exchange protocol called the \emph{Tor Authentication Protocol} (TAP) \cite{backes2012ace}.
+		Tor currently uses an interactive forward-secret key-exchange protocol called the Tor Authentication Protocol (TAP) \cite{backes2012ace}.
 This protocol uses telescoping, which means that the initiator negotiates session keys with each successive hop in the circuit.
 There are several proposals for more efficient key exchange methods.
-One of them is \emph{ACE}, an one-way authenticated key exchange protocol.
+One of them is ACE, an one-way authenticated key exchange protocol.
 The authors of this methods claim to have a 46\% efficiency improvement on the side of the client and nearly 19\% on the side of the Onion Routers.
@@
 		Gnutella is a decentralized peer-to-peer network used for distributed search of files.
-Since the network is fully decentralized, peers in the network are called \emph{servents}, a combination of the words servers and clients.
+Since the network is fully decentralized, peers in the network are called servents, a combination of the words servers and clients.
 Each peer can act both as a server, answering queries, or as a client, requesting and executing search queries.

### 2014-03-26 paper.tex
Neighbourhood Authorithy -> neighborhood authority

@@
 
-		Instead of the directory servers, it uses a DHT and a new Neighbourhood Authority.
+		Instead of the directory servers, it uses a DHT and a new neighbourhood authority.
 The DHT is a combination of Kademlia DHT and Myrmic DHT.
@@
 
-		The Myrmic DHT runs on top of Kademlia, and introduces the Neighbourhood Authority.
+		The Myrmic DHT runs on top of Kademlia, and introduces the neighbourhood authority.
 This authority issues certificates to nodes that participate in the DHT, but it does not participate in the DHT itself.
-The Neighbourhood Authority makes this solution not a fully decentralized one, but its role is a lot smaller than the current directory servers.
+The neighbourhood authority makes this solution not a fully decentralized one, but its role is a lot smaller than the current directory servers.
 This does not solve the trust issue, but it does solve the scalability issue.

### 2014-03-26 paper.tex
fixed typo

@@
 
-		The first router in a circuit is the entrance router. The entrance router sends the data to one of the middle router which forwards the data to the exit router.
+		The first router in a circuit is the entrance router. The entrance router sends the data to one of the middle routers which forwards the data to the exit router.
 
@@
 
-			\item Some Tor users put more traffic on the network than they contribute by running a Onion Router.
+			\item Some Tor users put more traffic on the network than they contribute by running an Onion Router.
 This means that these users are slowing the network down as they use more traffic than giving back.

### 2014-03-26 paper.tex
Changed Onion Router -> onion router
And Onion Proxy -> onion proxy etc

@@
 		The Tor network consists of several components.
-The clients in the Tor network are known as Onion Proxies.
-The software to run an Onion Proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy for users to configure.
-The Onion Proxies are responsible for downloading the directory information, establishing circuits across the network and handling connections from user applications.
+The clients in the Tor network are known as onion proxies.
+The software to run an onion proxy is available for free on the Tor website \cite{torprojectwebsite} and is easy for users to configure.
+The onion proxies are responsible for downloading the directory information, establishing circuits across the network and handling connections from user applications.
 
-		The routing in the network is done by Onion Routers, also called relay nodes.
-The relay nodes relay the data from the Onion Proxy to the web server across a circuit (circuits are described in \ref{ss:tor_circuit}).
-Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}.
-Each circuit has three type of Onion Routers \cite{mccoy2008shining}:
+		The routing in the network is done by onion routers, also called relay nodes.
+The relay nodes relay the data from the onion proxy to the web server across a circuit (circuits are described in \ref{ss:tor_circuit}).
+Each onion router is connected to every other onion router with a TLS connection \cite{tlsprotocol}.
+Each circuit has three type of onion routers \cite{mccoy2008shining}:
 
 		\begin{itemize}
-			\item{The entrance Tor router:} this router is directly connected to an Onion Proxy and can observe the origin of a request through the Tor network.
+			\item{The entrance Tor router:} this router is directly connected to an onion proxy and can observe the origin of a request through the Tor network.
 The entrance router sends the packet to the middle Tor router.
@@
 
-		Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a web server.
+		Suppose Alice is an onion proxy that wants to connect through the Tor network to a web server.
 Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
@@
 
-		Alice now has a connection with the first Onion Router in the circuit.
+		Alice now has a connection with the first onion router in the circuit.
 To extend the circuit to $ OR_2 $, Alice first sends a \emph{relay extend} cell to $ OR_1 $.
-This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and $ OR_2 $.
+This cell contains the address of the next onion router in the circuit and the first half of the key to use in the communication between her and $ OR_2 $.
 $ OR_1 $ takes this first half of the key and sends a \emph{create} cell with this key to $ OR_2 $.
@@
 
-			\item Some Tor users put more traffic on the network than they contribute by running an Onion Router.
+			\item Some Tor users put more traffic on the network than they contribute by running an onion router.
 This means that these users are slowing the network down as they use more traffic than giving back.
-A possible solution for this is to throttle certain high-bandwidth protocols such as BitTorrent at exit nodes or at Onion Proxies.
+A possible solution for this is to throttle certain high-bandwidth protocols such as BitTorrent at exit nodes or at onion proxies.
 
@@
 As Tor uses 3 hops by default, this means that a 1 GiB transfer would result in a network cost of 8 GiB.
-By increasing the amount of Onion Routing nodes in the Tor network, the capacity is increased.
-Incentives such as LIRA \cite{jansen13lira} could make more users run an Onion Router, thus increasing the capacity of the network and making it faster.
+By increasing the amount of onion routing nodes in the Tor network, the capacity is increased.
+Incentives such as LIRA \cite{jansen13lira} could make more users run an onion router, thus increasing the capacity of the network and making it faster.
 
@@
 With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resources, thus compromising the anonymity Tor provides.
-The idea of this attack is that a malicious Onion router can lie about its bandwidth, thus advertising a much higher bandwidth than it actually has.
+The idea of this attack is that a malicious onion router can lie about its bandwidth, thus advertising a much higher bandwidth than it actually has.
 Because of the Tor path selection algorithm that prefers high-bandwidth nodes, the chance that a malicious entry and exit node are chosen is high.
 
-		Once a malicious entry and exit node have been chosen, an analysis of the traffic can be done to link Onion proxies with the web servers they communicate with.
+		Once a malicious entry and exit node have been chosen, an analysis of the traffic can be done to link onion proxies with the web servers they communicate with.
 Experimental research in a test setting has shown that with a total of 66 non-malicious and 6 malicious nodes, is possible to compromise 46\% of the built circuits.
@@
 One of them is ACE, an one-way authenticated key exchange protocol.
-The authors of this methods claim to have a 46\% efficiency improvement on the side of the client and nearly 19\% on the side of the Onion Routers.
+The authors of this methods claim to have a 46\% efficiency improvement on the side of the client and nearly 19\% on the side of the onion routers.
 ACE requires clients to send one extra element in the key exchange.

### 2014-03-26 paper.tex
Full spellcheck over final version

@@
 	The most widely used anonymous communication system is Tor.
-In this technical report we will analyze Tor and its semi-centralized nature.
+In this technical report we will analyse Tor and its semi-centralized nature.
 Tor struggles to keep up with the bandwidth demands of its users.
@@
 Navy Research Laboratory, as a means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}.
-The idea behind onion routing traces back to 1981, where Chaum described it in his famous paper "Untraceable electronic mail, return addresses, and digital pseudonyms" \cite{chaum1981untraceable}.
+The idea behind onion routing traces back to 1981, where Chaum described it in his famous paper \textquotedblleft Untraceable electronic mail, return addresses, and digital pseudonyms\textquotedblright \cite{chaum1981untraceable}.
 
@@
 This algorithm selects nodes based on the bandwidth of the nodes \cite{wang2012congestion}.
-Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup.
+Nodes that have more bandwidth, have a higher probability to be chosen for the circuit creation.
 The same node cannot be used more than once in a single circuit.
@@
 		Suppose Alice is an onion proxy that wants to connect through the Tor network to a web server.
-Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
+Circuit creation uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes.
 To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake to the first node in her selected path (for example, $ OR_1 $).
@@
 		The third proposal is Reciprocity-Based Schemes.
-Using this approach, a peer maintains a behavior history of other peers in the network.
+Using this approach, a peer maintains a behaviour history of other peers in the network.
 These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity.
@@
 Many such systems have been proposed, yet only some have been implemented and are currently in use and actively maintained \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}.
-Here we focus on fully decentralized networks with the exception of Torsk (which is almost fully decentralized but still requires a Neighborhood Authority).
+Here we focus on fully decentralized networks with the exception of Torsk (which is almost fully decentralized but still requires a neighbourhood authority).
 
@@
 It relies on nested encryption and routing traffic over multiple nodes to ensure anonymity of its users' communication.
-Additionally, MorphMix uses the typical behavior of a MIX network, where it reorders messages that enter a node before sending them out.
+Additionally, MorphMix uses the typical behaviour of a MIX network, where it reorders messages that enter a node before sending them out.
 
@@
 	\subsection{Torsk} % 2009
-		Torsk \cite{mclachlan2009scalable} is an extension to Tor, designed to be an interoperable replacement for the circuit creation and Directory Service as used by Tor.
-The authors argue that the current Directory Service does not scale, with the percentage of the traffic in a network dedicated to node discovery growing as the number of nodes grow.
+		Torsk \cite{mclachlan2009scalable} is an extension to Tor, designed to be an interoperable replacement for the circuit creation and directory servers as used by Tor.
+The authors argue that the current directory servers do not scale, with the percentage of the traffic in a network dedicated to node discovery growing as the number of nodes grow.
 With the 2009 version of Tor, they argue that 100\% of the networks traffic would consist of node discovery traffic with roughly 1.2 million clients.

### 2014-03-28 alternative-internet-crawler/generate_tables.py
Add option to specify logger level

@@ -171,7 +171,6 @@ def main():
     """
     Main entry point of the application, execution starts here
     """
-    logging.getLogger().setLevel(logging.INFO)
     description = 'Parses JSON files generated by the alternative internet crawler and generates a markdown table.'
     parser = ArgumentParser(description=description)
 
@@ -190,8 +189,12 @@ def main():
                         help='Link from header to sorted versions, plus link from entries to readme.md')
     parser.add_argument('-a', '-all', action='store_true', dest='generate_all', required=False,
                         help='Generate all files as TABLE_COLUMN_NAME.md (-s, -r, -o are ignored)')
+    parser.add_argument('--debug', action='store_true', dest='debug', required=False, help='Enable debug output')
 
     args = parser.parse_args()
+    logging.getLogger().setLevel(logging.DEBUG if args.debug == True else logging.INFO)
+
+    logging.debug(args)
 
     run_parser(directory=args.directory, output=args.output, sort_on=args.sort, sort_reverse=args.sort_reverse,
                add_links=args.add_links, generate_all=args.generate_all)

### 2014-03-28 alternative-internet-crawler/generate_tables.py
Don't need the api key in the generator

@@ -174,9 +174,6 @@ def main():
     description = 'Parses JSON files generated by the alternative internet crawler and generates a markdown table.'
     parser = ArgumentParser(description=description)
 
-    #parser.add_argument('-a', '--api', action='store', dest='api', metavar="api", default='', required=True,
-    #                    help='Your Ohloh API key.')
-
     parser.add_argument('-d', '--directory', action='store', dest='directory', metavar='directory/',
                         default='projects', required=False, help='Directory to read the JSON files from')
     parser.add_argument('-o', '--output', action='store', dest='output', metavar='output.md', default='readme.md',

### 2014-03-28 alternative-internet-crawler/generate_tables.py
Add option to add 'totals:' entry at the bottom of the table as suggested by Pouwelse

@@ -69,6 +69,19 @@ def get_markdown_table_header(columns, add_links, sort_on=None):
         return '%s%s%s\n' % ('| ', ' | '.join(columns.values()), ' |')
 
 
+def get_markdown_table_totals(columns, projects):
+    total_entry = {}
+    for key in columns.keys():
+        entries = filter(lambda k: key in k.keys(), projects)
+        total_entry[key] = sum(int(project[key]) if (not project[key] is None and project[key].isdigit()) else 0 for project in entries)
+        if total_entry[key] == 0:
+            total_entry[key] = '-'
+
+    total_entry['name'] = '**Total:**'
+
+    return get_markdown_table_entry(columns, total_entry, False)
+
+
 def get_markdown_table_divider(columns):
     divider = columns.copy()
     for key in divider.keys():
@@ -123,7 +136,7 @@ def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
     return sorted_list
 
 
-def write_output(projects, table_columns, output='readme.md', sort_on='name', sort_reverse=False, add_links=False):
+def write_output(projects, table_columns, output='readme.md', sort_on='name', sort_reverse=False, add_links=False, add_totals=False):
 
     with codecs.open(output, 'w', 'utf-8-sig') as output_file:
         if add_links:
@@ -144,10 +157,14 @@ def write_output(projects, table_columns, output='readme.md', sort_on='name', so
             except:
                 logging.warning('Parsing entry failed (%s)' % project)
 
+        if add_totals:
+            header = get_markdown_table_totals(table_columns, projects)
+            output_file.write(header)
+
     logging.info('Wrote table to %s' % output)
 
 
-def run_parser(directory='projects', output='readme.md', sort_on='name', sort_reverse=False, add_links=False, generate_all=False):
+def run_parser(directory='projects', output='readme.md', sort_on='name', sort_reverse=False, add_links=False, generate_all=False, add_totals=False):
     table_columns = OrderedDict([('name', 'Name'), ('main_language', 'Language'), ('min_month', 'Age'),
                                  ('updated_at', 'Last activity'), ('total_code_lines', 'LOC'),
                                  ('total_commit_count', 'Commits'), ('total_contributor_count', 'Contributors')])
@@ -161,10 +178,10 @@ def run_parser(directory='projects', output='readme.md', sort_on='name', sort_re
         for key in table_columns.keys():
             write_output(projects=projects, table_columns=table_columns,
[…]

### 2014-03-28 alternative-internet-crawler/generate_tables.py
== True not needed

@@ -208,7 +208,7 @@ def main():
     parser.add_argument('--debug', action='store_true', dest='debug', required=False, help='Enable debug output')
 
     args = parser.parse_args()
-    logging.getLogger().setLevel(logging.DEBUG if args.debug == True else logging.INFO)
+    logging.getLogger().setLevel(logging.DEBUG if args.debug else logging.INFO)
 
     logging.debug(args)
 

### 2014-03-28 alternative-internet-crawler/generate_tables.py
Also sum the project age

@@ -23,7 +23,7 @@ Otherwise, to use "readme.md" and "projects" as defaults, use:
 
 from argparse import ArgumentParser
 from collections import OrderedDict
-from datetime import datetime
+from datetime import datetime, timedelta
 import logging
 import json
 import os
@@ -73,7 +73,19 @@ def get_markdown_table_totals(columns, projects):
     total_entry = {}
     for key in columns.keys():
         entries = filter(lambda k: key in k.keys(), projects)
-        total_entry[key] = sum(int(project[key]) if (not project[key] is None and project[key].isdigit()) else 0 for project in entries)
+
+        if key == 'min_month':
+            total_time = timedelta(0)
+
+            for x in entries:
+                entry_time = (datetime.utcnow() - datetime.strptime(x[key], '%Y-%m-%dT%H:%M:%SZ')) if not x[key] is None else timedelta(0)
+                total_time = total_time + entry_time
+
+            # datetime.strftime() doesn't like years before 1900, so we'll just use a modified isotime() instead
+            total_entry[key] = "%sZ" % ((datetime.utcnow() - total_time).isoformat().strip().split(".")[0])
+        else:
+            total_entry[key] = sum(int(project[key]) if (not project[key] is None and project[key].isdigit()) else 0 for project in entries)
+
         if total_entry[key] == 0:
             total_entry[key] = '-'
 
@@ -102,6 +114,7 @@ def get_markdown_table_entry_format_timedelta(td):
         return '%s month(s)' % int(td.total_seconds() / (sday * 30))
     else:
         return '%s year(s)' % int(td.total_seconds() / (sday * 356))
+
 
 def get_markdown_table_entry(columns, project, add_links):
     format_functions = {'name': lambda s, l: get_markdown_table_entry_format_name(s) if l else s,

### 2014-03-28 alternative-internet-crawler/generate_tables.py
Move function up

@@ -69,6 +69,14 @@ def get_markdown_table_header(columns, add_links, sort_on=None):
         return '%s%s%s\n' % ('| ', ' | '.join(columns.values()), ' |')
 
 
+def get_markdown_table_divider(columns):
+    divider = columns.copy()
+    for key in divider.keys():
+        divider[key] = '-' * len(divider[key])
+
+    return get_markdown_table_header(divider, add_links=False)
+
+
 def get_markdown_table_totals(columns, projects):
     total_entry = {}
     for key in columns.keys():
@@ -92,13 +100,6 @@ def get_markdown_table_totals(columns, projects):
     total_entry['name'] = '**Total:**'
 
     return get_markdown_table_entry(columns, total_entry, False)
-
-
-def get_markdown_table_divider(columns):
-    divider = columns.copy()
-    for key in divider.keys():
-        divider[key] = '-' * len(divider[key])
-    return get_markdown_table_header(divider, add_links=False)
 
 
 def get_markdown_table_entry_format_name(entry):

### 2014-03-28 alternative-internet-crawler/generate_tables.py
Remove contributor(s) and commit(s)

@@ -120,8 +120,8 @@ def get_markdown_table_entry_format_timedelta(td):
 def get_markdown_table_entry(columns, project, add_links):
     format_functions = {'name': lambda s, l: get_markdown_table_entry_format_name(s) if l else s,
                         'updated_at': lambda s, l: datetime.strptime(s, '%Y-%m-%dT%H:%M:%SZ').strftime('%Y-%m-%d'),
-                        'total_contributor_count': lambda s, l: '{:,} contributor(s)'.format(int(s)),
-                        'total_commit_count': lambda s, l: '{:,} commit(s)'.format(int(s)),
+                        'total_contributor_count': lambda s, l: '{:,}'.format(int(s)),
+                        'total_commit_count': lambda s, l: '{:,}'.format(int(s)),
                         'total_code_lines': lambda s, l: '<{:,} K'.format(1) if (int(s) / 1000) <= 1 else '{:,} K'.format(int(s) / 1000),
                         'min_month': lambda s, l: '%s' % get_markdown_table_entry_format_timedelta(datetime.utcnow() - datetime.strptime(s, '%Y-%m-%dT%H:%M:%SZ'))}
 

### 2014-03-28 alternative-internet-crawler/generate_tables.py
Add option to right align table columns

@@ -69,10 +69,13 @@ def get_markdown_table_header(columns, add_links, sort_on=None):
         return '%s%s%s\n' % ('| ', ' | '.join(columns.values()), ' |')
 
 
-def get_markdown_table_divider(columns):
+def get_markdown_table_divider(columns, columns_align_right=[]):
     divider = columns.copy()
     for key in divider.keys():
-        divider[key] = '-' * len(divider[key])
+        if key in columns_align_right:
+            divider[key] = '-' * (len(divider[key]) - 1) + ':'
+        else:
+            divider[key] = '-' * len(divider[key])
 
     return get_markdown_table_header(divider, add_links=False)
 
@@ -150,7 +153,7 @@ def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
     return sorted_list
 
 
-def write_output(projects, table_columns, output='readme.md', sort_on='name', sort_reverse=False, add_links=False, add_totals=False):
+def write_output(projects, table_columns, output='readme.md', sort_on='name', sort_reverse=False, add_links=False, add_totals=False, columns_align_right=[]):
 
     with codecs.open(output, 'w', 'utf-8-sig') as output_file:
         if add_links:
@@ -160,7 +163,7 @@ def write_output(projects, table_columns, output='readme.md', sort_on='name', so
         header = get_markdown_table_header(table_columns, add_links, sort_on)
         output_file.write(header)
 
-        header = get_markdown_table_divider(table_columns)
+        header = get_markdown_table_divider(table_columns, columns_align_right)
         output_file.write(header)
 
         for project in get_sorted_list(projects, sort_on, sort_reverse):
@@ -184,6 +187,8 @@ def run_parser(directory='projects', output='readme.md', sort_on='name', sort_re
                                  ('total_commit_count', 'Commits'), ('total_contributor_count', 'Contributors')])
 
     table_columns_default_reverse = ['updated_at', 'total_code_lines', 'total_commit_count', 'total_contributor_count']
+    table_columns_align_right = ['total_code_lines', 'total_commit_count', 'total_contributor_count', 'min_month',
+                                 'updated_at']
 
     projects = get_projects(directory)
     logging.info('Loaded %s projects' % len(projects))
@@ -192,10 +197,12 @@ def run_parser(directory='projects', output='readme.md', sort_on='name', sort_re
         for key in table_columns.keys():
             write_output(projects=projects, table_columns=table_columns,
[…]

### 2014-04-02 alternative-internet-crawler/generate_tables.py
Add possibility to use description field in the table with a maximum length (400 for now)

@@ -29,6 +29,8 @@ import json
 import os
 import codecs
 
+DESCRIPTION_MAX_LENGTH = 400
+
 
 def get_projects(path):
     """
@@ -126,7 +128,9 @@ def get_markdown_table_entry(columns, project, add_links):
                         'total_contributor_count': lambda s, l: '{:,}'.format(int(s)),
                         'total_commit_count': lambda s, l: '{:,}'.format(int(s)),
                         'total_code_lines': lambda s, l: '<{:,} K'.format(1) if (int(s) / 1000) <= 1 else '{:,} K'.format(int(s) / 1000),
-                        'min_month': lambda s, l: '%s' % get_markdown_table_entry_format_timedelta(datetime.utcnow() - datetime.strptime(s, '%Y-%m-%dT%H:%M:%SZ'))}
+                        'min_month': lambda s, l: '%s' % get_markdown_table_entry_format_timedelta(datetime.utcnow() - datetime.strptime(s, '%Y-%m-%dT%H:%M:%SZ')),
+                        'description': lambda s, l: '%s...' % s[:DESCRIPTION_MAX_LENGTH] if len(s) > DESCRIPTION_MAX_LENGTH else s,
+                        }
 
     entry = []
     for key in columns.keys():

### 2014-04-02 alternative-internet-crawler/generate_tables.py
Generate a table with the description included
as suggested in issue #8 (https://github.com/rjagerman/ANON/issues/8)

@@ -186,9 +186,14 @@ def write_output(projects, table_columns, output='readme.md', sort_on='name', so
 
 
 def run_parser(directory='projects', output='readme.md', sort_on='name', sort_reverse=False, add_links=False, generate_all=False, add_totals=False):
-    table_columns = OrderedDict([('name', 'Name'), ('main_language', 'Language'), ('min_month', 'Age'),
-                                 ('updated_at', 'Last activity'), ('total_code_lines', 'LOC'),
-                                 ('total_commit_count', 'Commits'), ('total_contributor_count', 'Contributors')])
+    # Proposed by Pouwelse (Project name, #commits, #LinesOfCode, Age in years, Description)
+    table_columns = OrderedDict([('name', 'Name'), ('total_commit_count', 'Commits'), ('total_code_lines', 'LOC'),
+                                 ('min_month', 'Age'), ('description', 'Description')])
+
+    # Original table columns
+    # table_columns = OrderedDict([('name', 'Name'), ('main_language', 'Language'), ('min_month', 'Age'),
+    #                              ('updated_at', 'Last activity'), ('total_code_lines', 'LOC'),
+    #                              ('total_commit_count', 'Commits'), ('total_contributor_count', 'Contributors')])
 
     table_columns_default_reverse = ['updated_at', 'total_code_lines', 'total_commit_count', 'total_contributor_count']
     table_columns_align_right = ['total_code_lines', 'total_commit_count', 'total_contributor_count', 'min_month',

### 2014-04-02 alternative-internet-crawler/generate_tables.py
Remove colon in Total entry

@@ -102,7 +102,7 @@ def get_markdown_table_totals(columns, projects):
         if total_entry[key] == 0:
             total_entry[key] = '-'
 
-    total_entry['name'] = '**Total:**'
+    total_entry['name'] = '**Total**'
 
     return get_markdown_table_entry(columns, total_entry, False)
 

### 2014-04-02 alternative-internet-crawler/generate_tables.py
Add extra errorchecks

@@ -97,7 +97,10 @@ def get_markdown_table_totals(columns, projects):
             # datetime.strftime() doesn't like years before 1900, so we'll just use a modified isotime() instead
             total_entry[key] = "%sZ" % ((datetime.utcnow() - total_time).isoformat().strip().split(".")[0])
         else:
-            total_entry[key] = sum(int(project[key]) if (not project[key] is None and project[key].isdigit()) else 0 for project in entries)
+            try:
+                total_entry[key] = sum(int(project[key]) if (not project[key] is None and project[key].isdigit()) else 0 for project in entries)
+            except:
+                total_entry[key] = 0
 
         if total_entry[key] == 0:
             total_entry[key] = '-'
@@ -150,7 +153,11 @@ def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
 
     logging.info('Sorting on \'%s\'' % sort_on)
 
-    sorted_list = sorted(dictionary, key=lambda k: (int(k[sort_on]) if (not k[sort_on] is None and k[sort_on].isdigit()) else k[sort_on]) if sort_on in k.keys() and not k[sort_on] is None else unknown_entry)
+    try:
+        sorted_list = sorted(dictionary, key=lambda k: (int(k[sort_on]) if (not k[sort_on] is None and k[sort_on].isdigit()) else k[sort_on]) if sort_on in k.keys() and not k[sort_on] is None else unknown_entry)
+    except:
+        sorted_list = dictionary
+        
     if sort_reverse:
         sorted_list.reverse()
 

### 2014-04-02 alternative-internet-crawler/generate_tables.py
Add factoids as a possible column

@@ -133,6 +133,7 @@ def get_markdown_table_entry(columns, project, add_links):
                         'total_code_lines': lambda s, l: '<{:,} K'.format(1) if (int(s) / 1000) <= 1 else '{:,} K'.format(int(s) / 1000),
                         'min_month': lambda s, l: '%s' % get_markdown_table_entry_format_timedelta(datetime.utcnow() - datetime.strptime(s, '%Y-%m-%dT%H:%M:%SZ')),
                         'description': lambda s, l: '%s...' % s[:DESCRIPTION_MAX_LENGTH] if len(s) > DESCRIPTION_MAX_LENGTH else s,
+                        'factoids': lambda s, l: ', '.join(s) if not s is None else '-'
                         }
 
     entry = []

### 2014-04-02 alternative-internet-crawler/generate_tables.py
Somewhat hacky way to generate README.md with tables included

@@ -53,10 +53,13 @@ def get_projects(path):
 
 def get_markdown_page_header():
     header = '# Alternative Internet\n' + \
-             'Project statistics fetched from [Ohloh](https://www.ohloh.net).\n' +\
+             'Pull requests VERY welcome!\n' + \
              '\n' + \
-             '[< Back to list](README.md)\n' + \
+             '[Compare projects in table](TABLE_NAME.md)\n' + \
+             '\n' + \
+             '[A](#a) - [B](#b) - [C](#c) - [D](#d) - [E](#e) - [F](#f) - [G](#g) - [H](#h) - [I](#i) - [J](#j) - [K](#k) - [L](#l) - [M](#m) - [N](#n) - [O](#o) - [P](#p) - [Q](#q) - [R](#r) - [S](#s) - [T](#t) - [U](#u) - [V](#v) - [W](#w) - [X](#x) - [Y](#y) - [Z](#z)\n' + \
              '\n'
+
     return header
 
 
@@ -143,8 +146,24 @@ def get_markdown_table_entry(columns, project, add_links):
         except:
             entry.append(project[key] if key in project.keys() and not project[key] is None else '-')
 
-    return '%s%s%s\n' % ('| ', ' | '.join(entry), ' |')
+    rows = '%s%s%s\n' % ('| ', ' | '.join(entry), ' |')
 
+
+    complete_entry = '## %s\n' % format_functions['name'](project['name'], False) + \
+        '\n'
+
+    if not rows == '| - | - | - | - | - | - |\n':
+        complete_entry = complete_entry + \
+            get_markdown_table_header(columns, False) + \
+            get_markdown_table_divider(columns) + \
+            rows + \
+            '\n'
+
+    complete_entry = complete_entry + \
+        format_functions['description'](project['description'], False) + \
+        '\n'
+
+    return complete_entry
 
 def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
     unknown_entry = -99999 if sort_reverse else 'zzzzz'
@@ -168,14 +187,7 @@ def get_sorted_list(dictionary, sort_on='name', sort_reverse=False):
 def write_output(projects, table_columns, output='readme.md', sort_on='name', sort_reverse=False, add_links=False, add_totals=False, columns_align_right=[]):
 
     with codecs.open(output, 'w', 'utf-8-sig') as output_file:
-        if add_links:
-            header = get_markdown_page_header()
-            output_file.write(header)
-
[…]

### 2014-04-03 paper.tex
Whitespace
Added IEEE compsoc header as template
Made table 2 span the whole page otherwise it would not fit
Prevent cutoff in section title on the hyphen in 'privacy-enhancing'
Changed authors and added an extra line in the abstract

@@
 % !TeX spellcheck = en_GB
-\documentclass{article}
-\usepackage{a4wide}
+\documentclass[12pt,journal,compsoc]{IEEEtran}
+%\usepackage{a4wide}
 
@@
 % Authors
-\author{Rolf Jagerman, Wendo Sab\'ee, Laurens Versluis, Martijn de Vos\\ Supervised by Dr. Ir. Johan Pouwelse}
+\author{Rolf Jagerman, Wendo Sab\'ee, Laurens Versluis, Martijn de Vos,\\ Johan Pouwelse (course supervisor)}
 \date{}
@@
 	Ever since the introduction of the internet, it has been void of any privacy.
+The majority of internet traffic currently is and always has been unencrypted.
 A number of anonymous communication overlay networks exist whose aim it is to provide privacy to its users.
@@
 	\label{sec:decentralized}
+
 	Fully decentralized systems with large scale usage are without exception based on the peer-to-peer paradigm.
@@
 
-	\begin{table}
+	\begin{table*}
 		\centering
@@
 		\label{tbl:altinternet}
-	\end{table}
+	\end{table*}
 

### 2014-04-03 paper.tex
Improved the text in chapter 5.11, to be more consistent

@@
 
-\section{Decentralized privacy-enhancing systems}
+\section{Decentralized \mbox{privacy-enhancing} systems}
 	\label{sec:decentralized}
@@
 	\subsection{Comparison}
-		In this subsection we will make a comparison between these networks, as seen in table \ref{tbl:comparison}. For each network, we will explain the following features:
+		Using the properties of each of the previously described networks, we can now draw a comparison between these networks.
+This is done in the form of a tabular overview, see table \ref{tbl:comparison}.
+The networks are compared according to the following features:
 
 		\begin{itemize}
-			\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
-			\item{Public implementation:} For each network we will explain whether a public implementation is available.
+			\item{Compatibility with Tor:} Is the network compatible with Tor? Could the network or some features of the network be used for the decentralization of Tor?
+			\item{Public implementation:} Does a publicly available implementation exist?
 			\item{Used in practice:} Is the network used in practice?
-			\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
+			\item{Attack resistance:} What weaknesses does the network have and which attacks are possible?
 			\item{Unlinkability:} Does the network hide the identities of the sender and/or receiver?
